### 2021-10-15 main.tex
Tex-Template

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2.5cm, vmargin=2.5cm]{geometry}
\usepackage{microtype}
\usepackage[english]{babel}
\parindent=0pt

\begin{document}
	\title{{\LARGE RM-PLACEHOLDER TITLE — FDA}}
	\author{Jonghun Baek, Jakob Juergens, Jona Willnow}
	\date{whenever}
	\maketitle
	\vspace{2.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

	\newpage

	\tableofcontents

	\newpage

	\section{Introduction}
	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nam molestie orci luctus lectus tincidunt rhoncus. In suscipit dolor nec magna cursus sodales. Praesent quam libero, imperdiet sit amet lectus varius, semper pellentesque mauris. Donec rhoncus tincidunt vulputate. Ut volutpat at mauris ac ultricies. Sed faucibus tincidunt suscipit. Phasellus turpis nunc, dignissim sed turpis sit amet, efficitur venenatis risus. Maecenas elementum enim vel facilisis congue. Vestibulum maximus, elit vel pharetra posuere, nulla quam pulvinar felis, ut sodales magna libero id elit. Nullam vitae elit placerat nibh blandit blandit.

	Aliquam posuere nec mi et consectetur. Nulla nulla tellus, pretium in vehicula non, euismod non odio. Integer venenatis lectus vitae tellus vehicula vehicula. Ut ac euismod augue, eu accumsan lacus. Vestibulum faucibus risus tempus nisi blandit tincidunt eu a turpis. Vivamus fermentum dictum quam, non facilisis mi condimentum sit amet. Suspendisse sed egestas nunc. Ut tortor nisi, consectetur ut luctus nec, volutpat id felis. Vestibulum sed sagittis quam. Nunc lorem quam, malesuada at felis sed, bibendum scelerisque nibh. Nullam id risus a mauris interdum euismod id quis velit.

	\section{Theory}
	Vestibulum dui arcu, euismod eget ullamcorper sed, faucibus id ipsum. Ut at augue vitae velit eleifend faucibus. Maecenas sed maximus lectus. Pellentesque ultrices ligula non tristique dictum. Etiam malesuada lacinia varius. Nulla pharetra dui sed felis sagittis auctor. Aenean non justo massa.

	Praesent congue felis et volutpat maximus. Phasellus neque diam, commodo hendrerit laoreet ut, condimentum bibendum arcu. Suspendisse placerat lorem at tincidunt condimentum. Curabitur metus arcu, lacinia non velit et, accumsan egestas lacus. Proin ultricies fermentum massa ac imperdiet. Nulla aliquam facilisis nisl at placerat. Ut in volutpat mi. Phasellus tristique nisl nisl, quis maximus velit vulputate quis. Aenean non sapien purus. Quisque eget ipsum quis mi accumsan hendrerit. Nam tincidunt lectus in tellus luctus, eu sodales dolor dictum. Integer erat mauris, ultricies sed ex sit amet, gravida hendrerit nulla. Aliquam eget ultrices justo. Pellentesque congue arcu eget diam varius, at laoreet diam condimentum. Sed imperdiet aliquam placerat.

	Mauris efficitur, leo vel commodo tristique, arcu ipsum bibendum velit, id accumsan ex nunc tristique ex. Praesent sodales placerat dolor a laoreet. Integer sit amet dignissim sem, non tempus diam. Nam sodales enim dolor, ut condimentum velit tristique eu. Maecenas lorem justo, dignissim quis enim ac, maximus gravida lorem. Vestibulum sit amet urna arcu. Nam tristique mollis arcu non convallis. Duis ut pulvinar erat. Quisque et consequat orci. Nullam et sem mattis, semper purus a, semper lorem. Phasellus tempor aliquet velit. In suscipit, nisi a venenatis viverra, nisi enim finibus quam, ac rutrum nisl purus et erat. Proin vitae erat elit.

	\section{Simulation}
	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nam molestie orci luctus lectus tincidunt rhoncus. In suscipit dolor nec magna cursus sodales. Praesent quam libero, imperdiet sit amet lectus varius, semper pellentesque mauris. Donec rhoncus tincidunt vulputate. Ut volutpat at mauris ac ultricies. Sed faucibus tincidunt suscipit. Phasellus turpis nunc, dignissim sed turpis sit amet, efficitur venenatis risus. Maecenas elementum enim vel facilisis congue. Vestibulum maximus, elit vel pharetra posuere, nulla quam pulvinar felis, ut sodales magna libero id elit. Nullam vitae elit placerat nibh blandit blandit.

	Aliquam posuere nec mi et consectetur. Nulla nulla tellus, pretium in vehicula non, euismod non odio. Integer venenatis lectus vitae tellus vehicula vehicula. Ut ac euismod augue, eu accumsan lacus. Vestibulum faucibus risus tempus nisi blandit tincidunt eu a turpis. Vivamus fermentum dictum quam, non facilisis mi condimentum sit amet. Suspendisse sed egestas nunc. Ut tortor nisi, consectetur ut luctus nec, volutpat id felis. Vestibulum sed sagittis quam. Nunc lorem quam, malesuada at felis sed, bibendum scelerisque nibh. Nullam id risus a mauris interdum euismod id quis velit.

	\section{Application}
	Vestibulum dui arcu, euismod eget ullamcorper sed, faucibus id ipsum. Ut at augue vitae velit eleifend faucibus. Maecenas sed maximus lectus. Pellentesque ultrices ligula non tristique dictum. Etiam malesuada lacinia varius. Nulla pharetra dui sed felis sagittis auctor. Aenean non justo massa.

	Praesent congue felis et volutpat maximus. Phasellus neque diam, commodo hendrerit laoreet ut, condimentum bibendum arcu. Suspendisse placerat lorem at tincidunt condimentum. Curabitur metus arcu, lacinia non velit et, accumsan egestas lacus. Proin ultricies fermentum massa ac imperdiet. Nulla aliquam facilisis nisl at placerat. Ut in volutpat mi. Phasellus tristique nisl nisl, quis maximus velit vulputate quis. Aenean non sapien purus. Quisque eget ipsum quis mi accumsan hendrerit. Nam tincidunt lectus in tellus luctus, eu sodales dolor dictum. Integer erat mauris, ultricies sed ex sit amet, gravida hendrerit nulla. Aliquam eget ultrices justo. Pellentesque congue arcu eget diam varius, at laoreet diam condimentum. Sed imperdiet aliquam placerat.

	Mauris efficitur, leo vel commodo tristique, arcu ipsum bibendum velit, id accumsan ex nunc tristique ex. Praesent sodales placerat dolor a laoreet. Integer sit amet dignissim sem, non tempus diam. Nam sodales enim dolor, ut condimentum velit tristique eu. Maecenas lorem justo, dignissim quis enim ac, maximus gravida lorem. Vestibulum sit amet urna arcu. Nam tristique mollis arcu non convallis. Duis ut pulvinar erat. Quisque et consequat orci. Nullam et sem mattis, semper purus a, semper lorem. Phasellus tempor aliquet velit. In suscipit, nisi a venenatis viverra, nisi enim finibus quam, ac rutrum nisl purus et erat. Proin vitae erat elit.

\end{document}

### 2021-10-23 main.tex
Bibliography
Bibliography
Heading Removed
Added Folders
Increment
Citation_fix
Set-up Draft

@@
 \documentclass[11pt,twoside,a4paper]{article}
-\usepackage[hmargin=2.5cm, vmargin=2.5cm]{geometry}
+\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
 \usepackage{microtype}
 \usepackage[english]{babel}
+\usepackage{setspace}
+\usepackage{xcolor}
+\usepackage[
+backend=biber,
+style=authoryear-comp,
+]{biblatex}
+
+\addbibresource{RMbibliography.bib}
+\onehalfspacing
 \parindent=0pt
@@
 \begin{document}
-	\title{{\LARGE RM-PLACEHOLDER TITLE — FDA}}
-	\author{Jonghun Baek, Jakob Juergens, Jona Willnow}
-	\date{whenever}
+	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}}
+	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
+	\date{{\color{red}whenever}}
 	\maketitle
-	\vspace{2.5 cm}
+	\vspace{1.5 cm}
 	\begin{center}
@@
 	\section{Introduction}
-	Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nam molestie orci luctus lectus tincidunt rhoncus.
-In suscipit dolor nec magna cursus sodales.
-Praesent quam libero, imperdiet sit amet lectus varius, semper pellentesque mauris.
-Donec rhoncus tincidunt vulputate.
-Ut volutpat at mauris ac ultricies.
-Sed faucibus tincidunt suscipit.
-Phasellus turpis nunc, dignissim sed turpis sit amet, efficitur venenatis risus.
-Maecenas elementum enim vel facilisis congue.
-Vestibulum maximus, elit vel pharetra posuere, nulla quam pulvinar felis, ut sodales magna libero id elit.
-Nullam vitae elit placerat nibh blandit blandit.
 
-	Aliquam posuere nec mi et consectetur.
-Nulla nulla tellus, pretium in vehicula non, euismod non odio.
-Integer venenatis lectus vitae tellus vehicula vehicula.
-Ut ac euismod augue, eu accumsan lacus.
-Vestibulum faucibus risus tempus nisi blandit tincidunt eu a turpis.
-Vivamus fermentum dictum quam, non facilisis mi condimentum sit amet.
-Suspendisse sed egestas nunc.
-Ut tortor nisi, consectetur ut luctus nec, volutpat id felis.
-Vestibulum sed sagittis quam.
-Nunc lorem quam, malesuada at felis sed, bibendum scelerisque nibh.
-Nullam id risus a mauris interdum euismod id quis velit.
+	\begin{itemize}
+		\item Describe the idea of regressing a scalar on functional data
+		\item Describing the difference to multiple linear regression intuitively
+		\item Giving an intuitive example
+	\end{itemize}
 
 	\section{Theory}
-	Vestibulum dui arcu, euismod eget ullamcorper sed, faucibus id ipsum.
-Ut at augue vitae velit eleifend faucibus.
-Maecenas sed maximus lectus.
-Pellentesque ultrices ligula non tristique dictum.
-Etiam malesuada lacinia varius.
-Nulla pharetra dui sed felis sagittis auctor.
-Aenean non justo massa.
 
-	Praesent congue felis et volutpat maximus.
-Phasellus neque diam, commodo hendrerit laoreet ut, condimentum bibendum arcu.
-Suspendisse placerat lorem at tincidunt condimentum.
-Curabitur metus arcu, lacinia non velit et, accumsan egestas lacus.
-Proin ultricies fermentum massa ac imperdiet.
-Nulla aliquam facilisis nisl at placerat.
-Ut in volutpat mi.
-Phasellus tristique nisl nisl, quis maximus velit vulputate quis.
-Aenean non sapien purus.
-Quisque eget ipsum quis mi accumsan hendrerit.
-Nam tincidunt lectus in tellus luctus, eu sodales dolor dictum.
-Integer erat mauris, ultricies sed ex sit amet, gravida hendrerit nulla.
-Aliquam eget ultrices justo.
-Pellentesque congue arcu eget diam varius, at laoreet diam condimentum.
-Sed imperdiet aliquam placerat.
+	\subsection{Draft-Overview}
+	\begin{itemize}
+		\item Introduce the concept of random functions
+		\item Introduce the concept of square integrable deterministic \& random functions
+		\item Explain basis expansions (so basis of the vector space $L^2$ and b-spline basis as an example) 
+		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		
+		\item Explain Scalar-on-Function Regression
+		\item Estimation through basis-expansion (incl. Eigenbasis) and estimation with roughness penalty
+		\item Address approximation error due to basis-truncation
+	\end{itemize}
 
-	Mauris efficitur, leo vel commodo tristique, arcu ipsum bibendum velit, id accumsan ex nunc tristique ex.
-Praesent sodales placerat dolor a laoreet.
-Integer sit amet dignissim sem, non tempus diam.
-Nam sodales enim dolor, ut condimentum velit tristique eu.
-Maecenas lorem justo, dignissim quis enim ac, maximus gravida lorem.
-Vestibulum sit amet urna arcu.
-Nam tristique mollis arcu non convallis.
-Duis ut pulvinar erat.
-Quisque et consequat orci.
-Nullam et sem mattis, semper purus a, semper lorem.
-Phasellus tempor aliquet velit.
-In suscipit, nisi a venenatis viverra, nisi enim finibus quam, ac rutrum nisl purus et erat.
-Proin vitae erat elit.
+	\subsection{Literature}
+	\begin{itemize}
+		\item \cite{kokoszka_introduction_2017}
+		\item \cite{hsing_theoretical_2015}
+		\item \cite{ramsay_functional_2005}
+		\item \cite{horvath_inference_2012}
+	\end{itemize}
 
+	\newpage
 	\section{Simulation}
-	Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nam molestie orci luctus lectus tincidunt rhoncus.
-In suscipit dolor nec magna cursus sodales.
-Praesent quam libero, imperdiet sit amet lectus varius, semper pellentesque mauris.
-Donec rhoncus tincidunt vulputate.
-Ut volutpat at mauris ac ultricies.
-Sed faucibus tincidunt suscipit.
-Phasellus turpis nunc, dignissim sed turpis sit amet, efficitur venenatis risus.
-Maecenas elementum enim vel facilisis congue.
-Vestibulum maximus, elit vel pharetra posuere, nulla quam pulvinar felis, ut sodales magna libero id elit.
-Nullam vitae elit placerat nibh blandit blandit.
 
-	Aliquam posuere nec mi et consectetur.
-Nulla nulla tellus, pretium in vehicula non, euismod non odio.
-Integer venenatis lectus vitae tellus vehicula vehicula.
-Ut ac euismod augue, eu accumsan lacus.
-Vestibulum faucibus risus tempus nisi blandit tincidunt eu a turpis.
-Vivamus fermentum dictum quam, non facilisis mi condimentum sit amet.
-Suspendisse sed egestas nunc.
-Ut tortor nisi, consectetur ut luctus nec, volutpat id felis.
-Vestibulum sed sagittis quam.
-Nunc lorem quam, malesuada at felis sed, bibendum scelerisque nibh.
-Nullam id risus a mauris interdum euismod id quis velit.
+	\subsection{Draft-Overview}
+	\begin{itemize}
+		\item Motivate Simulation for some data generating process from application
+		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
+		\item Present Results
+		\item Explain relevance for application
+	\end{itemize}
 
+	\subsection{Literature}
+	\begin{itemize}
+		\item \cite{shonkwiler_explorations_2009}
+	\end{itemize}
+
+	\newpage
 	\section{Application}
-	Vestibulum dui arcu, euismod eget ullamcorper sed, faucibus id ipsum.
-Ut at augue vitae velit eleifend faucibus.
-Maecenas sed maximus lectus.
-Pellentesque ultrices ligula non tristique dictum.
-Etiam malesuada lacinia varius.
-Nulla pharetra dui sed felis sagittis auctor.
-Aenean non justo massa.
 
-	Praesent congue felis et volutpat maximus.
-Phasellus neque diam, commodo hendrerit laoreet ut, condimentum bibendum arcu.
-Suspendisse placerat lorem at tincidunt condimentum.
-Curabitur metus arcu, lacinia non velit et, accumsan egestas lacus.
-Proin ultricies fermentum massa ac imperdiet.
-Nulla aliquam facilisis nisl at placerat.
-Ut in volutpat mi.
-Phasellus tristique nisl nisl, quis maximus velit vulputate quis.
-Aenean non sapien purus.
-Quisque eget ipsum quis mi accumsan hendrerit.
-Nam tincidunt lectus in tellus luctus, eu sodales dolor dictum.
-Integer erat mauris, ultricies sed ex sit amet, gravida hendrerit nulla.
-Aliquam eget ultrices justo.
-Pellentesque congue arcu eget diam varius, at laoreet diam condimentum.
-Sed imperdiet aliquam placerat.
+	\subsection{Draft-Overview}
+	\begin{itemize}
+		\item 
+	\end{itemize}
 
-	Mauris efficitur, leo vel commodo tristique, arcu ipsum bibendum velit, id accumsan ex nunc tristique ex.
-Praesent sodales placerat dolor a laoreet.
-Integer sit amet dignissim sem, non tempus diam.
-Nam sodales enim dolor, ut condimentum velit tristique eu.
-Maecenas lorem justo, dignissim quis enim ac, maximus gravida lorem.
-Vestibulum sit amet urna arcu.
-Nam tristique mollis arcu non convallis.
-Duis ut pulvinar erat.
-Quisque et consequat orci.
-Nullam et sem mattis, semper purus a, semper lorem.
-Phasellus tempor aliquet velit.
-In suscipit, nisi a venenatis viverra, nisi enim finibus quam, ac rutrum nisl purus et erat.
-Proin vitae erat elit.
+	\subsection{Literature}
+	\begin{itemize}
+		\item 
+	\end{itemize}
+
+	\section{Appendix}
+
+	\section{Bibliography}
+	\printbibliography[heading=none]
 

### 2021-10-24 main.tex
First_Draft

@@
 \usepackage{microtype}
+\usepackage{hyperref}
 \usepackage[english]{babel}
@@
 		\item Explain Scalar-on-Function Regression
-		\item Estimation through basis-expansion (incl. Eigenbasis) and estimation with roughness penalty
+		\item Estimation through basis-expansion (incl. Eigenbasis) [and estimation with roughness penalty]
 		\item Address approximation error due to basis-truncation
@@
 		\item \cite{horvath_inference_2012}
+		\item \cite{cai_prediction_2006}
+		\item \cite{levitin_introduction_2007}
 	\end{itemize}
@@
 		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
+		\item Prediction not Inference
 		\item Present Results
@@
 		\item \cite{shonkwiler_explorations_2009}
+		\item R-packages: fda, refund, mgcv
 	\end{itemize}
@@
 	\begin{itemize}
-		\item 
+		\item Prediction not Inference
+		\item IID data set (no dependence between the curves, don't want to do functional time series)
+		\item Not necessarily data from economics (like biology, sports, whatever)
+		\item Smooth curves or random walk (both fine)
+		\item \href{https://functionaldata.wordpress.ncsu.edu/resources/}{https://functionaldata.wordpress.ncsu.edu/resources/}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item 
+		\item \cite{carey_life_2002}
+	\end{itemize}
+
+	\section{Outlook}
+
+	\subsection{Literature}
+	\begin{itemize}
+		\item \cite{James.2009} (shape-restrictions)
 	\end{itemize}
@@
 	\section{Appendix}
+
+	\newpage
 

### 2021-10-25 main.tex
Increment

@@
 		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
-		\item Prediction not Inference
+
+		\item Compare estimation with \begin{enumerate}
+			\item b-spline basis without addressing approximation error
+			\item ... including proper treatment of approximation error
+			\item Eigenbasis constructed from observations
+			\end{enumerate}
+
+		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
 		\item Present Results
@@
 	\begin{itemize}
-		\item Prediction not Inference
+		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the data set)
 		\item IID data set (no dependence between the curves, don't want to do functional time series)

### 2021-10-28 main.tex
Jonathan commit
Changes to introduction, adding to BibTex, adding fda_gasoline example

@@
 	\end{itemize}	
+	Function Data Analysis (FDA) is a relatively new field which is getting more attention as researchers from different fields collect more data from an continuous underlying process.
+This data still can be processed by classical statistical methods, but only FDA allows to answer questions that are tied to the information given by the smoothness of the underlying continuous process.
+(see \cite{levitin_introduction_2007})\\
+	 As Kokoszka and Reimherr (2017) describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (see \cite[S.~17]{kokoszka_introduction_2017}.
+	 To motivate the use of scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an continuous underlying process.
+In economics, on application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (see~\cite{Das_2019}).
 

### 2021-10-30 main.tex
Theory_Overview
Added a more detailed plan for the theory section

--- 2021-10-25 main.tex
@@
 	\end{itemize}	
+	Function Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process.
+This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process.
+(cf.
+\cite{levitin_introduction_2007})\\
+	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf.
+\cite[S.~17]{kokoszka_introduction_2017}).
+	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of a continuous underlying process.
+In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
+\cite{Das_2019}).
 
@@
 
+	\subsection{Detailed Draft}
+	\begin{itemize}
+		\item Motivate random functions from introduction and the general concept of random variables
+		\item Formalize random function in this context as random variables realizing in a Hilbert space
+		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
+		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
+		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
+		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
+		\item Introduce b-spline and Fourier bases
+		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
+		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
+		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
+		\item Explain the concept of iid data in a functional setting
+		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
+		\item Explain approximations of functional observations using truncated basis representations
+		\item Introduce linear operator $L_1$ and sufficient condition associated with it
+		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
+		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
+		\item Solution: estimation using truncated basis expansion to approximate data (theoretical description)
+		\item Problem: truncation error $\delta$ and how to deal with it?
+		\item Explain how to address truncation error in standard errors
+		\item Motivate three estimation procedures
+		\begin{enumerate}
+			\item truncated b-spline basis expansion without addressing truncation error
+			\item truncated b-spline basis expansion WITH addressing truncation error
+			\item truncated Eigenbasis expansion (advantages: low number of basis functions get low approximation error)
+		\end{enumerate}
+	\end{itemize}
+
 	\subsection{Draft-Overview}
 	\begin{itemize}
-		\item Introduce the concept of random functions
-		\item Introduce the concept of square integrable deterministic \& random functions
-		\item Explain basis expansions (so basis of the vector space $L^2$ and b-spline basis as an example) 
 		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		

### 2021-10-31 main.tex
Add_Intro

@@
 	\end{itemize}	
-	Function Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process.
-This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process.
-(cf.
-\cite{levitin_introduction_2007})\\
+	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process.
+This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process (cf.
+\cite{levitin_introduction_2007}).\\
 	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf.
@@
 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
-\cite{Das_2019}).
+\cite{Das_2019}).\\
+	 The focus of this paper is to introduce Functional Linear Regression (FLR) in terms of scalar-on-function.
+We will be importing the standard FLR model, which shows functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
+	 $$Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
+	 \qquad i = 1, ..., n,$$
+	 where $\{(X_{1}, Y_{1}), …, (X_{n}, Y_{n})\}$ is the realization of data, where $X_{i}$’s are independent and identically distributed random function X and $\beta(s)$ is the coefficient function.
+The distinct is that the estimator is not a scalar but a function, which leads to compelling interest in $\beta(s)$ for prediction.
+The information about the function comes up with how large or small a future observation $x$ of $X$ will influence the response with the leverage on $\int{\beta(s)xds}$.
+For instance, fluctuation in $X$ does not have any effect on $Y$, where $\beta(s)$ = 0, or has a greater effect on $Y$ with larger $\beta(s)$.
+Additionally, assume that $\beta(s)$ is exactly a linear function for any interval.
+The effect of X is, then, constant on that interval.\\
+	 Estimation of $\beta(s)$ is inherent in a problem of infinite dimension.
+In Section 2, after constructing necessary theoretical properties to understand FDA, we progress to reduce dimension by utilizing smoothing with two types of basis function, namely, b-spline and eigenfunction.
+The results of the Monte-Carlo simulation regarding three different situations are reported in Section 3.
+Finally, in Section 4, we test the prediction of FLR with the actual data set.
+{\color{red} (We may put some simple descriptions of results about each of MC and Application)}
 

### 2021-10-31 main.tex
new

--- 2021-10-30 main.tex
@@
 		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
+	\end{itemize}
+\subsection{Kokoszka Reimherr (2017) p51-53}
+There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to Kokoszka and Reimherr (2017): In functional regression, the aim is not only to compute an estimate of the function $\beta$ because this function needs also to have an useful interpretation.
+Without this useful interpretation, there can be no effective and feasible prediction of the scalar responses from new explanatory functions.
+Hereby applies, that intervals with larger values of $|\beta(s)|$ are contributing more to to the response than small values of  $|\beta(s)|$.
+The sign of $\beta(s)$ within the intervals of the value s show either negative or positive association of  $|\beta(s)|$ for this interval.
+To get an useful interpretation, the estimate $\beta$ cannot jump in a seemingly random fashion, because then an useful interpretation is not possible and predictions from this model tend to have large variances and center around the mean of the responses.
+(see ~\cite{kokoszka_introduction_2017})
+
+	\begin{itemize}
 		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
+	\end{itemize}
+	Considering the population model of scalar-on-function linear regression
+	\begin{equation}
+     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
+    \end{equation}
+    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because there are infinitely many solutions for finding the minimizing argument for $\hat{\beta}$.
+Define
+    \begin{equation}
+  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
+    \end{equation}
+   Under the assumption that $X$ is independent from $\epsilon$ we obtain
+   \begin{equation}
+     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
+   \end{equation}
+    \begin{equation}
+     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
+  	\end{equation}
+   	\begin{equation}
+    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
+   \end{equation}
+
+  This results in practice in a large number of equations, which are difficult to solve.
+Even if solved, this results in a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does bot utilize the intuition of smooth functions.
+Another reason why estimation is not feasible using this approach is colinearity.
+Approximate the scalar-on-functional regression as
+  	\begin{equation}
+     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
+    \end{equation}, it becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.
+
+	\begin{itemize}
 		\item Solution: estimation using truncated basis expansion to approximate data (theoretical description)

### 2021-10-31 main.tex
Merge and Edit

--- 2021-10-31 main.tex
@@
 	\end{itemize}	
-	Function Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process.
-This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process.
-(cf.
-\cite{levitin_introduction_2007})\\
-	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf.
-\cite[S.~17]{kokoszka_introduction_2017}).
-	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of a continuous underlying process.
+	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature.
+This data can often be processed by classical statistical methods, but only FDA allows extracting information given by the smoothness of the underlying process (cf.
+\cite{levitin_introduction_2007}).
+	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf.
+\cite[S.~17]{kokoszka_introduction_2017}).\\
+	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process.
 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
-\cite{Das_2019}).
+\cite{Das_2019}).\\
+	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting.
+We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
+	 \begin{equation}
+	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
+	 	\qquad i = 1, ..., n
+	 \end{equation}
+	 where the $X_{i}$ are observations of a random function $X$, $Y_i$ are realizations of the response variable and $\beta(s)$ is the coefficient function.
+The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation.
+As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction.
+For instance, fluctuation in $X$ at a point $s_0$ will not have any effect on $Y$ if $\beta(s_0)$ = 0.
+\\
+	 Estimation of $\beta(s)$ is inherently an infinite dimensional problem.
+In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion.
+The results of the Monte-Carlo simulation regarding these three different methods are reported in Section 3.
+Finally, in Section 4, we test the prediction of FLR in a real world setting.
+{\color{red} (We may put some simple descriptions of results about each of MC and Application)}
 
@@
 \subsection{Kokoszka Reimherr (2017) p51-53}
-There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to Kokoszka and Reimherr (2017): In functional regression, the aim is not only to compute an estimate of the function $\beta$ because this function needs also to have an useful interpretation.
-Without this useful interpretation, there can be no effective and feasible prediction of the scalar responses from new explanatory functions.
-Hereby applies, that intervals with larger values of $|\beta(s)|$ are contributing more to to the response than small values of  $|\beta(s)|$.
-The sign of $\beta(s)$ within the intervals of the value s show either negative or positive association of  $|\beta(s)|$ for this interval.
-To get an useful interpretation, the estimate $\beta$ cannot jump in a seemingly random fashion, because then an useful interpretation is not possible and predictions from this model tend to have large variances and center around the mean of the responses.
+There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ because this function also needs to have a useful interpretation.
+Without it, there might be prediction of the scalar responses from new explanatory functions, but the increase in understanding of the underlying question will be minimal.
+Thereby, intervals with larger values of $|\beta(s)|$ will contribute more to the response than small values of  $|\beta(s)|$.
+The sign of $\beta(s)$ indicates either negative or positive influence of $X(s)$ for a specific value of s.
+To get a useful interpretation, the estimate $\beta$ should not jump in a seemingly random fashion, because a useful interpretation of this erratic behavior will often be impossible and predictions from these model tend to have larger variances and to center around the mean of the responses.
 (see ~\cite{kokoszka_introduction_2017})
@@
 	\end{itemize}
-	Considering the population model of scalar-on-function linear regression
+	Assuming a data generating process of the form:
 	\begin{equation}
@@
     \end{equation}
-    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because there are infinitely many solutions for finding the minimizing argument for $\hat{\beta}$.
-Define
+    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
+Define therefore
     \begin{equation}
@@
 
-  This results in practice in a large number of equations, which are difficult to solve.
-Even if solved, this results in a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does bot utilize the intuition of smooth functions.
+   In practice, this results in a large and often difficult to solve system of equations.
+Even if solved, the result is often a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does not utilize the intuition of smooth functions.
 Another reason why estimation is not feasible using this approach is colinearity.
-Approximate the scalar-on-functional regression as
+\\
+
+   If we approximate the scalar-on-functional regression as
   	\begin{equation}
      Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
-    \end{equation}, it becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.
+    \end{equation}, it becomes clear that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$ there will be vectors $X_{i}$ that are highly correlated and thus lead to large variances.
 

### 2021-10-31 main.tex
commits

--- 2021-10-31 main.tex
@@
     \begin{equation}
-  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
+  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y].
     \end{equation}
@@
    \begin{equation}
-     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
+     c_{XY}(t) = E[X(t)\int \beta(s)X(s) \,ds \ +\epsilon]
    \end{equation}
     \begin{equation}
-     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
+     c_{XY}(t) =  E[\int \beta(s)X(s)X(t)\,ds\:|\: X] + E[\epsilon |X]
   	\end{equation}
@@
   	\begin{equation}
-     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
-    \end{equation}, it becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.
+     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}.
+    \end{equation}It becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.
 

### 2021-10-31 main.tex
Increment

--- 2021-10-31 main.tex
@@
 	 \end{equation}
-	 where the $X_{i}$ are observations of a random function $X$, $Y_i$ are realizations of the response variable and $\beta(s)$ is the coefficient function.
+	 where the $X_{i}$ are realizations of a random function $\mathbf{X}$, $Y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function.
 The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation.
 As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction.
-For instance, fluctuation in $X$ at a point $s_0$ will not have any effect on $Y$ if $\beta(s_0)$ = 0.
+For instance, fluctuation in $X_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0.
 \\
@@
     \begin{equation}
-  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
+  	c_{\mathbf{X}}(t,s) = E[\mathbf{X}(t)\mathbf{X}(s)],\: c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\mathbf{Y}], 
     \end{equation}
@@
    \begin{equation}
-     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
+     c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
    \end{equation}
     \begin{equation}
-     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
+     c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
   	\end{equation}
    	\begin{equation}
-    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
+    	c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
    \end{equation}
@@
   	\begin{equation}
-     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
-    \end{equation}, it becomes clear that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$ there will be vectors $X_{i}$ that are highly correlated and thus lead to large variances.
+     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{j}
+    \end{equation}, it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances.
+{\color{red} isn't something missing here?
+Like "and employ standard multivariate linear regression"}
 

### 2021-10-31 main.tex
Increment

@@
    In practice, this results in a large and often difficult to solve system of equations.
-Even if solved, the result is often a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does not utilize the intuition of smooth functions.
+Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
 Another reason why estimation is not feasible using this approach is colinearity.
-\\
-
-   If we approximate the scalar-on-functional regression as
+   If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
   	\begin{equation}

### 2021-10-31 main.tex
Increment
Jona

@@
 	\end{itemize}
-\subsection{Kokoszka Reimherr (2017) p51-53}
+
 There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ because this function also needs to have a useful interpretation.
@@
 To get a useful interpretation, the estimate $\beta$ should not jump in a seemingly random fashion, because a useful interpretation of this erratic behavior will often be impossible and predictions from these model tend to have larger variances and to center around the mean of the responses.
-(see ~\cite{kokoszka_introduction_2017})
 
@@
   	\begin{equation}
-     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{j}
-    \end{equation}, it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances.
-{\color{red} isn't something missing here?
+     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
+    \end{equation} it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
+(cf.
+~\cite{kokoszka_introduction_2017}) {\color{red} isn't something missing here?
 Like "and employ standard multivariate linear regression"}
@@
 		\item Solution: estimation using truncated basis expansion to approximate data (theoretical description)
+	\end{itemize}
+	\begin{itemize}
 		\item Problem: truncation error $\delta$ and how to deal with it?
+	\end{itemize}
+
 		\item Explain how to address truncation error in standard errors

### 2021-10-31 main.tex
Auto stash before merge of "main" and "origin/main"

@@
 	\end{itemize}
-
-There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ because this function also needs to have a useful interpretation.
-Without it, there might be prediction of the scalar responses from new explanatory functions, but the increase in understanding of the underlying question will be minimal.
-Thereby, intervals with larger values of $|\beta(s)|$ will contribute more to the response than small values of  $|\beta(s)|$.
-The sign of $\beta(s)$ indicates either negative or positive influence of $X(s)$ for a specific value of s.
-To get a useful interpretation, the estimate $\beta$ should not jump in a seemingly random fashion, because a useful interpretation of this erratic behavior will often be impossible and predictions from these model tend to have larger variances and to center around the mean of the responses.
+\subsection{Kokoszka Reimherr (2017) p51-53}
+There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation.
+Without it, there might be prediction, but the increase in understanding of the underlying question will be minimal.
+One aspect of a useful interpretation is that the estimate $\beta$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.
 
@@
 	\end{itemize}
+	A common setting in non-functional regression is akin to the following. Assume a data generating as follows:
+	\begin{equation}
+		Y = X\beta + \epsilon
+	\end{equation}
+	where $X$ is a vector of random variables, $\beta = (\beta_0, \dots, \beta_J)'$ is a coefficient vector and $epsilon$ is an
+
 	Assuming a data generating process of the form:

### 2021-10-31 main.tex
Update main.tex
add itemize
Theory increment

@@
 \usepackage{xcolor}
+\usepackage{amssymb}
 \usepackage[
@@
 		\item Formalize random function in this context as random variables realizing in a Hilbert space
-		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
-		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
-		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
-		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
+		\item Introduce $\mathbb{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
+		\item Specialize to Hilbert space being $\mathbb{L}^2[0,1]$ for this context
+		\item Define mean and covariance function of a random function realizing in $\mathbb{L}^2[0,1]$
+		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbb{L}^2[0,1]$
 		\item Introduce b-spline and Fourier bases
@@
 		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
-		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
+		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbb{L}^2[0,1]$
 		\item Explain the concept of iid data in a functional setting
@@
 Without it, there might be prediction, but the increase in understanding of the underlying question will be minimal.
-One aspect of a useful interpretation is that the estimate $\beta$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.
+One aspect of a useful interpretation is that the estimate $\beta(s)$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.
 
@@
 	\end{itemize}
-	A common setting in non-functional regression is akin to the following. Assume a data generating as follows:
+	A common setting in non-functional regression is akin to the following. Assume a model as follows:
 	\begin{equation}
-		Y = X\beta + \epsilon
+		Y = X'\beta + \epsilon
 	\end{equation}
-	where $X$ is a vector of random variables, $\beta = (\beta_0, \dots, \beta_J)'$ is a coefficient vector and $epsilon$ is an
-
+	where $X \in \mathbb{R}^{n\times J}$ is a matrix containing the regressors, $\beta \in \mathbb{R}^J$ is a coefficient vector and $epsilon$ is a vector containing the error term.
+For simplicity, assume that the data generating process fulfills the Markov assumptions.
+Then the famous OLS-estimator is given by:
+	\begin{equation}
+		\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
+	\end{equation}
+	A naive approach to FLR would be to try to generalize this to the functional setting.
 	Assuming a data generating process of the form:
@@
     it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
+Where in the finite dimensional setting the OLS estimator can be derived as a method of moments estimator by solving a system of equations of sample moment restrictions, this leads to a system of infinitely many equations in the functional setting.
+    In practice, functional observations are never truly continuously observed.
+If we assume that the functional observations are observed at a finite set of points $\{t_1, \dots, t_J\}$ this makes the derivation of an OLS estimator possible as before.
+
+    \begin{equation}\label{discrete_time_model}
+    	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
+    \end{equation}
+
+    However, this often still results in a large and difficult to solve system of equations.
+Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
+Another reason why estimation is not feasible using this approach is colinearity.
+    Looking at equation \ref{discrete_time_model} and assuming continuous functions $X_i$ it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$.
+Thereby, there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
+(cf.
+~\cite{kokoszka_introduction_2017})\\
+    A different approach is necessary.
+
     Define therefore
@@
 
-   In practice, this results in a large and often difficult to solve system of equations.
-Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
-Another reason why estimation is not feasible using this approach is colinearity.
-   If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
-  	\begin{equation}
-     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
-    \end{equation} it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
-(cf.
-~\cite{kokoszka_introduction_2017}) {\color{red} isn't something missing here?
-Like "and employ standard multivariate linear regression"}
-
 	\begin{itemize}
@@
 	\end{itemize}
-
+	\begin{itemize}	
 		\item Explain how to address truncation error in standard errors

### 2021-11-01 main.tex

@@
 
+   In practice, this results in a large and often difficult to solve system of equations.
+Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
+Another reason why estimation is not feasible using this approach is colinearity.
+   If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
+  	\begin{equation}
+     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
+    \end{equation} it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
+(cf.
+~\cite{kokoszka_introduction_2017}) {\color{red} isn't something missing here?
+Like "and employ standard multivariate linear regression" // Will be done (Jona)}
+
 	\begin{itemize}
@@
 	\end{itemize}
+	\begin{itemize}
+
 	\begin{itemize}	

### 2021-11-01 main.tex
jona

@@
 	\end{itemize}
-\subsection{Kokoszka Reimherr (2017) p51-53}
+
 There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation.
@@
 	\end{itemize}
-	\begin{itemize}
 

### 2021-11-08 main.tex
Commiting changes
Commiting changes and adding seperation

@@
 		\item Explain the concept of iid data in a functional setting
+
+-----------------------------------
+
 		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
@@
    In practice, this results in a large and often difficult to solve system of equations.
-Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
+If solved, a  perfect fit is possible,but results in a noisy and erratic function $\hat{\beta}(s)$ that is not useful for interpretation since it does not utilize the intuition of smooth functions (cf.~\cite{horvath_inference_2012}).
 Another reason why estimation is not feasible using this approach is colinearity.
@@
 	\end{itemize}
+
+The simplest approach to regularize the noisy estimate of $\hat{\beta}(s)$	is to expand it with deterministic basis function. Assume 
+	\begin{equation}
+     \beta(t) =  \sum_{k=1}^{K} c_{k}B_{k}(t)
+    \end{equation}
+    to expand
+    \begin{equation}
+    \int \beta(s)X(s) \,dt \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,dt =: \sum_{k=1}^{K} x_{ik} c_{k} 
+    \end{equation}
+    to the linear model of equation 2 with $\mathbf{c} = [\alpha, c_1, c_2,...,c_K]^T$ (corresponding to $\mathbf{\beta}$) estimated by $\mathbf{\hat{c}} = \mathbf{(X^{T}X)^{-1}X^{T}Y}$.
+Hence, the estimate $\hat{\beta}$ depends on the basis function $B_{k}$ and its corresponding shape, where $K$ is a subjective choice of the researcher.
+This subjective choice highly depends on the researchers intuition of the smoothness of the estimate.
+It is best practice to use the same basis functions as in {\color{red} add link to smoothing} (cf.
+~\cite{kokoszka_introduction_2017})
+
+    {\color{red} include Part about CI´s? its about inference and not about prediction}
+
 	\begin{itemize}

### 2021-11-13 main.tex
Some Theory

@@
 \usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 	\section{Theory}
+
+	To understand functional linear regression and the differences between the methods presented in this paper, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
+One integral concept in inferential statistics are random variables.
+Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
+	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
+As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers, but as a function in a function space.
+A formalization of this idea makes some measure theoretical considerations necessary.
+
+	\subsection{Hilbert Spaces}
 

### 2021-11-13 main.tex
More Theory

@@
 \usepackage{xcolor}
+\usepackage{multicol}
 \usepackage{amsmath}
@@
 As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers, but as a function in a function space.
-A formalization of this idea makes some measure theoretical considerations necessary.
+A formalization of this idea makes some more theoretical considerations necessary.
 
-	\subsection{Hilbert Spaces}
+	\subsection{Inner Products and Hilbert Spaces}
+	The following definitions follow \cite{hsing_theoretical_2015} {\color{red}[chapters 2.3 and 2.4]}. \\
+	A function $\langle \cdot, \cdot \rangle$ on a vector space $\mathbb{V}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
+	\begin{multicols}{2}
+			\begin{enumerate}
+			\item $\langle v, v \rangle \geq 0$
+			\item $\langle v, v \rangle = 0$ if $v = 0$
+			\item $\langle a_1 v_1 = a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
+			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
+		\end{enumerate}
+	\end{multicols}
+	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
+	The inner product naturally defines a norm and an associated distance on the vector space as follows.
+
+	\begin{equation}
+		\lvert \lvert v \rvert \rvert = {\langle v, v \rangle}^{\frac{1}{2}}
+	\end{equation}
+	\begin{equation}
+	d(v_1, v_2) = {\langle v_2 - v_1, v_2 - v_1 \rangle}^{\frac{1}{2}}
+	\end{equation}
+
+	If the inner product space is complete with respect to the induced distance, it is called a Hilbert space, denoted $\mathbb{H}$ in the following.
+To extend the known concept of a basis in a finite dimensional space to the potentially infinite Hilbert spaces, it is necessary to define the closed span of a sequence of elements of $\mathbb{H}$.
+Recall that the span of a set of vectors $S \subseteq \mathbb{R}^P$ is given by
+
+	\begin{equation}
+		span(S) = \left\{\sum_{i = 1}^{k} \lambda_i v_i \: \bigg\vert \: k \in \mathbb{N}, \: v_i \in S, \: \lambda_i \in \mathbb{R} \right\}
+	\end{equation}
+
+	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm.
+$S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$.
+\\
+	It is called an orthonornal basis, if the following properties hold. 
+	\begin{multicols}{2}
+		\begin{enumerate}
+			\item $\langle v_i, v_j \rangle = 0 \quad \forall v_i, v_j \in S \quad i \neq j$
+			\item $\lvert \lvert v \rvert \rvert = 1 \quad \forall v \in S$
+		\end{enumerate}
+	\end{multicols}
 

### 2021-11-14 main.tex
increment
More Theory

@@
 	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature.
-This data can often be processed by classical statistical methods, but only FDA allows extracting information given by the smoothness of the underlying process (cf.
+Classical statistical methods can often process this data, but only FDA allows extracting information given by the smoothness of the underlying process (cf.
 \cite{levitin_introduction_2007}).
@@
 \\
-	 Estimation of $\beta(s)$ is inherently an infinite dimensional problem.
+	 Estimation of $\beta(s)$ is inherently an infinite-dimensional problem.
 In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion.
-The results of the Monte-Carlo simulation regarding these three different methods are reported in Section 3.
-Finally, in Section 4, we test the prediction of FLR in a real world setting.
+We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3.
+Finally, in Section 4, we test the prediction of FLR in a real-world setting.
 {\color{red} (We may put some simple descriptions of results about each of MC and Application)}
@@
 	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
-As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers, but as a function in a function space.
+As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
 A formalization of this idea makes some more theoretical considerations necessary.
+The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.
 
 	\subsection{Inner Products and Hilbert Spaces}
-	The following definitions follow \cite{hsing_theoretical_2015} {\color{red}[chapters 2.3 and 2.4]}. \\
 	A function $\langle \cdot, \cdot \rangle$ on a vector space $\mathbb{V}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
@@
 \\
-	It is called an orthonornal basis, if the following properties hold. 
+	It is called an orthonornal basis, if in addition the following properties hold. 
 	\begin{multicols}{2}
@@
 	\end{multicols}
+
+	\subsection{Hilbert Space of Square-Integrable Functions}
+	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
+To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.\\
+	Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
+
+	\begin{equation}
+		\int_{0}^{1} \lvert f \rvert^2 d\mu < \infty
+	\end{equation}
+
+	Its inner product is defined as
+
+	\begin{equation}
+		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 d\mu.
+	\end{equation}
 

### 2021-11-15 main.tex
theory

@@
 	\subsection{Inner Products and Hilbert Spaces}
-	A function $\langle \cdot, \cdot \rangle$ on a vector space $\mathbb{V}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
+	Data for simple regression and multivariate regression are constructed by either random variable or random vector so that statistics are possibly defined on Euclidean space, $\mathbb{R}^n$.
+However, the statistics derived from the random function which has infinite dimension cannot be defined on the space.
+It leads to motivating to import a new space, Hilbert space.\\
+	In this paper, the field of scalars to define inner product is limited to the field of real numbers $\mathbb{R}$.
+Let $\mathbb{V}$ be a vector space.
+A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
 	\begin{multicols}{2}
@@
 \\
-	It is called an orthonornal basis, if in addition the following properties hold. 
+	It is called an orthonormal basis, if in addition the following properties hold. 
 	\begin{multicols}{2}

### 2021-11-15 main.tex
Increment

--- 2021-11-14 main.tex
@@
 	\section{Theory}
-
-	To understand functional linear regression and the differences between the methods presented in this paper, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
+	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
+However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space.
+To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
 One integral concept in inferential statistics are random variables.
@@
 	\subsection{Inner Products and Hilbert Spaces}
-	A function $\langle \cdot, \cdot \rangle$ on a vector space $\mathbb{V}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
+	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
+A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
 	\begin{multicols}{2}
@@
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space as follows.
+	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we will restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
 

### 2021-11-15 Code/prediction_works.R
Prediction

@@ -1,0 +1,67 @@
+rm(list = ls())
+library(refund)
+library(tidyverse)
+library(fda)
+set.seed(100)
+
+data(gasoline)
+data <- t(as.matrix(gasoline))
+
+octane <- data[1, ]
+waves <- data[-1, ]
+wavelengths <- seq(from = 900, to = 1700, by = 2)
+test <- seq(1, 30, 1)
+
+waves_test <- waves[, test]
+octane_test <- octane[test]
+waves_train <- waves[, -test]
+octane_train <- octane[-test]
+
+# smallbasis <- create.bspline.basis(rangeval = c(min(wavelengths), max(wavelengths)), 
+#                                    nbasis = 20, norder = 5)
+# harmFdpar <- fdPar(smallbasis)
+# 
+# gasoline_fd_train <- smooth.basis(argvals = wavelengths,
+#                                   y = waves_train, fdParobj = smallbasis)$fd
+#                          
+# gasoline_fd_test <- smooth.basis(argvals = wavelengths,
+#                                  y = waves_test, fdParobj = smallbasis)$fd
+# 
+# gasoline_pcaObj <- pca.fd(fdobj = gasoline_fd_train, 
+#                           nharm = 4, harmfdPar = harmFdpar, centerfns = FALSE)
+
+smallbasis <- create.bspline.basis(rangeval = c(0, max(wavelengths)),
+                                   nbasis = 20, norder = 5)
+harmFdpar <- fdPar(smallbasis)
+
+gasoline_fd_train <- smooth.basis(argvals = seq(0, to = 1700, length.out = 401),
+                                  y = waves_train, fdParobj = smallbasis)$fd
+
+gasoline_fd_test <- smooth.basis(argvals = seq(0, to = 1700, length.out = 401),
+                                 y = waves_test, fdParobj = smallbasis)$fd
+
+gasoline_pcaObj <- pca.fd(fdobj = gasoline_fd_train,
+                          nharm = 4, harmfdPar = harmFdpar, centerfns = FALSE)
+
+# plot(gasoline_fd_train)
+
+betabasis1 <- create.constant.basis(c(0, 30))
+betafd1    <- fd(0, betabasis1)
+betafdPar1 <- fdPar(betafd1)
+betafd2    <- create.bspline.basis(rangeval = c(0, 1700), nbasis = 20, 5)
+betafdPar2  <- fdPar(betafd2)
+betalist <- list(const=betafdPar1, gasoline_fd=betafdPar2)
+
[…]

### 2021-11-19 Code/prediction_works.R
Pred_fix

@@ -53,11 +53,12 @@ betafdPar2  <- fdPar(betafd2)
 betalist <- list(const=betafdPar1, gasoline_fd=betafdPar2)
 
 f_regress <- fRegress(y = octane_train, 
-                      xfdlist = list(const = rep(1, 30), gasoline_fd = gasoline_fd_train),
-                      betalist = betalist)
+                      xfdlist = list(#const = rep(1, 30), 
+                        gasoline_fd = gasoline_fd_train),
+                      betalist = list(gasoline_fd = betafdPar2)) #betalist)
 
 prec <- predict(object = f_regress, 
-                newdata = list(const = fd(matrix(rep(1, 30), 1, 30), betabasis1), 
+                newdata = list(#const = fd(matrix(rep(1, 30), 1, 30), betabasis1), 
                                gasoline_fd = gasoline_fd_test))
 
 #  plot the data and the fit

### 2021-11-19 Code/prediction_works.R
Color Guide

@@ -48,14 +48,12 @@ gasoline_pcaObj <- pca.fd(fdobj = gasoline_fd_train,
 betabasis1 <- create.constant.basis(c(0, 30))
 betafd1    <- fd(0, betabasis1)
 betafdPar1 <- fdPar(betafd1)
-betafd2    <- create.bspline.basis(rangeval = c(0, 1700), nbasis = 20, 5)
-betafdPar2  <- fdPar(betafd2)
 betalist <- list(const=betafdPar1, gasoline_fd=betafdPar2)
 
 f_regress <- fRegress(y = octane_train, 
                       xfdlist = list(#const = rep(1, 30), 
                         gasoline_fd = gasoline_fd_train),
-                      betalist = list(gasoline_fd = betafdPar2)) #betalist)
+                      betalist = list(gasoline_fd = harmFdpar)) #betalist)
 
 prec <- predict(object = f_regress, 
                 newdata = list(#const = fd(matrix(rep(1, 30), 1, 30), betabasis1), 

### 2021-11-19 main.tex
Prediction

@@
 	\newpage
+
+	\section{Colour Guide}
+		\begin{itemize}
+			\item {\color{red} RED}: is for general comments for your own text
+			\item {\color{green} GREEN}: is for Jona's comments
+			\item {\color{orange} ORANGE}: is for Jonghun's comments
+			\item {\color{blue} BLUE}: is for Jakob's comments
+		\end{itemize}
 
@@
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we will restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
+	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
 

### 2021-12-01 main.tex
update main.tex / added two articles to .bib

@@
 	\end{itemize}
+	\subsection{Motivate Simulation for some data generating process from application}
+	For the simulation study, we use Reiss and Ogden (2007) as a guideline.
+Similar to them, we will use the gasoline dataset in order to predict the octane rating of gasoline samples by relying on the introduced methods.
+This has become more relevant as modern internal combustion engines become more complex and rely on precisely tuned fuels.
+The dataset, which contains 60 observations with each 400 measurements was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf.
+\cite{Bohacs_Ovadi_Salgo1998}).
+Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness:
+\begin{equation}
+    f_1 = 2\sin(0.5\pi*t) + 4\sin(1.5\pi*t) + 5*\sin(2.5*\pi*t) 
+    \end{equation}
+    \begin{equation}
+    f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}
+    \end{equation}
+
+Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(X\omega) / (var(X\omega) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+These two error-terms are than computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset.
+These four combinations are then used with different number of basis-function $(5,6,...,25)$ of the order 5 to predict the responses using the b-spline basis approach and the FPCR approach.
+Within one repetition, the data is randomly sampled into a training and a test set to calculate the reported test MSE.
+In total we carried out 2000 simulations for each combination of data and number of basis functions.
 

### 2021-12-01 Code/simulation_study_approach.R
fixed cites

@@ -60,30 +60,23 @@ Y_train <- Y[-test]
 X_test <- final_X[, test]
 Y_test <- Y[test]
 
-smallbasis <- create.bspline.basis(rangeval = c(0, length(grid)), 
-                                   nbasis = 12, 7)
+largebasis <- create.bspline.basis(rangeval = c(0, length(grid)),
+                                   nbasis = 100, 7)
 
-harmFdpar <- fdPar(smallbasis)
+harmFdpar <- fdPar(largebasis)
 
-smooth_basis_train <- smooth.basis(y = X_train, 
-                                   fdParobj = smallbasis)
+smooth_basis_train <- smooth.basis(y = X_train,
+                                   fdParobj = largebasis)
 
 smooth_basis_train_fd <- smooth_basis_train$fd
-
-smooth_basis_test <- smooth.basis(y = X_test, 
-                                  fdParobj = smallbasis)
-
-smooth_basis_test_fd <- smooth_basis_test$fd
 
 simulated_pcaObj_train <- pca.fd(smooth_basis_train_fd, 
                                  nharm = nharm, 
                                  harmfdPar = harmFdpar, 
-                                 centerfns = FALSE)
+                                 centerfns = TRUE)
 
-simulated_pcaObj_test <- pca.fd(smooth_basis_test_fd, 
-                                nharm = nharm, 
-                                harmfdPar = harmFdpar, 
-                                centerfns = FALSE)
+test_in_train_basis <- smooth.basis(y = X_test, 
+                                    fdParobj = simulated_pcaObj_train$harmonics)
 
 xfdlist <- list(smooth_basis = smooth_basis_train_fd)
 betalist <- list(smooth_basis_fd = smallbasis)

### 2021-12-01 main.tex
Theory Increment

@@
 	\end{equation}
+
+	The Hilbert space of square integrable functions on $[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis.
+Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
+For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
+
+	\subsection{Different Bases of $\mathbb{L}^2$}
+
+	\paragraph{b-spline Basis}
+
+	\paragraph{Fourier Basis}
 
@@
 \begin{equation}
-    f_1 = 2\sin(0.5\pi*t) + 4\sin(1.5\pi*t) + 5*\sin(2.5*\pi*t) 
+    f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
     \end{equation}

### 2021-12-06 main.tex
start application, updating ss

@@
 	\newpage
-	\section{Simulation}
+	\section{Simulation Study}
 
@@
 	\subsection{Motivate Simulation for some data generating process from application}
-	For the simulation study, we use Reiss and Ogden (2007) as a guideline.
-Similar to them, we will use the gasoline dataset in order to predict the octane rating of gasoline samples by relying on the introduced methods.
+	For the simulation study, we use the gasoline dataset to predict the octane ratings of gasoline samples relying on the introduced methods.
 This has become more relevant as modern internal combustion engines become more complex and rely on precisely tuned fuels.
-The dataset, which contains 60 observations with each 400 measurements was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf.
+The dataset, which contains 60 i.i.d.
+observations with each 400 measurements, was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf.
 \cite{Bohacs_Ovadi_Salgo1998}).
+The study follows Reiss and Ogden (2007) as a guideline.
 Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness:
@@
 
-Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(X\omega) / (var(X\omega) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
-These two error-terms are than computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset.
+Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+The two error-terms are then computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset.
 These four combinations are then used with different number of basis-function $(5,6,...,25)$ of the order 5 to predict the responses using the b-spline basis approach and the FPCR approach.
 Within one repetition, the data is randomly sampled into a training and a test set to calculate the reported test MSE.
+The simulation was done with R (version...).
 In total we carried out 2000 simulations for each combination of data and number of basis functions.
+{\color{green} Information about version and link to repo / package in footnote??}
+
+\subsection{Results}
+
+\subsubsection{Interpretation and Relevance for Application}
 
@@
 	\section{Application}
+The application uses the insights from the previous sections to predict the octane ratings of the introduced gasoline dataset. Following the results from the simulation study,... 
+\begin{itemize}
+\item
+{\color{green} incorporate results of simulation study: number of basis, components, etc...}
+\item
+point out difficulties estimating sderror
+\item
+describe setup and results
+\end{itemize}
 

### 2021-12-09 main.tex
Increment

@@
 	\subsection{Different Bases of $\mathbb{L}^2$}
-
+	Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.
 	\paragraph{b-spline Basis}
@@
 	\paragraph{Fourier Basis}
+	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions.
+	\begin{equation}
+		S_{FB, i}(x) = \begin{cases}
+			1 & \text{if} \quad i = 1\\
+			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
+			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
+		\end{cases}
+	\end{equation}
+
+	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
 

### 2021-12-09 Code/Plot_Generators/Fourier_basis_plot.R

@@ -1,0 +1,3 @@
+##### This script generates a plot showing of a chosen number of fourier basis functions #####
+
+n_funcs <- 6

### 2021-12-09 Code/Plot_Generators/Fourier_basis_plot.R
Example plot
Added plot for Fourier Basis

@@ -1,3 +1,61 @@
 ##### This script generates a plot showing of a chosen number of fourier basis functions #####
 
+# Load packages
+library(tidyverse)
+
+# setup for plot generation
 n_funcs <- 6
+n_points <- 1000
+
+# function factory that generates the basis functions
+basis_func <- function(i){
+  if(i == 1){
+    ret_func <- function(x){return(1)}
+  } else
+  if(i %% 2 == 0){
+      ret_func <- function(x){return(sqrt(2)*cos(pi * i * x))}
+  } else
+  if(i > 1 && i %% 2 == 1){
+    ret_func <- function(x){return(sqrt(2)*sin(pi * (i-1) * x))}
+  } else{
+    stop('Malformed Index chosen.')
+  }
+}
+
+# Create points for calculation of basis functions
+points <- seq(from = 0, to = 1, length.out = n_points)
+
+# Calculate basis functions at points
+res_list <- list()
+for(i in 1:n_funcs){
+  tmp_func <- basis_func(i)
+  res_list[[i]] <- unlist(
+    map(.x = points, .f = tmp_func)
+    )
+}
+
+# convert to tibble
+res_tibble <- cbind(tibble(x = points),
+                    as_tibble(res_list, .name_repair = 'unique'))
+names(res_tibble) <- c('x', paste0('S_', 1:n_funcs))
+
+# pivot_longer to allow for easy plotting
+plot_tibble <- res_tibble %>% 
+  pivot_longer(cols = !x, names_to = 'Function', values_to = 'Value')
+
+# generate plot
+fourier_plot <- ggplot(data = plot_tibble) +
+  geom_line(aes(x = x, y = Value, col = Function)) +
+  ggtitle("Fourier Basis") +
+  theme_light() +
+  scale_colour_brewer(palette="Set1") + 
+  theme(legend.position="bottom",
+        plot.title = element_text(size = 30),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 20),
+        legend.title = element_text(size = 24),
+        legend.text = element_text(size = 20))
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/Fourier_Basis.pdf', plot = fourier_plot,
+       width = 20, height = 8, units = "in", dpi = 600)

### 2021-12-09 main.tex
Example plot
Added plot for Fourier Basis
B-spline basis

@@
 \usepackage{microtype}
+\usepackage{graphicx}
 \usepackage{hyperref}
@@
 	Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.
-	\paragraph{b-spline Basis}
+
+	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
+On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
+Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$.
+	A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
+Let $S_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
+
+	\begin{equation}
+	\begin{split}
+		S_{l,0}^{BS}(x) = &
+		\begin{cases}
+			1 & \text{if} \quad x \in \left[\tau_l, \tau_{l+1}\right)\\
+			0 & \text{otherwise}
+		\end{cases}\\ \\
+		S_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} S_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} S_{l+1,m-1}^{BS}(x)
+	\end{split}
+	\end{equation}
 
 	\paragraph{Fourier Basis}
-	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions.
+	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
 	\begin{equation}
-		S_{FB, i}(x) = \begin{cases}
+		S_{i}^{FB}(x) = \begin{cases}
 			1 & \text{if} \quad i = 1\\
@@
 	\end{equation}
+
+	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
 

### 2021-12-09 Code/Plot_Generators/BSpline_basis_plot.R
B-spline plot

@@ -2,51 +2,35 @@
 
 # Load packages
 library(tidyverse)
+library(fda)
 
 # setup for plot generation
-n_funcs <- 6
 n_points <- 1000
-
-# function factory that generates the basis functions
-basis_func <- function(i){
-  if(i == 1){
-    ret_func <- function(x){return(1)}
-  } else
-  if(i %% 2 == 0){
-      ret_func <- function(x){return(sqrt(2)*cos(pi * i * x))}
-  } else
-  if(i > 1 && i %% 2 == 1){
-    ret_func <- function(x){return(sqrt(2)*sin(pi * (i-1) * x))}
-  } else{
-    stop('Malformed Index chosen.')
-  }
-}
+knots <- seq(from = 0, to = 1, length.out = 8)
+order <- 3
 
 # Create points for calculation of basis functions
 points <- seq(from = 0, to = 1, length.out = n_points)
 
+# function factory that generates the basis functions
+bspline_basis <- create.bspline.basis(rangeval = c(0,1), norder = order,
+                                        breaks = knots)
+
 # Calculate basis functions at points
-res_list <- list()
-for(i in 1:n_funcs){
-  tmp_func <- basis_func(i)
-  res_list[[i]] <- unlist(
-    map(.x = points, .f = tmp_func)
-    )
-}
+res_matrix <- eval.basis(evalarg = points, basisobj = bspline_basis)
 
 # convert to tibble
-res_tibble <- cbind(tibble(x = points),
-                    as_tibble(res_list, .name_repair = 'unique'))
-names(res_tibble) <- c('x', paste0('S_', 1:n_funcs))
+res_tibble <- cbind(x = points, as_tibble(res_matrix))
+names(res_tibble) <- c('x', paste0('S_', 1:dim(res_matrix)[2]))
 
 # pivot_longer to allow for easy plotting
 plot_tibble <- res_tibble %>% 
   pivot_longer(cols = !x, names_to = 'Function', values_to = 'Value')
 
 # generate plot
-fourier_plot <- ggplot(data = plot_tibble) +
+bspline_plot <- ggplot(data = plot_tibble) +
   geom_line(aes(x = x, y = Value, col = Function)) +
-  ggtitle("Fourier Basis") +
+  ggtitle("B-spline Basis") +
   theme_light() +
   #scale_colour_brewer(palette="Set1") + 
   theme(legend.position="bottom",
[…]

### 2021-12-09 Code/Plot_Generators/BSpline_basis_plot.R
Plot improvements

@@ -30,11 +30,11 @@ plot_tibble <- res_tibble %>%
 # generate plot
 bspline_plot <- ggplot(data = plot_tibble) +
   geom_line(aes(x = x, y = Value, col = Function)) +
-  ggtitle("B-spline Basis") +
+  #ggtitle("B-spline Basis") +
   theme_light() +
   #scale_colour_brewer(palette="Set1") + 
-  theme(legend.position="bottom",
-        plot.title = element_text(size = 30),
+  theme(legend.position = "none",
+        #plot.title = element_text(size = 30),
         axis.title = element_text(size = 20),
         axis.text = element_text(size = 20),
         legend.title = element_text(size = 24),

### 2021-12-09 Code/Plot_Generators/Fourier_basis_plot.R

@@ -46,11 +46,11 @@ plot_tibble <- res_tibble %>%
 # generate plot
 fourier_plot <- ggplot(data = plot_tibble) +
   geom_line(aes(x = x, y = Value, col = Function)) +
-  ggtitle("Fourier Basis") +
+  #ggtitle("Fourier Basis") +
   theme_light() +
   #scale_colour_brewer(palette="Set1") + 
-  theme(legend.position="bottom",
-        plot.title = element_text(size = 30),
+  theme(legend.position = "none",
+        #plot.title = element_text(size = 30),
         axis.title = element_text(size = 20),
         axis.text = element_text(size = 20),
         legend.title = element_text(size = 24),

### 2021-12-10 main.tex
B-spline plot
Plot improvements
Labels
Added labels
BasisRepresentation

@@
 \usepackage{multicol}
+\usepackage{float}
 \usepackage{amsmath}
 \usepackage{amssymb}
+\usepackage[font=small,skip=2pt]{caption}
 \usepackage[
@@
 We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
+
 	 \begin{equation}
@@
 	 \end{equation}
+
 	 where the $X_{i}$ are realizations of a random function $\mathbf{X}$, $Y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function.
@@
 A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
+
 	\begin{multicols}{2}
@@
 	\end{multicols}
+
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
@@
 	\end{equation}
+
 	\begin{equation}
@@
 	It is called an orthonormal basis, if in addition the following properties hold.
+
 	\begin{multicols}{2}
@@
 	\end{multicols}
+
+	As in the case of a Banach space, each element of a Hilbert space can be expressed in terms of a corresponding basis.
+This can be done using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t.
+a basis $S = \{s_n\}$ as follows.
+
+	\begin{equation}
+		x = \sum_{j = 1}^{\infty}{\langle x, s_j \rangle}s_j
+	\end{equation}
+
+	As can be seen, differing from the case of a Banach space, these representations can be limits of series as previously hinted at by using the closed span of the basis.
+As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space, is to use a truncated series.
+
+	\begin{equation}
+		x \approx \sum_{j = 1}^{K}{\langle x, s_j \rangle}s_j
+	\end{equation}
 
@@
 	\subsection{Different Bases of $\mathbb{L}^2$}
+	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
 Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.
@@
 
+	{\color{red}Explain what happens when $l+m+1 > L$ !!!}
+
+	\begin{figure}[H]\label{bspline_basis}
+		\includegraphics[width = \textwidth]{Graphics/Bspline_Basis.pdf}
+		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
+	\end{figure}
+
 	\paragraph{Fourier Basis}
@@
 	\begin{equation}
-		S_{i}^{FB}(x) = \begin{cases}
+		S_{i}^{FB}(x) = 
+		\begin{cases}
 			1 & \text{if} \quad i = 1\\
@@
 
+	\begin{figure}[H]\label{fourier_basis}
 	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
+	\caption{Fourier basis functions for $i = 1,\dots,6$}
+	\end{figure}
 
@@
 	\end{itemize}
+
 	A common setting in non-functional regression is akin to the following. Assume a model as follows:
+
 	\begin{equation}
@@
 	\end{equation}
+
 	where $X \in \mathbb{R}^{n\times J}$ is a matrix containing the regressors, $\beta \in \mathbb{R}^J$ is a coefficient vector and $epsilon$ is a vector containing the error term.
@@
 Then the famous OLS-estimator is given by:
+
 	\begin{equation}
@@
 	\end{equation}
+
 	A naive approach to FLR would be to try to generalize this to the functional setting.
 	Assuming a data generating process of the form:
+
 	\begin{equation}
@@
     \end{equation}
+
     it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
@@
     Define therefore
+
     \begin{equation}
@@
     \end{equation}
+
    Under the assumption that $X$ is independent from $\epsilon$ we obtain
+
    \begin{equation}
@@
    \end{equation}
+
    \begin{equation}
@@
    If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
+
   	\begin{equation}
     	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
-    \end{equation} it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
+    \end{equation}
+
+	it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
 (cf.
@@
 The simplest approach to regularize the noisy estimate of $\hat{\beta}(s)$	is to expand it with deterministic basis function. Assume
+
 	\begin{equation}
@@
     \end{equation}
+
     to expand
+
     \begin{equation}
@@
     \end{equation}
+
     to the linear model of equation 2 with $\mathbf{c} = [\alpha, c_1, c_2,...,c_K]^T$ (corresponding to $\mathbf{\beta}$) estimated by $\mathbf{\hat{c}} = \mathbf{(X^{T}X)^{-1}X^{T}Y}$.
@@
 	\end{itemize}
+
 	\subsection{Motivate Simulation for some data generating process from application}
@@
 Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness:
+
 	\begin{equation}
@@
     \end{equation}
+
     \begin{equation}

### 2021-12-13 main.tex
small correction
B-spline basis & sim_JJ_tmp.R
Added more details to section on b-splines and saved reformatted and commented code as simulation_study_JJ_tmp.R

@@
 			\item $\langle v, v \rangle = 0$ if $v = 0$
-			\item $\langle a_1 v_1 = a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
+			\item $\langle a_1 v_1 + a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
 			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
@@
 
+	\paragraph{Fourier Basis}
+	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
+	\begin{equation}
+		S_{i}^{FB}(x) = 
+		\begin{cases}
+			1 & \text{if} \quad i = 1\\
+			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
+			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
+		\end{cases}
+	\end{equation}
+
+	\begin{figure}[H]\label{fourier_basis}
+	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
+	\caption{Fourier basis functions for $i = 1,\dots,6$}
+	\end{figure}
+
 	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
@@
 
-	{\color{red}Explain what happens when $l+m+1 > L$ !!!}
+	This, however, does not really yield a basis of $\mathbb{L}^2$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2$.
+To really obtain a basis of $\mathbb{L}^2$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
+As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2$ will serve as a sufficient approximation for an appropriately chosen B-spline basis.
+	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
+
+	{\color{red}Explain what happens when $l+m+1 > L$ !!!\\
+		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.}
 
@@
 	\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
-	\end{figure}
-
-	\paragraph{Fourier Basis}
-	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
-	\begin{equation}
-		S_{i}^{FB}(x) = 
-		\begin{cases}
-			1 & \text{if} \quad i = 1\\
-			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
-			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
-		\end{cases}
-	\end{equation}
-
-	\begin{figure}[H]\label{fourier_basis}
-	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
-	\caption{Fourier basis functions for $i = 1,\dots,6$}
 \end{figure}

### 2021-12-13 Code/simulation_study_JJ_tmp.R

@@ -1,0 +1,176 @@
+# Clear Workspace
+rm(list = ls())
+
+# load libraries
+library(fda)
+
+# Define Data generator
+data_generation <- function(fun) {
+  # Variables for the data generation
+  var1 <- 1
+  var2 <- 2
+  var3 <- 0.2
+
+  # Container for observations
+  X <- matrix(data = 0, nrow = n_obs, ncol = length(grid))
+
+  for (i2 in 1:n_obs) {
+    X[i2, ] <- {
+      rnorm(n = length(grid), mean = 2, sd = var1)
+      +runif(n = 1, min = 0, max = var2)
+      +rnorm(n = 1, mean = 0, sd = var3) * grid
+    } * fun
+
+    for (j2 in 1:5) {
+      e <- abs(rnorm(n = 2, mean = 0, sd = var1 / j2^(2)))
+      X[i2, ] <- X[i2, ] + {
+        e[1] * sin((2 * pi) * grid * j2)
+        +e[2] * cos((2 * pi) * grid * j2)
+      }
+    }
+  }
+  return(X)
+}
+
+data(gasoline)
+octane <- (gasoline$octane)
+NIR <- as.matrix(gasoline$NIR)
+
+###################################################################################################################
+# set up "global" variables
+###################################################################################################################
+
+set.seed(100)
+
+n_obs <- 60
+nharm <- 4
+n_var <- 400
+grid <- seq(0, 1, length = n_var + 1) # why do we use exactly n_var = 1? (Jakob)
+
+# smooth
+f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+# bumpy
+f2 <- {
+  1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2)
+  -4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2)
+  +8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2)
+  -1 * exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
+}
+
+# two different variances of error
+sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
+sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
+sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
[…]

### 2021-12-13 main.tex
Increment

@@
 
-	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
+	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.

### 2021-12-13 Code/simulation_study_JJ_tmp.R

@@ -3,9 +3,10 @@ rm(list = ls())
 
 # load libraries
 library(fda)
+library(caret)
 
 # Define Data generator
-data_generation <- function(fun) {
+data_generation <- function(fun, n_obs, grid) {
   # Variables for the data generation
   var1 <- 1
   var2 <- 2
@@ -49,7 +50,7 @@ grid <- seq(0, 1, length = n_var + 1) # why do we use exactly n_var = 1? (Jakob)
 
 # smooth
 f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
-# bumpy
+# bumpy (where does it come from?)
 f2 <- {
   1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2)
   -4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2)
@@ -58,6 +59,7 @@ f2 <- {
 }
 
 # two different variances of error
+# noise for dependent variable in bootstrapping approach
 sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
 sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
 sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
@@ -145,10 +147,14 @@ fpcr_function <- function(rep) {
         data <- t(NIR)
 
         # print(dim(NIR))
-        smallbasis <- create.bspline.basis(rangeval = c(0, length(grid)), nbasis = as.numeric(j), norder = as.numeric(order))
+        smallbasis <- create.bspline.basis(
+          rangeval = c(0, length(grid)), nbasis = as.numeric(j), 
+          norder = as.numeric(order))
+        
         smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
 
-        simulated_pcaObj <- pca.fd(smooth_basis_fd, nharm = nharm, centerfns = TRUE)
+        simulated_pcaObj <- pca.fd(smooth_basis_fd, nharm = nharm, 
+                                   centerfns = TRUE)
 
 
         dataframe1_1 <- data.frame(Y1_1, simulated_pcaObj$scores)

### 2021-12-13 main.tex
Theory Increment

@@
 
+	\subsection{Functional Data Sets}
+	In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions.
+In the following, all random functions are assumed to realize in $\mathbb{L}^2$.
+As in the finite dimensional setting the concept of identically distributed and independent data is important.
+This concept generalizes intuitively to the case of functional data using the concepts for general random variables.
+{\color{red} Explain this better!}\\
+	An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process.
+A definition and a plotted example for the Wiener process are given in \ref{Wiener}.
+
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
+	Given a set of i.i.d. functional observations, it is possible to represent them in terms of their generating stochastic process.
 
@@
 
+	\subsection{Wiener Process}\label{Wiener}
+	A Wiener process $W_t$ is a real-valued continuous-time stochastic process {\color{red} ... This is wikipedia, look for right citation!}
+	It is characterized by the following properties.
+
+	\begin{multicols}{2}
+		\begin{enumerate}
+			\item $W_0 = 0$
+			\item $\forall t > 0 W_{t+u} - W_t \perp\!\!\!\perp W_s \forall s \leq t$
+			\item $W_{t+u} - W_t \sim \mathcal{N}(0,u)$
+			\item $W_t$ is continuous in $t$
+		\end{enumerate}
+	\end{multicols}
+
+	\begin{figure}[H]\label{Wiener_plot}
+		\includegraphics[width = \textwidth]{Graphics/Wiener_plot.pdf}
+		\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
+	\end{figure}
+
 	\newpage

### 2021-12-13 Code/Plot_Generators/Wiener_process.R

@@ -1,0 +1,44 @@
+##### This script generates an iid data set from wiener processes and plots it
+
+# Load packages
+library(tidyverse)
+
+# setup for plot generation
+n_points <- 10000
+points <- seq(from = 0, to = 1, length.out = n_points)
+realizations <- 25
+
+Wiener_process <- function(grid){
+  values <- rep(0, times = length(grid))
+  for(i in 2:length(grid)){
+    values[i] <- values[i-1] + rnorm(n = 1, mean = 0, sd = sqrt(grid[i] - grid[i-1]))
+  }
+  return(values)
+}
+
+data_mat <- matrix(data = unlist(map(.x = 1:realizations,
+                                     .f = function(i) Wiener_process(points))),
+                   nrow = n_points, ncol = realizations, byrow = FALSE)
+
+data_tibble <- cbind(tibble(x = points), as_tibble(data_mat, .name_repair = 'unique'))
+names(data_tibble) <- c('t', paste0('Realization_', 1:realizations))
+
+plot_tibble <- data_tibble %>% 
+  pivot_longer(cols = !x, names_to = 'Realization', values_to = 'Value')
+
+# generate plot
+Wiener_plot <- ggplot(data = plot_tibble) +
+  geom_line(aes(x = t, y = Value, col = Realization)) +
+  #ggtitle("B-spline Basis") +
+  theme_light() +
+  #scale_colour_brewer(palette="Set1") + 
+  theme(legend.position = "none",
+        #plot.title = element_text(size = 30),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 20),
+        legend.title = element_text(size = 24),
+        legend.text = element_text(size = 20))
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/Wiener_plot.pdf', plot = Wiener_plot,
+       width = 20, height = 8, units = "in", dpi = 600)

### 2021-12-13 Code/Plot_Generators/Wiener_process.R
Correction

@@ -24,7 +24,7 @@ data_tibble <- cbind(tibble(x = points), as_tibble(data_mat, .name_repair = 'uni
 names(data_tibble) <- c('t', paste0('Realization_', 1:realizations))
 
 plot_tibble <- data_tibble %>% 
-  pivot_longer(cols = !x, names_to = 'Realization', values_to = 'Value')
+  pivot_longer(cols = !t, names_to = 'Realization', values_to = 'Value')
 
 # generate plot
 Wiener_plot <- ggplot(data = plot_tibble) +

### 2021-12-15 Presentation/slides.tex
Presentation Template
Added folder presentation and its contents

% Inbuilt themes in beamer
\documentclass{beamer}

% Theme choice:
\usetheme{Berlin}
\usecolortheme{seahorse}

% packages
%\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
%\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

\addbibresource{../RMbibliography.bib}
\parindent=0pt

% Title page details: 
\title{{\color{red} TEMPORARY TITLE}}
\author{Jona Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

\begin{document}

	% Title page frame
	\begin{frame}
		\titlepage 
	\end{frame}

	% Remove logo from the next slides
	\logo{}

	% I'm not really a fan of a table of contents in short presenations (Jakob)
	% Outline frame
	%\begin{frame}{Outline}
	%	\tableofcontents
	%\end{frame}

	\begin{frame}{Lorem Ipsum}
		Lorem Ipsum dolor sit amet.
	\end{frame}

\end{document}

### 2021-12-16 main.tex
Karhunen-Loeve stuff

@@
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
-	Given a set of i.i.d. functional observations, it is possible to represent them in terms of their generating stochastic process.
+	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process.
+To motivate it, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$.
+Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
+	Then the mean and covariance functions of $F$ are defined as follows.
+
+	\begin{equation}\label{MeanFunction}
+		\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]
+	\end{equation}
+
+	\begin{equation}\label{CovarianceFunction}
+		c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]
+	\end{equation}
+
+	Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
+
+	\begin{equation}\label{KarhunenLoeve}
+		F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
+	\end{equation}
+
+	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ of the following equation.
+
+	\begin{equation}
+		\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
+	\end{equation}
+
+	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$.
+
+	In the typical scalar setting, a similar consideration leads to the concept of principal components.
+This is also possible in a functional setting.
+Let $\{f_1(t), \dots, f_n(t)\}$ be a set of i.i.d.
+realizations generated by a random function $F(\omega) \mapsto \mathbb{L}^2[0,1]$.
+	Define the following sample analogues for the mean and covariance functions.
+
+	\begin{equation}
+		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)
+	\end{equation}
+
+	\begin{equation}
+		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)
+	\end{equation}
+
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ as the solutions of the following equation.
+{\color{red} I think the number of principal components has to be smaller then the number of observations.
+So I can give more information about $\mathcal{I}$.}
+
+	\begin{equation}
+		\int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t)
+	\end{equation}
+
+	This naturally leads to the following representation.
+
+	\begin{equation}
+		f_i(t) = \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
+	\end{equation}
+
+	\subsection{Generating Similar Curves}
 

### 2021-12-31 Presentation/slides.tex
Slides update

@@
 % Title page details: 
-\title{{\color{red} TEMPORARY TITLE}}
-\author{Jona Willnow, Jakob Juergens, Jonghun Baek}
+\title{Scalar on Function Regression}
+\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
 \date{{\color{red}}Presentation Day}
@@
 
-	% I'm not really a fan of a table of contents in short presenations (Jakob)
+	% I'm not really a fan of a table of contents in short presentations (Jakob)
 	% Outline frame
@@
 
-	\begin{frame}{Lorem Ipsum}
-		Lorem Ipsum dolor sit amet.
+	\begin{frame}{Introduction}
+		Jona \\
+		Introductory Example $\rightarrow$ Octane/NIR-spectrum
+	\end{frame}
+
+	\begin{frame}{Theory}
+		Jona \\
+		Motivation from multivariate regression (multivariate dgp).
+	\end{frame}
+
+	\begin{frame}{Theory}
+		Jonghun
+		\begin{itemize}
+			\item Random Functions (name square integrable functions)
+			\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
+			\item Use curves to predict a scalar response (show typical dgp)
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Theory}
+		Jonghun
+		\begin{itemize}
+			\item Basis expansions (b-splines and fourier)
+			\item Talk about purposes
+			\item Plots and show bias variance tradeoff
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Theory}
+		Jakob
+		\begin{itemize}
+			\item Random function represented as linear combination of basis functions
+			\item Just transform to multiple linear regression setting
+			\item You already know that from the beginning
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Theory - FPCA}
+		Jakob
+		\begin{itemize}
+			\item Let's assume you know the theory of PCA (pc from varcov matrix)
+			\item Introduce mean and covariance functions of random functions
+			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion)
+			\item Sample Analog! (create a basis from observations and use for basis regression)
+			\item Plot fpcs and approximation of function realization
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application}
+		Jona
+		\begin{itemize}
+			\item Compare b-spline / fourier regression chosen via criterion (cv/aic/...)
+			\item Similar for fpca
+			\item generate new curves from observed curves motivated by Karhunen-Loeve expansion
+			\item Compare optimal variants with test and training sets
+			\item Connect to Application
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Summary}
+		Jona \\
+		Just summarize what we have done...
+	\end{frame}
+
+	\begin{frame}{further reading}
+		Put footnotes here!
 	\end{frame}

### 2022-01-01 main.tex
Some theory

@@
 
-	\subsection{Generating Similar Curves}
+	\subsection{Scalar-on-Function Regression}
+	In the simple scalar setting one of the most important tools in econometrics is the linear regression.
+Its goal is to predict the value of a dependent variable given a set of associated variables.
+This approach has two main purposes: inference and prediction.
+	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
+	A general data generating process in this scenario could look like the following equation.
+
+	\begin{equation}
+		y = \alpha + \Psi(f) + \epsilon
+	\end{equation}
+
+	Here $\Psi$ is a functional that maps a realization of a random function in $\mathbb{L}^2[0,1]$ into $\mathbb{R}$.
+One simple example to illustrate the principle is the maximum $\Psi(f) = \max_{x \in [0,1]}f(x)$.
+	However, the typical setup is often as follows mimicking the structure of the multivariate linear model extended from summation to integration.
+
+	\begin{equation}
+		y = \alpha + \int_{0}^{1} \beta(s)f(s) \mathrm{d}s + \epsilon
+	\end{equation}
+
+	Where $f(s)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(s)$ is a coefficient function.
 
@@
 		\item Explain the concept of iid data in a functional setting		
-
------------------------------------
-
 		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
@@
 
+	\subsection{Generating Similar Curves}
+    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
+    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
+Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience...
+No theoretical reasoning)}
 	\subsection{Results}

### 2022-01-01 main.tex
Some more theory

@@
 Its goal is to predict the value of a dependent variable given a set of associated variables.
-This approach has two main purposes: inference and prediction.
+For reference assume a data generating process as follows.
+{\color{red} Structure is bad...
+This will be changed.}
+
+	\begin{equation}
+		Y = X\beta + \epsilon
+	\end{equation}
+
+	Where $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
+	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$.
+The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
+{\color{red}List Assumptions?
+Then we need to list the assumptions for functional linear regression as well I think.}
+
+	\begin{equation}
+		\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
+	\end{equation}
+
 	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
-	A general data generating process in this scenario could look like the following equation.
+	A general data generating process in this functional scenario could look like the following equation.
 
@@
 	However, the typical setup is often as follows mimicking the structure of the multivariate linear model extended from summation to integration.
+This structure is crucial for the extension of linear regression to the case of functional regressors.
+Therefore, in this paper we always implicitly assume that a data generating process has the following structure.
+{\color{red} maybe a better motivation is the one Jona gave: from very dense observations that run into problems of colinearity when using the original OLS estimator}
 
@@
 
-	Where $f(s)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(s)$ is a coefficient function.
+	Where $f(s)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(s)$ is an unknown coefficient function. 
+	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(s)$ given a data set containing realizations of a random function and associated scalar response variables.
+However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible.
+Therefore, other options have to be considered.
+
+	\subsection{Estimation via Basis-Representation}
+	The most common way to make this problem tractable is via a basis representation of the originally observed function.
 
@@
 One aspect of a useful interpretation is that the estimate $\beta(s)$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.
-
-	\begin{itemize}
-		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
-	\end{itemize}
 

### 2022-01-01 Presentation/slides.tex
Some slide stuff

@@
 
+	\begin{frame}{Principal Component Analysis}
+		Setting: $Y = X\beta + \epsilon$ \: with standardized regressors in $X$ \\
+		Goal: \textbf{Dimension Reduction} 
+		\vspace{0.3cm}
+
+		Let $\Sigma_X = Cov(x)$ and let $\{\lambda_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvalues} of $\Sigma_X$ and $\{\gamma_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvectors} of $\Sigma_X$.
+	\end{frame}
+
+	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
+
+		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]$$
+
+		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]$$
+
+		The \textbf{Eigenvalues} and \textbf{Eigenfunctions}: $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$  are solutions of the following equation:
+		$$ \int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t) $$
+	\end{frame}
+
+	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
+		A random function $F$ can be expressed in terms of its mean function and its Eigenfunctions:
+		$$F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$
+
+		Where the $\xi_j$ are scalar-valued random variables with variance $\lambda_j$.\\
+		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
+	\end{frame}
+
 	\begin{frame}{Simulation Setup \& Application}

### 2022-01-02 Presentation/slides.tex
PCA & Karhunen-Loeve Stuff

@@
 
+	\begin{frame}{Spectral Representation of Random Vectors}
+		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
+
+		\begin{itemize}
+			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
+			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
+			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
+		\end{itemize}
+
+		\vspace{0.2cm}
+		Then $X$ can also be represented as
+		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
+		where the $\xi_i(\omega)$ have the following properties
+
+		\begin{multicols}{2}
+			\begin{enumerate}
+				\item $\mathbb{E}[\xi_i(\omega)] = 0$
+				\item $var(\xi_i(\omega)) = \lambda_i$
+				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
+			\end{enumerate}
+		\end{multicols}
+	\end{frame}
+
 	\begin{frame}{Principal Component Analysis}
-		Setting: $Y = X\beta + \epsilon$ \: with standardized regressors in $X$ \\
-		Goal: \textbf{Dimension Reduction} 
-		\vspace{0.3cm}
+		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
 
-		Let $\Sigma_X = Cov(x)$ and let $\{\lambda_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvalues} of $\Sigma_X$ and $\{\gamma_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvectors} of $\Sigma_X$.
+		\begin{itemize}
+			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ be the matrix containing the standardized regressors in the usual configuration.
+			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
+			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
+			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
+		\end{itemize}
+
 	\end{frame}
@@
 
-		Where the $\xi_j$ are scalar-valued random variables with variance $\lambda_j$.\\
+		Where the $\xi_j$ are scalar-valued random variables with the following properties.
+		\begin{multicols}{2}
+			\begin{enumerate}
+				\item $\mathbb{E}[\xi_i(\omega)] = 0$
+				\item $var(\xi_i(\omega)) = \lambda_i$
+				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
+			\end{enumerate}
+		\end{multicols}
+
 		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.

### 2022-01-02 Presentation/slides.tex
Increment
More FPCA stuff

@@
 				\item $\mathbb{E}[\xi_i(\omega)] = 0$
-				\item $var(\xi_i(\omega)) = \lambda_i$
+				\item $Var(\xi_i(\omega)) = \lambda_i$
 				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
@@
 		\end{multicols}
-	\end{frame}
-
-	\begin{frame}{Principal Component Analysis}
-		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
-
-		\begin{itemize}
-			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ be the matrix containing the standardized regressors in the usual configuration.
-			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
-			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
-			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
-		\end{itemize}
-
 	\end{frame}
@@
 		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
+	\end{frame}
+
+	\begin{frame}{Principal Component Analysis}
+		A related concept is \textbf{Principal Component Analysis} (PCA).
+		\vspace{0.2cm}
+
+		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
+
+		\begin{itemize}
+			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
+			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
+			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
+			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
+		\begin{multicols}{2}
+			\begin{enumerate}
+				\item $\mathbb{E}[Z_i(\omega)] = 0$
+				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
+				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
+			\end{enumerate}
+		\end{multicols}
+	\end{frame}
+
+	\begin{frame}{Functional Principal Component Analysis}
+		This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
+		\vspace{0.2cm}
+
+		\textbf{Empirical Mean Function}:
+		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)$$
+
+		\textbf{Empirical Autocovariance Function}:
+		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)$$
+
+	\end{frame}
+
+	\begin{frame}{Functional Principal Component Analysis}
+
+		The \textbf{Eigenvalues} and \textbf{Eigenfunctions}: $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$  are solutions of the following equation:
+		$$ \int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t) $$
+		\vspace{0.2cm}
+
+		The principal components are then defined analogously to before:
+		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
+
 	\end{frame}

### 2022-01-02 Presentation/slides.tex
Correction

@@
 
-		The principal components are then defined analogously to before:
-		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
+		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are then called the functional principal components and the corresponding scores $\xi_i$ can be derived using the following equation.
+		$$\xi_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
 

### 2022-01-03 Presentation/slides.tex
Some Estimation Stuff

--- 2022-01-02 Presentation/slides.tex
@@
 
+	\begin{frame}{Estimation via Basis Representation}
+		Assume the following data generating process
+		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
+		\begin{itemize}
+			\item $Y$ and $\epsilon$ realize in $\mathbb{R}$ and $F$ realizes in $\mathbb{L}^2[0,1]$
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Assume that we have a data set containing observations each of which is made up of:
+		\begin{itemize}
+			\item $y_i$: \quad a scalar realizations of $Y$
+			\item $f_i(t)$: \quad a realization of $F$
+		\end{itemize}
+
+	\end{frame}
+
+	\begin{frame}{Estimation via Basis Representation}
+		Let $\{b_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$
+		\vspace{0.2cm}
+
+		Then we have the following representation of $\beta(t)$
+		$$\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t) = \sum_{j = 1}^{L} \psi_j b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j b_j(t)$$
+		and we can transform the data generating process into:
+		\begin{equation}\notag
+			\begin{split}
+				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+						  & = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	  
+			\end{split}
+		\end{equation}
+	\end{frame}
+
+	\begin{frame}
+		$$\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
+		This is a scalar we can calculate for each observation and for each deterministic basis function $b_j(t)$.
+	\end{frame}
+
 	\begin{frame}{Theory - FPCA}
@@
 		\begin{itemize}
-			\item Let's assume you know the theory of PCA (pc from varcov matrix)
-			\item Introduce mean and covariance functions of random functions
-			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion)
-			\item Sample Analog! (create a basis from observations and use for basis regression)
+			\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
+			\item Introduce mean and covariance functions of random functions $\checkmark$
+			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
+			\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
 			\item Plot fpcs and approximation of function realization
@@
 
-		The principal components are then defined analogously to before:
-		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
+		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are called \textbf{Functional Principal Components} and can serve as a basis for representing the original curves. 
+		\vspace{0.2cm}
+
+		The corresponding scores $\hat{\xi}_i$ can be derived as
+		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
 

### 2022-01-03 Presentation/slides.tex
Estimation

@@
 		\begin{itemize}
-			\item $y_i$: \quad a scalar realizations of $Y$
-			\item $f_i(t)$: \quad a realization of $F$
+			\item $y_i$: a scalar realization of $Y$
+			\item $f_i(t)$: a realization of $F$
 		\end{itemize}
@@
 
-	\begin{frame}
-		$$\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
-		This is a scalar we can calculate for each observation and for each deterministic basis function $b_j(t)$.
+	\begin{frame}{Estimation via Basis Representation}
+		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
+		This is a scalar random variable for which we can calculate a realization for each observation $f_i(t)$ and for each deterministic basis function $b_j(t)$.
+		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
+		Leading to the following transformation
+		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
+
+	\end{frame}
+
+	\begin{frame}{Estimation via Basis Representation}
+		This allows us to write each observation in the data set as
+		\begin{itemize}
+			\item $y_i$: a scalar realization of $Y$
+			\item $\left(Z_{i,j}\right)_{j \in \mathbb{N}}$: a countably infinite sequence of scalars
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Truncating the functional basis allows us to approximate the data set in the usual multivariate form.
+		\begin{itemize}
+			\item $y_i$: a scalar realization of $Y$
+			\item $\left(Z_{i,1} \: \dots \:  Z_{i,L} \right)'$: a vector of scalar regressors
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\beta}_L \in \mathbb{R}^L$.
+	\end{frame}
+
+	\begin{frame}{Estimation via Basis Representation}
+		This can then be translated into an estimated coefficient function $\hat{\beta}(t)$ via:
 	\end{frame}

### 2022-01-04 Presentation/slides.tex
Plot_generator for PCA

@@
 		\begin{itemize}
-			\item Random function represented as linear combination of basis functions
-			\item Just transform to multiple linear regression setting
-			\item You already know that from the beginning
+			\item Random function represented as linear combination of basis functions $\checkmark$
+			\item Just transform to multiple linear regression setting $\checkmark$
+			\item You already know that from the beginning $\checkmark$
 		\end{itemize}
@@
 		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
-		This is a scalar random variable for which we can calculate a realization for each observation $f_i(t)$ and for each deterministic basis function $b_j(t)$.
+		This is a scalar random variable leading to the following transformation
+		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
+		Each combination of observation $f_i(t)$ and deterministic basis function $b_j(t)$ effectively gives us a realization of this random variable.
 		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
-		Leading to the following transformation
-		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
 

### 2022-01-04 Code/Plot_Generators/Principal_Components_NIR.R

@@ -1,0 +1,147 @@
+##### This script generates a plot showing of a chosen number of principal components #
+# of the NIR-spectrum data from the gasoline data set and representations of the
+# original curves approximated by different numbers of these curves #####
+
+# Clear Workspace
+rm(list = ls())
+
+# load libraries
+library(fda)
+library(refund)
+library(tidyverse)
+
+# gasoline load data set
+data(gasoline)
+NIR <- as.matrix(gasoline$NIR)
+
+# set up parameters
+n_basis_fun <- 20
+n_order <- 4
+n_harm <- 5
+stepsize <- 0.1
+
+# generate fitting functional basis (b-spline basis)
+smallbasis <- create.bspline.basis(
+  rangeval = c(0, dim(NIR)[2]), nbasis = n_basis_fun,
+  norder = n_order
+)
+
+# evaluate basis at grid points
+basis_values <- eval.basis(
+  evalarg = seq(from = 0, to = dim(NIR)[2], by = stepsize),
+  basisobj = smallbasis
+)
+
+# translate observations in matrix into basis representation
+NIR_fd <- smooth.basis(y = t(NIR), fdParobj = smallbasis)$fd
+
+# get principal components
+NIR_pcaObj <- pca.fd(fdobj = NIR_fd, nharm = n_harm, centerfns = TRUE)
+
+# get coefficients for principal components
+NIR_pc_coefs <- NIR_pcaObj$harmonics$coefs
+
+# calculate values of principal components
+NIR_pc_values <- basis_values %*% NIR_pc_coefs
+
+# extract real wavelengths
+wavelengths <- unlist(
+  map(
+    .x = colnames(NIR),
+    .f = function(str) strtoi(strsplit(x = str, split = " nm"))
+  )
+)
+
+nm <- (seq(from = 0, to = dim(NIR)[2], by = stepsize) / dim(NIR)[2]) * (max(wavelengths) - min(wavelengths)) + min(wavelengths)
+
+### this is for plotting the principal components themselves ###
+# form into tibble
+NIR_pc_tibble <- cbind(
+  nm, as_tibble(NIR_pc_values, .name_repair = "unique")
+)
+names(NIR_pc_tibble) <- c("nm", paste0("PC_", 1:n_harm))
+
+# bring into format for plotting with ggplot
+NIR_plotting_tibble <- NIR_pc_tibble %>%
+  pivot_longer(cols = !nm, names_to = "PC", values_to = "Value")
+
+# generate plot
[…]

### 2022-01-04 Code/Plot_Generators/Principal_Components_NIR.R
Increment

@@ -119,7 +119,7 @@ approx_obs_tibble <- cbind(
   nm, as_tibble(NIR_approx[[1]], .name_repair = "unique")
 )
 
-names(approx_obs_tibble) <- c("nm", paste0("Num_pcs: ", 1:n_harm))
+names(approx_obs_tibble) <- c("nm", 1:n_harm)
 
 # bring into format for plotting with ggplot
 plotting_approx_obs_tibble <- approx_obs_tibble %>%

### 2022-01-04 Code/Plot_Generators/Principal_Components_NIR.R
Added mean function

@@ -87,18 +87,30 @@ ggsave(
 )
 
 ### from here on out it's about the approximated curves ###
+# get mean function as vector values
+mean_func <- colMeans(NIR)
+
+# represent mean function using basis from above
+mean_func_fd <- smooth.basis(y = mean_func, fdParobj = smallbasis)$fd
+
+# get mean function coefs
+mean_func_coefs <- mean_func_fd$coefs
+
+# get mean func at grid points
+mean_func_values <- basis_values %*% mean_func_coefs
+
 # extract scores - weights for the approximation
 NIR_pc_scores <- NIR_pcaObj$scores
 
 # define helper function to get matrix format as wanted for further processing
-approx_helper <- function(obs_index, score_mat, pc_value_mat) {
+approx_helper <- function(obs_index, score_mat, pc_value_mat, mean_function) {
   # get scores for current observation
   obs_scores <- score_mat[obs_index, ]
   # create matrix container for approximations
   approx_mat <- matrix(data = NA, nrow = dim(pc_value_mat)[1], ncol = dim(pc_value_mat)[2])
   # fill in approximations
   for (i in 1:dim(pc_value_mat)[2]) {
-    approx_mat[, i] <- colSums(obs_scores[1:i] %*% t(pc_value_mat[, 1:i]))
+    approx_mat[, i] <- colSums(obs_scores[1:i] %*% t(pc_value_mat[, 1:i])) + mean_function
   }
   # return matrix
   return(approx_mat)
@@ -109,7 +121,8 @@ NIR_approx <- map(
   .x = 1:dim(NIR)[1],
   .f = function(i) {
     approx_helper(
-      obs_index = i, score_mat = NIR_pc_scores, pc_value_mat = NIR_pc_values
+      obs_index = i, score_mat = NIR_pc_scores, pc_value_mat = NIR_pc_values, 
+      mean_function = mean_func_values
     )
   }
 )

### 2022-01-04 Code/Plot_Generators/True_coefficient_functions.R
Create True_coefficient_functions.R

@@ -1,0 +1,42 @@
+##### This script generates an iid data set from wiener processes and plots it
+
+# Load packages
+library(tidyverse)
+
+# setup for plot generation
+n_points <- 10000
+grid <- seq(from = 0, to = 1, length.out = n_points)
+realizations <- 25
+#smooth
+f1 <- 2*sin(0.5*pi*grid) + 4*sin(1.5*pi*grid) + 5*sin(2.5*pi*grid)
+#bumpy
+f2 <- 1.5*exp(-0.5*(grid-0.3)^2/0.02^2) -  4*exp(-0.5*(grid-0.45)^2/0.015^2) +  8*exp(-0.5*(grid-0.6)^2/0.02^2) -  exp(-0.5*(grid-0.8)^2/0.03^2)
+#two different variances of error
+
+data_mat <- matrix(data = f2,
+                   nrow = n_points, ncol = realizations, byrow = FALSE)
+
+data_tibble <- cbind(tibble(x = points), as_tibble(data_mat, .name_repair = 'unique'))
+names(data_tibble) <- c('t', paste0('Realization_', 1:realizations))
+
+plot_tibble <- data_tibble %>% 
+  pivot_longer(cols = !t, names_to = 'Realization', values_to = 'Value')
+
+# generate plot
+Wiener_plot <- ggplot(data = plot_tibble) +
+  geom_line(aes(x = t, y = Value, col = Realization)) +
+  #ggtitle("B-spline Basis") +
+  theme_light() +
+  #scale_colour_brewer(palette="Set1") + 
+  theme(legend.position = "none",
+        #plot.title = element_text(size = 30),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 20),
+        legend.title = element_text(size = 24),
+        legend.text = element_text(size = 20))
+
+Wiener_plot
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/Wiener_plot.pdf', plot = Wiener_plot,
+       width = 20, height = 8, units = "in", dpi = 600)

### 2022-01-04 Presentation/slides.tex
Added pca plots
Update slides.tex

--- 2022-01-03 Presentation/slides.tex
@@
 		Jona \\	
-		Introductory Example $\rightarrow$ Octane/NIR-spectrum
+		\begin{itemize}
+			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
+			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
+
+			\item Spectroscopy results in high-dimensional dataset.
+			\item
+			This set of measurements along a continuum can be viewed as set of smooth spectral curves
+			\item
+			Regression to determine relationship between octane rating and spectral curves
+			\end{itemize}
 	\end{frame}
@@
 	\begin{frame}{Theory}
-		Jona \\
+
 		Motivation from multivariate regression (multivariate dgp).
+
+		\begin{itemize}
+			\item
+			A simple functional dataset is given by $x_{n}(t_{j,n}) \in \mathbb{R}, t_{j,n} \in [T_1, T_2], n = 1,2,...,N, j = 1,2,..., J_n  $
+			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$
+			\item NIR-spectroscopy measurements, financial data, medical data, human perception (musical pitch, ...)
+
+			\item To abstract information from the curves, they must be interpretable!
+
+			\end{itemize}
 	\end{frame}
@@
 
-	\begin{frame}{Estimation via Basis Representation}
-		Assume the following data generating process
-		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
-		\begin{itemize}
-			\item $Y$ and $\epsilon$ realize in $\mathbb{R}$ and $F$ realizes in $\mathbb{L}^2[0,1]$
-		\end{itemize}
-		\vspace{0.2cm}
-
-		Assume that we have a data set containing observations each of which is made up of:
-		\begin{itemize}
-			\item $y_i$: \quad a scalar realizations of $Y$
-			\item $f_i(t)$: \quad a realization of $F$
-		\end{itemize}
-
-	\end{frame}
-
-	\begin{frame}{Estimation via Basis Representation}
-		Let $\{b_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$
-		\vspace{0.2cm}
-
-		Then we have the following representation of $\beta(t)$
-		$$\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t) = \sum_{j = 1}^{L} \psi_j b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j b_j(t)$$
-		and we can transform the data generating process into:
-		\begin{equation}\notag
-			\begin{split}
-				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-						  & = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	  
-			\end{split}
-		\end{equation}
-	\end{frame}
-
-	\begin{frame}
-		$$\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
-		This is a scalar we can calculate for each observation and for each deterministic basis function $b_j(t)$.
-	\end{frame}
-
 	\begin{frame}{Theory - FPCA}
@@
 		\begin{itemize}
-			\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
-			\item Introduce mean and covariance functions of random functions $\checkmark$
-			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
-			\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
+			\item Let's assume you know the theory of PCA (pc from varcov matrix)
+			\item Introduce mean and covariance functions of random functions
+			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion)
+			\item Sample Analog! (create a basis from observations and use for basis regression)
 			\item Plot fpcs and approximation of function realization
@@
 
-		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are called \textbf{Functional Principal Components} and can serve as a basis for representing the original curves. 
-		\vspace{0.2cm}
-
-		The corresponding scores $\hat{\xi}_i$ can be derived as
-		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
+		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are then called the functional principal components and the corresponding scores $\xi_i$ can be derived using the following equation.
+		$$\xi_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
 
@@
 	\begin{frame}{Simulation Setup \& Application}
-		Jona
 		\begin{itemize}
-			\item Compare b-spline / fourier regression chosen via criterion (cv/aic/...)
-			\item Similar for fpca
-			\item generate new curves from observed curves motivated by Karhunen-Loeve expansion
-			\item Compare optimal variants with test and training sets
-			\item Connect to Application
+		\item
+		 Use the gasoline dataset (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
+		\item 
+		Generate new curves from gasoline dataset, motivated by Karhunen-Loeve expansion:
+
+		$$F^{new}(\omega)(t) = \mu^{NIR}(t) + \sum_{j = 1}^{\infty} \xi_j^{new} \nu_j(t)^{new}$$ \\
+		where \\
+		 \vspace{0.1cm}
+		$$\xi_{j}^{new} \in  \mathcal{N}_{n}(0,\Sigma)$$ \\
+		and $\nu_j(t)^{new}$ be a $grid \times n_{FPC}$ matrix.
+
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+		Following Reiss and Ogden (2007), let $f_1$ and $f_2$ be two true coefficient functions that differ in smoothness: 
+		\vspace{0.4cm}
+
+   $f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
+   \vspace{0.1cm}
+
+    $	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}$
+
+		\end{itemize}
+		\vspace{0.1cm}
+		\begin{figure}
+\centering
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[height=3cm]{smooth_function.png}
+  \captionof{figure}{$f_1$, smooth function}
+  \label{fig:test1}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[height=3cm]{bumpy_function.png}
+  \captionof{figure}{$f_2$, bumpy function}
+  \label{fig:test2}
+\end{minipage}
+\end{figure}
+
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+    		Let \\
+    		 \vspace{0.1cm}
+
+    		$Y_{1,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
+    		  $Y_{2,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
+    		 	\item
+    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
+			\item Compare results via criteria (CV, Mallows CP,...)
+			\item 
+			{\color{green} add results here!}
+
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+    		Use insights from the simulation study to uncover dependence.
+    		\item
+    		Same setup, but without generated curves.
+    		\item
+    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
+    		\item
+    		Report results by MSE scaled by variance.
 		\end{itemize}

### 2022-01-04 Presentation/slides.tex

--- 2022-01-04 Presentation/slides.tex
@@
 
+	\begin{frame}{FPCA - Plots}
+		\begin{minipage}[t]{0.79\textwidth}
+			\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
+			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
+		\end{minipage}
+		\begin{minipage}[t]{0.19\textwidth}
+			Lorem Ipsum Dolor Sit Amet
+		\end{minipage}
+	\end{frame}
+
 	\begin{frame}{Simulation Setup \& Application}
-		Jona
 		\begin{itemize}
-			\item Compare b-spline / fourier regression chosen via criterion (cv/aic/...)
-			\item Similar for fpca
-			\item generate new curves from observed curves motivated by Karhunen-Loeve expansion
-			\item Compare optimal variants with test and training sets
-			\item Connect to Application
+		\item
+		 Use the gasoline dataset (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
+		\item 
+		Generate new curves from gasoline dataset, motivated by Karhunen-Loeve expansion:
+
+		$$F^{new}(\omega)(t) = \mu^{NIR}(t) + \sum_{j = 1}^{\infty} \xi_j^{new} \nu_j(t)^{new}$$ \\
+		where \\
+		 \vspace{0.1cm}
+		$$\xi_{j}^{new} \in  \mathcal{N}_{n}(0,\Sigma)$$ \\
+		and $\nu_j(t)^{new}$ be a $grid \times n_{FPC}$ matrix.
+
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+		Following Reiss and Ogden (2007), let $f_1$ and $f_2$ be two true coefficient functions that differ in smoothness: 
+		\vspace{0.4cm}
+
+   $f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
+   \vspace{0.1cm}
+
+    $	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}$
+
+		\end{itemize}
+		\vspace{0.1cm}
+		\begin{figure}
+\centering
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[height=3cm]{smooth_function.png}
+  \captionof{figure}{$f_1$, smooth function}
+  \label{fig:test1}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[height=3cm]{bumpy_function.png}
+  \captionof{figure}{$f_2$, bumpy function}
+  \label{fig:test2}
+\end{minipage}
+\end{figure}
+
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+    		Let \\
+    		 \vspace{0.1cm}
+
+    		$Y_{1,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
+    		  $Y_{2,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
+    		 	\item
+    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
+			\item Compare results via criteria (CV, Mallows CP,...)
+			\item 
+			{\color{green} add results here!}
+
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Setup \& Application cont.}
+		\begin{itemize}
+		\item
+    		Use insights from the simulation study to uncover dependence.
+    		\item
+    		Same setup, but without generated curves.
+    		\item
+    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
+    		\item
+    		Report results by MSE scaled by variance.
 		\end{itemize}

### 2022-01-05 Presentation/slides.tex
Update slides.tex

@@
 	\begin{frame}{Introduction}
-		Jona \\	
+
 		\begin{itemize}
@@
 
-		Motivation from multivariate regression (multivariate dgp).
-
 		\begin{itemize}
@@
 			A simple functional dataset is given by $x_{n}(t_{j,n}) \in \mathbb{R}, t_{j,n} \in [T_1, T_2], n = 1,2,...,N, j = 1,2,..., J_n  $
-			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$
-			\item NIR-spectroscopy measurements, financial data, medical data, human perception (musical pitch, ...)
+			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$, eg.: growth curves, financial data, human perception (music pitch,...).
 
@@
 
-    		$Y_{1,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
-    		  $Y_{2,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
+    		$Y_{1,f} = \mathbf{NIR \times f}  + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
+    		  $Y_{2,f} = \mathbf{NIR \times f} + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
     		 	\item
@@
     		\item
-    		Same setup, but without generated curves.
+    		Similar setup, but using only bsplie basis expansion and initial 60 spectral curves.
     		\item

### 2022-01-05 Code/simulation_study_v2.R
Update simulation_study_v2.R

@@ -3,9 +3,10 @@ suppressMessages(library(ggplot2))
 suppressMessages(library(dplyr))
 suppressMessages(library(reshape2)) 
 suppressMessages(library(fda))
-suppressMessages(library(fdaACF))
+#suppressMessages(library(fdaACF))
 suppressMessages(library(fpca))
-library(caret)
+suppressMessages(library(caret))
+
 
 source("C:/Users/Jonathan/Desktop/RM_Stats/Code/data_generator.R") 
 source("C:/Users/Jonathan/Desktop/RM_Stats/Code/auxiliary_functions.R") 
@@ -259,21 +260,20 @@ input_data = as.matrix(generated_curves[,-1])
 ###             Run function using the NIR data          ###
 ############################################################
 
+
+test_bspline_function = bspline_function(500, NIR, 60)
+write.table(test_bspline_function,file="Results/test_bspline_expansion_NIR.csv")
+test_bspline_function
+
 test_fourier_function = fourier_function(500, NIR, 60)
 write.table(test_fourier_function,file="Results/test_fourier_expansion_NIR.csv")
 test_fourier_function
 
-
-test_bspline_function = bspline_function(2, input_data, 100)
-write.table(test_bspline_function,file="Results/test_bspline_expansion_NIR.csv")
-test_bspline_function
-
-
-test_fpcr = fpcr_function(2, NIR, 60)
+test_fpcr = fpcr_function(500, NIR, 60)
 write.table(test_fpcr,file="Results/test_fpcr_bsplines_NIR.csv")
 test_fpcr
 
-test_fpcr2 = fpcr_fourier_function(2, NIR, 60)
+test_fpcr2 = fpcr_fourier_function(500, NIR, 60)
 write.table(test_fpcr2,file="Results/test_fpcr_fourier_NIR.csv")
 test_fpcr2
 

### 2022-01-06 Presentation/slides.tex
Update slides.tex
\hat{\beta} stuff...

@@
 			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
+			\item Spectroscopy results in high-dimensional dataset.
 
-			\item Spectroscopy results in high-dimensional dataset.
 			\item
 			This set of measurements along a continuum can be viewed as set of smooth spectral curves
+
 			\item
@@
 
-		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\beta}_L \in \mathbb{R}^L$.
+		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
 	\end{frame}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		This can then be translated into an estimated coefficient function $\hat{\beta}(t)$ via:
+		This can be translated into an estimated coefficient function $\hat{\beta}(t)$:
+
+		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{\psi}_{L,j} b_j(t)$$
+		\vspace{0.2cm}
+
+		This is dependent on...
+		\begin{itemize}
+			\item The functional basis $(b_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
+			\item The truncation parameter $L$
+			\item (The functional basis used to approximate the observations)
+			\item (The truncation parameter in the approximation of the observations)
+		\end{itemize}
 	\end{frame}

### 2022-01-06 Presentation/slides.tex
Removed Jakob ToDo Slides

@@
 
-	\begin{frame}{Theory}
-		Jakob
-		\begin{itemize}
-			\item Random function represented as linear combination of basis functions $\checkmark$
-			\item Just transform to multiple linear regression setting $\checkmark$
-			\item You already know that from the beginning $\checkmark$
-		\end{itemize}
-	\end{frame}
+	%\begin{frame}{Theory}
+	%	Jakob
+	%	\begin{itemize}
+	%		\item Random function represented as linear combination of basis functions $\checkmark$
+	%		\item Just transform to multiple linear regression setting $\checkmark$
+	%		\item You already know that from the beginning $\checkmark$
+	%	\end{itemize}
+	%\end{frame}
 
@@
 
-	\begin{frame}{Theory - FPCA}
-		Jakob
-		\begin{itemize}
-			\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
-			\item Introduce mean and covariance functions of random functions $\checkmark$
-			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
-			\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
-			\item Plot fpcs and approximation of function realization
-		\end{itemize}
-	\end{frame}
+	%\begin{frame}{Theory - FPCA}
+	%	Jakob
+	%	\begin{itemize}
+	%		\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
+	%		\item Introduce mean and covariance functions of random functions $\checkmark$
+	%		\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
+	%		\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
+	%		\item Plot fpcs and approximation of function realization
+	%	\end{itemize}
+	%\end{frame}
 

### 2022-01-06 Presentation/slides.tex
Notation

@@
 			\item Spectroscopy results in high-dimensional dataset.	
-
-			\item
-			This set of measurements along a continuum can be viewed as set of smooth spectral curves
-
-			\item
-			Regression to determine relationship between octane rating and spectral curves
+			\item This set of measurements along a continuum can be viewed as set of smooth spectral curves
+			\item Regression to determine relationship between octane rating and spectral curves
 			\end{itemize}
@@
 	\begin{frame}{Theory}
+		A simple functional dataset is given by 
+		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \:  t_{j,n} \in [T_1, T_2], \; i = 1,2,...,N, \; j = 1,2,..., J_i  \}$$
 
 		\begin{itemize}
-			\item
-			A simple functional dataset is given by $x_{n}(t_{j,n}) \in \mathbb{R}, t_{j,n} \in [T_1, T_2], n = 1,2,...,N, j = 1,2,..., J_n  $
-			\item Continuous underlying process, where $x_n(t)$ exists at any point $t$, but is only observed at $x_{n}(t_{j,n})$, eg.: growth curves, financial data, human perception (music pitch,...).
-
+			\item Continuous underlying process, where $x_n(t)$ exists $\forall t \in [T_1, T_2]$
+			\item Only observed at $x_{n}(t_{j,n})$
+			\item Growth curves, financial data, human perception (pitch), ...
 			\item To abstract information from the curves, they must be interpretable!
-
 			\end{itemize}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Assume the following data generating process
+		Assume the following \textbf{data generating process}
 		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
 		\begin{itemize}
-			\item $Y$ and $\epsilon$ realize in $\mathbb{R}$ and $F$ realizes in $\mathbb{L}^2[0,1]$
+			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $F(\omega)$ realizes in $\mathbb{L}^2[0,1]$
 		\end{itemize}
@@
 		\begin{itemize}
-			\item $y_i$: a scalar realization of $Y$
-			\item $f_i(t)$: a realization of $F$
+			\item $y_i$: a scalar realization of $Y(\omega)$
+			\item $f_i(t)$: a realization of $F(\omega)$
 		\end{itemize}
@@
 		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
-		This is a scalar random variable leading to the following transformation
+		This is a \textbf{scalar random variable} leading to the following transformation
 		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
@@
 
-		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
+		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
 	\end{frame}
@@
 	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
-		A random function $F$ can be expressed in terms of its mean function and its Eigenfunctions:
+		A random function $F(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
 		$$F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$
@@
 	\begin{frame}{FPCA - Plots}
-		\begin{minipage}[t]{0.79\textwidth}
+		\begin{minipage}[c]{0.78\textwidth}
 			\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
@@
 		\end{minipage}
-		\begin{minipage}[t]{0.19\textwidth}
-			Lorem Ipsum Dolor Sit Amet
+		\begin{minipage}[c]{0.19\textwidth}
+			The math is for intuition. In practice there are problems and the fpc's are derived differently.
 		\end{minipage}
@@
 		\begin{itemize}
-		\item
-		 Use the gasoline dataset (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
-		\item 
-		Generate new curves from gasoline dataset, motivated by Karhunen-Loeve expansion:
+			\item Use the \textbf{gasoline dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
+			\item Generate \textbf{similar curves} from gasoline dataset:
+		\end{itemize}
 
-		$$F^{new}(\omega)(t) = \mu^{NIR}(t) + \sum_{j = 1}^{\infty} \xi_j^{new} \nu_j(t)^{new}$$ \\
-		where \\
-		 \vspace{0.1cm}
-		$$\xi_{j}^{new} \in  \mathcal{N}_{n}(0,\Sigma)$$ \\
-		and $\nu_j(t)^{new}$ be a $grid \times n_{FPC}$ matrix.
+		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{\infty} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
 
+		\begin{itemize}
+			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ (simplification - the $\xi_{j}$ do not follow a normal)
+			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
 		\end{itemize}
+
 	\end{frame}
@@
 	\begin{frame}{Simulation Setup \& Application cont.}
-		\begin{itemize}
-		\item
-		Following Reiss and Ogden (2007), let $f_1$ and $f_2$ be two true coefficient functions that differ in smoothness: 
-		\vspace{0.4cm}
+		%\begin{itemize}
+		%\item
+		Following \textbf{Reiss and Ogden (2007)}, let $f_1(t)$ and $f_2(t)$ be two coefficient functions: 
+		%\vspace{0.2cm}
 
-   $f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
-   \vspace{0.1cm}
+   		%$f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
+   		%\vspace{0.1cm}
 
-    $	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}$
+        %$f_2(t) = 1.5 \exp(\frac{-0.5(t-0.3)^2}{0.02^2}) - 4 \exp(\frac{-0.5(t-0.45)^2}{0.015^2}) +  8 \exp(\frac{-0.5(t-0.6)^2}{0.02^2}) - \exp(\frac{-0.5(t-0.8)^2}{0.03^2})$
 
-		\end{itemize}
+		%\end{itemize}
 		\vspace{0.1cm}
@@
 				\centering
-  \includegraphics[height=3cm]{smooth_function.png}
-  \captionof{figure}{$f_1$, smooth function}
+  				\includegraphics[width=\textwidth]{smooth_function.png}
+  				\caption{$f_1(t)$, smooth function}
   				\label{fig:test1}
@@
 	  			\centering
-  \includegraphics[height=3cm]{bumpy_function.png}
-  \captionof{figure}{$f_2$, bumpy function}
+  				\includegraphics[width=\textwidth]{bumpy_function.png}
+  				\caption{$f_2(t)$, bumpy function}
   				\label{fig:test2}
@@
 	\begin{frame}{Simulation Setup \& Application cont.}
+		Let 
+		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
+		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$
+
+		where $Z \sim \mathcal{N}(0,1)$ be two responses for $f \in \{f_1(t), f_2(t)\}$.	
 		\begin{itemize}
-		\item
-    		Let \\
-    		 \vspace{0.1cm}
-
-    		$Y_{1,f} = \mathbf{NIR \times f}  + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
-    		  $Y_{2,f} = \mathbf{NIR \times f} + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
-    		 	\item
-    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
+    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
 			\item Compare results via criteria (CV, Mallows CP,...)
-			\item 
-			{\color{green} add results here!}
-
+			\item {\color{green} add results here!}
 		\end{itemize}

### 2022-01-06 Presentation/slides.tex
Increment

@@
 		A simple functional dataset is given by 
-		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \:  t_{j,n} \in [T_1, T_2], \; i = 1,2,...,N, \; j = 1,2,..., J_i  \}$$
+		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \: i = 1,2,...,N, \; j = 1,2,..., J_i, \; t_{j,i} \in [T_1, T_2] \}$$
 

### 2022-01-06 Presentation/slides.tex
Increment
Presentation

@@
 \parindent=0pt
+
+ \newcommand{\independent}{\perp\!\!\!\!\perp}
 
@@
 		\begin{itemize}
-			\item Continuous underlying process, where $x_n(t)$ exists $\forall t \in [T_1, T_2]$
-			\item Only observed at $x_{n}(t_{j,n})$
+			\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
+			\item Only observed at $x_{i}(t_{j,i})$
 			\item Growth curves, financial data, human perception (pitch), ...
@@
 		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Random Function}
+		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}$
+		\begin{itemize}
+			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
+			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
+			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Random Function}
+		Let $E$ be the index set and this can be described as
+		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
+		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$\\
+		\begin{itemize}
+			\item It can be shortened to $X(t)$ by omitting $\omega$
+			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Square Integrable Function}
+		If a function $f$ satisfies:
+		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
+		the function $f$ is called square integrable function
+		\begin{itemize}
+			\item Without loss of generality, the interval is defined in $[0,1] $
+			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
+			\item We focus on $\mathbb{L}^{2} [0,1]$ since the dimension of the domain of our function is 1
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Stochastic Process Perspective}
+		Functional data are the sample curves observed from continuous time stochastic precess\\
+		\begin{itemize}
+			\item From this perspective, $X(t)$ is a random variable (?)\\
+			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
+			\item Realizations of a random function belong in large collection of functions
+		\end{itemize}		
+	\end{frame}
+
+	\begin{frame}{Plots}
+		Two plots of stock and human growth
+	\end{frame}
+
+	\begin{frame}{Plots}
+		point plots to link basis expansion
+	\end{frame}
+	\begin{frame}{Basis Expansion}
+		Basis expansion is a linear combination of functions defining a function as described:
+		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
+		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient
+		\begin{itemize}
+			\item To make the function smoother
+			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
+		\end{itemize}		
+	\end{frame}
+
+	\begin{frame}{Two Typical Types of Basis Function}
+		Fourier basis function is written as
+		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
+		\vspace{2\baselineskip}
+		B-spline basis function is a flexible curve defined by degree and knots \\
+		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula(Do you think I need to put the formula?)
+	\end{frame}
+
+	\begin{frame}{Plots of Basis Functions }
+		\begin{minipage}[t]{\textwidth}
+			\includegraphics[height = 3.5cm]{../Graphics/Bspline_Basis.pdf}
+			\includegraphics[height = 3.5cm]{../Graphics/Fourier_Basis.pdf}
+		\end{minipage}
+	\end{frame}
+
+	\begin{frame}{Trade Off between Bias and Variance}
+		How do we choose the number $K$ of basis functions?
+		\begin{itemize}
+			\item The larger $K$, the better fit to the data with also fitting noise
+			\item If $K$ is too small, it would miss some significant information that we want to estimate 
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Trade Off between Bias and Variance}
+		\begin{itemize}
+			\item $\textbf{Bias}[\hat{x}(t)] = x(t) - E[\hat{x}(t)]$
+			\item $\textbf{Var}[\hat{x}(t)] = E[\{\hat{x}(t) - E[x(t)]\}^2]$
+			\item $\textbf{MSE}[\hat{x}(t)] = E[\{\hat{x}(t) - x(t)\}]$
+			\item $\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$
+		\end{itemize}
+		In the sense of that, we need to concentrate on decreasing \textbf{MSE}.
+	\end{frame}
+
+	\begin{frame}{Trade Off between Bias and Variance}
+		\begin{minipage}[t]{\textwidth}
+			\includegraphics[height = 7cm]{../Graphics/Trade_off.png}
+		\end{minipage}
 	\end{frame}
@@
 		\begin{itemize}
-			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ (simplification - the $\xi_{j}$ do not follow a normal)
+			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
+			\item Simplification: the $\xi_{j}$ do not follow a normal
 			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.

### 2022-01-07 Presentation/slides.tex
Adding

@@
 	\begin{frame}{Random Function}
-		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}$
+		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
 		\begin{itemize}
@@
 		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
-		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$\\
+		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
 		\begin{itemize}
@@
 
+	\begin{frame}{Square Integrable Function}
+		If $f, g \in \mathbb{L}^{2}$,
+		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
+		, where $a$ and $b$ are scalars. (Maybe don't need)\\
+		We can additionally define the inner product as follows:
+		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
+		\begin{itemize}
+			\item Orthogonolality of two different functions
+			\item Distance between functions
+		\end{itemize}
+	\end{frame}
+
 	\begin{frame}{Stochastic Process Perspective}
-		Functional data are the sample curves observed from continuous time stochastic precess\\
+		Functional data are the sample curves observed from continuous time stochastic precess.\\
 		\begin{itemize}
@@
 		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
-		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient
+		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
 		\begin{itemize}
@@
 		\vspace{2\baselineskip}
-		B-spline basis function is a flexible curve defined by degree and knots \\
-		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula(Do you think I need to put the formula?)
+		B-spline basis function is a flexible curve defined by degree and knots. \\
+		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
 	\end{frame}

### 2022-01-07 Presentation/slides.tex
To add images

@@
 	\begin{frame}{Plots}
-		Two plots of stock and human growth
+		\begin{figure}
+			\centering
+			\begin{minipage}{.5\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
+				\caption{\tiny Growth curves of 54 girls age 1-18}
+			\end{minipage}%
+			\begin{minipage}{.5\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../Graphics/NIR.png}
+				\caption {\tiny NIR spectrum of 60 gasoline samples}
+			\end{minipage}
+		\end{figure}
 	\end{frame}
@@
 
-	\begin{frame}{Plots of Basis Functions }
-		\begin{minipage}[t]{\textwidth}
-			\includegraphics[height = 3.5cm]{../Graphics/Bspline_Basis.pdf}
-			\includegraphics[height = 3.5cm]{../Graphics/Fourier_Basis.pdf}
-		\end{minipage}
+	\begin{frame}{Plots of Basis Functions}
+		\begin{figure}
+			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
+			\caption {Fourier basis functions with order 9}
+		\end{figure}
+
+	\end{frame}
+
+	\begin{frame}{Plots of Basis Functions}
+		\begin{figure}
+			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
+			\caption {Bspline Basis with order 9}
+		\end{figure}
 	\end{frame}
@@
 		\begin{minipage}[t]{\textwidth}
-			\includegraphics[height = 7cm]{../Graphics/Trade_off.png}
+			\includegraphics[height = 7cm]{../Graphics/Tradeoff.png}
 		\end{minipage}

### 2022-01-07 Presentation/slides.tex
Correction
Update

@@
 		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
-		the function $f$ is called square integrable function
+		the function $f$ is called square integrable function\\
+		and in the set $\mathbb{L}^{2}[0,1]$.
 		\begin{itemize}
@@
 			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
-			\item We focus on $\mathbb{L}^{2} [0,1]$ since the dimension of the domain of our function is 1
+			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
 		\end{itemize}
@@
 	\begin{frame}{Square Integrable Function}
-		If $f, g \in \mathbb{L}^{2}$,
+		If $f, g \in \mathbb{L}^{2}[0,1]$,
 		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
@@
 
-	\begin{frame}{Plots}
-		point plots to link basis expansion
+	\begin{frame}{Data Generating Process}
+		With $X_{i}(t_{ij}) \in \mathbb{L}^{2}[0,1]$, the measurement of $X_{ij}$ is assumed to have noise with $\mathbb{E}(\epsilon)_{ij}=0$ and $\textbf{Var}(\epsilon_{ij}^{2})$, which are independent across $i$ and $j$.\\
+		When the functional data has the same grid of domain, (SKIP)	
 	\end{frame}
+
 	\begin{frame}{Basis Expansion}

### 2022-01-07 Presentation/slides.tex
increment

--- 2022-01-07 Presentation/slides.tex
@@
 		\begin{itemize}
-			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
+			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum (2,500–750 nm)
 			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Assume the following \textbf{data generating process}
+		Assume the following \textbf{Data Generating Process}
 		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
@@
 		\begin{itemize}
-			\item Use the \textbf{gasoline dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
+			\item Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
 			\item Generate \textbf{similar curves} from gasoline dataset:

### 2022-01-07 main.tex
increment

@@
 	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
-Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.
+Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.
+
+	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
+Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega') = f(t)$ of $F(\omega)$.
+
+	\begin{equation}
+		F(\omega') = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega') b_j(t)
+	\end{equation}
 
@@
 	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process.
-To motivate it, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$.
+To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
+
+	\begin{equation}
+		\text{{\color{red} Introduce spectral representation of random vector here.}}
+	\end{equation}
+
+	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$.
 Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
@@
 
-	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ of the following equation.
+	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ of the following equation.
 
@@
 
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ as the solutions of the following equation.
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathbb{N}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ as the solutions of the following equation.
 {\color{red} I think the number of principal components has to be smaller then the number of observations.
-So I can give more information about $\mathcal{I}$.}
+So I can give more information about $\mathbb{N}$.}
 
@@
 	\begin{equation}
-		y = \alpha + \Psi(f) + \epsilon
+		Y(\omega) = \alpha + \Psi\left(F(\omega)\right) + \epsilon(\omega)
 	\end{equation}
@@
 
-	\begin{equation}
-		y = \alpha + \int_{0}^{1} \beta(s)f(s) \mathrm{d}s + \epsilon
+	\begin{equation}\label{DGP}
+		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)F(\omega)(s) \mathrm{d}s + \epsilon(\omega)
 	\end{equation}
 
-	Where $f(s)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(s)$ is an unknown coefficient function. 
-	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(s)$ given a data set containing realizations of a random function and associated scalar response variables.
+	Where $f(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
+	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
 However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible.
@@
 	\subsection{Estimation via Basis-Representation}
-	The most common way to make this problem tractable is via a basis representation of the originally observed function.
+	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
+Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
+
+	\begin{equation}
+		\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t)
+	\end{equation}
+
+	This enables us to write equation \ref{DGP} with $\beta(t)$ represented in this way to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
+			& = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{\langle F(\omega), b_j \rangle} + \epsilon(\omega) 
+			  = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
+		\end{split}
+	\end{equation}
 

### 2022-01-07 Presentation/slides.tex
presentation

@@
 			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
-			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
+			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
 		\end{itemize}
@@
 	\begin{frame}{Random Function}
-		Let $E$ be the index set and this can be described as
-		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
+		Let $\mathbb{E}$ be the index set and this can be described as
+		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
 		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
@@
 			\item It can be shortened to $X(t)$ by omitting $\omega$
-			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
+			\item The function is realized when the $X(t)$ have been observed for every $t \in \mathbb{E}$
 		\end{itemize}
@@
 		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
-		the function $f$ is called square integrable function\\
+		the function $f$ is called \textbf{Square Integrable Function}\\
 		and in the set $\mathbb{L}^{2}[0,1]$.
@@
 
-	\begin{frame}{Data Generating Process}
-		With $X_{i}(t_{ij}) \in \mathbb{L}^{2}[0,1]$, the measurement of $X_{ij}$ is assumed to have noise with $\mathbb{E}(\epsilon)_{ij}=0$ and $\textbf{Var}(\epsilon_{ij}^{2})$, which are independent across $i$ and $j$.\\
-		When the functional data has the same grid of domain, (SKIP)	
-	\end{frame}
-
 	\begin{frame}{Basis Expansion}
-		Basis expansion is a linear combination of functions defining a function as described:
+		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
 		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
@@
 	\begin{frame}{Two Typical Types of Basis Function}
-		Fourier basis function is written as
+		\textbf{Fourier Basis Function} is written as
 		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
 		\vspace{2\baselineskip}
-		B-spline basis function is a flexible curve defined by degree and knots. \\
+		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
 		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
@@
 			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
-			\caption {Bspline Basis with order 9}
+			\caption {Bspline basis functions with order 9}
 		\end{figure}

### 2022-01-07 Presentation/slides.tex
Slides Meeting

@@
 % Title page details: 
-\title{Scalar on Function Regression}
+\title{Scalar on Function Regression \\
+with Applications to Near-Infrared Spectography}
 \author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
@@
 		\begin{itemize}
-			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum (2,500–750 nm)
-			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
+			\item \textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum (from 780 nm to 2500 nm)
+			\item Suited for field-monitoring / on-line analysis
 			\item Spectroscopy results in high-dimensional dataset.	
-			\item This set of measurements along a continuum can be viewed as set of smooth spectral curves
+			\item This set of measurements serves as set of discretized approximations of smooth spectral curves
 			\item Regression to determine relationship between octane rating and spectral curves
@@
 
-	\begin{frame}{Theory}
-		Jonghun
-		\begin{itemize}
-			\item Random Functions (name square integrable functions)
-			\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
-			\item Use curves to predict a scalar response (show typical dgp)
-		\end{itemize}
-	\end{frame}
+	%\begin{frame}{Theory}
+	%	Jonghun
+	%	\begin{itemize}
+	%		\item Random Functions (name square integrable functions)
+	%		\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
+	%		\item Use curves to predict a scalar response (show typical dgp)
+	%	\end{itemize}
+	%\end{frame}
 
-	\begin{frame}{Theory}
-		Jonghun
-		\begin{itemize}
-			\item Basis expansions (b-splines and fourier)
-			\item Talk about purposes
-			\item Plots and show bias variance tradeoff
-		\end{itemize}
-	\end{frame}
+	%\begin{frame}{Theory}
+	%	Jonghun
+	%	\begin{itemize}
+	%		\item Basis expansions (b-splines and fourier)
+	%		\item Talk about purposes
+	%		\item Plots and show bias variance tradeoff
+	%	\end{itemize}
+	%\end{frame}
 
 	\begin{frame}{Random Function}
-		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
+		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
 		\begin{itemize}
-			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
-			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
+			\item If $\mathcal{S} = \mathbb{R}$ then $X$ is a random variable
+			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random vector
 			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
@@
 			\item It can be shortened to $X(t)$ by omitting $\omega$
-			\item The function is realized when the $X(t)$ have been observed for every $t \in \mathbb{E}$
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Square Integrable Function}
-		If a function $f$ satisfies:
-		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
-		the function $f$ is called \textbf{Square Integrable Function}\\
-		and in the set $\mathbb{L}^{2}[0,1]$.
-		\begin{itemize}
-			\item Without loss of generality, the interval is defined in $[0,1] $
-			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
-			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Square Integrable Function}
-		If $f, g \in \mathbb{L}^{2}[0,1]$,
-		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
-		, where $a$ and $b$ are scalars. (Maybe don't need)\\
-		We can additionally define the inner product as follows:
-		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
-		\begin{itemize}
-			\item Orthogonolality of two different functions
-			\item Distance between functions
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Stochastic Process Perspective}
-		Functional data are the sample curves observed from continuous time stochastic precess.\\
-		\begin{itemize}
-			\item From this perspective, $X(t)$ is a random variable (?)\\
-			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
-			\item Realizations of a random function belong in large collection of functions
+			\item The function is realized when the $X(t)$ exists $\forall t \in \mathbb{E}$
 		\end{itemize}
@@
 
+	\begin{frame}{Square Integrable Function}
+		If a function $f(t)$ satisfies:
+		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
+		the function $f$ is called \textbf{Square Integrable Function}\\
+		and in the set $\mathbb{L}^{2}[0,1]$.
+		\begin{itemize}
+			\item Without loss of generality, the interval is defined in $[0,1] $
+			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
+			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Square Integrable Function}
+		Let $f, g \in \mathbb{L}^{2}[0,1]$, then
+		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
+		%, where $a$ and $b$ are scalars. (Maybe don't need)\\
+		%We can additionally define the inner product as follows:
+		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
+		%\begin{itemize}
+		%	\item 
+		Orthogonality of two different functions $\langle f,g \rangle = 0$
+			%\item Distance between functions
+		%\end{itemize}
+	\end{frame}
+
+	%\begin{frame}{Stochastic Process Perspective}
+	%	Functional data are the sample curves observed from continuous time stochastic precess.\\
+	%	\begin{itemize}
+	%		\item From this perspective, $X(t)$ is a random variable (?)\\
+	%		\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
+	%		\item Realizations of a random function belong in large collection of functions
+	%	\end{itemize}		
+	%\end{frame}
+
 	\begin{frame}{Basis Expansion}
 		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
-		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
-		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
+		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$
+		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
+		\vspace{0.2cm}
+
 		\begin{itemize}
-			\item To make the function smoother
-			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
+			\item make the function smoother
+			\item replace the original curves $X_{i}(t)$ by a smaller collection of $c_{nm}$
+			%\item replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
 		\end{itemize}		
@@
 		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
-		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
+		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.
 	\end{frame}
@@
 		How do we choose the number $K$ of basis functions?
+		$$\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$$
+
+		{\color{red} Integrated Mean Squared Error}
 		\begin{itemize}
@@
 		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Trade Off between Bias and Variance}
-		\begin{itemize}
-			\item $\textbf{Bias}[\hat{x}(t)] = x(t) - E[\hat{x}(t)]$
-			\item $\textbf{Var}[\hat{x}(t)] = E[\{\hat{x}(t) - E[x(t)]\}^2]$
-			\item $\textbf{MSE}[\hat{x}(t)] = E[\{\hat{x}(t) - x(t)\}]$
-			\item $\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$
-		\end{itemize}
-		In the sense of that, we need to concentrate on decreasing \textbf{MSE}.
 	\end{frame}
@@
 		Assume the following \textbf{Data Generating Process}
-		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
+		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) X(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
+		\vspace{-0.6cm}
 		\begin{itemize}
-			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $F(\omega)$ realizes in $\mathbb{L}^2[0,1]$
+			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $X(\omega)$ realizes in $\mathbb{L}^2[0,1]$
 		\end{itemize}
-		\vspace{0.2cm}
+		\vspace{0.3cm}
 
-		Assume that we have a data set containing observations each of which is made up of:
-		\begin{itemize}
-			\item $y_i$: a scalar realization of $Y(\omega)$
-			\item $f_i(t)$: a realization of $F(\omega)$
-		\end{itemize}
+		Let $\{\phi_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$ leading to the following representation of $\beta(t)$
+
+		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j b_j(t)$$
+		%Assume that we have a data set containing observations each of which is made up of:
+		%\begin{itemize}
+		%	\item $y_i$: a scalar realization of $Y(\omega)$ - the octane rating of gasoline
+		%	\item $x_i(t)$: a realization of $X(\omega)$ - the measured NIR spectrum
+		%\end{itemize}
 
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Let $\{b_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$
-		\vspace{0.2cm}
-
-		Then we have the following representation of $\beta(t)$
-		$$\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t) = \sum_{j = 1}^{L} \psi_j b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j b_j(t)$$
-		and we can transform the data generating process into:
+		We can transform the data generating process into:
 		\begin{equation}\notag
 			\begin{split}
-				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-						  & = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	  
+				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
+						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  
 			\end{split}
 		\end{equation}
+
+		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
 	\end{frame}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
-		This is a \textbf{scalar random variable} leading to the following transformation
-		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
-		Each combination of observation $f_i(t)$ and deterministic basis function $b_j(t)$ effectively gives us a realization of this random variable.
-		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
+		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
+		$$Z_{i,j} = \int_{0}^{1} x_i(s) b_j(s)\mathrm{d}s$$
 
-	\end{frame}
+		\begin{itemize}
+			\item This allows us to write each observation in the data set as $\{y_i, Z_{i,1}, Z_{i,2}, \dots\}$
+			\item Truncating the functional basis yields an approximation $\{y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\}$
+		\end{itemize}
 
-	\begin{frame}{Estimation via Basis Representation}
-		This allows us to write each observation in the data set as
-		\begin{itemize}
-			\item $y_i$: a scalar realization of $Y$
-			\item $\left(Z_{i,j}\right)_{j \in \mathbb{N}}$: a countably infinite sequence of scalars
-		\end{itemize}
-		\vspace{0.2cm}
-
-		Truncating the functional basis allows us to approximate the data set in the usual multivariate form.
-		\begin{itemize}
-			\item $y_i$: a scalar realization of $Y$
-			\item $\left(Z_{i,1} \: \dots \:  Z_{i,L} \right)'$: a vector of scalar regressors
-		\end{itemize}
-		\vspace{0.2cm}
-
-		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
+		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$.
 	\end{frame}
@@
 
-		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{\psi}_{L,j} b_j(t)$$
-		\vspace{0.2cm}
+		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$
 
@@
 		\begin{itemize}
-			\item The functional basis $(b_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
+			\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
 			\item The truncation parameter $L$
-			\item (The functional basis used to approximate the observations)
-			\item (The truncation parameter in the approximation of the observations)
+			\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the expansion of the observations
+			\item The truncation parameter in the approximation of the observations $K$
 		\end{itemize}
@@
 
-	\begin{frame}{Spectral Representation of Random Vectors}
-		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
+	%\begin{frame}{Spectral Representation of Random Vectors}
+	%	Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
 
-		\begin{itemize}
-			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
-			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
-			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
-		\end{itemize}
+	%	\begin{itemize}
+	%		\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
+	%		\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
+	%		\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
+	%	\end{itemize}
 
-		\vspace{0.2cm}
-		Then $X$ can also be represented as
-		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
-		where the $\xi_i(\omega)$ have the following properties
+	%	\vspace{0.2cm}
+	%	Then $X$ can also be represented as
+	%	$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
+	%	where the $\xi_i(\omega)$ have the following properties
 
-		\begin{multicols}{2}
-			\begin{enumerate}
-				\item $\mathbb{E}[\xi_i(\omega)] = 0$
-				\item $Var(\xi_i(\omega)) = \lambda_i$
-				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
-			\end{enumerate}
-		\end{multicols}
-	\end{frame}
+	%	\begin{multicols}{2}
+	%		\begin{enumerate}
+	%			\item $\mathbb{E}[\xi_i(\omega)] = 0$
+	%			\item $Var(\xi_i(\omega)) = \lambda_i$
+	%			\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
+	%		\end{enumerate}
+	%	\end{multicols}
+	%\end{frame}
 
@@
 
-		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]$$
+		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]$$
 
-		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]$$
+		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]$$
 
@@
 	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
-		A random function $F(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
-		$$F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$
+		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
+		$$X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$
 
@@
 
-		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
+		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis.
 	\end{frame}
 
-	\begin{frame}{Principal Component Analysis}
-		A related concept is \textbf{Principal Component Analysis} (PCA).
-		\vspace{0.2cm}
+	%\begin{frame}{Principal Component Analysis}
+	%	A related concept is \textbf{Principal Component Analysis} (PCA).
+	%	\vspace{0.2cm}
+	%	
+	%	$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
+	%
+	%	\begin{itemize}
+	%		\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
+	%		\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
+	%		\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
+	%		\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
+	%	\end{itemize}
+	%	\vspace{0.2cm}
 
-		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
-
-		\begin{itemize}
-			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
-			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
-			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
-			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
-		\end{itemize}
-		\vspace{0.2cm}
-
-		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
-		\begin{multicols}{2}
-			\begin{enumerate}
-				\item $\mathbb{E}[Z_i(\omega)] = 0$
-				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
-				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
-			\end{enumerate}
-		\end{multicols}
-	\end{frame}
+	%	Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
+	%	\begin{multicols}{2}
+	%		\begin{enumerate}
+	%			\item $\mathbb{E}[Z_i(\omega)] = 0$
+	%			\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
+	%			\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
+	%		\end{enumerate}
+	%	\end{multicols}
+	%\end{frame}
 
 	\begin{frame}{Functional Principal Component Analysis}
-		This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
+		{\color{red} Rephrase this!} This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
 		\vspace{0.2cm}
@@
 
-		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{\infty} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
+		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
 
@@
 		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
-		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$
+		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$
 

### 2022-01-07 Presentation/slides.tex
Increment

@@
 \usepackage[font=small,skip=2pt]{caption}
+\captionsetup[figure]{labelformat=empty}
 \usepackage[
@@
 	\begin{frame}{Plots}
+		\begin{minipage}{.5\textwidth}
 			\begin{figure}
-			\centering
-			\begin{minipage}{.5\textwidth}
-				\centering
 				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
-				\caption{\tiny Growth curves of 54 girls age 1-18}
+				\caption{Growth curves of \\ 54 girls age 1-18}
+			\end{figure}
 		\end{minipage}%
 		\begin{minipage}{.5\textwidth}
-				\centering
+			\begin{figure}
 				\includegraphics[width=\textwidth]{../Graphics/NIR.png}
-				\caption {\tiny NIR spectrum of 60 gasoline samples}
+				\caption{NIR spectrum of 60 \\ gasoline samples}
+			\end{figure}
 		\end{minipage}
-		\end{figure}
 	\end{frame}
@@
 	\begin{frame}{Square Integrable Function}
-		If a function $f(t)$ satisfies:
-		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
-		the function $f$ is called \textbf{Square Integrable Function}\\
-		and in the set $\mathbb{L}^{2}[0,1]$.
+		If a function $f(t)$ satisfies
+		$$\int_{0}^{1} \left(f(t)\right)^{2}dt < \infty$$
+		the function $f(t)$ is called \textbf{Square Integrable Function} written $f(t) \in \mathbb{L}^{2}[0,1]$.
 		\begin{itemize}
@@
 
-	%\begin{frame}{Theory}
-	%	Jakob
-	%	\begin{itemize}
-	%		\item Random function represented as linear combination of basis functions $\checkmark$
-	%		\item Just transform to multiple linear regression setting $\checkmark$
-	%		\item You already know that from the beginning $\checkmark$
-	%	\end{itemize}
-	%\end{frame}
-
 	\begin{frame}{Estimation via Basis Representation}
@@
 		\begin{itemize}
-			\item This allows us to write each observation in the data set as $\{y_i, Z_{i,1}, Z_{i,2}, \dots\}$
-			\item Truncating the functional basis yields an approximation $\{y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\}$
+			\item This allows us to write each observation in the data set as $\left(y_i, Z_{i,1}, Z_{i,2}, \dots \right)$
+			\item Truncating the functional basis yields an approximation $\left(y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\right)$
 		\end{itemize}
@@
 	\end{frame}
-
-	%\begin{frame}{Theory - FPCA}
-	%	Jakob
-	%	\begin{itemize}
-	%		\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
-	%		\item Introduce mean and covariance functions of random functions $\checkmark$
-	%		\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
-	%		\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
-	%		\item Plot fpcs and approximation of function realization
-	%	\end{itemize}
-	%\end{frame}
-
-	%\begin{frame}{Spectral Representation of Random Vectors}
-	%	Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
-
-	%	\begin{itemize}
-	%		\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
-	%		\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
-	%		\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
-	%	\end{itemize}
-
-	%	\vspace{0.2cm}
-	%	Then $X$ can also be represented as
-	%	$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
-	%	where the $\xi_i(\omega)$ have the following properties
-
-	%	\begin{multicols}{2}
-	%		\begin{enumerate}
-	%			\item $\mathbb{E}[\xi_i(\omega)] = 0$
-	%			\item $Var(\xi_i(\omega)) = \lambda_i$
-	%			\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
-	%		\end{enumerate}
-	%	\end{multicols}
-	%\end{frame}
 
@@
 
-	%\begin{frame}{Principal Component Analysis}
-	%	A related concept is \textbf{Principal Component Analysis} (PCA).
-	%	\vspace{0.2cm}
-	%	
-	%	$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
-	%
-	%	\begin{itemize}
-	%		\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
-	%		\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
-	%		\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
-	%		\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
-	%	\end{itemize}
-	%	\vspace{0.2cm}
-
-	%	Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
-	%	\begin{multicols}{2}
-	%		\begin{enumerate}
-	%			\item $\mathbb{E}[Z_i(\omega)] = 0$
-	%			\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
-	%			\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
-	%		\end{enumerate}
-	%	\end{multicols}
-	%\end{frame}
-
 	\begin{frame}{Functional Principal Component Analysis}
-		{\color{red} Rephrase this!} This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
-		\vspace{0.2cm}
+		\textbf{Principal Component Analysis} can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
+		\vspace{0.4cm}
 
@@
 	\begin{frame}{Simulation Setup \& Application cont.}
-		%\begin{itemize}
-		%\item
+
 		Following \textbf{Reiss and Ogden (2007)}, let $f_1(t)$ and $f_2(t)$ be two coefficient functions:
-		%\vspace{0.2cm}
 
-   		%$f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
-   		%\vspace{0.1cm}
-
-        %$f_2(t) = 1.5 \exp(\frac{-0.5(t-0.3)^2}{0.02^2}) - 4 \exp(\frac{-0.5(t-0.45)^2}{0.015^2}) +  8 \exp(\frac{-0.5(t-0.6)^2}{0.02^2}) - \exp(\frac{-0.5(t-0.8)^2}{0.03^2})$
-
-		%\end{itemize}
 		\vspace{0.1cm}
@@
 
-	\begin{frame}{further reading}
+	\begin{frame}
+		\topskip0pt
+		\vspace*{\fill}
+		\begin{center}
+			{\LARGE Thank you for your time!}
+		\end{center}	
+		\vspace*{\fill}
+		%
+	\end{frame}
+
+	\begin{frame}{Further Reading}
 		 Put footnotes here!
@@
 
+	% From here on out are the supplementary slides.
+
+	\begin{frame}{Spectral Representation of Random Vectors}
+		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
+
+		\begin{itemize}
+			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
+			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
+			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
+		\end{itemize}
+
+		\vspace{0.2cm}
+		Then $X$ can also be represented as
+		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
+		where the $\xi_i(\omega)$ have the following properties
+
+		\begin{multicols}{2}
+			\begin{enumerate}
+				\item $\mathbb{E}[\xi_i(\omega)] = 0$
+				\item $Var(\xi_i(\omega)) = \lambda_i$
+				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
+			\end{enumerate}
+		\end{multicols}
+	\end{frame}
+
+	\begin{frame}{Principal Component Analysis}
+		A related concept is \textbf{Principal Component Analysis} (PCA).
+		\vspace{0.2cm}
+
+		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
+
+		\begin{itemize}
+			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
+			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
+			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
+			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
+		\begin{multicols}{2}
+			\begin{enumerate}
+				\item $\mathbb{E}[Z_i(\omega)] = 0$
+				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
+				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
+			\end{enumerate}
+		\end{multicols}
+	\end{frame}
+
 \end{document}

### 2022-01-07 main.tex
Some theory

@@
 	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
-Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega') = f(t)$ of $F(\omega)$.
+Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega_0) = f(t)$ of $F(\omega)$.
 
 	\begin{equation}
-		F(\omega') = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega') b_j(t)
+		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t)
 	\end{equation}
@@
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
-	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process.
+	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
 To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
+Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$.
+Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\
+
+	This decomposition can be used to express the random vector $X(\omega)$ in the following way.
 
 	\begin{equation}
-		\text{{\color{red} Introduce spectral representation of random vector here.}}
+		X(\omega) = \mu_x + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_x + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
 	\end{equation}
 
-	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$.
+	where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\
+
+	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$.
 Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
@@
 
-	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$.
+	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
+
+		\begin{multicols}{2}
+		\begin{enumerate}
+			\item $\mathbb{E}\left[\xi_j(\omega)\right] = 0$
+			\item $Var\left(\xi_j(\omega)\right) = \lambda_i$
+			\item $Cov\left(\xi_j(\omega), \xi_k(\omega)\right) = 0$ if $j \neq k$
+		\end{enumerate}
+	\end{multicols}
 

### 2022-01-07 main.tex
Some theory

@@
 	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting.
-We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
+We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:
 
 	 \begin{equation}
-	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
+	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
 	 	\qquad i = 1, ..., n
@@
 	\begin{equation}
-		\int_{0}^{1} \lvert f \rvert^2 d\mu < \infty
+		\int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
 	\end{equation}
@@
 	\begin{equation}
-		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 d\mu.
+		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
 	\end{equation}
@@
 
-	\subsection{Different Bases of $\mathbb{L}^2$}
+	\subsection{Bases of $\mathbb{L}^2$}
 	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
@@
 
-	This, however, does not really yield a basis of $\mathbb{L}^2$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2$.
-To really obtain a basis of $\mathbb{L}^2$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
-As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2$ will serve as a sufficient approximation for an appropriately chosen B-spline basis.
+	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
+As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen B-spline basis.
 	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
@@
 	\end{figure}
+
+	\subsection{Approximation and Smoothing via Basis Truncation}
+	{\color{red} Write something about how to approximate functions by truncating the basis.}
+
+	\begin{equation}
+		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t) = \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t)
+	\end{equation}
 
@@
 
+	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors.
+Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.
+
+	\begin{equation}
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} \psi_j Z_j(\omega) + \epsilon(\omega)
+	\end{equation}
+
 	\subsection{Detailed Draft}
@@
 	\begin{equation}
-    	 Y =  \int \beta(s)X(s) \,dt \ +\epsilon
+    	 Y =  \int \beta(s)X(s) \,\mathrm{d}t \ +\epsilon
     \end{equation}
@@
    \begin{equation}
-	   c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
+	   c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,\mathrm{d}s \ +\epsilon]
    \end{equation}
@@
    \begin{equation}
- 	  c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
+ 	  c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, \mathrm{d}s \: | \: X]  + E[\epsilon |\mathbf{X}]
    \end{equation}
@@
    \begin{equation}
-      c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
+      c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,\mathrm{d}s
    \end{equation}
@@
     \begin{equation}
-    	\int \beta(s)X(s) \,dt \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,dt =: \sum_{k=1}^{K} x_{ik} c_{k} 
+    	\int \beta(s)X(s) \,\mathrm{d}t \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,\mathrm{d}t =: \sum_{k=1}^{K} x_{ik} c_{k} 
     \end{equation}
@@
     \begin{equation}
-    	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}
+    	f_2 = 1.5^{\frac{-0.5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0.5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0.5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0.5(t-0.8)^2}{0.03^2}}
     \end{equation}

### 2022-01-08 Code/simulation_study_v2.R
Simulation study ready for parallelization

@@ -92,7 +92,7 @@ bspline_function <- function(rep, NIR, n_obs){
 fourier_function <- function(rep, NIR, n_obs){
   CV_container_spline  <- c()
   
-  for(j in seq(1,10,1)){
+  for(j in seq(1,25,1)){
     success_count = 0
     CV_container  <- matrix(NaN, nrow = rep, ncol = 4)
     
@@ -199,7 +199,7 @@ fpcr_function <- function(rep, NIR, n_obs){
 fpcr_fourier_function <- function(rep, NIR, n_obs){
   CV_container_spline  <- c()
   train.control <- caret::trainControl(method = "cv", number = 10)
-  for(j in seq(1,10,1)){
+  for(j in seq(1,25,1)){
     success_count = 0
     CV_container  <- matrix(NaN, nrow = rep, ncol = 5)
     
@@ -252,28 +252,44 @@ fpcr_fourier_function <- function(rep, NIR, n_obs){
 
 
 #############
-generated_curves = NIR_curve_generator(n=100)
+generated_curves = NIR_curve_generator(n=1000, n_harmonics = 30)
 input_data = as.matrix(generated_curves[,-1])
 #############
 
-############################################################
-###             Run function using the NIR data          ###
-############################################################
+#############################################################################
+###             Run function using the NIR data / generated data          ###
+#############################################################################
 
 
-test_bspline_function = bspline_function(500, NIR, 60)
-write.table(test_bspline_function,file="Results/test_bspline_expansion_NIR.csv")
+test_bspline_function = bspline_function(1000, input_data, 1000)
+#write.table(test_bspline_function,file="Results/test_bspline_expansion_1000.csv")
 test_bspline_function
 
-test_fourier_function = fourier_function(500, NIR, 60)
-write.table(test_fourier_function,file="Results/test_fourier_expansion_NIR.csv")
+test_fourier_function = fourier_function(1000, input_data, 1000)
+#write.table(test_fourier_function,file="Results/test_fourier_expansion_1000.csv")
 test_fourier_function
 
-test_fpcr = fpcr_function(500, NIR, 60)
-write.table(test_fpcr,file="Results/test_fpcr_bsplines_NIR.csv")
+test_fpcr = fpcr_function(1000, input_data, 1000)
[…]

### 2022-01-08 Code/Plot_Generators/True_coefficient_functions.R
miscellaneous and unfinished parallelization

@@ -1,4 +1,6 @@
-##### This script generates an iid data set from wiener processes and plots it
+##### This script plots the true coefficient functions from Reiss and Ogden (2007)
+# Clear Workspace
+rm(list = ls())
 
 # Load packages
 library(tidyverse)
@@ -7,36 +9,34 @@ library(tidyverse)
 n_points <- 10000
 grid <- seq(from = 0, to = 1, length.out = n_points)
 realizations <- 25
-#smooth
-f1 <- 2*sin(0.5*pi*grid) + 4*sin(1.5*pi*grid) + 5*sin(2.5*pi*grid)
-#bumpy
-f2 <- 1.5*exp(-0.5*(grid-0.3)^2/0.02^2) -  4*exp(-0.5*(grid-0.45)^2/0.015^2) +  8*exp(-0.5*(grid-0.6)^2/0.02^2) -  exp(-0.5*(grid-0.8)^2/0.03^2)
-#two different variances of error
+# smooth
+f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+# bumpy
+f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
 
-data_mat <- matrix(data = f2,
-                   nrow = n_points, ncol = realizations, byrow = FALSE)
+# Create tibble containing grid points and function values
+coef_func_tibble <- tibble(t = grid, `f1(t)` = f1, `f2(t)` = f2)
 
-data_tibble <- cbind(tibble(x = points), as_tibble(data_mat, .name_repair = 'unique'))
-names(data_tibble) <- c('t', paste0('Realization_', 1:realizations))
-
-plot_tibble <- data_tibble %>% 
-  pivot_longer(cols = !t, names_to = 'Realization', values_to = 'Value')
+# Pivot tibble for plotting
+plot_tibble <- coef_func_tibble %>%
+  pivot_longer(cols = !t, names_to = "Coefficient-Function", values_to = "Value")
 
 # generate plot
-Wiener_plot <- ggplot(data = plot_tibble) +
[…]

### 2022-01-08 Code/simulation_study_v2.R

@@ -1,312 +1,728 @@
+##### Set up R session for simulation #####
+### Clear Workspace
+rm(list = ls())
+
+### load libraries
 suppressMessages(library(refund))
 suppressMessages(library(ggplot2))
 suppressMessages(library(dplyr))
-suppressMessages(library(reshape2)) 
+suppressMessages(library(reshape2))
 suppressMessages(library(fda))
-#suppressMessages(library(fdaACF))
+# suppressMessages(library(fdaACF))
 suppressMessages(library(fpca))
 suppressMessages(library(caret))
+suppressMessages(library(parallel))
 
+### load code from other source files
+source("data_generator.R")
+source("auxiliary_functions.R")
 
-source("C:/Users/Jonathan/Desktop/RM_Stats/Code/data_generator.R") 
-source("C:/Users/Jonathan/Desktop/RM_Stats/Code/auxiliary_functions.R") 
+### set seed for reproducibility
 set.seed(100)
 
-###################################################
-
+### load data set
 data(gasoline)
 octane <- (gasoline$octane)
-NIR    <- as.matrix(gasoline$NIR)
+NIR <- as.matrix(gasoline$NIR)
 
-###################################################################################################################
-# set up "global" variables
-###################################################################################################################
-set.seed(100)
-n_obs = 60
-nharm = 4
-n_var = 400
-grid = seq(0, 1, length = n_var+1)
-#smooth
-f1 <- 2*sin(0.5*pi*grid) + 4*sin(1.5*pi*grid) + 5*sin(2.5*pi*grid)
-#bumpy
-f2 <- 1.5*exp(-0.5*(grid-0.3)^2/0.02^2) -  4*exp(-0.5*(grid-0.45)^2/0.015^2) +  8*exp(-0.5*(grid-0.6)^2/0.02^2) -  exp(-0.5*(grid-0.8)^2/0.03^2)
-#two different variances of error
-sigma_eps_squared1_1 = as.numeric((var(NIR %*% f1)/0.9) - var(NIR %*% f1))
-sigma_eps_squared1_2 = as.numeric((var(NIR %*% f1)/0.6) - var(NIR %*% f1) )
-sigma_eps_squared2_1 = as.numeric((var(NIR %*% f2)/0.9) - var(NIR %*% f2))
-sigma_eps_squared2_2 = as.numeric((var(NIR %*% f2)/0.6) - var(NIR %*% f2) )
+##### Define Simulation Parameters #####
[…]

### 2022-01-08 Code/simulation_study_v2.R
Parallelized (non fpca stuff)

@@ -45,33 +45,65 @@ sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
 
 ##### Define Simulation Functions #####
 ### b_spline simulation function
-bspline_function <- function(rep, NIR = NULL, n_obs) {
+bspline_function <- function(rep, NIR = NULL, n_obs, debug = FALSE) {
   # check if data (NIR) is provided
   if (is.null(NIR)) {
     data_cond <- FALSE
   } else {
     data_cond <- TRUE
   }
-
+  
+  # specfiy number of basis functions that should be considered
+  n_basis <- seq(from = 5, to = 25, by = 1)
+  
   # set up container for averaged cross validation scores
-  CV_container_spline <- c()
-
-  # loop over number of basis functions
-  for (j in seq(5, 25, 1)) {
-    # create container for cross validation scores for each iteration
-    CV_container <- matrix(NaN, nrow = rep, ncol = 4)
-    success_count <- 0
-
+  CV_container <- as.data.frame(
+    matrix(data = 0, nrow = length(n_basis), ncol = 6)
+  )
+  
+  colnames(CV_container) <- c(
+    "f1_e1_spline", "f1_e2_spline", "f2_e1_spline", "f2_e2_spline",
+    "n_basis", "success_count"
+  )
+  
+  CV_container$n_basis <- n_basis
+  CV_container$success_count <- rep(x = 0, times = length(n_basis))
+  
+  # create basis functions
+  basis_functions <- map(
+    .x = n_basis,
+    .f = function(j) create.bspline.basis(rangeval = c(0, length(grid)), nbasis = j, norder = 4)
+  )
+  
+  # prepare objects for functional linear regression
+  betafdPar2_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) fdPar(basis_functions[[i]])
+  )
+  
+  betalist_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) list(smooth_basis_fd_data = betafdPar2_list[[i]])
+  )
+  
+  # loop over repetitions
+  for (i in 1:rep) {    
+    if(debug){print(paste0('Repetition: ', i, ' out of ', rep))}
+    
+    # if no data (NIR) is provided generate new curves
+    if (data_cond == FALSE) {
+      generated_curves <- NIR_curve_generator(n = n_obs, n_harmonics = 30)
+      NIR <- as.matrix(generated_curves[, -1])
+    }
+    
[…]

### 2022-01-11 main.tex
miscellaneous and unfinished parallelization
Push

@@
 
-	\subsection{Motivate Simulation for some data generating process from application}
-	For the simulation study, we use the gasoline dataset to predict the octane ratings of gasoline samples relying on the introduced methods.
-This has become more relevant as modern internal combustion engines become more complex and rely on precisely tuned fuels.
+	\subsection{Motivation}
+	For the simulation study, we deviate from the standart simulation setting.
+Instead of generating data by ourself, we use the data from the gasoline dataset ($NIR$) to predict the octane ratings of gasoline samples, relying on the introduced methods.
 The dataset, which contains 60 i.i.d.
@@
 \cite{Bohacs_Ovadi_Salgo1998}).
-The study follows Reiss and Ogden (2007) as a guideline.
-Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness:
+
+	\subsection{Generating Similar Curves}
+	To avoid small sample problems, we generated similar curves from the gasoline dataset. This is motivated by the Karhunen-Loeve-Expansion {\color{green} link formula}
+	 First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots.
+These smooth curves are then centred, before performing FPCA.
+For simplification, we assume that
+	$\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$
+
+		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
+
+		\begin{itemize}
+			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
+			\item Simplification: the $\xi_{j}$ do not follow a normal
+			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
+		\end{itemize}
+
+    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
+    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
+Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience...
+No theoretical reasoning)}
+
+    \subsection{Simulation setup}
+	The simulation study follows Reiss and Ogden (2007) as a guideline.
+Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1(t)$ and $f_2(t)$ were chosen that differ in their smoothness:
 
 	\begin{equation}
-    	f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
+    	f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
     \end{equation}
@@
     \begin{equation}
-    	f_2 = 1.5^{\frac{-0.5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0.5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0.5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0.5(t-0.8)^2}{0.03^2}}
+    	\begin{split}
+    		f_2(t) = & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
+    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)}
+    	\end{split}
     \end{equation}
 
-Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
-The two error-terms are then computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset.
-These four combinations are then used with different number of basis-function $(5,6,...,25)$ of the order 5 to predict the responses using the b-spline basis approach and the FPCR approach.
-Within one repetition, the data is randomly sampled into a training and a test set to calculate the reported test MSE.
+		\vspace{0.1cm}
+		\begin{figure}
+			\centering
+			\begin{minipage}{.5\textwidth}
+				\centering
+  				\includegraphics[width=\textwidth]{Graphics/smooth_function.png}
+  				\caption{$f_1(t)$, smooth function}
+  				\label{fig:test1}
+			\end{minipage}%
+			\begin{minipage}{.5\textwidth}
+	  			\centering
+  				\includegraphics[width=\textwidth]{Graphics/bumpy_function.png}
+  				\caption{$f_2(t)$, bumpy function}
+  				\label{fig:test2}
+			\end{minipage}
+		\end{figure}
+
+Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.
+
+$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$
+
+$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$
+
+		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios.
+In total we create four combinations for the simulation, using the two true coefficient functions and the two sets of responses.
+These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach.
+For the evaluation, we use 10f cross-validation.
 The simulation was done with R (version...).
@@
 
-	\subsection{Generating Similar Curves}
-    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
-    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
-Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience...
-No theoretical reasoning)}
 	\subsection{Results}

### 2022-01-11 Code/Main_Simulation.R

@@ -40,26 +40,42 @@ source("k_fold_CV_function.R")
 
 ##### Perform Simulations #####
 
-test_bspline_function <- bspline_function(rep = 1000, my_data = NULL, n_obs = 200, seed = 103, debug = TRUE)
+# How to safe files? --> Please safe them accrondingly in their folder and name them with reps, obs, seed!
+# conduct 5x500 reps for seed 100-seed 104
+
+
+# Jakob 5x500
+test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
 saveRDS(test_bspline_function,file = "Results/bspline_sim_partial/rep1000_n_obs200_seed103.RDS")
 
-test_fourier_function <- fourier_function(rep = 1000, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fourier_function,file = "Results/fourier_sim_partial/n_obs200_seed100.RDS")
+# Jonghun 5x500
+test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
+saveRDS(test_fourier_function,file = "Results/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
-test_fpcr <- fpcr_function(rep = 1000, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/n_obs200_seed100.RDS")
+# Jona 5x500
+test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
+saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/reps500_n_obs200_seed100.RDS")
 
-test_fpcr2 <- fpcr_fourier_function(rep = 1000, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr2, file = "Results/pca_fourier_sim_partial/n_obs200_seed100.RDS")
+# Jakob 5x500
+test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
+saveRDS(test_fpcr2, file = "Results/pca_fourier_sim_partial/reps_n_obs200_seed100.RDS")
 
[…]

### 2022-01-11 Code/Main_Simulation.R
Small correction

@@ -40,13 +40,13 @@ source("k_fold_CV_function.R")
 
 ##### Perform Simulations #####
 
-# How to safe files? --> Please safe them accrondingly in their folder and name them with reps, obs, seed!
+# How to safe files? --> Please safe them accordingly in their folder and name them with reps, obs, seed!
 # conduct 5x500 reps for seed 100-seed 104
 
 
 # Jakob 5x500
 test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_bspline_function,file = "Results/bspline_sim_partial/rep1000_n_obs200_seed103.RDS")
+saveRDS(test_bspline_function,file = "Results/bspline_sim_partial/rep500_n_obs200_seed103.RDS")
 
 # Jonghun 5x500
 test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
@@ -54,11 +54,11 @@ saveRDS(test_fourier_function,file = "Results/fourier_sim_partial/rep500_n_obs20
 
 # Jona 5x500
 test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/reps500_n_obs200_seed100.RDS")
+saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jakob 5x500
 test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr2, file = "Results/pca_fourier_sim_partial/reps_n_obs200_seed100.RDS")
+saveRDS(test_fpcr2, file = "Results/pca_fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
 ################################################################
 ##### The following simulations use the original NIR data ######

### 2022-01-11 Code/Simulation_Functions.R
Fixing n_nbasis to 1-25

@@ -20,7 +20,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specify number of basis functions that should be considered
-  n_basis <- seq(from = 5, to = 25, by = 1)
+  n_basis <- seq(from = 1, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -145,7 +145,7 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 5, to = 25, by = 1)
+  n_basis <- seq(from = 1, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -270,7 +270,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 5, to = 25, by = 1)
+  n_basis <- seq(from = 1, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -406,7 +406,7 @@ fpcr_fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALS
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 5, to = 25, by = 1)
+  n_basis <- seq(from = 1, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(

### 2022-01-11 Code/Main_Simulation.R
Increment

@@ -45,8 +45,10 @@ source("k_fold_CV_function.R")
 
 
 # Jakob 5x500
-test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_bspline_function,file = "Results/bspline_sim_partial/rep500_n_obs200_seed103.RDS")
+for(i in 100:104){
+  test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = 103, debug = TRUE)
+  saveRDS(test_bspline_function,file = paste0("Results/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+}
 
 # Jonghun 5x500
 test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)

### 2022-01-11 Code/Simulation_Functions.R

@@ -20,7 +20,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specify number of basis functions that should be considered
-  n_basis <- seq(from = 1, to = 25, by = 1)
+  n_basis <- seq(from = 4, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -270,7 +270,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 1, to = 25, by = 1)
+  n_basis <- seq(from = 4, to = 25, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(

### 2022-01-11 Code/Main_Simulation.R
Quick loop for me

@@ -46,7 +46,7 @@ source("k_fold_CV_function.R")
 
 # Jakob 5x500
 for(i in 100:104){
-  test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = 103, debug = TRUE)
+  test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
   saveRDS(test_bspline_function,file = paste0("Results/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 
@@ -59,9 +59,10 @@ test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, d
 saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jakob 5x500
-test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr2, file = "Results/pca_fourier_sim_partial/rep500_n_obs200_seed100.RDS")
-
+for(i in 100:104){
+  test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
+  saveRDS(test_fpcr2, file = paste0("Results/pca_fourier_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+}
 ################################################################
 ##### The following simulations use the original NIR data ######
 ################################################################

### 2022-01-11 Code/Main_Simulation.R
Error term problem Fixed

@@ -47,16 +47,16 @@ source("k_fold_CV_function.R")
 # Jakob 5x500
 for(i in 100:104){
   test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
-  saveRDS(test_bspline_function,file = paste0("Results/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+  saveRDS(test_bspline_function, file = paste0("Results/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 
 # Jonghun 5x500
 test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fourier_function,file = "Results/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
+saveRDS(test_fourier_function, file = "Results/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jona 5x500
 test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
-saveRDS(test_fpcr,file="Results/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
+saveRDS(test_fpcr, file="Results/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jakob 5x500
 for(i in 100:104){

### 2022-01-11 Code/Simulation_Functions.R

@@ -67,6 +67,12 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
     # transpose data for use with fda package
     data <- t(my_data)
     
+    # calculate responses
+    Y1_1 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_1)
+    Y1_2 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_2)
+    Y2_1 <- as.numeric(my_data %*% f2 + rnorm(n_obs, 0, 1) * sigma_eps_squared2_1)
+    Y2_2 <- as.numeric(my_data %*% f2 + rnorm(n_obs, 0, 1) * sigma_eps_squared2_2)
+    
     # loop over diferent number of basis functions
     for (j in 1:length(n_basis)) {
       if (debug) {
@@ -75,12 +81,6 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
       
       tryCatch(
       {
-      # calculate responses
-      Y1_1 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_1)
-      Y1_2 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_2)
-      Y2_1 <- as.numeric(my_data %*% f2 + rnorm(n_obs, 0, 1) * sigma_eps_squared2_1)
-      Y2_2 <- as.numeric(my_data %*% f2 + rnorm(n_obs, 0, 1) * sigma_eps_squared2_2)
-      
       # construct basis for functional representation
       smallbasis <- basis_functions[[j]]
       
@@ -192,6 +192,12 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
     # transpose data for use with fda package
     data <- t(my_data)
     
+    # calculate responses
+    Y1_1 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_1)
+    Y1_2 <- as.numeric(my_data %*% f1 + rnorm(n_obs, 0, 1) * sigma_eps_squared1_2)
+    Y2_1 <- as.numeric(my_data %*% f2 + rnorm(n_obs, 0, 1) * sigma_eps_squared2_1)
[…]

### 2022-01-11 Code/Main_Simulation.R
Fourier Fix

@@ -40,9 +40,8 @@ source("k_fold_CV_function.R")
 
 ##### Perform Simulations #####
 
-# How to safe files? --> Please safe them accordingly in their folder and name them with reps, obs, seed!
+# How to save files? --> Please safe them accordingly in their folder and name them with reps, obs, seed!
 # conduct 5x500 reps for seed 100-seed 104
-
 
 # Jakob 5x500
 for(i in 100:104){

### 2022-01-11 Code/Simulation_Functions.R

@@ -124,7 +124,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
 }
 
 ### Fourier simulation function
-fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
+fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis = FALSE, debug = FALSE) {
   set.seed(seed)
   ### set up coefficient "functions" / error terms
   # smooth
@@ -145,7 +145,11 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 1, to = 25, by = 1)
+  if(even_basis == TRUE){
+    n_basis <- seq(from = 1, to = 25, by = 1)
+  } else{
+    n_basis <- seq(from = 1, to = 25, by = 2)
+  }
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -161,11 +165,24 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   CV_container$success_count <- rep(x = 0, times = length(n_basis))
   
   # create basis functions
-  basis_functions <- map(
-    .x = n_basis,
-    .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j)
-  )
-  
+  if(even_basis == TRUE){
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) {
+        if(j %% 2 == 1){
+          return(create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j))
+        } else{
+          return(create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j, dropind = j))
+        }
+      }
+    )
+  } else{
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j, norder = 4)
+    )
+  }
+
   # prepare objects for functional linear regression
   betafdPar2_list <- map(
     .x = 1:length(n_basis),
@@ -385,7 +402,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
 }
 
 ### FPCA simulation function - Fourier basis
[…]

### 2022-01-11 Code/Main_Simulation.R
Increment

@@ -50,7 +50,7 @@ for(i in 100:104){
 }
 
 # Jonghun 5x500
-test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, debug = TRUE)
+test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, even_basis = TRUE, debug = TRUE)
 saveRDS(test_fourier_function, file = "Results/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jona 5x500
@@ -59,7 +59,7 @@ saveRDS(test_fpcr, file="Results/pca_bspline_sim_partial/rep500_n_obs200_seed100
 
 # Jakob 5x500
 for(i in 100:104){
-  test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
+  test_fpcr2 <- fpcr_fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, even_basis = TRUE, debug = TRUE)
   saveRDS(test_fpcr2, file = paste0("Results/pca_fourier_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 ################################################################
@@ -67,17 +67,17 @@ for(i in 100:104){
 ################################################################
 
 # Jonghun 5x500
-test_bspline_function_NIR <- bspline_function(rep = 500, my_data = NIR, n_obs = 60)
+test_bspline_function_NIR <- bspline_function(rep = 500, my_data = NIR, n_obs = 60, debug = TRUE)
 saveRDS(test_bspline_function_NIR,file = "Results/bspline_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
 
 # Jona 5x500
-test_fourier_function_NIR <- fourier_function(rep = 500, my_data = NIR, n_obs = 60)
+test_fourier_function_NIR <- fourier_function(rep = 500, my_data = NIR, n_obs = 60, even_basis = TRUE, debug = TRUE)
 saveRDS(test_fourier_function_NIR,file = "Results/fourier_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
 
 # Jona 5x500
-test_fpcr_NIR <- fpcr_function(rep = 500, my_data = NIR, n_obs = 60)
[…]

### 2022-01-11 Code/Simulation_Functions.R
Increment

@@ -179,7 +179,7 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis = FALS
   } else{
     basis_functions <- map(
       .x = n_basis,
-      .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j, norder = 4)
+      .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j)
     )
   }
 
@@ -457,7 +457,7 @@ fpcr_fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis =
   } else{
     basis_functions <- map(
       .x = n_basis,
-      .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j, norder = 4)
+      .f = function(j) create.fourier.basis(rangeval = c(0, length(grid)), nbasis = j)
     )
   }
   

### 2022-01-12 Presentation/slides.tex
Edit simulation in main.tex, edit presentation

@@
 			\item Only observed at $x_{i}(t_{j,i})$
-			\item Growth curves, financial data, human perception (pitch), ...
-			\item To abstract information from the curves, they must be interpretable!
+			\item Example: Gasoline dataset (60 x 400)
+			\item Other Examples: Growth curves, financial data, human perception (pitch), ...
+
 		\end{itemize}
@@
 
-	\begin{frame}{Simulation Setup \& Application}
+	\begin{frame}{Simulation Setup}
 		\begin{itemize}
@@
 
-		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
+		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
 
@@
 			\item Simplification: the $\xi_{j}$ do not follow a normal
-			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
+			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
 		\end{itemize}
@@
 
-	\begin{frame}{Simulation Setup \& Application cont.}
+	\begin{frame}{Simulation Setup cont.}
 
@@
 
-	\begin{frame}{Simulation Setup \& Application cont.}
+	\begin{frame}{Simulation Setup cont.}
 		Let 
-		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
-		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$
+		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
+		$$Y_{2,f} = \langle NIR, f\rangle + Z\left( \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\right)$$
 
@@
 		\begin{itemize}
-    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
+    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (4,5,...,25)$ and fourier functions $(1,3,...,25)$ to perform regression using basis expansion and the FPCR approach.
 			\item Compare results via criteria (CV, Mallows CP,...)
+
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Results}
+
+		\begin{itemize}
+
 			\item {\color{green} add results here!}
@@
 
-	\begin{frame}{Simulation Setup \& Application cont.}
+	\begin{frame}{Application setup}
 		\begin{itemize}
@@
     		\item
-    		Similar setup, but using only bsplie basis expansion and initial 60 spectral curves.
+    		Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
     		\item
-    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
+    		Validation set approach:	Scores of test data needs to be estimated by the training data. 
     		\item
@@
 	\begin{frame}{Summary}
-		Jona \\
-		Just summarize what we have done...
+		\begin{itemize}
+		\item
+    		Concepts of functional data: 
+    		\begin{itemize}
+			\item See dataset as smooth curve than as set of discrete measurements.
+    			\item Theory of Random Functions, motivated from random variable.
+    			\item Basis expansion and its Bias-Variance tradeoff.
+    			\item Scalar on Function Regression via Basis Expansion.
+    			\item Functional principal component Analysis and FPCR.
+		\end{itemize}
+    		\item
+    		Simulation study results: specification depends on function and signal-to-noise ratio
+    		\item
+    		% Guided you  from the beginning to the end of the presentaion through one application ....
+    		Guided through application to predict octane ratings.
+
+		\end{itemize}
 	\end{frame}
@@
 		 Put footnotes here!
+		 Yuanpeng Li et al.(2020): Early Diagnosis of Type 2 Diabetes Based on Near-Infrared Spectroscopy Combined With Machine Learning and Aquaphotomics, Frontiers of Chemistry (8)
 	\end{frame}

### 2022-01-13 Code/Main_Simulation.R
Slight structure change

@@ -46,24 +46,24 @@ source("k_fold_CV_function.R")
 # Jakob 5x500
 for (i in 100:104) {
   test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
-  saveRDS(test_bspline_function, file = paste0("Results/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+  saveRDS(test_bspline_function, file = paste0("Results/Partial/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 
 # Jonghun 5x500
 test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, even_basis = TRUE, debug = TRUE)
-saveRDS(test_fourier_function, file = "Results/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
+saveRDS(test_fourier_function, file = "Results/Partial/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jona 5x500
 test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, nharm = 4, seed = 100, debug = TRUE)
-saveRDS(test_fpcr, file = "Results/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
+saveRDS(test_fpcr, file = "Results/Partial/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jakob 5x500
 for (i in 100:104) {
   test_fpcr2 <- fpcr_fourier_function(
-    rep = 500, my_data = NULL, nharm = 4, n_obs = 200,
+    rep = 500, my_data = NULL, nharm = 3, n_obs = 200,
     seed = i, even_basis = FALSE, debug = TRUE
   )
-  saveRDS(test_fpcr2, file = paste0("Results/pca_fourier_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+  saveRDS(test_fpcr2, file = paste0("Results/Partial/pca_fourier_nharm3_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 ################################################################
 ##### The following simulations use the original NIR data ######
@@ -72,18 +72,18 @@ for (i in 100:104) {
 # Jonghun 5x500
[…]

### 2022-01-13 Presentation/slides.tex
update
Added bibliography

@@
 		Let $\mathbb{E}$ be the index set and this can be described as
-		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
+		$${X = \{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
 		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
@@
 		\begin{itemize}
-			\item Without loss of generality, the interval is defined in $[0,1] $
-			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
-			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
+			\item Without loss of generality, the interval is defined in $[0,1]$.
+			\item $\mathbb{L}^{2}$ is the set of all square integrable functions.
 		\end{itemize}
@@
 	\begin{frame}{Square Integrable Function}
-		Let $f, g \in \mathbb{L}^{2}[0,1]$, then
+		Let $f, g \in \mathbb{L}^{2}[0,1]$, then we can define inner product by
 		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
@@
 		%	\item
-		Orthogonality of two different functions $\langle f,g \rangle = 0$
-			%\item Distance between functions
-		%\end{itemize}
+		\begin{itemize}
+			\item Orthogonality of two different functions with $\langle f,g \rangle = 0$
+			\item Distance between functions
+		\end{itemize}
 	\end{frame}
@@
 	\begin{frame}{Basis Expansion}
-		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
+		\textbf{Basis Expansion} is a linear combination of functions as described:
+
 		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$
+
 		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
@@
 	\begin{frame}{Two Typical Types of Basis Function}
-		\textbf{Fourier Basis Function} is written as
-		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
+		\textbf{Fourier Basis Function} is an element of the set:
+
+		$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$
+
+		%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
+
 		\vspace{2\baselineskip}
-		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
-		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.
+		\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\
+
 	\end{frame}
@@
 			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
-			\caption {Fourier basis functions with order 9}
+			\caption {Fourier basis functions}
 		\end{figure}
@@
 			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
-			\caption {Bspline basis functions with order 9}
+			\caption {Bspline basis functions}
 		\end{figure}
@@
 		How do we choose the number $K$ of basis functions?
-		$$\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$$
 
-		{\color{red} Integrated Mean Squared Error}
+		$$\textbf{MSE}[\hat{X}(t)] = \textbf{Bias}^2[\hat{X}(t)] + \textbf{Var}[\hat{X}(t)]$$
+
+		$$\textbf{MISE}[\hat{X}] = \int_{0}^{1} \textbf{MSE}[\hat{X}(t)] dt$$
+
 		\begin{itemize}
 			\item The larger $K$, the better fit to the data with also fitting noise
-			\item If $K$ is too small, it would miss some significant information that we want to estimate 
+			\item If $K$ is too small, it would miss some significant information
 		\end{itemize}
@@
 	\begin{frame}{Further Reading}
-		 Put footnotes here!
-		 Yuanpeng Li et al.(2020): Early Diagnosis of Type 2 Diabetes Based on Near-Infrared Spectroscopy Combined With Machine Learning and Aquaphotomics, Frontiers of Chemistry (8)
+		 Further Reading:
+		 \nocite{Bohacs_Ovadi_Salgo1998}
+		 \nocite{FR_li_et_al_2020} 
+		 \nocite{Reiss_2007b}
+		 \AtNextBibliography{\tiny}
+		 \printbibliography[heading=none]
 	\end{frame}

### 2022-01-13 Code/Plot_Generators/Gasoline_data_different_smoothing.R
Create Gasoline_data_different_smoothing.R

@@ -1,0 +1,40 @@
+##### This script plots the true coefficient functions from Reiss and Ogden (2007)
+# Clear Workspace
+rm(list = ls())
+
+# Load packages
+library(tidyverse)
+suppressMessages(library(refund))
+suppressMessages(library(MASS))
+suppressMessages(library(tidyverse))
+suppressMessages(library(fda))
+suppressMessages(library(fpca))
+suppressMessages(library(caret))
+
+##### import simulation functions #####
+# this depends on the grid variable above
+source("Simulation_Functions.R")
+### load code from other source files
+source("data_generator.R")
+source("k_fold_CV_function.R")
+
+grid = seq(0, 1, length = 401)
+#smooth
+f1 <- 2*sin(0.5*pi*grid) + 4*sin(1.5*pi*grid) + 5*sin(2.5*pi*grid)
+bumpy
+f2 <- 1.5*exp(-0.5*(grid-0.3)^2/0.02^2) -  4*exp(-0.5*(grid-0.45)^2/0.015^2) +  8*exp(-0.5*(grid-0.6)^2/0.02^2) -  exp(-0.5*(grid-0.8)^2/0.03^2)
+#two different variances of error
+plot(f1*1/401)
+
+generated_curves <- NIR_curve_generator(n = 200, n_harmonics = 30)
+my_data <- as.matrix(generated_curves[, -1])
+
+data = t(my_data)
+
+#print(dim(NIR))
+smallbasis      <- create.bspline.basis(rangeval = c(0, length(grid)), nbasis = as.numeric(4), norder = 4)
+smooth_basis_fd <- smooth.basis(y = data, fdParobj=smallbasis)$fd
+xfdlist = list(smooth_basis=smooth_basis_fd)
+
+plot(smooth_basis_fd, xlab = "wavelength")
+

### 2022-01-13 Code/Main_Simulation.R
Sims and Structure

@@ -60,10 +60,10 @@ saveRDS(test_fpcr, file = "Results/Partial/pca_bspline_sim_partial/rep500_n_obs2
 # Jakob 5x500
 for (i in 100:104) {
   test_fpcr2 <- fpcr_fourier_function(
-    rep = 500, my_data = NULL, nharm = 3, n_obs = 200,
+    rep = 500, my_data = NULL, nharm = 2, n_obs = 200,
     seed = i, even_basis = FALSE, debug = TRUE
   )
-  saveRDS(test_fpcr2, file = paste0("Results/Partial/pca_fourier_nharm3_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
+  saveRDS(test_fpcr2, file = paste0("Results/Partial/pca_fourier_nharm2_sim_partial/rep500_n_obs200_seed", i, ".RDS"))
 }
 ################################################################
 ##### The following simulations use the original NIR data ######
@@ -78,9 +78,13 @@ for (i in 100:104) {
 test_fourier_function_NIR <- fourier_function(rep = 500, my_data = NIR, n_obs = 60, seed = 100, even_basis = TRUE, debug = TRUE)
 saveRDS(test_fourier_function_NIR, file = "Results/Partial/fourier_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
 
-# Jona 5x500
-test_fpcr_NIR <- fpcr_function(rep = 500, my_data = NIR, n_obs = 60, seed = 100, debug = TRUE)
-saveRDS(test_fpcr_NIR, file = "Results/Partial/pca_bspline_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
+# Jona 5x500 (Jakob)
+for(j in 2:4){
+  for (i in 100:104) {
+    test_fpcr_NIR <- fpcr_function(rep = 500, my_data = NIR, n_obs = 60, nharm = j, seed = i, debug = TRUE)
+    saveRDS(test_fpcr_NIR, file = "Results/Partial/pca_bspline_nharm", j, "_NIR_partial/NIRrep500_n_obs60_seed", i, ".RDS")
+  }
+}
 
 # Jonghun 5x500
 for (i in 100:104) {

### 2022-01-13 Code/Main_Simulation.R
Update Main_Simulation.R

@@ -54,8 +54,8 @@ test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200
 saveRDS(test_fourier_function, file = "Results/Partial/fourier_sim_partial/rep500_n_obs200_seed100.RDS")
 
 # Jona 5x500
-test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, nharm = 4, seed = 100, debug = TRUE)
-saveRDS(test_fpcr, file = "Results/Partial/pca_bspline_sim_partial/rep500_n_obs200_seed100.RDS")
+test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, nharm = 4, seed = 104, debug = TRUE)
+saveRDS(test_fpcr, file = "Results/Partial/pca_bspline_nharm4_sim_partial/rep500_n_obs200_seed104.RDS")
 
 # Jakob 5x500
 for (i in 100:104) {
@@ -75,10 +75,12 @@ for (i in 100:104) {
   saveRDS(test_bspline_function_NIR, file = "Results/Partial/bspline_NIR_partial/NIRrep500_n_obs60_seed", i, ".RDS")
 }
 # Jona 5x500
-test_fourier_function_NIR <- fourier_function(rep = 500, my_data = NIR, n_obs = 60, seed = 100, even_basis = TRUE, debug = TRUE)
-saveRDS(test_fourier_function_NIR, file = "Results/Partial/fourier_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
+for (i in 100:104) {
+test_fourier_function_NIR <- fourier_function(rep = 500, my_data = NIR, n_obs = 60, seed = i, debug = TRUE)
+saveRDS(test_fourier_function_NIR, file = paste0("Results/Partial/fourier_NIR_partial/NIR_fourier_rep500_n_obs60_seed", i, ".RDS"))
+}
 
-# Jona 5x500
+# Jakob 5x500
 test_fpcr_NIR <- fpcr_function(rep = 500, my_data = NIR, n_obs = 60, seed = 100, debug = TRUE)
 saveRDS(test_fpcr_NIR, file = "Results/Partial/pca_bspline_NIR_partial/NIRrep500_n_obs60_seed100.RDS")
 

### 2022-01-14 Code/Plot_Generators/Tradeoff_plot.R
Slide Update

@@ -1,7 +1,12 @@
-library('refund')
-library('fda')
+# Clear Workspace
+rm(list = ls())
+
+# load libraries
+library(fda)
+library(refund)
 library(tidyverse)
 
+# load data
 data(gasoline)
 NIR    <- t(as.matrix(gasoline$NIR))
 
@@ -77,11 +82,26 @@ NIR_data = rbind(NIR,NIR_plot5,NIR_plot10,NIR_plot30,NIR_plot50,NIR_plot100)
 label <- paste0("K=",c(0,5,10,30,50,100))
 label[1] <- "Real Line"
 
-ggplot(data = NIR_data, aes(x=time, y=wavelength,color=K)) +
+basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength,color=K)) +
   geom_line()+
-  xlab('Wavelength') +
+  xlab('Wavelength in nm') +
   ylab('Spectrum') +
   scale_color_discrete(breaks=c('K=0','K=5','K=10','K=30','K=50','K=100'), 
                        labels=label)+
-  ggtitle('Basis expansions according to the different number of B-spline basis functions')
+  ggtitle('Basis expansions according to the different number of B-spline basis functions') +
+  theme_light() +
+  theme(
+    legend.position = "bottom",
+    plot.title = element_text(size = 30),
+    axis.title = element_text(size = 20),
+    axis.text = element_text(size = 20),
+    legend.title = element_text(size = 24),
+    legend.text = element_text(size = 20)
+  )
+
+# save plot in appropriate folder
+ggsave(
+  filename = "../Graphics/basis_expansions.pdf", plot = basis_exp_plot,
+  width = 20, height = 12, units = "in", dpi = 600
+)
   

### 2022-01-14 Presentation/slides.tex
Update slides.tex
Slide Update
Slides Update

@@
 		\begin{itemize}
-			\item The larger $K$, the better fit to the data with also fitting noise
-			\item If $K$ is too small, it would miss some significant information
+			\item The larger $K$, the better fit to the data, but also more fitting noise
+			\item If $K$ is too small, the expansion would miss some significant information
 		\end{itemize}
@@
 	\begin{frame}{Trade Off between Bias and Variance}
-		\begin{minipage}[t]{\textwidth}
-			\includegraphics[height = 7cm]{../Graphics/Tradeoff.png}
-		\end{minipage}
+		\begin{figure}\notag
+			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
+		\end{figure}
 	\end{frame}
@@
 	\begin{frame}{FPCA - Plots}
-		\begin{minipage}[c]{0.78\textwidth}
-			\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
+			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
 			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
-		\end{minipage}
-		\begin{minipage}[c]{0.19\textwidth}
-			The math is for intuition. In practice there are problems and the fpc's are derived differently.
-		\end{minipage}
 	\end{frame}

### 2022-01-14 Presentation/slides.tex
Added links to slides

@@
 % Theme choice:
-\usetheme{Berlin}
-\usecolortheme{seahorse}
+\usetheme{Dresden}
+\usecolortheme{whale}
 
@@
 
-	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
+	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}\label{KLE}
 		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
@@
 
-		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis.
+		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis. \\
+
+		\hyperlink{spectral}{\beamergotobutton{Spectral Representation of Random Vectors}}
 	\end{frame}
@@
 
-	\begin{frame}{Functional Principal Component Analysis}
+	\begin{frame}{Functional Principal Component Analysis}\label{FPCA}
 
@@
 
+		\hyperlink{PCA}{\beamergotobutton{PCA for Random Vectors}}
 	\end{frame}
@@
 
-	\begin{frame}{Spectral Representation of Random Vectors}
+	\begin{frame}{Spectral Representation of Random Vectors}\label{spectral}
 		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.
@@
 		\end{multicols}
+
+		\hyperlink{KLE}{\beamergotobutton{Karhunen-Lo\'{e}ve Expansion}}
 	\end{frame}
 
-	\begin{frame}{Principal Component Analysis}
+	\begin{frame}{Principal Component Analysis}\label{PCA}
 		A related concept is \textbf{Principal Component Analysis} (PCA).
@@
 		\end{multicols}
+		\hyperlink{FPCA}{\beamergotobutton{Functional Principal Component Analysis}}
 	\end{frame}
-
 \end{document}

### 2022-01-14 Code/Plot_Generators/Principal_Components_NIR.R

@@ -156,5 +156,5 @@ pc_approx_plot <- ggplot(data = plotting_approx_obs_tibble) +
 # save plot in appropriate folder
 ggsave(
   filename = "../Graphics/pc_approx.pdf", plot = pc_approx_plot,
-  width = 20, height = 8, units = "in", dpi = 600
+  width = 20, height = 12, units = "in", dpi = 600
 )

### 2022-01-14 Presentation/slides.tex
Correction
Increment

@@
 \title{Scalar on Function Regression \\
-with Applications to Near-Infrared Spectography}
+with Applications to Near-Infrared Spectroscopy}
 \author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
-\date{{\color{red}}Presentation Day}
+\date{18.01.2022}
 
@@
 
-		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j b_j(t)$$
+		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j \phi_j(t)$$
 		%Assume that we have a data set containing observations each of which is made up of:
@@
 		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
-		$$Z_{i,j} = \int_{0}^{1} x_i(s) b_j(s)\mathrm{d}s$$
+		$$Z_{i,j} = \int_{0}^{1} x_i(s) \phi_j(s)\mathrm{d}s$$
 
@@
 		\textbf{Empirical Mean Function}:
-		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)$$
+		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)$$
 
 		\textbf{Empirical Autocovariance Function}:
-		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)$$
+		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)$$
 
@@
 
-	\begin{frame}{FPCA - Plots}
+	\begin{frame}{FPCA - Plot}
 			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}

### 2022-01-15 Code/Main_Stitching.R
Summaries

@@ -1,27 +1,35 @@
 # import libraries
 library(stringr)
+library(tidyverse)
 
 # import stitching functions
 source("Simulation_Stitch_Functions.R")
 
 # get subfolders of Results/partial
-sbfldrs <- list.files(path = 'Results/Partial')
+sbfldrs <- list.files(path = "Results/Partial")
 
 # create paths to subfolders
-sbfldr_paths <- map(.x = sbfldrs,
-                    .f = function(fldr) paste0('Results/Partial', fldr))
+sbfldr_paths <- map(
+  .x = sbfldrs,
+  .f = function(fldr) paste0("Results/Partial/", fldr)
+)
 
 # create names for summary objects
-output_names <- map(.x = sbfldrs,
-                    .f = function(fldr) str_split(string = fldr, pattern = '_partial'))
+output_names <- map(
+  .x = sbfldrs,
+  .f = function(fldr) str_split(string = fldr, pattern = "_partial")
+)
 
 # summarize partial results
-summary_results <- map(.x = sbfldr_paths,
-                       .f = function(p) try(simulation_stitch(path = p)))
+summary_results <- map(
+  .x = sbfldr_paths,
+  .f = function(p) try(simulation_stitch(path = p))
+)
 
 # save in summaries folder
-for(i in 1:length(sbfldrs)){
-  saveRDS(object = summary_results[[i]], 
-          file = paste0('Results/Summaries/', output_names[[i]], '.RDS'))
+for (i in 1:length(sbfldrs)) {
+  saveRDS(
+    object = summary_results[[i]],
+    file = paste0("Results/Summaries/", output_names[[i]][[1]][1], ".RDS")
+  )
 }
-

### 2022-01-15 Code/Simulation_Stitch_Functions.R

@@ -8,7 +8,7 @@ simulation_stitch <- function(path) {
   
   # read into list
   output_dfs <- map(.x = path_files,
-                    .f = function(obj) readRDS(paste0(path, obj)))
+                    .f = function(obj) readRDS(paste0(path, '/', obj)))
   
   # Generate object for the results
   n_row <- dim(output_dfs[[1]])[1]
@@ -41,7 +41,7 @@ simulation_stitch <- function(path) {
           map(
             .x = 1:length(output_dfs),
             .f = function(index){
-             output_dfs[[index]][j, i] * (output_dfs[[index]]$success_count[j] / results$success_count[j])
+             output_dfs[[index]][j, i] * ifelse(results$success_count[j] != 0, (output_dfs[[index]]$success_count[j] / results$success_count[j]), 0)
             }
           )
         )
@@ -61,7 +61,7 @@ fpcr_simulation_stitch <- function(path) {
   
   # read into list
   output_dfs <- map(.x = path_files,
-                    .f = function(obj) readRDS(paste0(path, obj)))
+                    .f = function(obj) readRDS(paste0(path, '/', obj)))
   
   # Generate object for the results
   n_row <- dim(output_dfs[[1]])[1]
@@ -94,7 +94,7 @@ fpcr_simulation_stitch <- function(path) {
           map(
             .x = 1:length(output_dfs),
             .f = function(index){
-              output_dfs[[index]][j, i] * (output_dfs[[index]]$success_count[j] / results$success_count[j])
+              output_dfs[[index]][j, i] * ifelse(results$success_count[j] != 0, (output_dfs[[index]]$success_count[j] / results$success_count[j]), 0)
             }
           )
         )

### 2022-01-15 Code/Main_Stitching.R
Correction

@@ -17,19 +17,25 @@ sbfldr_paths <- map(
 # create names for summary objects
 output_names <- map(
   .x = sbfldrs,
-  .f = function(fldr) str_split(string = fldr, pattern = "_partial")
+  .f = function(fldr) str_split(string = fldr, pattern = "_partial")[[1]][1]
 )
 
 # summarize partial results
 summary_results <- map(
-  .x = sbfldr_paths,
-  .f = function(p) try(simulation_stitch(path = p))
+  .x = 1:length(sbfldr_paths),
+  .f = function(p) {
+    if (grepl(pca, output_names[[p]], fixed = TRUE)) {
+      try(fpcr_simulation_stitch(path = sbfldr_paths[[p]]))
+    } else {
+      try(simulation_stitch(path = sbfldr_paths[[p]]))
+    }
+  }
 )
 
 # save in summaries folder
 for (i in 1:length(sbfldrs)) {
   saveRDS(
     object = summary_results[[i]],
-    file = paste0("Results/Summaries/", output_names[[i]][[1]][1], ".RDS")
+    file = paste0("Results/Summaries/", output_names[[i]], ".RDS")
   )
 }

### 2022-01-15 Code/Simulation_Stitch_Functions.R

@@ -5,11 +5,13 @@ simulation_stitch <- function(path) {
 
   # get files in path
   path_files <- list.files(path = path)
-  
+
   # read into list
-  output_dfs <- map(.x = path_files,
-                    .f = function(obj) readRDS(paste0(path, '/', obj)))
-  
+  output_dfs <- map(
+    .x = path_files,
+    .f = function(obj) readRDS(paste0(path, "/", obj))
+  )
+
   # Generate object for the results
   n_row <- dim(output_dfs[[1]])[1]
   n_col <- dim(output_dfs[[1]])[2]
@@ -19,7 +21,7 @@ simulation_stitch <- function(path) {
   rownames(results) <- rownames(output_dfs[[1]])
   colnames(results) <- colnames(output_dfs[[1]])
   results$n_basis <- output_dfs[[1]]$n_basis
-  
+
   # Combine elements of the list par_results to be one result.
   # for success_count do summation
   for (j in 1:n_row) {
@@ -32,7 +34,7 @@ simulation_stitch <- function(path) {
       )
     )
   }
-  
+
   # for cv_scores do weighted averaging
   for (i in 1:4) {
     for (j in 1:n_row) {
@@ -40,15 +42,16 @@ simulation_stitch <- function(path) {
         unlist(
           map(
             .x = 1:length(output_dfs),
-            .f = function(index){
-             output_dfs[[index]][j, i] * ifelse(results$success_count[j] != 0, (output_dfs[[index]]$success_count[j] / results$success_count[j]), 0)
+            .f = function(index) {
+              output_dfs[[index]][j, i] * ifelse(results$success_count[j] != 0, (output_dfs[[index]]$success_count[j] / results$success_count[j]), 0)
             }
           )
-        )
+        ),
+        na.rm = TRUE
       )
     }
   }
-  
+
   # return averaged object
   return(results)
 }
@@ -58,11 +61,13 @@ fpcr_simulation_stitch <- function(path) {
 
   # get files in path
   path_files <- list.files(path = path)
-  
+
   # read into list
-  output_dfs <- map(.x = path_files,
-                    .f = function(obj) readRDS(paste0(path, '/', obj)))
-  
+  output_dfs <- map(
+    .x = path_files,
+    .f = function(obj) readRDS(paste0(path, "/", obj))
+  )
+
   # Generate object for the results
   n_row <- dim(output_dfs[[1]])[1]
   n_col <- dim(output_dfs[[1]])[2]
[…]

### 2022-01-15 Code/Main_Stitching.R
Increment

@@ -24,7 +24,7 @@ output_names <- map(
 summary_results <- map(
   .x = 1:length(sbfldr_paths),
   .f = function(p) {
-    if (grepl(pca, output_names[[p]], fixed = TRUE)) {
+    if (grepl('pca', output_names[[p]], fixed = TRUE)) {
       try(fpcr_simulation_stitch(path = sbfldr_paths[[p]]))
     } else {
       try(simulation_stitch(path = sbfldr_paths[[p]]))

### 2022-01-15 Presentation/slides.tex
push tables

@@
 \usepackage{microtype}
+\usepackage{adjustbox}
 \usepackage{graphicx}
@@
 
-	\begin{frame}{Simulation Results}
+	\begin{frame}{Recap: Trade Off between Bias and Variance}
+		\begin{figure}\notag
+			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
+		\end{figure}
+	\end{frame}
 
-		\begin{itemize}
+	\begin{frame}{Simulation Results - bspline}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{6.5cm}{%
+\begin{tabular}{lllllll}
+\cline{2-6}
+ & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+ & 2.13178119016857                        & {\color[HTML]{FD6864} 71.7099603226115} & 0.608171495504618                         & 1.53453412563582                        & 4                 &  \\
+ & 2.00756061672648                        & 71.9395214288329                        & 0.342736147598609                         & 1.29059813220677                        & 5                 &  \\
+ & {\color[HTML]{FD6864} 1.99374215191544} & 72.2563479644725                        & 0.245623228181924                         & 1.20138156565603                        & 6                 &  \\
+ & 2.03648199621352                        & 73.7857088138923                        & 0.279709073157873                         & 1.24948462939122                        & 7                 &  \\
+ & 2.18614795862507                        & 79.0485254545422                        & 0.104397806306425                         & 1.145842683177                          & 8                 &  \\
+ & 2.05113790304629                        & 74.1783834857012                        & 0.0355899940503619                        & {\color[HTML]{FD6864} 1.02172959116332} & 9                 &  \\
+ & 2.10522981230773                        & 76.1883552769234                        & 0.029691294210754                         & 1.03929073546751                        & 10                &  \\
+ & 2.1011969989178                         & 76.4030798206724                        & {\color[HTML]{FD6864} 0.0296057602994908} & 1.04246508005367                        & 11                &  \\
+ & 2.38150697658292                        & 86.1706579685565                        & 0.0369986801764011                        & 1.18191116948046                        & 12                &  \\
+ & 2.21136870222925                        & 80.6207607207599                        & 0.0363026864816967                        & 1.10242516644568                        & 13                &  \\
+ & 2.44947712911835                        & 87.6976578759761                        & 0.0380185616636571                        & 1.21257716080672                        & 14                &  \\
+ & 2.28870905624113                        & 83.4755186453129                        & 0.0315198808793299                        & 1.13630733462095                        & 15                &  \\
+ & 2.5490614406393                         & 93.593040512565                         & 0.0351718970102256                        & 1.26520057279256                        & 16                &  \\
+ & 2.55139454545527                        & 93.3074090320499                        & 0.0352440364348144                        & 1.26610962599564                        & 17                &  \\
+ & 2.75160520792553                        & 100.556190093422                        & 0.0380316879790874                        & 1.3620304183365                         & 18                &  \\
+ & 3.02429148497643                        & 109.987580398216                        & 0.0409879625688711                        & 1.4813467852555                         & 19                &  \\
+ & 3.42548075922108                        & 122.395980857659                        & 0.0471595536208038                        & 1.68537882583396                        & 20                &  \\
+ & 3.63355571510069                        & 132.077208928751                        & 0.0490939239286374                        & 1.7750377827367                         & 21                &  \\
+ & 5.93680459997264                        & 209.128064205703                        & 0.0779161032701813                        & 2.86105576687348                        & 22                &  \\
+ & 9.63325470698287                        & 339.676032195418                        & 0.126422677097386                         & 4.65363116820157                        & 23                &  \\
+ & 15.2728939666428                        & 545.827184915647                        & 0.200212312881423                         & 7.22652606521015                        & 24                &  \\
+ & 13.9781506322669                        & 495.957265678323                        & 0.184269309019229                         & 6.6968929082163                         & 25                & 
+\end{tabular}%
+}
+\end{table}
+	\end{frame}
 
-			\item {\color{green} add results here!}
-		\end{itemize}
+	\begin{frame}{Simulation Results - bspline}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{!}{%
+\begin{tabular}{lllllll}
+\cline{2-6}
+ & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+ & 2.02918344408687                       & {\color[HTML]{FD6864} 72.0085477229407} & 0.511999648510189                         & 1.47468049635309                         & 3                &  \\
+ & {\color[HTML]{FD6864} 2.0220366421201} & 72.60172284215                          & 0.16157756089415                          & 1.13746697354709                         & 5                &  \\
+ & 2.0354924731897                        & 73.1836346250812                        & 0.0293072016650537                        & {\color[HTML]{FD6864} 0.990682620987463} & 7                &  \\
+ & 2.06199840536677                       & 73.9631412481736                        & {\color[HTML]{FD6864} 0.0290190767234641} & 0.999385186246351                        & 9                &  \\
+ & 2.08808310984254                       & 75.0920660376146                        & 0.0290873388349217                        & 1.01393568534507                         & 11               &  \\
+ & 2.09974789215127                       & 75.9422236701681                        & 0.0294100223429063                        & 1.02909474969485                         & 13               &  \\
+ & 2.1086767501285                        & 76.7123085769457                        & 0.0298036585996321                        & 1.03713735705978                         & 15               &  \\
+ & 2.13013296583489                       & 77.4907530428231                        & 0.0300236821233963                        & 1.03980406503428                         & 17               &  \\
+ & 2.15348157839283                       & 78.3942553410957                        & 0.030307463717998                         & 1.0508902800978                          & 19               &  \\
+ & 2.17750745519215                       & 79.2057575714294                        & 0.0306501467540424                        & 1.06172373892826                         & 21               &  \\
+ & 2.20581113466118                       & 80.3800790338639                        & 0.0309985992677207                        & 1.07695651700849                         & 23               &  \\
+ & 2.23717951397715                       & 81.5089652049561                        & 0.0314869147262958                        & 1.09052842774153                         & 25               & 
+\end{tabular}%
+}
+\end{table}
 	\end{frame}

### 2022-01-15 Presentation/slides.tex
Slide Update

@@
 		\titlepage 
+		\begin{center}
+			{\small
+			Research Module in Econometrics and Statistics \\
+			Winter Semester 2021/2022}
+		\end{center}
 	\end{frame}
@@
 
-	%\begin{frame}{Theory}
-	%	Jonghun
-	%	\begin{itemize}
-	%		\item Random Functions (name square integrable functions)
-	%		\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
-	%		\item Use curves to predict a scalar response (show typical dgp)
-	%	\end{itemize}
-	%\end{frame}
-
-	%\begin{frame}{Theory}
-	%	Jonghun
-	%	\begin{itemize}
-	%		\item Basis expansions (b-splines and fourier)
-	%		\item Talk about purposes
-	%		\item Plots and show bias variance tradeoff
-	%	\end{itemize}
-	%\end{frame}
-
 	\begin{frame}{Random Function}
 		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
+		\vspace{0.2cm}
+
 		\begin{itemize}
@@
 
-	\begin{frame}{Two Typical Types of Basis Function}
-		\textbf{Fourier Basis Function} is an element of the set:
+	%\begin{frame}{Two Typical Types of Basis Function}
+	%	\textbf{Fourier Basis Function} is an element of the set:
+	%	
+	%	$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$
+	%	
+	%	%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
+	%	
+	%	\vspace{2\baselineskip}
+	%	\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\
 
-		$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$
+	%\end{frame}
 
-		%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
-
-		\vspace{2\baselineskip}
-		\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\
-
-	\end{frame}
-
-	\begin{frame}{Plots of Basis Functions}
+	\begin{frame}{Basis Functions}
+		\textbf{Fourier Basis Functions} are elements of the set:
+		$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup \{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$
+		\vspace{-0.5cm}
 		\begin{figure}
-			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
-			\caption {Fourier basis functions}
+			\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
+			%\caption {Fourier basis functions}
 		\end{figure}
@@
 
-	\begin{frame}{Plots of Basis Functions}
+	\begin{frame}{Basis Functions}
+		\textbf{B-spline Basis Functions} are polynomial functions defined by an order and a set of knots.
 		\begin{figure}
-			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
-			\caption {Bspline basis functions}
+			\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
+			%\caption {Bspline basis functions}
 		\end{figure}
@@
 						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
-						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  
+						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
 			\end{split}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
-		$$Z_{i,j} = \int_{0}^{1} x_i(s) \phi_j(s)\mathrm{d}s$$
-
-		\begin{itemize}
-			\item This allows us to write each observation in the data set as $\left(y_i, Z_{i,1}, Z_{i,2}, \dots \right)$
-			\item Truncating the functional basis yields an approximation $\left(y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\right)$
-		\end{itemize}
-
-		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$.
-	\end{frame}
-
-	\begin{frame}{Estimation via Basis Representation}
-		This can be translated into an estimated coefficient function $\hat{\beta}(t)$:
-
+		Truncating the functional basis allows us to estimate coefficients using \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
+		\vspace{-0.2cm}
 		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$
 
-		This is dependent on...
+		This is dependent on...\vspace{-0.2cm}
+		\begin{multicols}{2}
 			\begin{itemize}
 				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
-			\item The truncation parameter $L$
-			\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the expansion of the observations
-			\item The truncation parameter in the approximation of the observations $K$
+				\item The truncation parameter $L$\vfill\null
+				\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the observations
+				\item The truncation parameter for the observations $K$
 			\end{itemize}
+		\end{multicols}
+
 	\end{frame}
@@
 	\begin{frame}{FPCA - Plot}
-			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
 			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
@@
 
-	\begin{frame}{Simulation Results - bspline}
+	\begin{frame}{Simulation Results - Fourier}
 		\begin{table}
@@
 
-	\begin{frame}{Summary}
-		\begin{itemize}
-		\item
-    		Concepts of functional data: 
-    		\begin{itemize}
-			\item See dataset as smooth curve than as set of discrete measurements.
-    			\item Theory of Random Functions, motivated from random variable.
-    			\item Basis expansion and its Bias-Variance tradeoff.
-    			\item Scalar on Function Regression via Basis Expansion.
-    			\item Functional principal component Analysis and FPCR.
-		\end{itemize}
-    		\item
-    		Simulation study results: specification depends on function and signal-to-noise ratio
-    		\item
+	%\begin{frame}{Summary}
+	%	\begin{itemize}
+	%	\item
+    %		Concepts of functional data: 
+    %		\begin{itemize}
+	%		\item See dataset as smooth curve than as set of discrete measurements.
+    %			\item Theory of Random Functions, motivated from random variable.
+    %			\item Basis expansion and its Bias-Variance tradeoff.
+    %			\item Scalar on Function Regression via Basis Expansion.
+    %			\item Functional principal component Analysis and FPCR.
+	%	\end{itemize}
+    %		\item
+    %		Simulation study results: specification depends on function and signal-to-noise ratio
+    %		\item
     		% Guided you  from the beginning to the end of the presentaion through one application ....
-    		Guided through application to predict octane ratings.
+    %		Guided through application to predict octane ratings.
 
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}
-		\topskip0pt
-		\vspace*{\fill}
-		\begin{center}
-			{\LARGE Thank you for your time!}
-		\end{center}	
-		\vspace*{\fill}
-		%
-	\end{frame}
+	%	\end{itemize}
+	%\end{frame}
 
 	\begin{frame}{Further Reading}
-		 Further Reading:
+		\nocite{hsing_theoretical_2015}
+		\nocite{kokoszka_introduction_2017}
 		\nocite{Bohacs_Ovadi_Salgo1998}
@@
 		\nocite{Reiss_2007b}
+		\nocite{ramsay_functional_2005}
 		\AtNextBibliography{\tiny}

### 2022-01-15 Presentation/slides.tex
push presentation / results

--- 2022-01-14 Presentation/slides.tex
@@
 
-	\begin{frame}{Simulation Results}
+	\begin{frame}{Recap: Trade Off between Bias and Variance}
+		\begin{figure}\notag
+			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
+		\end{figure}
+	\end{frame}
 
+	\begin{frame}{Simulation - Interpretation of results}
 		\begin{itemize}
+		\item Basis expansion regression
+			\begin{itemize}
+    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vis versa.
+    			\item Setup with higher noise requires smoother function.
+    			\item Bsplines perform overall better.
+		\end{itemize}
+    		\item FPCR
+    			\begin{itemize}
+    				\item Two PC enough to explain variation.
+    				\item 
+    			\end{itemize}
 
-			\item {\color{green} add results here!}
 		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - bspline basis expansion}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{6.5cm}{%
+\begin{tabular}{lllllll}
+\cline{2-6}
+ & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+ & 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
+ & 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
+ & {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
+ & 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
+ & 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
+ & 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
+ & 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
+ & 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
+ & 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
+ & 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
+ & 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
+ & 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
+ & 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               &  \\
+ & 2.5514                        & 93.3074                      & 0.0352                        & 1.2661                        & 17               &  \\
+ & 2.7516                        & 100.5562                     & 0.038                         & 1.362                         & 18               &  \\
+ & 3.0243                        & 109.9876                     & 0.041                         & 1.4813                        & 19               &  \\
+ & 3.4255                        & 122.396                      & 0.0472                        & 1.6854                        & 20               & 
+\end{tabular}%
+}
+\end{table}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - fourier basis expansion}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{!}{%
+\begin{tabular}{lllllll}
+\cline{2-6}
+ & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+ & 0                            & 0                              & 0                            & 0                             & 1                &  \\
+ & 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
+ & {\color[HTML]{FE0000} 2.022} & 72.6017                        & 0.1616                       & 1.1375                        & 5                &  \\
+ & 2.0355                       & 73.1836                        & 0.0293                       & {\color[HTML]{FE0000} 0.9907} & 7                &  \\
+ & 2.062                        & 73.9631                        & {\color[HTML]{FE0000} 0.029} & 0.9994                        & 9                &  \\
+ & 2.0881                       & 75.0921                        & 0.0291                       & 1.0139                        & 11               &  \\
+ & 2.0997                       & 75.9422                        & 0.0294                       & 1.0291                        & 13               &  \\
+ & 2.1087                       & 76.7123                        & 0.0298                       & 1.0371                        & 15               &  \\
+ & 2.1301                       & 77.4908                        & 0.03                         & 1.0398                        & 17               &  \\
+ & 2.1535                       & 78.3943                        & 0.0303                       & 1.0509                        & 19               &  \\
+ & 2.1775                       & 79.2058                        & 0.0307                       & 1.0617                        & 21               &  \\
+ & 2.2058                       & 80.3801                        & 0.031                        & 1.077                         & 23               &  \\
+ & 2.2372                       & 81.509                         & 0.0315                       & 1.0905                        & 25               & 
+\end{tabular}%
+}
+\end{table}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - bspline FPCR ($n_{harm}$ = 2)}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{!}{%
+\begin{tabular}{llllllll}
+\cline{2-7}
+ & \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
+variance} & \textbf{n\_basis} &  \\ \cline{2-7}
+ & 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
+ & {\color[HTML]{FE0000} 2.345} & {\color[HTML]{FE0000} 10.585} & 0.8649                        & 1.5631                        & 0.9776           & 5                &  \\
+ & 2.4187                       & 10.6889                       & 0.8739                        & 1.5759                        & 0.9556           & 6                &  \\
+ & 2.4971                       & 10.7287                       & 0.8625                        & 1.5723                        & 0.9472           & 7                &  \\
+ & 2.5799                       & 10.6971                       & 0.8716                        & 1.575                         & 0.9239           & 8                &  \\
+ & 2.6828                       & 10.7669                       & 0.853                         & 1.5661                        & 0.9178           & 9                &  \\
+ & 2.825                        & 10.7906                       & 0.8304                        & 1.5622                        & 0.8976           & 10               &  \\
+ & 2.9082                       & 10.7774                       & {\color[HTML]{FE0000} 0.8237} & {\color[HTML]{FE0000} 1.5424} & 0.906            & 11               &  \\
+ & 2.9519                       & 10.8126                       & 0.8286                        & 1.5561                        & 0.9036           & 12               &  \\
+ & 2.9972                       & 10.8221                       & 0.8404                        & 1.5551                        & 0.9052           & 13               &  \\
+ & 2.9755                       & 10.7706                       & 0.8396                        & 1.5614                        & 0.9074           & 14               &  \\
+ & 2.9762                       & 10.7946                       & 0.8476                        & 1.557                         & 0.9058           & 15               &  \\
+ & 2.9627                       & 10.8067                       & 0.8609                        & 1.5615                        & 0.9061           & 16               &  \\
+ & 2.9621                       & 10.7707                       & 0.857                         & 1.5628                        & 0.906            & 17               &  \\
+ & 2.9929                       & 10.8315                       & 0.8536                        & 1.5632                        & 0.8935           & 18               &  \\
+ & 2.9576                       & 10.7894                       & 0.8676                        & 1.5656                        & 0.901            & 19               &  \\
+ & 2.9835                       & 10.8445                       & 0.8514                        & 1.5612                        & 0.8934           & 20               & 
+\end{tabular}%
+}
+\end{table}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - fourier FPCR ($n_{harm}$ = 2)}
+		\begin{table}
+		\centering
+\resizebox*{\columnwidth}{!}{%
+\begin{tabular}{llllllll}
+\cline{2-7}
+ & \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
+variance} & \textbf{n\_basis} &  \\ \cline{2-7}
+ & 0                             & 0                              & 0                             & 0                             & 0       & 1       &  \\
+ & {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
+ & 2.2148                        & 11.2567                        & {\color[HTML]{FE0000} 0.8227} & {\color[HTML]{FE0000} 1.5215} & 0.9584  & 5       &  \\
+ & 2.2635                        & 11.2662                        & 0.8828                        & 1.5563                        & 0.9489  & 7       &  \\
+ & 2.2721                        & 11.2692                        & 0.8811                        & 1.5531                        & 0.9439  & 9       &  \\
+ & 2.2797                        & 11.2574                        & 0.879                         & 1.555                         & 0.9397  & 11      &  \\
+ & 2.3039                        & 11.2708                        & 0.8887                        & 1.5591                        & 0.9421  & 13      &  \\
+ & 2.3248                        & 11.2898                        & 0.8743                        & 1.5514                        & 0.9283  & 15      &  \\
+ & 2.3798                        & 11.2957                        & 0.875                         & 1.5511                        & 0.9182  & 17      &  \\
+ & 2.4233                        & 11.3049                        & 0.8632                        & 1.5453                        & 0.9167  & 19      &  \\
+ & 2.4589                        & 11.3094                        & 0.8619                        & 1.5432                        & 0.9133  & 21      &  \\
+ & 2.5306                        & 11.331                         & 0.8562                        & 1.5408                        & 0.9082  & 23      &  \\
+ & 2.5752                        & 11.3272                        & 0.8531                        & 1.5393                        & 0.9062  & 25      & 
+\end{tabular}%
+}
+\end{table}
 	\end{frame}

### 2022-01-15 Code/Main_Simulation.R

@@ -119,3 +119,17 @@ for (i in 100:104) {
     file = paste0("Results/Partial/pca_fourier_NIR_partial/NIRrep500_n_obs60_seed", i, ".RDS")
   )
 }
+
+
+
+
+
+
+
+
+#######################
+
+pca_fourier_nharm2_sim
+write.csv(round(pca_bspline_nharm2_sim,4), "Results/Presentation_CSV/pca_bspline_nharm2_sim_round4.csv")
+
+

### 2022-01-15 Code/Main_Simulation.R
Increment

@@ -45,7 +45,9 @@ source("k_fold_CV_function.R")
 
 # Jakob 5x500
 for (i in 100:104) {
-  test_bspline_function <- bspline_function(rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE)
+  test_bspline_function <- bspline_function(
+    rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE
+  )
   saveRDS(
     object = test_bspline_function,
     file = paste0("Results/Partial/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS")
@@ -53,24 +55,35 @@ for (i in 100:104) {
 }
 
 # Jonghun 5x500
-test_fourier_function <- fourier_function(rep = 500, my_data = NULL, n_obs = 200, seed = 100, even_basis = TRUE, debug = TRUE)
-saveRDS(
-  object = test_fourier_function,
-  file = "Results/Partial/fourier_sim_partial/rep500_n_obs200_seed100.RDS"
-)
+for (i in 100:104) {
+  test_fourier_function <- fourier_function(
+    rep = 500, my_data = NULL, n_obs = 200, seed = i, 
+    even_basis = FALSE, debug = TRUE
+  )
+  saveRDS(
+    object = test_fourier_function,
+    file = paste0("Results/Partial/fourier_sim_partial/rep500_n_obs200_seed", i, ".RDS")
+  )
+}
 
 # Jona 5x500
-test_fpcr <- fpcr_function(rep = 500, my_data = NULL, n_obs = 200, nharm = 4, seed = 104, debug = TRUE)
-saveRDS(
-  object = test_fpcr,
-  file = "Results/Partial/pca_bspline_nharm4_sim_partial/rep500_n_obs200_seed104.RDS"
-)
+for (j in 2:4) {
+  for (i in 100:104) {
+    test_fpcr <- fpcr_function(
+      rep = 500, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE
+    )
+    saveRDS(
+      object = test_fpcr,
+      file = paste0("Results/Partial/pca_bspline_nharm", j, "_sim_partial/rep500_n_obs200_seed", i, ".RDS")
+    )
+  }
+}
 
 # Jakob 5x500
 for (j in 2:4) {
   for (i in 100:104) {
[…]

### 2022-01-15 Presentation/slides.tex
Meeting Slides

@@
 	\begin{frame}{Introduction}
-
+		\textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum
 		\begin{itemize}
-			\item \textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum (from 780 nm to 2500 nm)
-			\item Suited for field-monitoring / on-line analysis
-			\item Spectroscopy results in high-dimensional dataset.	
+			\item Spectroscopy results in high-dimensional dataset: Gasoline dataset (60 x 401)
 			\item This set of measurements serves as set of discretized approximations of smooth spectral curves
-			\item Regression to determine relationship between octane rating and spectral curves
 		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Theory}
-		A simple functional dataset is given by 
+		\vspace{0.1cm}
 		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \: i = 1,2,...,N, \; j = 1,2,..., J_i, \; t_{j,i} \in [T_1, T_2] \}$$
@@
 		\begin{itemize}
-			\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
-			\item Only observed at $x_{i}(t_{j,i})$
-			\item Example: Gasoline dataset (60 x 400)
-			\item Other Examples: Growth curves, financial data, human perception (pitch), ...
+			\item Continuous underlying process where $x_i(t)$ exists $\forall t \in [T_1, T_2]$ but is only observed at $x_{i}(t_{j,i})$
+			\item Regression to determine relationship between octane rating and spectral curves
+		\end{itemize}
 
-		\end{itemize}
 	\end{frame}
 
+	%\begin{frame}{Theory}
+	%	A simple functional dataset is given by 
+	%	
+	%	
+	%	\begin{itemize}
+	%		\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
+	%		\item Only observed at $x_{i}(t_{j,i})$
+	%		\item Example: Gasoline dataset (60 x 400)
+	%		\item Other Examples: Growth curves, financial data, human perception (pitch), ...
+	%	\end{itemize}
+	%\end{frame}
+
 	 \begin{frame}{Random Function}
-		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
+		A \textbf{Random Variable} is a function $X : \Omega \rightarrow
+		\mathcal{S}$ which is defined on a common probability space $(\Omega,
+		\mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a
+		$\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
 		\vspace{0.2cm}
@@
 			\item If $\mathcal{S} = \mathbb{R}$ then $X$ is a random variable
-			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random vector
-			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
+			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random
+			vector
+			\item If $\mathcal{S}$ is a space of functions, $X$ is called a
+			\textbf{Random Function}
 		\end{itemize}
+		\vspace{0.2cm}
+
+		A \textbf{Realization} of a random function $X(\omega)$ is a function 
+		$$x_0(t) = X(\omega_0)(t) \quad t \in \mathbb{E}, \: \omega_0 \in \Omega$$
 	\end{frame}
 
-	\begin{frame}{Random Function}
-		Let $\mathbb{E}$ be the index set and this can be described as
-		$${X = \{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
-		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
-		\begin{itemize}
-			\item It can be shortened to $X(t)$ by omitting $\omega$
-			\item The function is realized when the $X(t)$ exists $\forall t \in \mathbb{E}$
-		\end{itemize}
-	\end{frame}
+	%\begin{frame}{Random Function}
+	%	The realization of random function can be described as
+	%	$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
+	%	where $\mathbb{E}$ is the index set and $X(t, \cdot)$ is
+	%	$\mathcal{F}$-measurable function on the sample space $\Omega$.\\
+	%	\begin{itemize}
+	%		\item It can be shortened to $X(t)$ by omitting $\omega$ or I can
+	%		be written as $X(t)(\omega)$.
+	%		\item The function is realized when the $X(t)$ exists $\forall t
+	%		\in \mathbb{E}$.
+	%	\end{itemize}
+	%\end{frame}
 
@@
 			\begin{figure}
+
 				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
@@
 	\begin{frame}{Square Integrable Function}
-		If a function $f(t)$ satisfies
+		A function is called \textbf{Square Integrable} written $f(t) \in \mathbb{L}^{2}[0,1]$ if
 		$$\int_{0}^{1} \left(f(t)\right)^{2}dt < \infty$$
-		the function $f(t)$ is called \textbf{Square Integrable Function} written $f(t) \in \mathbb{L}^{2}[0,1]$.
+
 		\begin{itemize}
 			\item Without loss of generality, the interval is defined in $[0,1]$.
-			\item $\mathbb{L}^{2}$ is the set of all square integrable functions.
+		\end{itemize}
+		\vspace{0.2cm}
+
+		Let $f, g \in \mathbb{L}^{2}[0,1]$, then we can define inner product by
+		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
+
+		\begin{itemize}
+			\item Orthogonality of two different functions with $\langle f,g\rangle = 0$
 		\end{itemize}
@@
 	\begin{frame}{Square Integrable Function}
-		Let $f, g \in \mathbb{L}^{2}[0,1]$, then we can define inner product by
-		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
-		%, where $a$ and $b$ are scalars. (Maybe don't need)\\
-		%We can additionally define the inner product as follows:
-		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
-		%\begin{itemize}
-		%	\item
-		\begin{itemize}
-			\item Orthogonality of two different functions with $\langle f,g \rangle = 0$
-			\item Distance between functions
-		\end{itemize}
+		A natural \textbf{Norm} to be defined on $\mathbb{L}^2[0,1]$ is the following norm induced by the inner product.
+		$$\vert\vert f \vert\vert = \sqrt{\langle f,f \rangle} = \sqrt{\int_{0}^{1} f(t)^2 dt}$$
+		\vspace{0.2cm}
+
+		This norm naturally induces a \textbf{Distance} on $\mathbb{L}^2[0,1]$.
+		$$d(f,g) =  \vert\vert f - g \vert\vert= \sqrt{\langle f-g, f-g \rangle} = \sqrt{\int_{0}^{1} \left[f(t) - g(t)\right]^2 dt}$$
+
 	\end{frame}
 
-	%\begin{frame}{Stochastic Process Perspective}
-	%	Functional data are the sample curves observed from continuous time stochastic precess.\\
-	%	\begin{itemize}
-	%		\item From this perspective, $X(t)$ is a random variable (?)\\
-	%		\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
-	%		\item Realizations of a random function belong in large collection of functions
-	%	\end{itemize}		
-	%\end{frame}
+	\begin{frame}{Basis Expansion}
+		\textbf{Basis Expansion} is a linear combination of functions as
+		described:
 
-	\begin{frame}{Basis Expansion}
-		\textbf{Basis Expansion} is a linear combination of functions as described:
+		$$x_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx
+		\sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in
+		\mathbb{E}$$
 
-		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$
-
-		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
+		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion
+		and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$
+		to:
 		\vspace{0.2cm}
@@
 			\item make the function smoother
-			\item replace the original curves $X_{i}(t)$ by a smaller collection of $c_{nm}$
-			%\item replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
+			\item replace the original curves $x_{i}(t)$ with a smaller
+			collection of $c_{nm}$
 		\end{itemize}     
@@
 
-	%\begin{frame}{Two Typical Types of Basis Function}
-	%	\textbf{Fourier Basis Function} is an element of the set:
-	%	
-	%	$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$
-	%	
-	%	%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
-	%	
-	%	\vspace{2\baselineskip}
-	%	\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\
-
-	%\end{frame}
-
 	\begin{frame}{Basis Functions}
 		\textbf{Fourier Basis Functions} are elements of the set:
-		$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup \{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$
+		$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup
+		\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$
 		\vspace{-0.5cm}
 		\begin{figure}
-			\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
+			\includegraphics[width =
+			\textwidth]{../Graphics/Fourier_Basis.pdf}
 			%\caption {Fourier basis functions}
@@
 	\begin{frame}{Basis Functions}
-		\textbf{B-spline Basis Functions} are polynomial functions defined by an order and a set of knots.
+		\textbf{B-spline Basis Functions} are polynomial functions defined by
+		an order and a set of knots.
 		\begin{figure}
-			\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
+			\includegraphics[width =
+			\textwidth]{../Graphics/Bspline_Basis.pdf}
 			%\caption {Bspline basis functions}
@@
 
-		$$\textbf{MSE}[\hat{X}(t)] = \textbf{Bias}^2[\hat{X}(t)] + \textbf{Var}[\hat{X}(t)]$$
+		$$\textbf{MSE}[\hat{X}(t)] = \textbf{Bias}^2[\hat{X}(t)] +
+		\textbf{Var}[\hat{X}(t)]$$
 
-		$$\textbf{MISE}[\hat{X}] = \int_{0}^{1} \textbf{MSE}[\hat{X}(t)] dt$$
+		$$\textbf{IMSE}[\hat{X}] = \int_{0}^{1} \textbf{MSE}[\hat{X}(t)] dt$$
 
 		\begin{itemize}
-			\item The larger $K$, the better fit to the data, but also more fitting noise
+			\item The larger $K$, the better the fit to the data, but also more fitting noise
 			\item If $K$ is too small, the expansion would miss some significant information
@@
 		\begin{figure}\notag
-			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
+			\includegraphics[width =
+			\textwidth]{../Graphics/basis_expansions.pdf}
 		\end{figure}
@@
 		\end{itemize}
-		\vspace{0.3cm}
+		\vspace{0.7cm}
 
-		Let $\{\phi_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$ leading to the following representation of $\beta(t)$
+		Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis leading to the following representation
 
-		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j \phi_j(t)$$
-		%Assume that we have a data set containing observations each of which is made up of:
-		%\begin{itemize}
-		%	\item $y_i$: a scalar realization of $Y(\omega)$ - the octane rating of gasoline
-		%	\item $x_i(t)$: a realization of $X(\omega)$ - the measured NIR spectrum
-		%\end{itemize}
+		$$\beta(t) = \sum_{j \in \mathcal{I}} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j \phi_j(t)$$
 
@@
 			\begin{split}
-				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
-						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
+				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+						  & = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
+						  & = \alpha + \sum_{j \in \mathcal{I}} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
 			\end{split}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Truncating the functional basis allows us to estimate coefficients using \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
+		Truncating the functional basis allows us to estimate coefficients using \textbf{Multivariate Regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
 		\vspace{-0.2cm}
@@
 	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}\label{KLE}
-		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
+		A random function $X(\omega)$ can be expressed in terms of its \textbf{Mean Function} and its \textbf{Eigenfunctions}:
 		$$X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$
 
-		Where the $\xi_j$ are scalar-valued random variables with the following properties.
+		Where the $\xi_j$ are \textbf{Scalar-Valued Random Variables} with the following properties.
 		\begin{multicols}{2}
@@
 
-	\begin{frame}{FPCA - Plot}
-			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
-	\end{frame}
-
 	\begin{frame}{Simulation Setup}
-		\begin{itemize}
-			\item Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
-			\item Generate \textbf{similar curves} from gasoline dataset:
-		\end{itemize}
+		Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to generate \textbf{Similar Curves}:
 
 		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$ 
+		\vspace{0.2cm}
 
@@
 			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
-			\item Simplification: the $\xi_{j}$ do not follow a normal
-			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
+			\item Simplification: the $\xi_{j}$ do not follow a normal distribution
+			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$
 		\end{itemize}
@@
 	\begin{frame}{Simulation Setup cont.}
-		Let 
 		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
@@
 
-		where $Z \sim \mathcal{N}(0,1)$ be two responses for $f \in \{f_1(t), f_2(t)\}$.	
+		Let these be two responses for $f \in \{f_1(t), f_2(t)\}$ with $Z \sim \mathcal{N}(0,1)$.	
+		\vspace{0.2cm}
+
 		\begin{itemize}
-    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (4,5,...,25)$ and fourier functions $(1,3,...,25)$ to perform regression using basis expansion and the FPCR approach.
-			\item Compare results via criteria (CV, Mallows CP,...)
+    		\item Four combinations with different number of cubic basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
+			\item Compare results via criteria (CV, Mallows CP, ...)
 
@@
 
-	\begin{frame}{Recap: Trade Off between Bias and Variance}
-		\begin{figure}\notag
-			\includegraphics[width = \textwidth]{../Graphics/basis_expansions.pdf}
-		\end{figure}
-	\end{frame}
+	\begin{frame}{Simulation - Interpretation of results}\label{Results}
+		\textbf{Basis Expansion Regression}
+		\begin{itemize}
+    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vice versa
+    			\item Setup with higher noise requires smoother function.
+    			\item  Bspline setup performs overall a bit better.
+		\end{itemize}
 
-	\begin{frame}{Simulation - Interpretation of results}
-		\begin{itemize}
-		\item Basis expansion regression
-			\begin{itemize}
-    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vis versa.
-    			\item Setup with higher noise requires smoother function.
-    			\item Bsplines perform overall better.
-		\end{itemize}
-    		\item FPCR
+		\textbf{FPCR}
     	\begin{itemize}
     		\item Two PC enough to explain variation.
-    				\item 
+    		\item Results quite similar, but bspline setup better for smooth function with noisy response.
     	\end{itemize}
 
-		\end{itemize}
-	\end{frame}
+    	Overall, fourier setup has lower complexity.
 
-	\begin{frame}{Simulation Results - bspline basis expansion}
-		\begin{table}
-		\centering
-\resizebox*{\columnwidth}{6.5cm}{%
-\begin{tabular}{lllllll}
-\cline{2-6}
- & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
- & 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
- & 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
- & {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
- & 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
- & 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
- & 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
- & 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
- & 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
- & 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
- & 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
- & 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
- & 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
- & 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               &  \\
- & 2.5514                        & 93.3074                      & 0.0352                        & 1.2661                        & 17               &  \\
- & 2.7516                        & 100.5562                     & 0.038                         & 1.362                         & 18               &  \\
- & 3.0243                        & 109.9876                     & 0.041                         & 1.4813                        & 19               &  \\
- & 3.4255                        & 122.396                      & 0.0472                        & 1.6854                        & 20               & 
-\end{tabular}%
-}
-\end{table}
-	\end{frame}
-
-	\begin{frame}{Simulation Results - fourier basis expansion}
-		\begin{table}
-		\centering
-\resizebox*{\columnwidth}{!}{%
-\begin{tabular}{lllllll}
-\cline{2-6}
- & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
- & 0                            & 0                              & 0                            & 0                             & 1                &  \\
- & 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
- & {\color[HTML]{FE0000} 2.022} & 72.6017                        & 0.1616                       & 1.1375                        & 5                &  \\
- & 2.0355                       & 73.1836                        & 0.0293                       & {\color[HTML]{FE0000} 0.9907} & 7                &  \\
- & 2.062                        & 73.9631                        & {\color[HTML]{FE0000} 0.029} & 0.9994                        & 9                &  \\
- & 2.0881                       & 75.0921                        & 0.0291                       & 1.0139                        & 11               &  \\
- & 2.0997                       & 75.9422                        & 0.0294                       & 1.0291                        & 13               &  \\
- & 2.1087                       & 76.7123                        & 0.0298                       & 1.0371                        & 15               &  \\
- & 2.1301                       & 77.4908                        & 0.03                         & 1.0398                        & 17               &  \\
- & 2.1535                       & 78.3943                        & 0.0303                       & 1.0509                        & 19               &  \\
- & 2.1775                       & 79.2058                        & 0.0307                       & 1.0617                        & 21               &  \\
- & 2.2058                       & 80.3801                        & 0.031                        & 1.077                         & 23               &  \\
- & 2.2372                       & 81.509                         & 0.0315                       & 1.0905                        & 25               & 
-\end{tabular}%
-}
-\end{table}
-	\end{frame}
-
-	\begin{frame}{Simulation Results - bspline FPCR ($n_{harm}$ = 2)}
-		\begin{table}
-		\centering
-\resizebox*{\columnwidth}{!}{%
-\begin{tabular}{llllllll}
-\cline{2-7}
- & \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
-variance} & \textbf{n\_basis} &  \\ \cline{2-7}
- & 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
- & {\color[HTML]{FE0000} 2.345} & {\color[HTML]{FE0000} 10.585} & 0.8649                        & 1.5631                        & 0.9776           & 5                &  \\
- & 2.4187                       & 10.6889                       & 0.8739                        & 1.5759                        & 0.9556           & 6                &  \\
- & 2.4971                       & 10.7287                       & 0.8625                        & 1.5723                        & 0.9472           & 7                &  \\
- & 2.5799                       & 10.6971                       & 0.8716                        & 1.575                         & 0.9239           & 8                &  \\
- & 2.6828                       & 10.7669                       & 0.853                         & 1.5661                        & 0.9178           & 9                &  \\
- & 2.825                        & 10.7906                       & 0.8304                        & 1.5622                        & 0.8976           & 10               &  \\
- & 2.9082                       & 10.7774                       & {\color[HTML]{FE0000} 0.8237} & {\color[HTML]{FE0000} 1.5424} & 0.906            & 11               &  \\
- & 2.9519                       & 10.8126                       & 0.8286                        & 1.5561                        & 0.9036           & 12               &  \\
- & 2.9972                       & 10.8221                       & 0.8404                        & 1.5551                        & 0.9052           & 13               &  \\
- & 2.9755                       & 10.7706                       & 0.8396                        & 1.5614                        & 0.9074           & 14               &  \\
- & 2.9762                       & 10.7946                       & 0.8476                        & 1.557                         & 0.9058           & 15               &  \\
- & 2.9627                       & 10.8067                       & 0.8609                        & 1.5615                        & 0.9061           & 16               &  \\
- & 2.9621                       & 10.7707                       & 0.857                         & 1.5628                        & 0.906            & 17               &  \\
- & 2.9929                       & 10.8315                       & 0.8536                        & 1.5632                        & 0.8935           & 18               &  \\
- & 2.9576                       & 10.7894                       & 0.8676                        & 1.5656                        & 0.901            & 19               &  \\
- & 2.9835                       & 10.8445                       & 0.8514                        & 1.5612                        & 0.8934           & 20               & 
-\end{tabular}%
-}
-\end{table}
-	\end{frame}
-
-	\begin{frame}{Simulation Results - fourier FPCR ($n_{harm}$ = 2)}
-		\begin{table}
-		\centering
-\resizebox*{\columnwidth}{!}{%
-\begin{tabular}{llllllll}
-\cline{2-7}
- & \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
-variance} & \textbf{n\_basis} &  \\ \cline{2-7}
- & 0                             & 0                              & 0                             & 0                             & 0       & 1       &  \\
- & {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
- & 2.2148                        & 11.2567                        & {\color[HTML]{FE0000} 0.8227} & {\color[HTML]{FE0000} 1.5215} & 0.9584  & 5       &  \\
- & 2.2635                        & 11.2662                        & 0.8828                        & 1.5563                        & 0.9489  & 7       &  \\
- & 2.2721                        & 11.2692                        & 0.8811                        & 1.5531                        & 0.9439  & 9       &  \\
- & 2.2797                        & 11.2574                        & 0.879                         & 1.555                         & 0.9397  & 11      &  \\
- & 2.3039                        & 11.2708                        & 0.8887                        & 1.5591                        & 0.9421  & 13      &  \\
- & 2.3248                        & 11.2898                        & 0.8743                        & 1.5514                        & 0.9283  & 15      &  \\
- & 2.3798                        & 11.2957                        & 0.875                         & 1.5511                        & 0.9182  & 17      &  \\
- & 2.4233                        & 11.3049                        & 0.8632                        & 1.5453                        & 0.9167  & 19      &  \\
- & 2.4589                        & 11.3094                        & 0.8619                        & 1.5432                        & 0.9133  & 21      &  \\
- & 2.5306                        & 11.331                         & 0.8562                        & 1.5408                        & 0.9082  & 23      &  \\
- & 2.5752                        & 11.3272                        & 0.8531                        & 1.5393                        & 0.9062  & 25      & 
-\end{tabular}%
-}
-\end{table}
+    	\hyperlink{Simulation}{\beamergotobutton{Basis Expansion Results}}
+    	\hyperlink{Simulation2}{\beamergotobutton{FPCR Results}}
 	\end{frame}
@@
 		\begin{itemize}
-		\item
-    		Use insights from the simulation study to uncover dependence.
-    		\item
-    		Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
-    		\item
-    		Validation set approach:	Scores of test data needs to be estimated by the training data. 
-    		\item
-    		Report results by MSE scaled by variance.
+			\item Use insights from the simulation study to uncover dependence.
+			\item Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
+			\item Validation set approach:	Scores of test data needs to be estimated by the training data. 
+			\item Report results by MSE scaled by variance.
 		\end{itemize}
@@
 	\end{frame}
+
+	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}
+		\begin{table}
+			\centering
+			\resizebox*{\columnwidth}{!}{%
+				\begin{tabular}{lllllll}
+					\cline{2-6}
+					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
+					& 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
+					& {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
+					& 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
+					& 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
+					& 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
+					& 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
+					& 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
+					& 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
+					& 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
+					& 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
+					& 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
+					& 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               
+				\end{tabular}%
+			}
+		\end{table}
+		\hyperlink{Results}{\beamergotobutton{Results}}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - fourier basis expansion}
+		\begin{table}
+			\centering
+			\resizebox*{\columnwidth}{!}{%
+				\begin{tabular}{lllllll}
+					\cline{2-6}
+					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+					& 0                            & 0                              & 0                            & 0                             & 1                &  \\
+					& 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
+					& {\color[HTML]{FE0000} 2.022} & 72.6017                        & 0.1616                       & 1.1375                        & 5                &  \\
+					& 2.0355                       & 73.1836                        & 0.0293                       & {\color[HTML]{FE0000} 0.9907} & 7                &  \\
+					& 2.062                        & 73.9631                        & {\color[HTML]{FE0000} 0.029} & 0.9994                        & 9                &  \\
+					& 2.0881                       & 75.0921                        & 0.0291                       & 1.0139                        & 11               &  \\
+					& 2.0997                       & 75.9422                        & 0.0294                       & 1.0291                        & 13               &  \\
+					& 2.1087                       & 76.7123                        & 0.0298                       & 1.0371                        & 15               &  \\
+					& 2.1301                       & 77.4908                        & 0.03                         & 1.0398                        & 17               &  \\
+					& 2.1535                       & 78.3943                        & 0.0303                       & 1.0509                        & 19               &  \\
+					& 2.1775                       & 79.2058                        & 0.0307                       & 1.0617                        & 21               &  \\
+					& 2.2058                       & 80.3801                        & 0.031                        & 1.077                         & 23               &  \\
+					& 2.2372                       & 81.509                         & 0.0315                       & 1.0905                        & 25               & 
+				\end{tabular}%
+			}
+		\end{table}
+		\hyperlink{Results}{\beamergotobutton{Results}}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - bspline FPCR ($n_{harm}$ = 2)}\label{Simulation2}
+		\begin{table}
+			\centering
+			\resizebox*{\columnwidth}{!}{%
+				\begin{tabular}{llllllll}
+					\cline{2-7}
+					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
+variance} & \textbf{n\_basis} &  \\ \cline{2-7}
+					& 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
+					& {\color[HTML]{FE0000} 2.345} & {\color[HTML]{FE0000} 10.585} & 0.8649                        & 1.5631                        & 0.9776           & 5                &  \\
+					& 2.4187                       & 10.6889                       & 0.8739                        & 1.5759                        & 0.9556           & 6                &  \\
+					& 2.4971                       & 10.7287                       & 0.8625                        & 1.5723                        & 0.9472           & 7                &  \\
+					& 2.5799                       & 10.6971                       & 0.8716                        & 1.575                         & 0.9239           & 8                &  \\
+					& 2.6828                       & 10.7669                       & 0.853                         & 1.5661                        & 0.9178           & 9                &  \\
+					& 2.825                        & 10.7906                       & 0.8304                        & 1.5622                        & 0.8976           & 10               &  \\
+					& 2.9082                       & 10.7774                       & {\color[HTML]{FE0000} 0.8237} & {\color[HTML]{FE0000} 1.5424} & 0.906            & 11               &  \\
+					& 2.9519                       & 10.8126                       & 0.8286                        & 1.5561                        & 0.9036           & 12               &  \\
+					& 2.9972                       & 10.8221                       & 0.8404                        & 1.5551                        & 0.9052           & 13               &  \\
+					& 2.9755                       & 10.7706                       & 0.8396                        & 1.5614                        & 0.9074           & 14               &  \\
+					& 2.9762                       & 10.7946                       & 0.8476                        & 1.557                         & 0.9058           & 15               &  \\
+					& 2.9627                       & 10.8067                       & 0.8609                        & 1.5615                        & 0.9061           & 16          
+				\end{tabular}%
+			}
+		\end{table}
+		\hyperlink{Results}{\beamergotobutton{Results}}
+	\end{frame}
+
+	\begin{frame}{Simulation Results - fourier FPCR ($n_{harm}$ = 2)}
+		\begin{table}
+			\centering
+			\resizebox*{\columnwidth}{!}{%
+				\begin{tabular}{llllllll}
+					\cline{2-7}
+					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
+variance} & \textbf{n\_basis} &  \\ \cline{2-7}
+					& 0                             & 0                              & 0                             & 0                             & 0       & 1       &  \\
+					& {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
+					& 2.2148                        & 11.2567                        & {\color[HTML]{FE0000} 0.8227} & {\color[HTML]{FE0000} 1.5215} & 0.9584  & 5       &  \\
+					& 2.2635                        & 11.2662                        & 0.8828                        & 1.5563                        & 0.9489  & 7       &  \\
+					& 2.2721                        & 11.2692                        & 0.8811                        & 1.5531                        & 0.9439  & 9       &  \\
+					& 2.2797                        & 11.2574                        & 0.879                         & 1.555                         & 0.9397  & 11      &  \\
+					& 2.3039                        & 11.2708                        & 0.8887                        & 1.5591                        & 0.9421  & 13      &  \\
+					& 2.3248                        & 11.2898                        & 0.8743                        & 1.5514                        & 0.9283  & 15      &  \\
+					& 2.3798                        & 11.2957                        & 0.875                         & 1.5511                        & 0.9182  & 17      &  \\
+					& 2.4233                        & 11.3049                        & 0.8632                        & 1.5453                        & 0.9167  & 19      &  \\
+					& 2.4589                        & 11.3094                        & 0.8619                        & 1.5432                        & 0.9133  & 21      &  \\
+					& 2.5306                        & 11.331                         & 0.8562                        & 1.5408                        & 0.9082  & 23      &  \\
+					& 2.5752                        & 11.3272                        & 0.8531                        & 1.5393                        & 0.9062  & 25      & 
+				\end{tabular}%
+			}
+		\end{table}
+		\hyperlink{Results}{\beamergotobutton{Results}}
+	\end{frame}
 \end{document}

### 2022-01-15 Presentation/slides.tex
Slides - Meeting

@@
 
-	% I'm not really a fan of a table of contents in short presentations (Jakob)
-	% Outline frame
-	%\begin{frame}{Outline}
-	%	\tableofcontents
-	%\end{frame}
-
 	\begin{frame}{Introduction}
@@
 		\begin{itemize}
-			\item Continuous underlying process where $x_i(t)$ exists $\forall t \in [T_1, T_2]$ but is only observed at $x_{i}(t_{j,i})$
+			\item Continuous underlying process where $x_i(t)$ exists $\forall t \in [T_1, T_2]$ but is only observed at $t_{j,i}$
 			\item Regression to determine relationship between octane rating and spectral curves
@@
 	\end{frame}
-
-	%\begin{frame}{Theory}
-	%	A simple functional dataset is given by 
-	%	
-	%	
-	%	\begin{itemize}
-	%		\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
-	%		\item Only observed at $x_{i}(t_{j,i})$
-	%		\item Example: Gasoline dataset (60 x 400)
-	%		\item Other Examples: Growth curves, financial data, human perception (pitch), ...
-	%	\end{itemize}
-	%\end{frame}
 
@@
 	\end{frame}
-
-	%\begin{frame}{Random Function}
-	%	The realization of random function can be described as
-	%	$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
-	%	where $\mathbb{E}$ is the index set and $X(t, \cdot)$ is
-	%	$\mathcal{F}$-measurable function on the sample space $\Omega$.\\
-	%	\begin{itemize}
-	%		\item It can be shortened to $X(t)$ by omitting $\omega$ or I can
-	%		be written as $X(t)(\omega)$.
-	%		\item The function is realized when the $X(t)$ exists $\forall t
-	%		\in \mathbb{E}$.
-	%	\end{itemize}
-	%\end{frame}
 
@@
 
-		$$x_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx
-		\sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in
+		$$x_{i}(t) = \sum_{j \in \mathcal{I}} c_{i,j}\phi_{j}(t) \approx
+		\sum_{j=1}^{L} c_{i, j}\phi_{j}(t), \quad i = 1, \dots, n, \quad \forall t \in
 		\mathbb{E}$$
 
-		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion
-		and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$
+		where $\phi_{j}(t)$ is the $j^{th}$ basis function of the expansion
+		and $c_{i, j}$ is the corresponding coefficient. We truncate the basis at $L$
 		to:
@@
 			\item replace the original curves $x_{i}(t)$ with a smaller
-			collection of $c_{nm}$
+			collection of $c_{n, m}$
 		\end{itemize}     
@@
 	\begin{frame}{Basis Functions}
-		\textbf{B-spline Basis Functions} are polynomial functions defined by
+		\textbf{B-spline Basis Functions} are piece-wise polynomial functions defined by
 		an order and a set of knots.
@@
 	\begin{frame}{Trade Off between Bias and Variance}
-		How do we choose the number $K$ of basis functions?
+		How do we choose the number $L$ of basis functions?
 
@@
 		\begin{itemize}
-			\item The larger $K$, the better the fit to the data, but also more fitting noise
-			\item If $K$ is too small, the expansion would miss some significant information
+			\item The larger $L$, the better the fit to the data, but also more fitting noise
+			\item If $L$ is too small, the expansion would miss some significant information
 		\end{itemize}
@@
 	\begin{frame}{Estimation via Basis Representation}
-		Truncating the functional basis allows us to estimate coefficients using \textbf{Multivariate Regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
+		Truncating the functional basis allows us to estimate coefficients using \textbf{Multivariate Regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an estimated coefficient function $\hat{\beta}_L(t)$:
 		\vspace{-0.2cm}
@@
 				\item The truncation parameter $L$\vfill\null
-				\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the observations
+				\item The basis $(\psi_j(t))_{j \in \mathcal{L}}$ used for the observations
 				\item The truncation parameter for the observations $K$
@@
 		\begin{itemize}
-    		\item Four combinations with different number of cubic basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
+    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
 			\item Compare results via criteria (CV, Mallows CP, ...)
@@
 
-	\begin{frame}{Simulation - Interpretation of results}\label{Results}
+	\begin{frame}{Simulation - Interpretation of Results}\label{Results}
 		\textbf{Basis Expansion Regression}
@@
 
-	\begin{frame}{Application setup}
+	\begin{frame}{Application Setup}
 		\begin{itemize}
@@
 	\end{frame}
-
-	%\begin{frame}{Summary}
-	%	\begin{itemize}
-	%	\item
-    %		Concepts of functional data: 
-    %		\begin{itemize}
-	%		\item See dataset as smooth curve than as set of discrete measurements.
-    %			\item Theory of Random Functions, motivated from random variable.
-    %			\item Basis expansion and its Bias-Variance tradeoff.
-    %			\item Scalar on Function Regression via Basis Expansion.
-    %			\item Functional principal component Analysis and FPCR.
-	%	\end{itemize}
-    %		\item
-    %		Simulation study results: specification depends on function and signal-to-noise ratio
-    %		\item
-    		% Guided you  from the beginning to the end of the presentaion through one application ....
-    %		Guided through application to predict octane ratings.
-
-	%	\end{itemize}
-	%\end{frame}
 

### 2022-01-16 main.tex
update
Added fancy equation to main document

@@
 
+\newcommand{\independent}{\perp\!\!\!\!\perp}
+
 \addbibresource{RMbibliography.bib}
@@
 \begin{document}
-	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}}
+	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}}
 	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
-	\date{{\color{red}whenever}}
+	\date{11.02.2022}
 	\maketitle
@@
 		\begin{split}
-			Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
-			& = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{\langle F(\omega), b_j \rangle} + \epsilon(\omega) 
-			  = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
+			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{\langle X(\omega), \phi_j \rangle} + \epsilon(\omega) 
+		      = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
 		\end{split}
@@
 			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} \psi_j Z_j(\omega) + \epsilon(\omega)
+	\end{equation}
+
+	{\color{red} This fancy equation will be very useful to explain our simulation.}
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
+			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
+			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}(\omega)} \right] + \epsilon(\omega)	
+		\end{split}
 	\end{equation}
@@
 		\begin{itemize}
-			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
+			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j}\independent \tilde{\xi}_{k}$ for $j \neq k$
 			\item Simplification: the $\xi_{j}$ do not follow a normal
@@
 {\color{green} Information about version and link to repo / package in footnote??}
+
+	\subsection{Put in appendix - Simulation setup cont.}
+
+	The
 

### 2022-01-16 Presentation/slides.tex
Additional Aux Slide

@@
 
-	\begin{frame}{Estimation via Basis Representation}
+	\begin{frame}{Estimation via Basis Representation}\label{ReducedEq}
 		We can transform the data generating process into:
@@
 		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
+
+		\hyperlink{FullEq}{\beamergotobutton{Equation with Approximated Functions}}
 	\end{frame}
@@
 		\end{multicols}
-
 	\end{frame}
@@
 
+	\begin{frame}{Estimation with Approximated Functions}\label{FullEq}
+		{\small
+		\begin{equation}\notag
+			\begin{split}
+				Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
+				& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+				& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) \\
+				& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
+				& \approx \alpha + \sum_{j = 1}^{L} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
+				= \alpha + \sum_{j = 1}^{L} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
+			\end{split}
+		\end{equation}}
+		\hyperlink{ReducedEq}{\beamergotobutton{Equation without Approximated Functions}}
+	\end{frame}
+
 	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}

### 2022-01-16 main.tex
Correction
Additional Aux Slide

@@
 	\begin{equation}
-			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} \psi_j Z_j(\omega) + \epsilon(\omega)
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} c_j Z_j(\omega) + \epsilon(\omega)
 	\end{equation}
@@
 			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
-			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}(\omega)} \right] + \epsilon(\omega)	
+			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
 		\end{split}

### 2022-01-16 Presentation/slides.tex
push presentation changes

@@
 		\begin{itemize}
-    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
-			\item Compare results via criteria (CV, Mallows CP, ...)
+    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach
+			\item Compare results via criteria (CV, Mallows' CP, ...)
 
@@
 		\begin{itemize}
-    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vice versa
-    			\item Setup with higher noise requires smoother function.
-    			\item  Bspline setup performs overall a bit better.
+    			\item Smooth function requires smaller number of $n_{basis}$ and vice versa
+    			\item Setup with higher noise requires smoother function
+
+    			%\item  Bspline setup performs overall a bit better.
 		\end{itemize}
 
-		\textbf{FPCR}
+		Performs better on bumpy function with low noise.\\
+	\vspace{0.4cm}
+		\textbf{Functional Principal Component Regression}
     	\begin{itemize}
-    		\item Two PC enough to explain variation.
-    		\item Results quite similar, but bspline setup better for smooth function with noisy response.
+    		\item Two Functional-PC enough to explain variation
+    		\item Results quite similar, but bspline setup better for smooth function with noisy response
+
     	\end{itemize}
 
-    	Overall, fourier setup has lower complexity.
+    	Performs better in the noisy setup with the smooth function.\\
+    	\vspace{0.4cm}
 
@@
 	\begin{frame}{Application Setup}
+	Use insights from the simulation study to \textbf{predict the Octane Ratings}.
+	\vspace{0.4cm}
 		\begin{itemize}
-			\item Use insights from the simulation study to uncover dependence.
-			\item Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
-			\item Validation set approach:	Scores of test data needs to be estimated by the training data. 
-			\item Report results by MSE scaled by variance.
+			\item Similar setup, but relying on the initial 60 spectral curves
+			\item Validation set approach:	Scores of test data needs to be estimated by the training data
+			\item Report results by \textbf{IMSE} for the evaluated best model specifications
 		\end{itemize}
@@
 			\centering
-			\resizebox*{\columnwidth}{!}{%
+			\resizebox*{8cm}{!}{%
 				\begin{tabular}{lllllll}
 					\cline{2-6}
-					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
+					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}
 					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
@@
 
-	\begin{frame}{Simulation Results - fourier basis expansion}
+	\begin{frame}{Simulation Results - Fourier basis expansion}
 		\begin{table}
 			\centering
-			\resizebox*{\columnwidth}{!}{%
+			\resizebox*{8cm}{!}{%
 				\begin{tabular}{lllllll}
 					\cline{2-6}
-					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
-					& 0                            & 0                              & 0                            & 0                             & 1                &  \\
+					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}
+
 					& 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
@@
 
-	\begin{frame}{Simulation Results - bspline FPCR ($n_{harm}$ = 2)}\label{Simulation2}
+	\begin{frame}{Simulation Results - Bspline FPCR ($n_{harm}$ = 2)}\label{Simulation2}
 		\begin{table}
 			\centering
-			\resizebox*{\columnwidth}{!}{%
+			\resizebox*{9cm}{!}{%
 				\begin{tabular}{llllllll}
 					\cline{2-7}
-					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
-variance} & \textbf{n\_basis} &  \\ \cline{2-7}
+					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}                & \textbf{expl.
+var} & \textbf{n\_basis} &  \\ \cline{2-7}
 					& 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
@@
 
-	\begin{frame}{Simulation Results - fourier FPCR ($n_{harm}$ = 2)}
+	\begin{frame}{Simulation Results - Fourier FPCR ($n_{harm}$ = 2)}
 		\begin{table}
 			\centering
-			\resizebox*{\columnwidth}{!}{%
+			\resizebox*{9cm}{!}{%
 				\begin{tabular}{llllllll}
 					\cline{2-7}
-					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl.
-variance} & \textbf{n\_basis} &  \\ \cline{2-7}
-					& 0                             & 0                              & 0                             & 0                             & 0       & 1       &  \\
+					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}                & \textbf{expl.
+var} & \textbf{n\_basis} &  \\ \cline{2-7}
+
 					& {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
@@
 		\end{table}
+		\vspace{0.2cm}
 		\hyperlink{Results}{\beamergotobutton{Results}}

### 2022-01-16 Presentation/slides.tex
Small change
Presentation

@@
 
- \newcommand{\independent}{\perp\!\!\!\!\perp}
-
 % Title page details: 
@@
 		\end{itemize}
-		\vspace{0.1cm}
-		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \: i = 1,2,...,N, \; j = 1,2,..., J_i, \; t_{j,i} \in [T_1, T_2] \}$$
+		\vspace{0.2cm}
+		$$x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]$$
 
@@
 		\mathcal{S}$ which is defined on a common probability space $(\Omega,
-		\mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a
+		\mathcal{F}, \mathbb{P})$ where $\Omega$ is a sample space with a
 		$\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
@@
 		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
+		\vspace{0.2cm}
 
@@
 		The corresponding scores $\hat{\xi}_i$ can be derived as
-		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
+		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (X(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
 
@@
 		\begin{itemize}
-			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
-			\item Simplification: the $\xi_{j}$ do not follow a normal distribution
+			\item $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$
+			\item \textbf{Simplification:} the $\xi_{j}$ do not follow a normal distribution
 			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$
@@
 
-	\begin{frame}{Simulation Setup cont.}
+	\begin{frame}{Simulation Setup}
 
@@
 
-	\begin{frame}{Simulation Setup cont.}
+	\begin{frame}{Simulation Setup}
 		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
@@
 		\begin{itemize}
-			\item Similar setup, but relying on the initial 60 spectral curves
+			\item Similar setup, but relying on the original 60 spectral curves
 			\item Validation set approach:	Scores of test data needs to be estimated by the training data
-			\item Report results by \textbf{IMSE} for the evaluated best model specifications
+			\item Report results by \textbf{Prediction MSE} for the evaluated best model specifications
 		\end{itemize}
@@
 		\nocite{Bohacs_Ovadi_Salgo1998}
-		\nocite{FR_li_et_al_2020} 
 		\nocite{Reiss_2007b}
@@
 
-	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}
+	\begin{frame}{Simulation Results - Bspline basis expansion}\label{Simulation}
 		\begin{table}

### 2022-01-17 Code/Checking.R
Create Checking.R

@@ -1,0 +1,272 @@
+rm(list=ls())
+
+suppressMessages(library(refund))
+suppressMessages(library(MASS))
+suppressMessages(library(tidyverse))
+suppressMessages(library(fda))
+suppressMessages(library(fpca))
+suppressMessages(library(caret))
+
+### load data set
+data(gasoline)
+octane <- (gasoline$octane)
+NIR <- as.matrix(gasoline$NIR)
+
+##### Define Simulation Parameters #####
+### set up "global" variables
+n_obs <- 60
+nharm <- 4
+n_var <- 400
+grid <- seq(0, 1, length = n_var + 1)
+
+### set up coefficient "functions" / error terms
+# smooth
+f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+# bumpy
+f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
+# two different variances of error
+sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
+sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
+sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
+sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
+
+##### import simulation functions #####
+# this depends on the grid variable above
+source("Simulation_Functions.R")
+### load code from other source files
+source("data_generator.R")
+source("k_fold_CV_function.R")
+
+
+scores <- function(test, train, nharms, accvarprop, startingpoint, endpoint, test_num){
+  #Change smooth function to pca
+  train.fd <- pca.fd(train, nharm = nharms,  centerfns = TRUE)
+  #Containers
+  acc_varprop <- 0
+  scores_vec  <- c()
+  #function to estimate scores of each harmonic(eigenfunction)
+  sc <- function(x){
+    for(i in 1 : nharms){
+      
[…]

### 2022-01-19 Paper/main.tex
Moved Paper to own directory
Increment

--- 2022-01-16 main.tex
@@
 \usepackage{amssymb}
+\usepackage{hyperref}
 \usepackage[font=small,skip=2pt]{caption}
@@
 	\begin{figure}[H]\label{fourier_basis}
-	\includegraphics[width = \textwidth]{Graphics/Fourier_Basis.pdf}
+	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
 	\caption{Fourier basis functions for $i = 1,\dots,6$}
@@
 	\begin{figure}[H]\label{bspline_basis}
-		\includegraphics[width = \textwidth]{Graphics/Bspline_Basis.pdf}
+		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
 		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
@@
 
-	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
+	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
 	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
@@
 	\subsection{Motivation}
-	For the simulation study, we deviate from the standart simulation setting.
-Instead of generating data by ourself, we use the data from the gasoline dataset ($NIR$) to predict the octane ratings of gasoline samples, relying on the introduced methods.
+	For the simulation study, we deviate from the standard simulation setting.
+Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate.
 The dataset, which contains 60 i.i.d.
-observations with each 400 measurements, was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf.
+observations with 401 measurements, allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf.
 \cite{Bohacs_Ovadi_Salgo1998}).
+The optimal number L of basis functions were chosen for each model through 10-fold Cross-Validation.
+Additionally, even for FPCR, we discovered what number of components produces the best.
+As a result, we progressed the application with the derived outcomes.
 
 	\subsection{Generating Similar Curves}
-	To avoid small sample problems, we generated similar curves from the gasoline dataset. This is motivated by the Karhunen-Loeve-Expansion {\color{green} link formula}
+	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset.
+This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots.
-These smooth curves are then centred, before performing FPCA.
-For simplification, we assume that
-	$\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$
+These smooth curves are then centered, before performing FPCA.
+It is supposed that each estimated score follows normal distribution with the assumption that the variance equals its eigenvalue.
+Finally, we obtain the generated curves
 
@@
 		\begin{itemize}
-			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j}\independent \tilde{\xi}_{k}$ for $j \neq k$
+			\item $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$
 			\item Simplification: the $\xi_{j}$ do not follow a normal
@@
 				\centering
-  				\includegraphics[width=\textwidth]{Graphics/smooth_function.png}
+  				\includegraphics[width=\textwidth]{../Graphics/smooth_function.png}
   				\caption{$f_1(t)$, smooth function}
@@
 	  			\centering
-  				\includegraphics[width=\textwidth]{Graphics/bumpy_function.png}
+  				\includegraphics[width=\textwidth]{../Graphics/bumpy_function.png}
   				\caption{$f_2(t)$, bumpy function}
@@
 	\begin{figure}[H]\label{Wiener_plot}
-		\includegraphics[width = \textwidth]{Graphics/Wiener_plot.pdf}
+		\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
 		\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}

### 2022-01-21 Paper/main.tex
Increment

@@
 	\end{equation}
+	{\color{orange}$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup
+	\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$}
 
@@
 	{\color{red} Write something about how to approximate functions by truncating the basis.}
-
+	As above-mentioned, the realized curves can be estimated with basis functions.
+For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$.
+On the one hand, this way is not efficient since the technique with too many basis functions can even approximate a noise of the sample curves which possibly interrupts the analysis.
+On the other hand, the important information on the curves would be missed with a too-small number of basis functions.
+This discussion challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, maintain significant fluctuation.
+The basis expansion with truncation is by:
 	\begin{equation}
@@
 	\end{equation}
+	where $\delta(t)$ is the truncation error.
+The number $L$ is subjectively chosen but we can fix the nubmer through a more reasonable method, Cross-Validation, which minimizes Mean Squared Error (MSE).
 
@@
 	\end{equation}
+	{\color{orange}suggestion from here}
+	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$.
+Let $K$ be the integral operater on $L^{2}[0,1]$ such that $K : v \rightarrow Kv$ for $v \in L^{2}[0,1]$, by
+	\begin{equation}
+		[Kv](t) = \int_{0}^{1}c(t,s)v(s)ds
+	\end{equation}
 
+	Then, the operator $K$ has orthonormal basis functions $v_{i} \in L^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
+Moreover, K holds following triats:
+
+		\begin{enumerate}
+			\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
+			\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
+			\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
+		\end{enumerate}
+
+	Therefore, we can approximate the function $F$ with first few eigenfunctions.
+{\color{orange}to here.
+Then, we can justify why the function F can be explaiend enough well with few eigenfunctions and how to find the variance proporation with Var($\xi$) = $\lambda$}
 	Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
@@
 First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots.
-These smooth curves are then centered, before performing FPCA.
-It is supposed that each estimated score follows normal distribution with the assumption that the variance equals its eigenvalue.
+These smooth curves are then centered({\color{orange} in this case, shouldn't mu be removed on the equation?}), before performing \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+It is supposed that each estimated score follows normal distribution with the fact that the mean is 0 and the variance equals its eigenvalue.
 Finally, we obtain the generated curves

### 2022-01-21 Paper/main.tex
Increment

@@
 	Then, the operator $K$ has orthonormal basis functions $v_{i} \in L^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
-Moreover, K holds following triats:
+Moreover, $K$ holds following traits:
 
@@
 	\begin{itemize}
+		\item \cite{alexanderian_KLexpansion_2015}
 		\item \cite{kokoszka_introduction_2017}
@@
 Additionally, even for FPCR, we discovered what number of components produces the best.
-As a result, we progressed the application with the derived outcomes.
+We finally progressed the application with the derived outcomes from our simulation study.
 
@@
 
-    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
-    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
+    %{\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
+    %Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
 Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience...
@@
     \subsection{Simulation setup}
-	The simulation study follows Reiss and Ogden (2007) as a guideline.
-Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1(t)$ and $f_2(t)$ were chosen that differ in their smoothness:
+	The simulation study follows \cite{Reiss_2007b} as a guideline.
+Two different true coefficient functions, smooth function $f_1(t)$ and bumpy function $f_2(t)$, were chosen to differentiate their smoothness.
+The bumpy function was generated by refering to \cite{cardot_bumpyfunction_2002}.
+The two functions are described as: {\color{orange} we might define the interval of t on the functions}
 
@@
 
-Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+		The intention of comparisons based on the two functions was to represent which type of expansions turn out better simulation results in each case where the functions are bumpy and smooth.
+Two different error-terms $\epsilon$ were created by first generating $i.i.d.$ standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
 The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.
@@
 		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios.
-In total we create four combinations for the simulation, using the two true coefficient functions and the two sets of responses.
+In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses.
 These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we use 10f cross-validation.
+For the evaluation, we used 10f cross-validation.
 The simulation was done with R (version...).
-In total we carried out 2000 simulations for each combination of data and number of basis functions.
+We carried out 2500 repetitions for each set of simulations.
 {\color{green} Information about version and link to repo / package in footnote??}

### 2022-01-21 Code/For_Checking/Checking.R

@@ -1,364 +1,0 @@
-rm(list=ls())
-
-suppressMessages(library(refund))
-suppressMessages(library(MASS))
-suppressMessages(library(tidyverse))
-suppressMessages(library(fda))
-suppressMessages(library(fpca))
-suppressMessages(library(caret))
-
-### load data set
-data(gasoline)
-octane <- (gasoline$octane)
-NIR <- as.matrix(gasoline$NIR)
-
-##### Define Simulation Parameters #####
-### set up "global" variables
-n_obs <- 60
-nharm <- 4
-n_var <- 400
-grid <- seq(0, 1, length = n_var + 1)
-
-### set up coefficient "functions" / error terms
-# smooth
-f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
-# bumpy
-f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
-# two different variances of error
-sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
-sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
-sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
-sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
-
-
-### load code from other source files
-source("data_generator.R")
-source("k_fold_CV_function.R")
-
-
-### FPCA simulation function - bspline basis
-fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE) {
-  set.seed(seed)
-  ### set up coefficient "functions" / error terms
-  # smooth
-  f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
-  # bumpy
[…]

### 2022-01-22 Code/Simulation_Functions.R
Meeting State of Project
- changed simulation functions to use constant
- added parts to paper (who does what)
- organized repo

@@ -32,12 +32,12 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
 
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
-    matrix(data = 0, nrow = length(n_basis), ncol = 7)
+    matrix(data = 0, nrow = length(n_basis), ncol = 6)
   )
 
   colnames(CV_container) <- c(
     "f1_e1_spline", "f1_e2_spline", "f2_e1_spline", "f2_e2_spline",
-    "IMSE", "n_basis", "success_count"
+    "n_basis", "success_count"
   )
 
   CV_container$n_basis <- n_basis
@@ -50,6 +50,8 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   )
 
   # prepare objects for functional linear regression
+  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
+  
   betafdPar2_list <- map(
     .x = 1:length(n_basis),
     .f = function(i) fdPar(basis_functions[[i]])
@@ -57,7 +59,9 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
 
   betalist_list <- map(
     .x = 1:length(n_basis),
-    .f = function(i) list(smooth_basis_fd_data = betafdPar2_list[[i]])
+    .f = function(i) list(const = betafdPar1, 
+                          smooth_basis = betafdPar2_list[[i]]
+                          )
   )
 
   # loop over repetitions
@@ -93,25 +97,19 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
           smallbasis <- basis_functions[[j]]
 
           # express my_data data in functional basis
-          smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
+          smooth_basis_fd <- smooth.basis(argvals = grid, y = data, fdParobj = smallbasis)$fd
 
           # prepare objects for functional regression
-          xfdlist <- list(smooth_basis = smooth_basis_fd)
+          xfdlist <- list(const = smooth.basis(argvals = grid, 
+                                               y = matrix(data = 1, nrow = 401, ncol = n_obs),
+                                               fdParobj = smallbasis)$fd, 
+                          smooth_basis = smooth_basis_fd)
 
[…]

### 2022-01-22 Code/k_fold_CV_function.R

@@ -36,10 +36,10 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
     
     # check if dataset can be divided evenly by number of CV number
     if (dataset_length %% CVobs == 0)  {
-      i <- dataset_length / CVobs
+      num_removed <- dataset_length / CVobs
     } else {print("ERROR")}##############################################################  do smth
     start = 1
-    stop = i
+    stop = num_removed
     # start CV
     for (m in 1:CVobs) {
       
@@ -63,13 +63,16 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
         xfdlisti[[j]] <- fd(coefj,basisj)
       }
       yveci         <- yvec[-(start:stop)]
+      
       fRegressListi <- fRegress(yveci, xfdlisti, betalist, wti)
       betaestlisti  <- fRegressListi$betaestlist
-      yhati <- c()
+      yhati <- rep(0, times = num_removed)
       
   
       for (j in 1:p) {
         # use test data on trained model, get yhat for test data
+        tmp_yhat <- c()
+        
         for (curve in start:stop){
           betafdParj <- betaestlisti[[j]]
           betafdj    <- betafdParj$fd
@@ -81,19 +84,22 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
           delta      <- tfine[2]-tfine[1]
           betavec    <- eval.fd(tfine, betafdj, 0, returnMatrix)
           xveci      <- eval.fd(tfine, xfdj[curve], 0, returnMatrix)
-          yhati     <- c(yhati, delta*(sum(xveci*betavec) -
+          tmp_yhat   <- c(tmp_yhat, delta*(sum(xveci*betavec) -
                                          0.5*( xveci[1]    *betavec[1] +
                                                  xveci[nfine]*betavec[nfine] )))
         }
-       
+        yhati <- yhati + tmp_yhat
       }
-      errfd[m] = mean(yvec[(start:stop)] - yhati);
-      SSE.CV <- SSE.CV + errfd[m]^2
-      start = start +i
-      stop = stop +i
+      print(yhati)
+      
+      errfd[m] = mean((yvec[(start:stop)] - yhati)^2);
+      SSE.CV <- SSE.CV + errfd[m]
+      start = start + num_removed
+      stop = stop + num_removed
     }
[…]

### 2022-01-22 Code/Main_Simulation.R
Simulation Update
- implemented changes to simulation function for bspline (added constant basis)
- added monomial functions to both the simulation functions and the main simulation document
- changed simulation structure to more partial runs with fewer observations
- removed some printing statements
- changed number of basis specifications due to collinearity problems

@@ -25,103 +25,127 @@ source("k_fold_CV_function.R")
 # conduct 5x500 reps for seed 100-seed 104
 
 # Jakob 5x500
-for (i in 100:109) {
+for (i in 100:149) {
   test_bspline_function <- bspline_function(
-    rep = 500, my_data = NULL, n_obs = 200, seed = i, debug = TRUE
+    rep = 100, my_data = NULL, n_obs = 200, seed = i, debug = TRUE
   )
   saveRDS(
     object = test_bspline_function,
-    file = paste0("Results/Paper/Partial/bspline_sim_partial/rep500_n_obs200_seed", i, ".RDS")
+    file = paste0("Results/Paper/Partial/bspline_sim_partial/rep100_n_obs200_seed", i, ".RDS")
   )
 }
 
 # Jonghun 5x500
-for (i in 100:109) {
+for (i in 100:149) {
   test_fourier_function <- fourier_function(
-    rep = 500, my_data = NULL, n_obs = 200, seed = i, 
+    rep = 100, my_data = NULL, n_obs = 200, seed = i, 
     even_basis = FALSE, debug = TRUE
   )
   saveRDS(
     object = test_fourier_function,
-    file = paste0("Results/Paper/Partial/fourier_sim_partial/rep500_n_obs200_seed", i, ".RDS")
+    file = paste0("Results/Paper/Partial/fourier_sim_partial/rep100_n_obs200_seed", i, ".RDS")
+  )
+}
+
+for (i in 100:149) {
+  test_monomial_function <- monomial_function(
+    rep = 100, my_data = NULL, n_obs = 200, seed = i, 
+    even_basis = FALSE, debug = TRUE
+  )
+  saveRDS(
+    object = test_fourier_function,
+    file = paste0("Results/Paper/Partial/monomial_sim_partial/rep100_n_obs200_seed", i, ".RDS")
   )
 }
 
 # Jona 5x500
 for (j in 2:4) {
-  for (i in 100:109) {
+  for (i in 100:149) {
     test_fpcr <- fpcr_function(
-      rep = 500, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE
+      rep = 100, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE
     )
     saveRDS(
       object = test_fpcr,
[…]

### 2022-01-22 Code/Simulation_Functions.R

@@ -28,7 +28,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   }
 
   # specify number of basis functions that should be considered
-  n_basis <- seq(from = 4, to = 25, by = 1)
+  n_basis <- seq(from = 4, to = 18, by = 1)
 
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -204,16 +204,15 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis = FALS
       .f = function(j) create.fourier.basis(rangeval = c(0, 1), nbasis = j)
     )
   }
-
-  # prepare objects for functional linear regression
+  
   betafdPar2_list <- map(
     .x = 1:length(n_basis),
     .f = function(i) fdPar(basis_functions[[i]])
   )
-
+  
   betalist_list <- map(
     .x = 1:length(n_basis),
-    .f = function(i) list(smooth_basis_fd_data = betafdPar2_list[[i]])
+    .f = function(i) list(smooth_basis = betafdPar2_list[[i]])
   )
 
   # loop over repetitions
@@ -249,7 +248,7 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis = FALS
           smallbasis <- basis_functions[[j]]
 
           # express my_data data in functional basis
-          smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
+          smooth_basis_fd <- smooth.basis(argvals = grid, y = data, fdParobj = smallbasis)$fd
 
           # prepare objects for functional regression
           xfdlist <- list(smooth_basis = smooth_basis_fd)
@@ -259,12 +258,6 @@ fourier_function <- function(rep, my_data = NULL, n_obs, seed, even_basis = FALS
           f_regress1_2 <- fRegress.CVk(y = Y1_2, xfdlist = xfdlist, betalist = betalist_list[[j]])
           f_regress2_1 <- fRegress.CVk(y = Y2_1, xfdlist = xfdlist, betalist = betalist_list[[j]])
           f_regress2_2 <- fRegress.CVk(y = Y2_2, xfdlist = xfdlist, betalist = betalist_list[[j]])
-
-          # extract fRegress objects
[…]

### 2022-01-22 Code/k_fold_CV_function.R

@@ -37,7 +37,9 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
     # check if dataset can be divided evenly by number of CV number
     if (dataset_length %% CVobs == 0)  {
       num_removed <- dataset_length / CVobs
-    } else {print("ERROR")}##############################################################  do smth
+    } else {
+      stop('Data set is not divisible into specified number of cv-sets')
+    }##############################################################  do smth
     start = 1
     stop = num_removed
     # start CV
@@ -90,7 +92,6 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
         }
         yhati <- yhati + tmp_yhat
       }
-      print(yhati)
       
       errfd[m] = mean((yvec[(start:stop)] - yhati)^2);
       SSE.CV <- SSE.CV + errfd[m]
@@ -98,8 +99,8 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
       stop = stop + num_removed
     }
   } 
-  return(list(SSE.CV=SSE.CV, errfd.cv=errfd, xfdlisti = xfdlisti, 
-              betalist = betalist, fRegress_obj = fRegressListi))
+  return(list(SSE.CV=SSE.CV, errfd.cv=errfd))
+              #xfdlisti = xfdlisti, betalist = betalist, fRegress_obj = fRegressListi))
 }
 
 

### 2022-01-22 Code/Simulation_Functions.R
FPCR and data_generator corrections

@@ -503,7 +503,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
           smallbasis <- basis_functions[[j]]
 
           # express my_data data in functional basis
-          smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
+          smooth_basis_fd <- smooth.basis(argvals = grid, y = data, fdParobj = smallbasis)$fd
 
           # perform fPCA
           simulated_pcaObj <- pca.fd(smooth_basis_fd, nharm = nharm, centerfns = TRUE)
@@ -663,7 +663,7 @@ fpcr_fourier_function <- function(rep, my_data = NULL, n_obs, nharm, seed, even_
           smallbasis <- basis_functions[[j]]
 
           # express my_data data in functional basis
-          smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
+          smooth_basis_fd <- smooth.basis(argvals = grid, y = data, fdParobj = smallbasis)$fd
 
           # perform fPCA
           simulated_pcaObj <- pca.fd(smooth_basis_fd, nharm = nharm, centerfns = TRUE)
@@ -749,7 +749,7 @@ fpcr_monomial_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debu
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 1, to = 25, by = 1)
+  n_basis <- seq(from = 4, to = 12, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -806,7 +806,7 @@ fpcr_monomial_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debu
           smallbasis <- basis_functions[[j]]
           
           # express my_data data in functional basis
-          smooth_basis_fd <- smooth.basis(y = data, fdParobj = smallbasis)$fd
+          smooth_basis_fd <- smooth.basis(argvals = grid, y = data, fdParobj = smallbasis)$fd
           
           # perform fPCA
           simulated_pcaObj <- pca.fd(smooth_basis_fd, nharm = nharm, centerfns = TRUE)

### 2022-01-22 Code/data_generator.R

@@ -20,14 +20,16 @@ NIR_curve_generator <- function(n = 1, n_harmonics = 4, n_order = 4,
 
   ### create basis object for fpca
   # generate vector of knots
-  breaks <- seq(from = 0, to = n_wl, length.out = n_knots)
+  breaks <- seq(from = 0, to = 1, length.out = n_knots)
+  
   # generate bspline basis accordingly
   bspline_basis <- create.bspline.basis(
-    rangeval = c(0, n_wl), norder = n_order, breaks = breaks
+    rangeval = c(0, 1), norder = n_order, breaks = breaks
   )
 
   # express NIR in terms of the bspline basis
-  NIR_bspline_fd <- smooth.basis(y = t(NIR), fdParobj = bspline_basis)$fd
+  NIR_bspline_fd <- smooth.basis(argvals = seq(0, 1, length.out = n_wl), 
+                                 y = t(NIR), fdParobj = bspline_basis)$fd
 
   # perform fpca
   NIR_pcaObj <- pca.fd(
@@ -48,7 +50,8 @@ NIR_curve_generator <- function(n = 1, n_harmonics = 4, n_order = 4,
   pc_basis_bspline_coef <- NIR_pcaObj$harmonics$coefs
 
   # get values of bspline basis functions at grid points
-  bspline_basis_vals <- eval.basis(evalarg = 1:n_wl, basisobj = bspline_basis)
+  bspline_basis_vals <- eval.basis(evalarg = seq(0, 1, length.out = n_wl), 
+                                   basisobj = bspline_basis)
 
   # get values of PCs at grid points
   pc_grid_vals <- bspline_basis_vals %*% pc_basis_bspline_coef

### 2022-01-22 Paper/main.tex
Meeting State of Project
- changed simulation functions to use constant
- added parts to paper (who does what)
- organized repo
Simulation study part, started monomial basis
rearranged and cleaned up simulations tudy part, started with writing about the monomial basis

@@
 
+	{\color{red} Jonghun (more detail)}
+
 	\subsection{Bases of $\mathbb{L}^2$}
@@
 	\end{equation}
+
+	\paragraph{Monomial Basis}
+This is the basis that is needed in order to build polynomials, one of the best known ways of basis expansion.
+For the polynomial of the form
+
+	\begin{equation}
+		f(t) = \sum_{i =1}^{\mathcal{I}} c_k(t -w)^{i-1}
+	\end{equation}
+	$(t -w)$ is the monomial basis function of the sequence
+
+	\begin{equation}
+		S_{i}^{MB}(t) = (t-w)^i, i = 0, 1, ..., \mathcal{I} 
+	\end{equation}
+
+	where the shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
+
+	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase.
+This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails.
+(cf.
+\cite{ramsay_functional_2005})
 
@@
 Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate.
-The dataset, which contains 60 i.i.d.
-observations with 401 measurements, allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf.
+NIR- spectroscopy allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf.
 \cite{Bohacs_Ovadi_Salgo1998}).
-The optimal number L of basis functions were chosen for each model through 10-fold Cross-Validation.
-Additionally, even for FPCR, we discovered what number of components produces the best.
-We finally progressed the application with the derived outcomes from our simulation study.
+This setup was chosen to improve the approach towards the application, which involves predicting the octane ratings from the gasoline dataset.
 
@@
 This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots.
-These smooth curves are then centered({\color{orange} in this case, shouldn't mu be removed on the equation?}), before performing \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is supposed that each estimated score follows normal distribution with the fact that the mean is 0 and the variance equals its eigenvalue.
-Finally, we obtain the generated curves
+First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots.
+These smooth curves are then centered, before performing \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$ Finally, we obtain the generated curves $NIR_{sim}$
 
@@
 
-		\begin{itemize}
-			\item $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$
-			\item Simplification: the $\xi_{j}$ do not follow a normal
-			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
-		\end{itemize}
+		where
+			$\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
 
@@
 	The simulation study follows \cite{Reiss_2007b} as a guideline.
-Two different true coefficient functions, smooth function $f_1(t)$ and bumpy function $f_2(t)$, were chosen to differentiate their smoothness.
-The bumpy function was generated by refering to \cite{cardot_bumpyfunction_2002}.
-The two functions are described as: {\color{orange} we might define the interval of t on the functions}
+Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the methods with differing true coefficient functions:
 
@@
     \end{equation}
+    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. 
+    Both functions were created such that the inner product $\langle NIR_{sim}, f \rangle, f \in \{f_1(t), f_2(t)\}$ creates responses similar to the original octane ratings of the gasoline dataset.
 
@@
 
-		The intention of comparisons based on the two functions was to represent which type of expansions turn out better simulation results in each case where the functions are bumpy and smooth.
-Two different error-terms $\epsilon$ were created by first generating $i.i.d.$ standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $.
+The error variations represent different signal-to-noise ratios and are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
 The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.
 
-		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$
+		$$Y_{1,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack$$
 
-		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$
+		$$Y_{2,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack$$
 

### 2022-01-22 Paper/main.tex
Follow up on monomial basis

@@
 	\paragraph{Monomial Basis}
-This is the basis that is needed in order to build polynomials, one of the best known ways of basis expansion.
-For the polynomial of the form
+This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
+The polynomial of the form
 
 	\begin{equation}
-		f(t) = \sum_{i =1}^{\mathcal{I}} c_k(t -w)^{i-1}
+		f(t) = \sum_{k =1}^{K} c_k(t -w)^{k-1}
 	\end{equation}
-	$(t -w)$ is the monomial basis function of the sequence
+	can be expressed as a linear combination of the monomials $(t - w)$ which form the basis
 
 	\begin{equation}
-		S_{i}^{MB}(t) = (t-w)^i, i = 0, 1, ..., \mathcal{I} 
+		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
 	\end{equation}
 
-	where the shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
+	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
 

### 2022-01-23 Paper/main.tex
Monomial basis & Fourier Basis

@@
 	\begin{equation}
-		f(t) = \sum_{k =1}^{K} c_k(t -w)^{k-1}
+		f(t) = \sum_{k =0}^{K} c_k(t -w)^{k}
 	\end{equation}
-	can be expressed as a linear combination of the monomials $(t - w)$ which form the basis
+	can be expressed as a finite linear combination of the monomials $(t - w)^{k}$ with coefficient $c_k$ which form the basis
 
@@
 	\end{equation}
-
+	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}).\\
 	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
-
 	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase.
@@
 	\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$}
-
+	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.
+Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthogonal when the values $t_j$ are equally spaced within $T$.
+This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
 	\begin{figure}[H]\label{fourier_basis}
@@
     \end{equation}
+    \vspace{0.2cm}\\
+
     The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. 
@@
 		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $.
-The error variations represent different signal-to-noise ratios and are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
-The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.
+The error variations represent different signal-to-noise ratios to test the methods both with a low and a high amount of noise.
+They are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
 
@@
 
-		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios.
+		where $Z \sim \mathcal{N}(0,1)$.
 In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses.
-These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we used 10f cross-validation.
+These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
+For the evaluation, we used 10 fold cross-validation.
 The simulation was done with R (version...).
-We carried out 2500 repetitions for each set of simulations.
+In total we conducted out 2500 repetitions for each set of simulations.
 {\color{green} Information about version and link to repo / package in footnote??}
 
-	\subsection{Put in appendix - Simulation setup cont.}
-
-	The
-
 	\subsection{Results}
+	DESCRIBE RESULTS
 

### 2022-01-28 Paper/main.tex
Paper work
3.2 random function

@@
 
+	All functions $f$ satisfying the above condition are called square-integrable functions.
+Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.\\
 	Its inner product is defined as
@@
 
-	The Hilbert space of square integrable functions on $[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis.
+	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.
 Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
 For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
+The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
 
-	{\color{red} Jonghun (more detail)}
+	\begin{equation}
+	\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
+	\end{equation}
+
+	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
 
@@
 	\end{equation}
-	{\color{orange}$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup
-	\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$}
+
 	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.

### 2022-01-28 Paper/main.tex
Paper work
3.2
Moved basis plots to appendix; added equation

@@
 	\begin{equation}
-		\int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
+		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
 	\end{equation}
@@
 This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
-	\begin{figure}[H]\label{fourier_basis}
-	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
-	\caption{Fourier basis functions for $i = 1,\dots,6$}
-	\end{figure}
 
@@
 		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.}
-
-	\begin{figure}[H]\label{bspline_basis}
-		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
-		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
-	\end{figure}
 
@@
 
+	\begin{equation}\label{basis_exp_transf}
+		\begin{split}
+			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j d_k(\omega)\sum_{k \in \mathcal{L}} \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
+			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j d_k(\omega) \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}} \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega) \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}} \right] + \epsilon(\omega)
+			= \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega)\textcolor{violet}{\tilde{Z}_{j}^{K}} \right] + \epsilon(\omega)	
+		\end{split}
+	\end{equation}
+
+	A typical choice in this scenario is to use the same functional basis and the same truncation parameter for both the coefficient function and the approximation of the observations.
+This leads to the following simplification of Equation \ref{basis_exp_transf}.
+
 	\begin{equation}
@@
 			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
-			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
-			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
+			& \approx \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{L} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k  = 1}^{L} d_k(\omega)  \phi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j = 1}^{L} \left[\sum_{k = 1}^{L} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) 	\phi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
+			= \alpha + \sum_{j = 1}^{L} \sum_{k = 1}^{L}  c_j d_k(\omega)\textcolor{teal}{Z_{j, k}}  + 	\epsilon(\omega)	
 		\end{split}
@@
 
+	\subsection{Basis Plots}
+
+	\begin{figure}[H]\label{fourier_basis}
+		\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
+		\caption{Fourier basis functions for $i = 1,\dots,6$}
+	\end{figure}
+
+	\begin{figure}[H]\label{bspline_basis}
+		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
+		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
+	\end{figure}
+
 	\subsection{Wiener Process}\label{Wiener}

### 2022-01-28 Paper/main.tex
Equation correction

@@
 \begin{document}
-	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}}
-	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
+	\title{{\LARGE Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
+	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
 	\date{11.02.2022}
@@
 			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j d_k(\omega)\sum_{k \in \mathcal{L}} \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
-			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j d_k(\omega) \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}} \right] + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega) \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}} \right] + \epsilon(\omega)
-			= \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega)\textcolor{violet}{\tilde{Z}_{j}^{K}} \right] + \epsilon(\omega)	
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[\sum_{k \in \mathcal{L}} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
+			= \alpha + \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} c_j d_k(\omega)  \textcolor{teal}{Z_{j, k}} + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} \sum_{k = 1}^{K} c_j d_k(\omega) \textcolor{violet}{Z_{j, k}}  + \epsilon(\omega)	
 		\end{split}
@@
 
-		$$Y_{1,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack$$
-
-		$$Y_{2,f} = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack$$
+		\begin{equation}
+			\begin{split}
+				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack \\
+				Y_{2,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack
+			\end{split}
+		\end{equation}
 

### 2022-01-28 Code/k_fold_CV_function.R
Revising k_fold_CV
No error found, rearranged comments, deleted  leftover from testing done by Jona

@@ -2,15 +2,15 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
                         returnMatrix=FALSE, ...)
 {
   
-  # FREGRESS.CV computes cross-validated error sum of squares
-  # for scalar or functional responses.
+  #  FREGRESS.CV computes cross-validated error sum of squares
+  #  for scalar or functional responses.
+  #
+  #  This function is a modified version of the function by Jim Ramsay
+  #  Original function: https://github.com/cran/fda/blob/master/R/fRegress.CV.R
+  #  Modification was done to use kfold CV, with the default of 10 folds
+  #
   
-  # This function is a modified version of the function by Jim Ramsay
-  # Original function: https://github.com/cran/fda/blob/master/R/fRegress.CV.R
-  # Modification was done to use kfold CV, with the default of 10 folds
-  
-  #  check the arguments
-  
+  # check the arguments
   argList  <- fRegressArgCheck(y, xfdlist, betalist, wt)
   
   yfdobj   <- argList$yfd
@@ -39,13 +39,13 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
       num_removed <- dataset_length / CVobs
     } else {
       stop('Data set is not divisible into specified number of cv-sets')
-    }##############################################################  do smth
+    }
     start = 1
     stop = num_removed
     # start CV
     for (m in 1:CVobs) {
       
-      #  eliminate case (start:stop) from the weights
+      #  eliminate case (start:stop) from the weights to treat it as holdout set
       wti <- wt[-(start:stop)]
       xfdlisti <- vector("list",p)
       for (j in 1:p) {
@@ -65,7 +65,7 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
         xfdlisti[[j]] <- fd(coefj,basisj)
       }
       yveci         <- yvec[-(start:stop)]
-      
+
       fRegressListi <- fRegress(yveci, xfdlisti, betalist, wti)
       betaestlisti  <- fRegressListi$betaestlist
       yhati <- rep(0, times = num_removed)
@@ -92,7 +92,7 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
         }
[…]

### 2022-01-28 Paper/main.tex
Equations for FPCA

@@
 
-	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
+	The $\xi_j(\omega)$ are then given as 
+	\begin{equation}
+		\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(F(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
+	\end{equation} 
+	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
 
@@
 			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} \left[\sum_{k \in \mathcal{L}} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
-			= \alpha + \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} c_j d_k(\omega)  \textcolor{teal}{Z_{j, k}} + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} \sum_{k = 1}^{K} c_j d_k(\omega) \textcolor{violet}{Z_{j, k}}  + \epsilon(\omega)	
+			& = \alpha + \sum_{j \in \mathcal{I}} c_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
+			= \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
+			= \alpha + \sum_{j = 1}^{J} c_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
 		\end{split}
@@
 
-	A typical choice in this scenario is to use the same functional basis and the same truncation parameter for both the coefficient function and the approximation of the observations.
+	A typical choice in this scenario is to use the same functional basis and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations.
 This leads to the following simplification of Equation \ref{basis_exp_transf}.
@@
 		\begin{split}
-			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
-			& \approx \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{L} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k  = 1}^{L} d_k(\omega)  \phi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j = 1}^{L} \left[\sum_{k = 1}^{L} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) 	\phi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
-			= \alpha + \sum_{j = 1}^{L} \sum_{k = 1}^{L}  c_j d_k(\omega)\textcolor{teal}{Z_{j, k}}  + 	\epsilon(\omega)	
+			Z_{j, k}(\omega) & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_j(\omega) & = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+		\end{split}
+	\end{equation}
+
+	\subsection{Regression using Functional Principal Components}
+
+	\begin{equation}\label{FPCA_basis_expansion}
+		\begin{split}
+			\hat{\xi}_{j, i} & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}(s)} \mathrm{d}s
+			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
+			& = \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
+			= \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}} \right]\\
+			&\approx \sum_{j = 1}^{J} \left[a_{i,j} {\color{violet}\sum_{k = 1}^{K} Z_{j,k}}  \right]
+			= \sum_{j = 1}^{J} a_{i,j} {\color{violet}\tilde{Z}_{j}}
+		\end{split}
+	\end{equation}
+
+	Again using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.
+
+	\begin{equation}
+		\begin{split}
+			Z_{j, k} & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_j& = \sum_{k = 1}^{L} \left[b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 		\end{split}

### 2022-01-28 Paper/main.tex
Chapter renaming
Reformatting for space reasons

@@
 
-	\subsection{Estimation via Basis-Representation}
+	\subsection{Estimation using Basis-Representation}
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
@@
 		\begin{split}
-			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{\langle X(\omega), \phi_j \rangle} + \epsilon(\omega) 
+			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
+			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
 		      = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
@@
 		\begin{split}
-			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
+			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
 			& = \alpha + \sum_{j \in \mathcal{I}} c_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
@@
 
-	\subsection{Regression using Functional Principal Components}
+	\subsection{Estimation using Functional Principal Components}
 

### 2022-01-28 Code/Simulation_Functions.R
Reviewing Simulation_functions

@@ -109,7 +109,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
           f_regress2_1 <- fRegress.CVk(y = Y2_1, xfdlist = xfdlist, betalist = betalist_list[[j]])
           f_regress2_2 <- fRegress.CVk(y = Y2_2, xfdlist = xfdlist, betalist = betalist_list[[j]])
 
-          # generate tmp variable for current number of succesful runs
+          # generate tmp variable for current number of successful runs
           tmp_sr <- CV_container$success_count[j]
 
           # save Cross validation criterion in provided container
@@ -454,7 +454,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
   } else {
     data_cond <- TRUE
   }
-
+  
   # specfiy number of basis functions that should be considered
   n_basis <- seq(from = 4, to = 25, by = 1)
 
@@ -518,7 +518,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
       tryCatch(
         {
           
-          #Randomly reorder samples
+          # Order samples
           shuffled <- 1:n_obs # sample(x = 1:n_obs, size = n_obs, replace = FALSE)
           
           for(m in 1:10){
@@ -612,7 +612,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
           
           MSPE_average <- colMeans(MSPE_mat)
 
-          # generate tmp variable for current number of succesful runs
+          # generate tmp variable for current number of successful runs
           tmp_sr <- CV_container$success_count[j]
 
           # Use results from FPCA to perform linear regression and obtain CV scores
@@ -624,7 +624,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
           # update varprop
           # CV_container$varprop[j] <- CV_container$varprop[j] * tmp_sr / (tmp_sr + 1) + sum(train_fd$varprop) * 1 / (tmp_sr + 1)
           
-          # count succesfull runs
+          # count successful runs
           CV_container$success_count[j] <- CV_container$success_count[j] + 1
         },
         error = function(cond) {
@@ -750,7 +750,7 @@ fpcr_fourier_function <- function(rep, my_data = NULL, n_obs, nharm, seed, even_
       tryCatch(
         {
           
-          #Randomly reorder samples
+          # Order samples
[…]

### 2022-01-28 Paper/main.tex
Equation changes and Title

@@
 \begin{document}
-	\title{{\LARGE Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
+	\title{{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
 	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
@@
 			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
-			= \sum_{j \in \mathcal{I}} \left[a_{i,j} \sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}} \right]\\
-			&\approx \sum_{j = 1}^{J} \left[a_{i,j} {\color{violet}\sum_{k = 1}^{K} Z_{j,k}}  \right]
-			= \sum_{j = 1}^{J} a_{i,j} {\color{violet}\tilde{Z}_{j}}
+			& = \sum_{j \in \mathcal{I}}\sum_{k \in \mathcal{L}} {\color{teal} a_{i,j} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}
+			= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} {\color{teal} Z_{i,j,k}} 
+			\approx \sum_{j = 1}^{J} {\color{violet}\sum_{k = 1}^{K} Z_{i,j,k}} 
+			= \sum_{j = 1}^{J} {\color{violet}\tilde{Z}_{i,j}}
 		\end{split}
@@
 		\begin{split}
-			Z_{j, k} & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_j& = \sum_{k = 1}^{L} \left[b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			Z_{i, j, k} & =  a_{i,j} b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_{i, j}& = a_{i,j} \sum_{k = 1}^{L} \left[ b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 		\end{split}

### 2022-01-28 Paper/main.tex
Equation notation

@@
 		\begin{split}
-			\hat{\xi}_{j, i} & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}(s)} \mathrm{d}s
-			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}}\sum_{k \in \mathcal{L}} {\color{teal} a_{i,j} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}
-			= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} {\color{teal} Z_{i,j,k}} 
-			\approx \sum_{j = 1}^{J} {\color{violet}\sum_{k = 1}^{K} Z_{i,j,k}} 
-			= \sum_{j = 1}^{J} {\color{violet}\tilde{Z}_{i,j}}
+			\hat{\xi}_{i}^m & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
+			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)}\right) \mathrm{d}s \\
+			& = \sum_{j \in \mathcal{I}}\sum_{k \in \mathcal{L}} {\color{teal} a_{i,j} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}
+			= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} {\color{teal} Z_{i,j,k}^m} 
+			\approx \sum_{j = 1}^{J} {\color{violet}\sum_{k = 1}^{K} Z_{i,j,k}^m} 
+			= \sum_{j = 1}^{J} {\color{violet}\tilde{Z}_{i,j}^m}
 		\end{split}
@@
 		\begin{split}
-			Z_{i, j, k} & =  a_{i,j} b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_{i, j}& = a_{i,j} \sum_{k = 1}^{L} \left[ b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			Z_{i, j, k}^m & =  a_{i,j} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_{i, j}^m& = a_{i,j} \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 		\end{split}

### 2022-01-28 Paper/main.tex
Equation Simplification

--- 2022-01-28 Paper/main.tex
@@
 		\begin{split}
-			\hat{\xi}_{j, i} & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}(s)} \mathrm{d}s
-			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}}\sum_{k \in \mathcal{L}} {\color{teal} a_{i,j} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}
-			= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} {\color{teal} Z_{i,j,k}} 
-			\approx \sum_{j = 1}^{J} {\color{violet}\sum_{k = 1}^{K} Z_{i,j,k}} 
-			= \sum_{j = 1}^{J} {\color{violet}\tilde{Z}_{i,j}}
+			\hat{\xi}_{i}^m & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
+			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)}\right) \mathrm{d}s \\
+			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
+			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
+			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
+			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
 		\end{split}
@@
 		\begin{split}
-			Z_{i, j, k} & =  a_{i,j} b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_{i, j}& = a_{i,j} \sum_{k = 1}^{L} \left[ b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 		\end{split}

### 2022-01-28 Paper/main.tex
Color changes

@@
 		\begin{split}
-			\hat{\xi}_{i}^m & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
-			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)}\right) \mathrm{d}s \\
+			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( f_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
+			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
 			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
@@
 ~\cite{kokoszka_introduction_2017})
-
-    {\color{red} include Part about CI´s? its about inference and not about prediction}
-
-	\begin{itemize}
-		\item Problem: truncation error $\delta$ and how to deal with it?
-	\end{itemize}
-
-	\begin{itemize}	
-		\item Explain how to address truncation error in standard errors
-		\item Motivate three estimation procedures
-		\begin{enumerate}
-			\item truncated b-spline basis expansion without addressing truncation error
-			\item truncated b-spline basis expansion WITH addressing truncation error
-			\item truncated Eigenbasis expansion (advantages: low number of basis functions get low approximation error)
-		\end{enumerate}
-	\end{itemize}
 
@@
 
+	\newpage
 	\section{Appendix}

### 2022-01-28 Code/Simulation_Functions.R

@@ -15,6 +15,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   # bumpy
   f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
   
+  # Move this to the iteration over repetitions and replace NIR by my_data 
   # two different variances of error
   sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
   sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))

### 2022-01-29 Paper/main.tex
Notation and add theorems regarding KL
Theorems regarding KL

@@
 	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be the integral operater on $L^{2}[0,1]$ such that $K : v \rightarrow Kv$ for $v \in L^{2}[0,1]$, by
+Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
 	\begin{equation}
-		[Kv](t) = \int_{0}^{1}c(t,s)v(s)ds
+		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
 	\end{equation}
 
-	Then, the operator $K$ has orthonormal basis functions $v_{i} \in L^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
+	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
 Moreover, $K$ holds following traits:
@@
 	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
+{\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}
 
@@
 			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L\\
 		\end{split}
@@
 
+	\subsection{Lemma}
+	{\color{orange} We might put the below theorems for KL.
+The deterministic basis expansions are pretty clear about why we can use the truncation version by itself.
+In contrast, I feel like that for the case of KL it does not.
+And in the centered case?}
+	The coefficients $\xi_{j}$ satisfy the following:
+	\begin{enumerate}
+		\item $\mathbb{E}[\xi_{j}] = 0$
+		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
+		\item Var[$\xi_{j}$] = $\lambda_{j}$
+	\end{enumerate}
+	\textit{Proof}. To obtain the first result, we can show that
+	\begin{equation}
+		\begin{split}
+		\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
+		= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
+		= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
+		= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt \\
+		= & \mu(t) \int_{0}^{1} \nu_{j}(t)
+		\end{split}
+	\end{equation}
+
+	For the case of centered process
+	\begin{equation}
+		\begin{split}
+			\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
+			= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
+			= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
+			= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt \\
+			= & \mu(t) \int_{0}^{1} \nu_{j}(t) = 0
+		\end{split}
+	\end{equation}
+	The second claim is proved as:
+	\begin{equation}
+		\begin{split}
+		\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
+		= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack\\
+		= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
+		= & \int_{0}^{1} (\int_{0}^{1}k(s,t)\nu_{j}(s)ds) \nu_{k}(t) dt \\
+		= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
+		= & \langle K \nu_{j}, \nu_{k} \rangle\\
+		= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
+		\end{split}
+	\end{equation}
+	where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
+	\begin{equation}
+		Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
+	\end{equation}
+
+	\subsection{Karhunen-Lo\'{e}ve expansion}
+	Let $F : [0,1]  \rightarrow \mathbb{R}$ be a centered mean-square continuous stochastic process with $F \in \mathbb{L}^{2}[0,1]$.
+Then there exists a basis ${\xi_{i}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
+	\begin{equation}
+		F(t) = \sum_{i=1}^{\infty} \xi_{i} \nu_{i}(t),
+	\end{equation}
+	where coefficients $\xi_{i}$ are given by $\xi_{i}(\omega) = \int_{0}^{1} F(t)(\omega) \nu_{i}(t)dt$ and satisfy the following conditions.
+	\begin{enumerate}
+		\item $\mathbb{E}[\xi_{j}] = 0$
+		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
+		\item Var[$\xi_{j}$] = $\lambda_{j}$
+	\end{enumerate}
+	\textit{Proof}. ...
+
 	\subsection{Wiener Process}\label{Wiener}

### 2022-01-29 Paper/main.tex
Drafting simulation results

@@
 First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots.
-These smooth curves are then centered, before performing \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$ Finally, we obtain the generated curves $NIR_{sim}$
+These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
+Finally, we obtain the generated curves $NIR_{sim}$
 
@@
 	The simulation study follows \cite{Reiss_2007b} as a guideline.
-Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the methods with differing true coefficient functions:
+Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the introduced methods with differing true coefficient functions:
 
@@
 The simulation was done with R (version...).
-In total we conducted out 2500 repetitions for each set of simulations.
-{\color{green} Information about version and link to repo / package in footnote??}
+In total, 5000 repetitions were done for each set of simulations.
 
 	\subsection{Results}
-	DESCRIBE RESULTS
+	{\color{green}DESCRIBE RESULTS: make paragraph for each setup? so 6 paragraphs? Like this: }
+
+	\subsubsection{Basis Expansion Regression}
+	This follows from the \hyperref[basis_exp_transf]{Basis Expansion Transformation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, tractable with typical multivariate regression theory.
+	\paragraph{Monomial Basis}
+	\paragraph{Bspline Basis}
+	\paragraph{Fourier Basis}
 

### 2022-01-29 Paper/main.tex
Simulation Study: Adding out of sample properties for FPCR

@@
 	For the simulation study, we deviate from the standard simulation setting.
-Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate.
-NIR- spectroscopy allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf.
+Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near Infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
+NIR- spectroscopy allows to analyse samples of gasoline much faster, cheaper and with the same reproducibility as standard tests while not destroying the sample (cf.
 \cite{Bohacs_Ovadi_Salgo1998}).
-This setup was chosen to improve the approach towards the application, which involves predicting the octane ratings from the gasoline dataset.
+We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
 
 	\subsection{Generating Similar Curves}
-	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset.
-This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots.
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
+It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
 Finally, we obtain the generated curves $NIR_{sim}$
@@
 These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we used 10 fold cross-validation.
-The simulation was done with R (version...).
-In total, 5000 repetitions were done for each set of simulations.
+For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
+		 To obtain valid out of sample properties for the FPCR, within the 10 fold cross validation we first calculate the Functional Principal Components of the trainig-set for each curve.
+These scores are then used to estimate the scores $\hat{\xi}_{i}^m$ for $i \in holdoutset$ for each curve by the equation:
+
+	\begin{equation}
+		\begin{split}
+			\hat{\xi}_{i}^m =  \int_{0}^{1} \left[ {\color{red} X_{i}(s) - \hat{\mu}(s)} \right] {\color{blue}\hat{\nu}^m }\mathrm{d}s) \\
+						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s 
+			 = \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} ( a_{i,j}   b_{k}^m ) \int_{0}^{1} (\phi_j(s) \psi_{k}(s)\mathrm{d}s)
+		\end{split}
+	\end{equation}
+
+		 The simulation was done with R (version...). In total, 5000 repetitions were done for each set of simulations.
 

### 2022-01-29 Paper/main.tex
KL_appendix

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{amssymb}
@@
 	\end{enumerate}
-	\textit{Proof}. To obtain the first result, we can show that
+
+	\begin{proof}
+		To obtain the first result, we can show that
 		\begin{equation}
@@
 				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-		= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt \\
-		= & \mu(t) \int_{0}^{1} \nu_{j}(t)
+				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
+				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
+				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
 			\end{split}
 		\end{equation}
-
+		where the constant function is always an eigenfunction of the operater $K$.
+It leads the inner product to 0 due to orthonormality of eigenfunctions.
+{\color{red} Another way to prove or use centered mean}
 		For the case of centered process
@@
 				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-			= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt \\
-			= & \mu(t) \int_{0}^{1} \nu_{j}(t) = 0
+				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
 			\end{split}
 		\end{equation}
+		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
 		The second claim is proved as:
@@
 				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
-		= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack\\
+				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
 				= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
-		= & \int_{0}^{1} (\int_{0}^{1}k(s,t)\nu_{j}(s)ds) \nu_{k}(t) dt \\
+				= & \int_{0}^{1} \left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right) \nu_{k}(t) dt \\
 				= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
@@
 		\end{equation}
+	\end{proof}
 
@@
 	\begin{equation}
-		F(t) = \sum_{i=1}^{\infty} \xi_{i} \nu_{i}(t),
+		F(t) = \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
 	\end{equation}
-	where coefficients $\xi_{i}$ are given by $\xi_{i}(\omega) = \int_{0}^{1} F(t)(\omega) \nu_{i}(t)dt$ and satisfy the following conditions.
+	where coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} F(t)(\omega) \nu_{j}(t)dt$ and satisfy the following conditions.
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\textit{Proof}. ...
+
+	\begin{proof}
+		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$.
+With the fact that $\xi_{j}(\omega) = \int_{0}^{1} F(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma.
+We prove it by considering
+		\begin{equation}
+			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
+		\end{equation}
+
+		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
+		\begin{equation}
+			\begin{split}
+				\epsilon_{n}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} 	\nu_{j}(t)\bigg)^2 \right]\\
+				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{j=1}^{n}\xi_{j}\nu_{j}(t)\bigg] + \mathbb{E}\bigg[\sum_{j=1}^{n}\sum_{k=1}^{n}\xi_{j}\xi_{k}\nu_{j}(t)\nu_{k}(t)\bigg]
+			\end{split}
+		\end{equation}
+
+		Now, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (18),
+		\begin{equation}
+			\begin{split}
+				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} \xi_{j}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} \bigg(\int_{0}^{1} F_{s}\nu_{i}(s)ds\bigg) \xi_{j}(t) \right]\\
+				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} \mathbb{E}[F(t)F(s)]\nu_{j}(s)ds\bigg)\nu_{j}\\
+				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} c(t,s) \nu_{j}(s)ds\bigg)\nu_{j}\\
+				= & \sum_{j=1}^{n}[K\nu_{j}](t)\nu_{j} = \sum_{j=1}^{n}\lambda_{j}\nu_{j}^{2}
+			\end{split}
+		\end{equation}
+
+		We derive from (54) that
+		\begin{equation}
+			\begin{split}
+				\mathbb{E}\bigg[\sum_{j=1}^{n} \sum_{k=1}^{n} \xi_{j} \xi_{k} \nu_{j}(t) \nu_{k}(t)\bigg] = & \sum_{j=1}^{n} \sum_{k=1}^{n} \mathbb{E}[\xi_{j} \xi_{k}] \nu_{j}(t) \nu_{k}(t)\\
+				= & \sum_{j=1}^{n} \sum_{k=1}^{n} \delta_{jk} \lambda_{j} \nu_{j}(t) \nu_{k}(t) = 		\sum_{j=1}^{n} \lambda_{j} \nu_{j}(t)^{2}
+			\end{split}	
+		\end{equation}
+		where $\delta_{jk} = 1$ if $j=k$, otherwise 0. Therefore, by (58), (59), and (60) we obtain
+		\begin{equation}
+			\epsilon_{n}(t) = c(t,t) - \sum_{j=1}^{n} \lambda_{j} \nu_{j}(t) \nu_{j}(t)
+		\end{equation}
+
+		implementing Mercer's Theorem this proof is concluded by
+		\begin{equation}
+			\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = \lim\limits_{n \rightarrow \infty} \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right] = 0
+		\end{equation}
+	\end{proof}
 

### 2022-01-29 Paper/main.tex
Link
KL

@@
 	Therefore, we can approximate the function $F$ with first few eigenfunctions.
-{\color{orange}to here.
-Then, we can justify why the function F can be explaiend enough well with few eigenfunctions and how to find the variance proporation with Var($\xi$) = $\lambda$}
+The functions $F$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g.
+$Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$).
 Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
+{\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}
 
@@
 	\begin{equation}
-		\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
+		{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
 	\end{equation}
@@
 
-	\subsection{Lemma}
+	\subsection{Lemma} \label{Proof1}
 	{\color{orange} We might put the below theorems for KL.
@@
 		For the case of centered process
-		\begin{equation}
+		\begin{equation}\label{Lemma1}
 			\begin{split}
@@
 		The second claim is proved as:
-		\begin{equation}
+		\begin{equation}\label{Lemma2}
 			\begin{split}
@@
 		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
-		\begin{equation}
+		\begin{equation}\label{Lemma3}
 			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
@@
 
-	\subsection{Karhunen-Lo\'{e}ve expansion}
+	\subsection{Karhunen-Lo\'{e}ve expansion} \label{Proof2}
 	Let $F : [0,1]  \rightarrow \mathbb{R}$ be a centered mean-square continuous stochastic process with $F \in \mathbb{L}^{2}[0,1]$.
@@
 		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
-		\begin{equation}
+		\begin{equation}\label{Thr1}
 			\begin{split}
@@
 
-		Now, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (18),
-		\begin{equation}
+		Now, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}),
+		\begin{equation}\label{Thr2}
 			\begin{split}
@@
 
-		We derive from (54) that
-		\begin{equation}
+		We derive from (\ref{Lemma2}) that
+		\begin{equation}\label{Thr3}
 			\begin{split}
@@
 		\end{equation}
-		where $\delta_{jk} = 1$ if $j=k$, otherwise 0. Therefore, by (58), (59), and (60) we obtain
+		where $\delta_{jk} = 1$ if $j=k$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain
 		\begin{equation}

### 2022-01-29 Code/Main_Simulation.R
Code meeting 29.01.2022

@@ -21,10 +21,7 @@ source("k_fold_CV_function.R")
 
 ##### Perform Simulations #####
 
-# How to save files? --> Please safe them accordingly in their folder and name them with reps, obs, seed!
-# conduct 5x500 reps for seed 100-seed 104
-
-# Jakob 5x500
+# Jakob
 for (i in 100:149) {
   test_bspline_function <- bspline_function(
     rep = 100, my_data = NULL, n_obs = 200, seed = i, debug = TRUE
@@ -35,10 +32,10 @@ for (i in 100:149) {
   )
 }
 
-# Jonghun 5x500
+# Jakob
 for (i in 100:149) {
   test_fourier_function <- fourier_function(
-    rep = 100, my_data = NULL, n_obs = 200, seed = i, 
+    rep = 100, my_data = NULL, n_obs = 200, seed = i,
     even_basis = FALSE, debug = TRUE
   )
   saveRDS(
@@ -47,9 +44,10 @@ for (i in 100:149) {
   )
 }
 
+# Jonghun
 for (i in 100:149) {
   test_monomial_function <- monomial_function(
-    rep = 100, my_data = NULL, n_obs = 200, seed = i, 
+    rep = 100, my_data = NULL, n_obs = 200, seed = i,
     even_basis = FALSE, debug = TRUE
   )
   saveRDS(
@@ -58,94 +56,42 @@ for (i in 100:149) {
   )
 }
 
-# Jona 5x500
+# Jona
 for (j in 2:4) {
   for (i in 100:149) {
-    test_fpcr <- fpcr_function(
+    test_bspline_fpcr <- fpcr_function(
       rep = 100, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE
     )
     saveRDS(
-      object = test_fpcr,
+      object = test_bspline_fpcr,
       file = paste0("Results/Paper/Partial/pca_bspline_nharm", j, "_sim_partial/rep100_n_obs200_seed", i, ".RDS")
     )
   }
 }
 
+# Jona
 for (j in 2:4) {
   for (i in 100:149) {
-    test_fpcr <- fpcr_monomial_function(
-      rep = 100, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE
-    )
-    saveRDS(
-      object = test_fpcr,
-      file = paste0("Results/Paper/Partial/pca_monomial_nharm", j, "_sim_partial/rep100_n_obs200_seed", i, ".RDS")
[…]

### 2022-01-29 Code/Simulation_Functions.R

@@ -15,7 +15,6 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   # bumpy
   f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
   
-  # Move this to the iteration over repetitions and replace NIR by my_data 
   # two different variances of error
   sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
   sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
@@ -37,7 +36,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
   )
 
   colnames(CV_container) <- c(
-    "f1_e1_spline", "f1_e2_spline", "f2_e1_spline", "f2_e2_spline",
+    "f1_e1", "f1_e2", "f2_e1", "f2_e2",
     "n_basis", "success_count"
   )
 
@@ -64,6 +63,9 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
                           smooth_basis = betafdPar2_list[[i]]
                           )
   )
+  
+  # find number of elements in fold
+  n_elem_fold <- floor(n_obs / 10)
 
   # loop over repetitions
   for (i in 1:rep) {
@@ -92,33 +94,126 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
         print(paste0("Basis specification: ", j, " out of ", length(n_basis)))
       }
 
+      # construct basis for functional representation
+      smallbasis <- basis_functions[[j]]
+      
+      # create container for values
+      MSPE_mat <- as.data.frame(matrix(0, nrow = 10, ncol = 4))
+      colnames(MSPE_mat) <- c('MSPE1_1', 'MSPE1_2', 'MSPE2_1', 'MSPE2_2')
+      
       tryCatch(
         {
-          # construct basis for functional representation
-          smallbasis <- basis_functions[[j]]
+          # Order samples
+          shuffled <- 1:n_obs # sample(x = 1:n_obs, size = n_obs, replace = FALSE)
[…]

### 2022-01-29 Code/k_fold_CV_function.R

@@ -90,8 +90,11 @@ fRegress.CVk <- function(y, xfdlist, betalist, wt=NULL, CVobs=10,
                                          0.5*( xveci[1]    *betavec[1] +
                                                  xveci[nfine]*betavec[nfine] )))
         }
+
         yhati <- yhati + tmp_yhat
       }
+      print(yhati)
+      print(yvec[(start:stop)])
       # calculate prediction MSE
       errfd[m] = mean((yvec[(start:stop)] - yhati)^2);
       SSE.CV <- SSE.CV + errfd[m]

### 2022-01-29 Code/Main_Simulation.R
quick correction

@@ -51,7 +51,7 @@ for (i in 100:149) {
     even_basis = FALSE, debug = TRUE
   )
   saveRDS(
-    object = test_fourier_function,
+    object = test_monomial_function,
     file = paste0("Results/Paper/Partial/monomial_sim_partial/rep100_n_obs200_seed", i, ".RDS")
   )
 }

### 2022-01-29 Paper/main.tex
Paper Meeting (29.01.2022)

@@
 	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.
-Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
+
+	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
 For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
+
 	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
@@
 
-	\subsection{Bases of $\mathbb{L}^2$}
+	\subsection{Bases of $\mathbb{L}^2$} % Maybe change title due to monomial and bspline basis not ful;filling this property
 	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
@@
 	\end{equation}
-	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}).\\
+	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
 	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
@@
 This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
+{\color{blue} Motivate from fourier series}
 
@@
 
-	\subsection{Detailed Draft}
-	\begin{itemize}
-		\item Motivate random functions from introduction and the general concept of random variables
-		\item Formalize random function in this context as random variables realizing in a Hilbert space
-		\item Introduce $\mathbb{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
-		\item Specialize to Hilbert space being $\mathbb{L}^2[0,1]$ for this context
-		\item Define mean and covariance function of a random function realizing in $\mathbb{L}^2[0,1]$
-		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbb{L}^2[0,1]$
-		\item Introduce b-spline and Fourier bases
-		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
-		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
-		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbb{L}^2[0,1]$
-		\item Explain the concept of iid data in a functional setting		
-		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
-		\item Explain approximations of functional observations using truncated basis representations
-		\item Introduce linear operator $L_1$ and sufficient condition associated with it
-		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
-	\end{itemize}
+	%\subsection{Detailed Draft}
+	%\begin{itemize}
+	%	\item Motivate random functions from introduction and the general concept of random variables
+	%	\item Formalize random function in this context as random variables realizing in a Hilbert space
+	%	\item Introduce $\mathbb{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
+	%	\item Specialize to Hilbert space being $\mathbb{L}^2[0,1]$ for this context
+	%	\item Define mean and covariance function of a random function realizing in $\mathbb{L}^2[0,1]$
+	%	\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbb{L}^2[0,1]$
+	%	\item Introduce b-spline and Fourier bases
+	%	\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
+	%	\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
+	%	\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbb{L}^2[0,1]$
+	%	\item Explain the concept of iid data in a functional setting		
+	%	\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
+	%	\item Explain approximations of functional observations using truncated basis representations
+	%	\item Introduce linear operator $L_1$ and sufficient condition associated with it
+	%	\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
+	%\end{itemize}
 
-There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation.
+%There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation.
 Without it, there might be prediction, but the increase in understanding of the underlying question will be minimal.
@@
 
-	A common setting in non-functional regression is akin to the following. Assume a model as follows:
+	%A common setting in non-functional regression is akin to the following. Assume a model as follows:
 
-	\begin{equation}
-		Y = X'\beta + \epsilon
-	\end{equation}
+	%\begin{equation}
+	%	Y = X'\beta + \epsilon
+	%\end{equation}
 
-	where $X \in \mathbb{R}^{n\times J}$ is a matrix containing the regressors, $\beta \in \mathbb{R}^J$ is a coefficient vector and $epsilon$ is a vector containing the error term.
+	%where $X \in \mathbb{R}^{n\times J}$ is a matrix containing the regressors, $\beta \in \mathbb{R}^J$ is a coefficient vector and $epsilon$ is a vector containing the error term.
 For simplicity, assume that the data generating process fulfills the Markov assumptions.
@@
 
-	\begin{equation}
-		\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
-	\end{equation}
+	%\begin{equation}
+	%	\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
+	%\end{equation}
 
-	A naive approach to FLR would be to try to generalize this to the functional setting.
-	Assuming a data generating process of the form:
+	%A naive approach to FLR would be to try to generalize this to the functional setting.
+	%Assuming a data generating process of the form:
 
-	\begin{equation}
-    	 Y =  \int \beta(s)X(s) \,\mathrm{d}t \ +\epsilon
-    \end{equation}
+	%\begin{equation}
+   % 	 Y =  \int \beta(s)X(s) \,\mathrm{d}t \ +\epsilon
+    %\end{equation}
 
-    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
+    %it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
 Where in the finite dimensional setting the OLS estimator can be derived as a method of moments estimator by solving a system of equations of sample moment restrictions, this leads to a system of infinitely many equations in the functional setting.
-    In practice, functional observations are never truly continuously observed.
+    %In practice, functional observations are never truly continuously observed.
 If we assume that the functional observations are observed at a finite set of points $\{t_1, \dots, t_J\}$ this makes the derivation of an OLS estimator possible as before.
 
-    \begin{equation}\label{discrete_time_model}
-    	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
-    \end{equation}
+    %\begin{equation}\label{discrete_time_model}
+    %	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
+    %\end{equation}
 
-    However, this often still results in a large and difficult to solve system of equations.
+    %However, this often still results in a large and difficult to solve system of equations.
 Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
 Another reason why estimation is not feasible using this approach is colinearity.
-    Looking at equation \ref{discrete_time_model} and assuming continuous functions $X_i$ it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$.
+    %Looking at equation \ref{discrete_time_model} and assuming continuous functions $X_i$ it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$.
 Thereby, there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
@@
 ~\cite{kokoszka_introduction_2017})\\
-    A different approach is necessary.
-
-    Define therefore
-
-    \begin{equation}
-  		c_{\mathbf{X}}(t,s) = E[\mathbf{X}(t)\mathbf{X}(s)],\: c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\mathbf{Y}], 
-    \end{equation}
-
-   Under the assumption that $X$ is independent from $\epsilon$ we obtain
-
-   \begin{equation}
-	   c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,\mathrm{d}s \ +\epsilon]
-   \end{equation}
-
-   \begin{equation}
- 	  c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, \mathrm{d}s \: | \: X]  + E[\epsilon |\mathbf{X}]
-   \end{equation}
-
-   \begin{equation}
-      c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,\mathrm{d}s
-   \end{equation}
-
-   In practice, this results in a large and often difficult to solve system of equations.
-If solved, a  perfect fit is possible,but results in a noisy and erratic function $\hat{\beta}(s)$ that is not useful for interpretation since it does not utilize the intuition of smooth functions (cf.~\cite{horvath_inference_2012}).
-Another reason why estimation is not feasible using this approach is colinearity.
-   If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
-
-  	\begin{equation}
-    	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
-    \end{equation}
-
-	it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
-(cf.
-~\cite{kokoszka_introduction_2017}) {\color{red} isn't something missing here?
-Like "and employ standard multivariate linear regression" // Will be done (Jona)}
-
-	\begin{itemize}
-		\item Solution: estimation using truncated basis expansion to approximate data (theoretical description)
-	\end{itemize}
-
-	The simplest approach to regularize the noisy estimate of $\hat{\beta}(s)$	is to expand it with deterministic basis function. Assume
-
-	\begin{equation}
-     	\beta(t) =  \sum_{k=1}^{K} c_{k}B_{k}(t)
-    \end{equation}
-
-    to expand
-
-    \begin{equation}
-    	\int \beta(s)X(s) \,\mathrm{d}t \ = \sum_{k=1}^{K} c_{k} \int B_{k}(t)X_{i}(t)\,\mathrm{d}t =: \sum_{k=1}^{K} x_{ik} c_{k} 
-    \end{equation}
-
-    to the linear model of equation 2 with $\mathbf{c} = [\alpha, c_1, c_2,...,c_K]^T$ (corresponding to $\mathbf{\beta}$) estimated by $\mathbf{\hat{c}} = \mathbf{(X^{T}X)^{-1}X^{T}Y}$.
-Hence, the estimate $\hat{\beta}$ depends on the basis function $B_{k}$ and its corresponding shape, where $K$ is a subjective choice of the researcher.
-This subjective choice highly depends on the researchers intuition of the smoothness of the estimate.
-It is best practice to use the same basis functions as in {\color{red} add link to smoothing} (cf.
-~\cite{kokoszka_introduction_2017})
 
@@
 
-	\subsection{Draft-Overview}
-	\begin{itemize}
-		\item Motivate Simulation for some data generating process from application
-		\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
-
-		\item Compare estimation with \begin{enumerate}
-			\item b-spline basis without addressing approximation error
-			\item ... including proper treatment of approximation error
-			\item Eigenbasis constructed from observations
-			\end{enumerate}
-
-		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
-		\item Present Results
-		\item Explain relevance for application
-	\end{itemize}
+	%\subsection{Draft-Overview}
+	%\begin{itemize}
+	%	\item Motivate Simulation for some data generating process from application
+	%	\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
+	%			\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
+	%	\item Present Results
+	%	\item Explain relevance for application
+	%\end{itemize}
 
@@
 		\begin{split}
-			\hat{\xi}_{i}^m =  \int_{0}^{1} \left[ {\color{red} X_{i}(s) - \hat{\mu}(s)} \right] {\color{blue}\hat{\nu}^m }\mathrm{d}s) \\
-						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s 
-			 = \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} ( a_{i,j}   b_{k}^m ) \int_{0}^{1} (\phi_j(s) \psi_{k}(s)\mathrm{d}s)
+			\hat{\xi}_{i}^m &=  \int_{0}^{1} \left[ {\color{red} X_{i}(s) - \hat{\mu}(s)} \right] {\color{blue}\hat{\nu}^m }\mathrm{d}s) 
+						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
+			 &= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} ( a_{i,j}   b_{k}^m ) \int_{0}^{1} (\phi_j(s) \psi_{k}(s)\mathrm{d}s)
 		\end{split}
@@
 	This follows from the \hyperref[basis_exp_transf]{Basis Expansion Transformation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, tractable with typical multivariate regression theory.
+	\paragraph{Monomial Basis}
+	\paragraph{Bspline Basis}
+	\paragraph{Fourier Basis}
+
+	\subsubsection{Functional Principal Component Regression}
 	\paragraph{Monomial Basis}
@@
 		\begin{itemize}
-\item
-{\color{green} incorporate results of simulation study: number of basis, components, etc...}
-\item
-point out difficulties estimating sderror
-\item
-describe setup and results
-\end{itemize}
-
-	\subsection{Draft-Overview}
-	\begin{itemize}
-		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the data set)
-		\item IID data set (no dependence between the curves, don't want to do functional time series)
-		\item Not necessarily data from economics (like biology, sports, whatever)
-		\item Smooth curves or random walk (both fine)
-		\item \href{https://functionaldata.wordpress.ncsu.edu/resources/}{https://functionaldata.wordpress.ncsu.edu/resources/}
+			\item {\color{green} incorporate results of simulation study: number of basis, components, etc...}
+			\item point out difficulties estimating sderror
+			\item describe setup and results
 \end{itemize}
@@
 
+\subsection{Wiener Process}\label{Wiener}
+A Wiener process $W_t$ is a real-valued continuous-time stochastic process {\color{red} ... This is wikipedia, look for right citation!}
+It is characterized by the following properties.
+
+\begin{multicols}{2}
+	\begin{enumerate}
+		\item $W_0 = 0$
+		\item $\forall t > 0 W_{t+u} - W_t \perp\!\!\!\perp W_s \forall s \leq t$
+		\item $W_{t+u} - W_t \sim \mathcal{N}(0,u)$
+		\item $W_t$ is continuous in $t$
+	\end{enumerate}
+\end{multicols}
+
+\begin{figure}[H]\label{Wiener_plot}
+	\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
+	\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
+\end{figure}
+
+	\section{Proofs}
 	\subsection{Lemma} \label{Proof1}
@@
 
-	\subsection{Wiener Process}\label{Wiener}
-	A Wiener process $W_t$ is a real-valued continuous-time stochastic process {\color{red} ... This is wikipedia, look for right citation!}
-	It is characterized by the following properties.
-
-	\begin{multicols}{2}
-		\begin{enumerate}
-			\item $W_0 = 0$
-			\item $\forall t > 0 W_{t+u} - W_t \perp\!\!\!\perp W_s \forall s \leq t$
-			\item $W_{t+u} - W_t \sim \mathcal{N}(0,u)$
-			\item $W_t$ is continuous in $t$
-		\end{enumerate}
-	\end{multicols}
-
-	\begin{figure}[H]\label{Wiener_plot}
-		\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
-		\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
-	\end{figure}
-
 	\newpage

### 2022-01-29 Code/Main_Simulation.R
Main adjustment, fkcv function moved

@@ -17,7 +17,6 @@ NIR <- as.matrix(gasoline$NIR)
 source("Simulation_Functions.R")
 ### load code from other source files
 source("data_generator.R")
-source("k_fold_CV_function.R")
 
 ##### Perform Simulations #####
 

### 2022-01-29 Paper/main.tex
Fixing out of samples properties - Introducing Test and Holdout set

@@
 For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
-		 To obtain valid out of sample properties for the FPCR, within the 10 fold cross validation we first calculate the Functional Principal Components of the trainig-set for each curve.
-These scores are then used to estimate the scores $\hat{\xi}_{i}^m$ for $i \in holdoutset$ for each curve by the equation:
+		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve.
+These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:
 
@@
 		\begin{split}
-			\hat{\xi}_{i}^m &=  \int_{0}^{1} \left[ {\color{red} X_{i}(s) - \hat{\mu}(s)} \right] {\color{blue}\hat{\nu}^m }\mathrm{d}s) 
+			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} ({\color{red} X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)} ) {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
 						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			 &= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} ( a_{i,j}   b_{k}^m ) \int_{0}^{1} (\phi_j(s) \psi_{k}(s)\mathrm{d}s)
+			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
 		\end{split}

### 2022-01-30 Paper/main.tex
Added Affidavit

@@
 
+	\newpage
+	\section{Affidavit}
+
+	\vspace{2cm}
+	"I hereby confirm that the work presented has been performed and
+	interpreted solely by myself except for where I explicitly identified the
+	contrary. I assure that this work has not been presented in any other
+	form for the fulfillment of any other degree or qualification. Ideas
+	taken from other works in letter and in spirit are identified in every
+	single case."
+
+	\vspace{2cm}
+	Bonn, 11.02.2021 \hrulefill \\
+	\hspace*{0mm}Jonghun Baek
+
+	\vspace{2cm}
+	Bonn, 11.02.2021 \hrulefill \\
+	\hspace*{0mm}Jakob R. Juergens
+
+	\vspace{2cm}
+	Bonn, 11.02.2021 \hrulefill \\
+	\hspace*{0mm}Jonathan Willnow
+
 \end{document}

### 2022-01-30 Paper/main.tex
Small notation thing for training and holdout set
Notation consistency changes

@@
 	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
-Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega_0) = f(t)$ of $F(\omega)$.
+Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.
 
 	\begin{equation}
-		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t)
+		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_{j}(\omega_0) \phi_j(t)
 	\end{equation}
@@
 	\begin{equation}
-		f(t) = \sum_{k =0}^{K} c_k(t -w)^{k}
+		x(t) = \sum_{i \in \mathcal{I}} c_i(t -w)^{i}
 	\end{equation}
-	can be expressed as a finite linear combination of the monomials $(t - w)^{k}$ with coefficient $c_k$ which form the basis
+	can be expressed as a finite linear combination of the monomials $(t - w)^{i}$ with coefficient $c_i$ which form the basis
 
 	\begin{equation}
-		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
+		\phi_{i}^{M}(t) = (t-w)^k \quad i \in \mathcal{I}
 	\end{equation}
@@
 	\begin{equation}
-		S_{i}^{FB}(x) = 
+		\phi_{i}^{F}(x) = 
 		\begin{cases}
@@
 		\begin{split}
-			S_{l,0}^{BS}(x) = &
+			\phi_{l,0}^{BS}(x) = &
 			\begin{cases}
@@
 			\end{cases}\\ \\
-			S_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} S_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} S_{l+1,m-1}^{BS}(x)
+			\phi_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} \phi_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} \phi_{l+1,m-1}^{BS}(x)
 		\end{split}
@@
 	\begin{equation}
-		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t) = \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t)
+		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
 	\end{equation}
@@
 To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
-Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$.
-Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\
+Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$.
+Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\
 
-	This decomposition can be used to express the random vector $X(\omega)$ in the following way.
+	This decomposition can be used to express the random vector $V(\omega)$ in the following way.
 
 	\begin{equation}
-		X(\omega) = \mu_x + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_x + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
+		V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
 	\end{equation}
@@
 	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$.
-Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
-	Then the mean and covariance functions of $F$ are defined as follows.
+Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
+	Then the mean and covariance functions of $X$ are defined as follows.
 
 	\begin{equation}\label{MeanFunction}
-		\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]
+		\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]
 	\end{equation}
@@
 	\begin{equation}\label{CovarianceFunction}
-		c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]
+		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
 	\end{equation}
@@
 
-	Therefore, we can approximate the function $F$ with first few eigenfunctions.
-The functions $F$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g.
+	Therefore, we can approximate the function $X$ with first few eigenfunctions.
+The functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g.
 $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$).
-Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
+Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
 {\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}
@@
 	\begin{equation}\label{KarhunenLoeve}
-		F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
+		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
 	\end{equation}
@@
 	\begin{equation}
-		\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(F(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
+		\xi_j(\omega) = \langle X(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
 	\end{equation} 
@@
 This is also possible in a functional setting.
-Let $\{f_1(t), \dots, f_n(t)\}$ be a set of i.i.d.
-realizations generated by a random function $F(\omega) \mapsto \mathbb{L}^2[0,1]$.
+Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d.
+realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
 	Define the following sample analogues for the mean and covariance functions.
@@
 	\begin{equation}
-		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)
+		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)
 	\end{equation}
@@
 	\begin{equation}
-		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)
+		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)
 	\end{equation}
@@
 	\begin{equation}
-		f_i(t) = \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
+		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
 	\end{equation}
@@
 	\begin{equation}
-		Y(\omega) = \alpha + \Psi\left(F(\omega)\right) + \epsilon(\omega)
+		Y(\omega) = \alpha + \Psi\left(X(\omega)\right) + \epsilon(\omega)
 	\end{equation}
@@
 	\begin{equation}\label{DGP}
-		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)F(\omega)(s) \mathrm{d}s + \epsilon(\omega)
+		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
 	\end{equation}
 
-	Where $f(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
+	Where $x(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
 	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
@@
 	\begin{equation}
-		\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t)
+		\beta(t) = \sum_{j = 1}^{\infty} b_j \phi_j(t)
 	\end{equation}
@@
 			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
-		      = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
+			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
+		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
 		\end{split}
@@
 	\begin{equation}
-			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} c_j Z_j(\omega) + \epsilon(\omega)
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} b_j Z_j(\omega) + \epsilon(\omega)
 	\end{equation}
@@
 			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
-			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} c_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
-			= \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
-			= \alpha + \sum_{j = 1}^{J} c_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
+			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
+			= \alpha + \sum_{j \in \mathcal{I}} \left[ b_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} \left[b_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
+			= \alpha + \sum_{j = 1}^{J} b_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
 		\end{split}
@@
 
+	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 		\begin{split}
-			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} ({\color{red} X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)} ) {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
-						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
+						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^{m, \mathcal{T}} \psi_{k}(s)\right)} \mathrm{d}s \\
+			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}^{\mathcal{H}}\sum_{k \in \mathcal{L}}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
 		\end{split}

### 2022-01-31 Code/Main_Simulation.R
Monomial expansion sim

@@ -32,7 +32,7 @@ for (i in 100:149) {
 }
 
 # Jakob
-for (i in 100:149) {
+for (i in 140:149) {
   test_fourier_function <- fourier_function(
     rep = 100, my_data = NULL, n_obs = 200, seed = i, debug = TRUE,
     even_basis = FALSE

### 2022-01-31 Code/Archive/monomial_fpcr_add_missing_runs.R
Updated Runs for monomial fpcr + summaries for BE regression

@@ -1,0 +1,275 @@
+### Add missing basis functions to monomial basis tables
+
+### load libraries
+suppressMessages(library(refund))
+suppressMessages(library(MASS))
+suppressMessages(library(tidyverse))
+suppressMessages(library(fda))
+suppressMessages(library(fpca))
+suppressMessages(library(caret))
+
+### load data generator
+source("data_generator.R")
+
+### load data set
+data(gasoline)
+# octane <- (gasoline$octane)
+NIR <- as.matrix(gasoline$NIR)
+
+### define function monomial fpcr for two and three basis functions
+### FPCA simulation function - monomial basis
+helper_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE) {
+  set.seed(seed)
+
+  # load NIR data
+  data(gasoline)
+  NIR <- as.matrix(gasoline$NIR)
+
+  ### set up coefficient "functions" / error terms
+  grid <- seq(0, 1, length.out = 401)
+  # smooth
+  f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+  # bumpy
+  f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
+
+  # two different variances of error
+  sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
+  sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
+  sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
+  sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
+
+  # check if data (my_data) is provided
+  if (is.null(my_data)) {
+    data_cond <- FALSE
+  } else {
+    data_cond <- TRUE
+  }
+
+  # specfiy number of basis functions that should be considered
+  n_basis <- seq(from = 2, to = 3, by = 1)
+
[…]

### 2022-01-31 Code/Main_Stitching.R
Added .csv summaries

@@ -30,8 +30,15 @@ summary_results <- map(
 
 # save in summaries folder
 for (i in 1:length(sbfldrs)) {
-  saveRDS(
-    object = summary_results[[i]],
-    file = paste0("Results/Paper/Summaries/", output_names[[i]], ".RDS")
-  )
+  if(length(summary_results[[i]]) != 1){
+    saveRDS(
+      object = summary_results[[i]],
+      file = paste0("Results/Paper/Summaries/", output_names[[i]], ".RDS")
+    )
+    write_csv(
+      x = summary_results[[i]], 
+      file = paste0("Results/Paper/Summaries/", output_names[[i]], ".RDS")
+    )
+  }
+  
 }

### 2022-01-31 Code/Main_Stitching.R
Correction

@@ -37,8 +37,7 @@ for (i in 1:length(sbfldrs)) {
     )
     write_csv(
       x = summary_results[[i]], 
-      file = paste0("Results/Paper/Summaries/", output_names[[i]], ".RDS")
+      file = paste0("Results/Paper/Summaries/", output_names[[i]], ".csv")
     )
   }
-  
 }

### 2022-01-31 Paper/main.tex
Some estimation theory

@@
 
-	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ of the following equation.
+	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.
 
@@
 	\begin{equation}
-		\xi_j(\omega) = \langle X(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
+		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
 	\end{equation} 
@@
 	\begin{equation}
-		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)
+		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
 	\end{equation}
@@
 	\begin{equation}
-		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)
+		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
 	\end{equation}
 
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathbb{N}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ as the solutions of the following equation.
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: i \in \mathcal{M}\}$ as the solutions of the following equation.
 {\color{red} I think the number of principal components has to be smaller then the number of observations.
-So I can give more information about $\mathbb{N}$.}
+So I can give more information about $\mathcal{M}$.}
 
@@
 		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
+	\end{equation}
+	where the $\hat{\xi}_{i}^m$ are derived as
+
+	\begin{equation}
+		\hat{\xi}_i^m(\omega) = \langle x_i - \hat{\mu}, \hat{\nu}^m\rangle = \int_{0}^{1} \left(x_i(s) - \hat{\mu}(s)\right) \hat{\nu}^m(s) \mathrm{d}s
+	\end{equation}
+
+	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
+
+	\begin{equation}\label{FPCA_basis_expansion}
+		\begin{split}
+			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
+			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
+			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
+			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]\\
+			& \approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
+			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
+		\end{split}
+	\end{equation}
+
+	Using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.
+
+	\begin{equation}
+		\begin{split}
+			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
+			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L\\
+		\end{split}
+	\end{equation}
+
+	For notational purposes in this paper we define the following convention:
+
+	\begin{equation}
+		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
 	\end{equation}
@@
 
-	\subsection{Estimation using Basis-Representation}
+	\subsubsection{Estimation using Basis-Representation}
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
@@
 
-	{\color{red} This fancy equation will be very useful to explain our simulation.}
+	In practice it is common to not only express the coefficient function in terms of a basis but also the observations.
+Therefore two bases ($\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and $\left(\psi_k(t)\right)_{k \in \mathcal{L}}$) and two corresponding truncation parameters ($J$ and $K$) can be chosen.
+This leads to the following representation.
 
@@
 			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
-			= \alpha + \sum_{j \in \mathcal{I}} \left[ b_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} \left[b_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
-			= \alpha + \sum_{j = 1}^{J} b_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
+			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega) 
+			\approx \alpha + \sum_{j = 1}^{J} \left[b_j \sum_{k = 1}^{K}  d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega)
 		\end{split}
@@
 
-	A typical choice in this scenario is to use the same functional basis and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations.
-This leads to the following simplification of Equation \ref{basis_exp_transf}.
+	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations.
+Defining the following notation
 
 	\begin{equation}
-		\begin{split}
-			Z_{j, k}(\omega) & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_j(\omega) & = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
-		\end{split}
+			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 	\end{equation}
 
-	\subsection{Estimation using Functional Principal Components}
+	This leads to a considerable simplification of Equation \ref{basis_exp_transf}.
+
+	\begin{equation}\label{simplified_model_basis_equation}
+		Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
+	\end{equation}
+
+	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.
+
+	\subsubsection{Estimation using Functional Principal Components}
 
 	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
-	\begin{equation}\label{FPCA_basis_expansion}
-		\begin{split}
-			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( f_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
-			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
-			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
-			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
-			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
-		\end{split}
-	\end{equation}
-
-	Again using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.
-
-	\begin{equation}
-		\begin{split}
-			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L\\
-		\end{split}
-	\end{equation}
 

### 2022-01-31 Paper/main.tex
Some fpcr theory

@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
-			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]\\
-			& \approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
-			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
+			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right] \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right]
 		\end{split}
@@
 
-	Using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.
-
-	\begin{equation}
-		\begin{split}
-			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
-			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L\\
-		\end{split}
-	\end{equation}
-
-	For notational purposes in this paper we define the following convention:
+	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
+This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
 

### 2022-01-31 Paper/main.tex
fpcr estimation theory

@@
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
+		X(\omega)(t) = \mu(t) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(t)
 	\end{equation}
@@
 	\begin{equation}
-		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
+		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
 	\end{equation}
@@
 
-	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors.
+	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors.
 Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.
@@
 
-	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
+	{\color{red} We have to clean this up theoretically. Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.}
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s) \phi_j(s)\right] \right] \mathrm{d}s + \epsilon(\omega) \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+		\end{split}
+	\end{equation}
+
+	Using sample analogues, we can use this form to obtain the following approximation.
+
+	\begin{equation}
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \hat{\xi}^m(\omega) \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+	\end{equation}
+
+	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.
+
+	\begin{equation}
+		y_i \approx \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{L} \left[b_j \sum_{m  = 1}^{M}  \tilde{\xi}^{m,L}_{i} \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+	\end{equation}
 

### 2022-01-31 Paper/main.tex
More fpcr regression theory

--- 2022-01-31 Paper/main.tex
@@
 
-	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
+	{\color{red} We have to clean this up theoretically.
+Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.
+In these equations the sum over m and the sum over j should be exchanged.}
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{m \in \mathcal{M}} \left[ \xi^m(\omega) \sum_{j \in \mathcal{I}} b_j \nu^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon(\omega) \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \xi^m(\omega) \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{m  = 1}^{M}\left[ \xi^m(\omega) \sum_{j = 1}^{J} b_j \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+		\end{split}
+	\end{equation}
+
+	Using sample analogues, we can use this form to obtain the following approximation.
+
+	\begin{equation}
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s +  \sum_{m  = 1}^{M} \left[ \hat{\xi}^m(\omega) \sum_{j = 1}^{J} b_j \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+	\end{equation}
+
+	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.
+
+	\begin{equation}
+		\begin{split}
+			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right] \right]+ \epsilon(\omega) \\
+		\end{split}
+	\end{equation}
 

### 2022-01-31 Paper/main.tex
fpcr theory

@@
 			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
-			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right] \right]+ \epsilon(\omega) \\
+			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
+			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}Z^{m,L}}+ \epsilon(\omega)
 		\end{split}

### 2022-01-31 Paper/main.tex
Starting creating tables

--- 2022-01-31 Paper/main.tex
@@
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(t)
+		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
 	\end{equation}
@@
 	\begin{equation}
-		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
+		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
 	\end{equation}
@@
 
-	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors.
+	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors.
 Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.
@@
 
-	{\color{red} We have to clean this up theoretically. Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.}
-
-	\begin{equation}
-		\begin{split}
-			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
-			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s) \phi_j(s)\right] \right] \mathrm{d}s + \epsilon(\omega) \\
-			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
-		\end{split}
-	\end{equation}
-
-	Using sample analogues, we can use this form to obtain the following approximation.
-
-	\begin{equation}
-			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \hat{\xi}^m(\omega) \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
-	\end{equation}
-
-	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.
-
-	\begin{equation}
-		y_i \approx \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{L} \left[b_j \sum_{m  = 1}^{M}  \tilde{\xi}^{m,L}_{i} \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
-	\end{equation}
+	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
 
@@
 	\end{figure}
+\newpage
+	\subsection{Simulation Study Results}
+
+	\begin{table}[htb]
+			\centering
+			\caption{Monomial Basis Expansion Regression}
+				\begin{tabular}{lllllll}
+					\cline{1-5}
+					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
+7.177234352026647                        & 131.92716520680838                        & 0.8936725847175324                         & 2.5839516380614462                        & 2       &  \\
+4.170391190343292                        & {\color[HTML]{FE0000} 129.64258934345224} & 0.8122408608804015                         & 2.511772278865247                         & 3       &  \\
+3.912749103345826                        & 130.1170783435205                         & 0.3807927171910713                         & 2.090474762002978                         & 4       &  \\
+{\color[HTML]{FE0000} 3.638501968909747} & 130.59817144950233                        & {\color[HTML]{FE0000} 0.09216751463887264} & {\color[HTML]{FE0000} 1.8134256416939782} & 5       &  \\
+6.016442343989896                        & 201.15534584991525                        & 0.7620805051836907                         & 3.3937342332820926                        & 6       & 
+\end{tabular}
+\end{table}
+
+\vspace{2cm}
+
+	\begin{table}[htb]
+			\centering
+			\caption{BSpline Basis Expansion Regression}
+				\begin{tabular}{lllllll}
+					\cline{1-5}
+					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
+3.9127490963955247                        & {\color[HTML]{FE0000} 130.1170783090359} & 0.3807927168700936                          & 2.090474761101881                         & 4       &  \\
+{\color[HTML]{FE0000} 3.6430480624640396} & 130.61094959896604                       & 0.09511820431115069                         & 1.8164314387816713                        & 5       &  \\
+3.6542611008674575                        & 131.35354539843397                       & 0.07775281510299467                         & {\color[HTML]{FE0000} 1.8091346529425483} & 6       &  \\
+3.6770545937377634                        & 132.14205183557064                       & 0.07518488287219192                         & 1.8168036577708813                        & 7       &  \\
+3.710740869697218                         & 133.3653658811635                        & 0.05810108378740701                         & 1.8164984632128844                        & 8       &  \\
+3.7192146351418724                        & 133.6814928169343                        & 0.05640282340664383                         & 1.8193083539013821                        & 9       &  \\
+3.742010447810594                         & 134.5121710907784                        & 0.0521785231194299                          & 1.8257576297312081                        & 10      &  \\
+3.7643964092462974                        & 135.29727347111702                       & {\color[HTML]{FE0000} 0.051902252769905684} & 1.8360966075573522                        & 11      &  \\
+3.80109308638683                          & 136.5758146586355                        & 0.052040315671138586                        & 1.8531479959118535                        & 12      &  \\
+3.834360204971099                         & 137.78406681481994                       & 0.052706573106132304                        & 1.869969847032031                         & 13      &  \\
+3.862166917165765                         & 138.73431326927349                       & 0.053068654178390816                        & 1.8826933364948355                        & 14      &  \\
+3.8685638723557956                        & 138.97427074660192                       & 0.0525955164519272                          & 1.8848221385552892                        & 15      &  \\
+3.88505750612787                          & 139.57418873526626                       & 0.05283448721173191                         & 1.8933474257957223                        & 16      &  \\
+3.912671952971778                         & 140.51490301138338                       & 0.053220205231306356                        & 1.9061942087104604                        & 17      &  \\
+3.948125713522542                         & 141.80885020010606                       & 0.053584434348457485                        & 1.9231184762987383                        & 18      & 
+\end{tabular}
+\end{table}
+
+\vspace{2cm}
+
+	\begin{table}[htb]
+			\centering
+			\caption{Fourier Basis Expansion Regression}
+				\begin{tabular}{lllllll}
+					\cline{1-5}
+					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
+3.6975216821108177                        & {\color[HTML]{FE0000} 129.19133735032568} & 0.6952364931614831                         & 2.394399533437222                         & 3       \\
+{\color[HTML]{FE0000} 3.6347035142043147} & 130.59281554182246                        & 0.07418129892625985                        & 1.795816800944426                         & 5       \\
+3.6762259845089287                        & 132.0824820138016                         & 0.05147130962678385                        & {\color[HTML]{FE0000} 1.7934269021325526} & 7       \\
+3.718852537544315                         & 133.67575428625497                        & {\color[HTML]{FE0000} 0.05104970622270979} & 1.812908100982769                         & 9       \\
+3.764506721475903                         & 135.26218648523314                        & 0.05146451789575423                        & 1.8346302450265894                        & 11      \\
+3.810949927900835                         & 136.90281800923086                        & 0.05197380387819929                        & 1.8572425102431276                        & 13      \\
+3.8567441840723165                        & 138.57257529224665                        & 0.05252120988973837                        & 1.8802107534919845                        & 15      \\
+3.9061852571557436                        & 140.29178124765565                        & 0.05304327165297495                        & 1.9028253007284568                        & 17      \\
+3.9551703628111876                        & 142.057266882177                          & 0.053647142499864804                       & 1.9271845824346567                        & 19     
+\end{tabular}
+\end{table}
 

### 2022-01-31 Paper/main.tex
PDF Rendering
Adding sim results draft for basis expansion regression

@@
 In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses.
-These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
+These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
 For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
@@
 	This follows from the \hyperref[basis_exp_transf]{Basis Expansion Transformation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, tractable with typical multivariate regression theory.
+
 	\paragraph{Monomial Basis}
+	Due to the high collinearity of these basis, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
+For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines, but show the weakest performance for the setup $f_2, Y_1$.
+In the setup with high noise, $f_2, Y_2$ this weakness is still visible, but way less pronounced.
+
 	\paragraph{Bspline Basis}
+	Simulations with bspline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happend here exactly?}
+The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low)-signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$.
+For $f_2$, 11(6) bspline basis functions are needed for the high(low) signal-to-noise ratios.
+For $f_2$, the bspline basis functions outperform the monomial basis, but come second to the fourier basis.
+
 	\paragraph{Fourier Basis}
+	The results are simialar to the previous results: For $f_1$, the simulation chooses a smaller number of fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
+With the low signal-to-noise ratio, the simulation chooses a smaller number to account for the higher noise in the response variable.
+	\\
+
+	The results follow the Bias-Variance Tradeoff: The function $f_1$ is rather smooth and not much bias is introduced here when choosing a small number of basis functions since $f_1$ lacks pronounced peculiarities.
+For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$: We can choose a higher number of basis functions since the amount of bias is decrasing much faster in the number of basis functions than the variance is increasing, compared to $f_1$.
 

### 2022-01-31 Paper/main.tex
More fpcr theory

--- 2022-01-31 Paper/main.tex
@@
 
-	\begin{equation}
-		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
+	\begin{equation}\label{score_approx}
+		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
 	\end{equation}
@@
 
-	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
+	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
+			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
+		\end{split}
+	\end{equation}
+
+	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogues is more interesting as a representation of an observation.
+
+	\begin{equation}
+		\begin{split}
+			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
+			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
+		\end{split}
+	\end{equation}
+
+	This, however, is a simplification for the purposes of real-world estimation as in most implementations the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely.
+Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
+
+	\begin{equation}
+		\begin{split}
+			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+		\end{split}
+	\end{equation}
+
+	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following.
+To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
+Additionally, the following approximation also truncates the basis for the expansion of the coeffieicnt function at the same parameter $L$ that was used for the approximation of the principal components and scores.
+
+	\begin{equation}
+		\begin{split}
+			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
+			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon(\omega)
+		\end{split}
+	\end{equation}
 

### 2022-01-31 Paper/main.tex
More fpcr estimation theory

@@
 To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
-Additionally, the following approximation also truncates the basis for the expansion of the coeffieicnt function at the same parameter $L$ that was used for the approximation of the principal components and scores.
-
-	\begin{equation}
-		\begin{split}
-			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
-			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
-			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
-			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon(\omega)
+Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
+The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+
+	\begin{equation}
+		\begin{split}
+			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
+			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
+			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon_i
+			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon_i
 		\end{split}
@@
 ~\cite{kokoszka_introduction_2017})\\
-
-	\subsection{Draft-Overview}
-	\begin{itemize}
-		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		
-		\item Explain Scalar-on-Function Regression
-		\item Estimation through basis-expansion (incl. Eigenbasis) [and estimation with roughness penalty]
-		\item Address approximation error due to basis-truncation
-	\end{itemize}
 

### 2022-01-31 Code/Plot_Generators/Monomial_basis_plot.R
Added Monomial basis plot

@@ -6,15 +6,12 @@ library(fda)
 
 # setup for plot generation
 n_points <- 1000
-knots <- seq(from = 0, to = 1, length.out = 8)
-order <- 4
 
 # Create points for calculation of basis functions
 points <- seq(from = 0, to = 1, length.out = n_points)
 
 # function factory that generates the basis functions
-bspline_basis <- create.bspline.basis(rangeval = c(0,1), norder = order,
-                                        breaks = knots)
+bspline_basis <- create.monomial.basis(rangeval = c(0,1), nbasis = 8)
 
 # Calculate basis functions at points
 res_matrix <- eval.basis(evalarg = points, basisobj = bspline_basis)
@@ -28,7 +25,7 @@ plot_tibble <- res_tibble %>%
   pivot_longer(cols = !x, names_to = 'Function', values_to = 'Value')
 
 # generate plot
-bspline_plot <- ggplot(data = plot_tibble) +
+monomial_plot <- ggplot(data = plot_tibble) +
   geom_line(aes(x = x, y = Value, col = Function)) +
   #ggtitle("B-spline Basis") +
   theme_light() +
@@ -41,5 +38,5 @@ bspline_plot <- ggplot(data = plot_tibble) +
         legend.text = element_text(size = 20))
 
 # save plot in appropriate folder
-ggsave(filename = '../Graphics/Bspline_Basis.pdf', plot = bspline_plot,
+ggsave(filename = '../Graphics/Monomial_Basis.pdf', plot = bspline_plot,
        width = 20, height = 8, units = "in", dpi = 600)

### 2022-01-31 Code/Plot_Generators/Monomial_basis_plot.R
Correction

@@ -11,10 +11,10 @@ n_points <- 1000
 points <- seq(from = 0, to = 1, length.out = n_points)
 
 # function factory that generates the basis functions
-bspline_basis <- create.monomial.basis(rangeval = c(0,1), nbasis = 8)
+monomial_basis <- create.monomial.basis(rangeval = c(0,1), nbasis = 8)
 
 # Calculate basis functions at points
-res_matrix <- eval.basis(evalarg = points, basisobj = bspline_basis)
+res_matrix <- eval.basis(evalarg = points, basisobj = monomial_basis)
 
 # convert to tibble
 res_tibble <- cbind(x = points, as_tibble(res_matrix))
@@ -38,5 +38,5 @@ monomial_plot <- ggplot(data = plot_tibble) +
         legend.text = element_text(size = 20))
 
 # save plot in appropriate folder
-ggsave(filename = '../Graphics/Monomial_Basis.pdf', plot = bspline_plot,
+ggsave(filename = '../Graphics/Monomial_Basis.pdf', plot = monomial_plot,
        width = 20, height = 8, units = "in", dpi = 600)

### 2022-01-31 Paper/main.tex
Added Monomial basis plot
Graphics Update
More stuff done on the simulation results, some stuff for introduction

--- 2022-01-31 Paper/main.tex
@@
 	\end{itemize}	
-	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature.
-Classical statistical methods can often process this data, but only FDA allows extracting information given by the smoothness of the underlying process (cf.
+	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.
+Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf.
 \cite{levitin_introduction_2007}).
@@
 \cite[S.~17]{kokoszka_introduction_2017}).\\
-	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process.
-In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
+	 Consider the case of a dataset which is containing observations of an underlying continuous process, measured at some discrete points $t_{j,i}$:
+
+\begin{equation}
+	x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]
+\end{equation}
+
+			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared spectrum which we will use for the simulation and application.
+This continuous underlying process for which
+ $x_i(t)$ exists $\forall t \in [T_1, T_2]$ is only observed at the discrete measurement points.
+This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable.
+To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
+%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
 \cite{Das_2019}).\\
-	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting.
-We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:
+The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:
 
@@
 
-	\begin{equation}\label{score_approx}
+	\begin{equation}
 		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
@@
 
-	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.
-
-	\begin{equation}
-		\begin{split}
-			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
-			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
-		\end{split}
-	\end{equation}
-
-	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogues is more interesting as a representation of an observation.
-
-	\begin{equation}
-		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
-			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
-		\end{split}
-	\end{equation}
-
-	This, however, is a simplification for the purposes of real-world estimation as in most implementations the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely.
-Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
-
-	\begin{equation}
-		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
-			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
-		\end{split}
-	\end{equation}
-
-	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following.
-To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
-Additionally, the following approximation also truncates the basis for the expansion of the coeffieicnt function at the same parameter $L$ that was used for the approximation of the principal components and scores.
+	{\color{red} We have to clean this up theoretically.
+Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.
+In these equations the sum over m and the sum over j should be exchanged.\\
+	M is the chosen number of principal components}
+
+	\begin{equation}
+		\begin{split}
+			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{m \in \mathcal{M}} \left[ \xi^m(\omega) \sum_{j \in \mathcal{I}} b_j \nu^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon(\omega) \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \xi^m(\omega) \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{m  = 1}^{M}\left[ \xi^m(\omega) \sum_{j = 1}^{J} b_j \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+		\end{split}
+	\end{equation}
+
+	Using sample analogues, we can use this form to obtain the following approximation.
+
+	\begin{equation}\label{fpc_exp_transf}
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s +  \sum_{m  = 1}^{M} \left[ \hat{\xi}^m(\omega) \sum_{j = 1}^{J} b_j \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
+	\end{equation}
+
+	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.
 
@@
 			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
-			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon(\omega)
+			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}Z^{m,L}}+ \epsilon(\omega)
 		\end{split}
@@
 	For the simulation study, we deviate from the standard simulation setting.
-Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near Infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
+Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
 NIR- spectroscopy allows to analyse samples of gasoline much faster, cheaper and with the same reproducibility as standard tests while not destroying the sample (cf.
@@
 	\end{equation}
+	\vspace{	0.2cm}
 
@@
 	\subsubsection{Basis Expansion Regression}
-	This follows from the \hyperref[basis_exp_transf]{Basis Expansion Transformation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, tractable with typical multivariate regression theory.
+	The following results origin from the \hyperref[basis_exp_transf]{\textbf{Estimation using Basis-Representation}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
 
@@
 	Due to the high collinearity of these basis, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
-For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines, but show the weakest performance for the setup $f_2, Y_1$.
-In the setup with high noise, $f_2, Y_2$ this weakness is still visible, but way less pronounced.
+For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
+For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
+This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
 
@@
 	\paragraph{Fourier Basis}
-	The results are simialar to the previous results: For $f_1$, the simulation chooses a smaller number of fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
+	For $f_1$, the simulation chooses a smaller number of fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
 With the low signal-to-noise ratio, the simulation chooses a smaller number to account for the higher noise in the response variable.
+The fourier basis functions performs the best in each setup for the basis expansion regression.
+When recalling $f_1$ and $f_2$, both, but especially $f_1$ shows similar curvature order across the domain which contributes to the strong performance of this basis.
 	\\
 
-	The results follow the Bias-Variance Tradeoff: The function $f_1$ is rather smooth and not much bias is introduced here when choosing a small number of basis functions since $f_1$ lacks pronounced peculiarities.
-For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$: We can choose a higher number of basis functions since the amount of bias is decrasing much faster in the number of basis functions than the variance is increasing, compared to $f_1$.
+	For all specifications, the effect of the Bias-Variance tradeoff can be observed:: The function $f_1$ is rather smooth and not much bias is introduced here when choosing a small number of basis functions since $f_1$ lacks pronounced peculiarities.
+For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$: We can choose a higher number of basis functions since the amount of bias is deceasing much faster in the number of basis functions than the variance is increasing, compared to $f_1$.
 
 	\subsubsection{Functional Principal Component Regression}
+	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
+
 	\paragraph{Monomial Basis}

### 2022-01-31 Paper/main.tex

--- 2022-01-31 Paper/main.tex
@@
 		\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
-		\caption{Fourier basis functions for $i = 1,\dots,6$}
+		\caption{Fourier basis functions for $i = 1,\dots,7$}
 	\end{figure}
@@
 		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
-		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
+		\caption{B-spline basis functions of order 4 for 8 equidistant knots on $[0,1]$}
 	\end{figure}
+
+	\begin{figure}[H]\label{monomial_basis}
+		\includegraphics[width = \textwidth]{../Graphics/Monomial_Basis.pdf}
+		\caption{Monomial basis functions of degree 0 to 7}
+	\end{figure}
+
 \newpage

### 2022-02-01 Paper/main.tex
Added some crowded matrix notation.

@@
 
-	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.
+	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
+
+	\begin{equation}
+		Y = \begin{pmatrix}
+				y_1 \\ \vdots \\ y_n
+			\end{pmatrix}, \quad
+		Z = \begin{pmatrix}
+				1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
+				\vdots & \vdots & \ddots & \vdots \\
+				1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
+			\end{pmatrix}
+	\end{equation}
+
+	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
+
+	\begin{equation}
+		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
+	\end{equation}
 
@@
 		\end{split}
+	\end{equation}
+
+	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
+
+	\begin{equation}
+		Y = \begin{pmatrix}
+			y_1 \\ \vdots \\ y_n
+			\end{pmatrix}, \quad
+		Z = \begin{pmatrix}
+			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
+			\vdots & \vdots & \ddots & \vdots \\
+			1 & \tilde{\xi}^{1,L}_{3} & \dots & \tilde{\xi}^{M,L}_{3}
+			\end{pmatrix}
+	\end{equation}
+
+	We can then derive the following estimators.
+
+	\begin{equation}
+			\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
 	\end{equation}

### 2022-02-01 Paper/main.tex
Paper work 3.2

@@
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
-To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.\\
+To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.
 Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
@@
 	\begin{equation}
-		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
+		\lvert \lvert f \rvert \rvert^2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
 	\end{equation}
@@
 	All functions $f$ satisfying the above condition are called square-integrable functions.
-Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.\\
+Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.
 Its inner product is defined as
@@
 
-	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.
+	 $\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
+We also focus on the interval $[0,1]$ for the purpose of this paper.
+The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
 
@@
 
-	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
-
 	\begin{equation}
@@
 
-	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
+	where $\Omega$ is a sample space. The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
 

### 2022-02-01 Paper/main.tex
Small correction

--- 2022-01-31 Paper/main.tex
@@
 
-			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared spectrum which we will use for the simulation and application.
+			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application.
+NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other.
+{\color{green} For more details refer to the appendix SECTION ??!??!}.
 This continuous underlying process for which
@@
     The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}.
-    Both functions were created such that the inner product $\langle NIR_{sim}, f \rangle, f \in \{f_1(t), f_2(t)\}$ creates responses similar to the original octane ratings of the gasoline dataset.
+The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline dataset.
 
@@
 	\subsection{Results}
-	{\color{green}DESCRIBE RESULTS: make paragraph for each setup? so 6 paragraphs? Like this: }
 
@@
 	\section{Appendix}
+
+	\subsection{Near-infrared (NIR) Spectroscopy}
+	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
+It therefore measures the absorption and interaction of this spectrum of radiation with the sample.
+NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another big advantage is that it does not need a reagent and thus does not destroy the sample.
+It is used for analysis in different sectors and fields, like the agrochemical industry but also in healthcare.
+Its non-invasive nature makes it also to an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy is able to detect the worsening of the blood glucose metabolic dysfunction (cf .
+\cite{FR_li_et_al_2020}).
+In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy.
+According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (eg.: carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).
+While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al.
+1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characktersitics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
 

### 2022-02-01 Paper/main.tex
Correction on 3.2

@@
 
-	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.
+	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
+We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
 
@@
 For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
-
-	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
 

### 2022-02-01 Paper/main.tex
Auto stash before merge of "main" and "origin/main"

@@
 
-	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.
+		A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
+
+	\begin{equation}
+		Y = \begin{pmatrix}
+			y_1 \\ \vdots \\ y_n
+		\end{pmatrix}, \quad
+		Z = \begin{pmatrix}
+			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
+			\vdots & \vdots & \ddots & \vdots \\
+			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
+		\end{pmatrix}
+	\end{equation}
+
+	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
+
+	\begin{equation}
+		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
+	\end{equation}
 
@@
 		\end{split}
+	\end{equation}
+
+	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
+
+	\begin{equation}
+		Y = \begin{pmatrix}
+			y_1 \\ \vdots \\ y_n
+		\end{pmatrix}, \quad
+		Z = \begin{pmatrix}
+			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
+			\vdots & \vdots & \ddots & \vdots \\
+			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
+		\end{pmatrix}
+	\end{equation}
+
+	We can then derive the following estimators.
+
+	\begin{equation}
+		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
 	\end{equation}

### 2022-02-01 Paper/main.tex
3.6 KL

@@
 	\end{equation}
-	{\color{orange}suggestion from here}
-	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$.
+	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
 Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
@@
 	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
-Moreover, $K$ holds following traits:
-
-		\begin{enumerate}
-			\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
-			\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
-			\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
-		\end{enumerate}
-
-	Therefore, we can approximate the function $X$ with first few eigenfunctions.
-The functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g.
+Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index.
+Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g.
+$Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m > n$).
+Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
+
+	%\begin{enumerate}
+	%\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
+	%\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
+	%\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
+	%\end{enumerate}
+	%Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g.
 $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$).
@@
 	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.
+The proofs are provided at \ref{Proof1} and \ref{Proof2}.
 
@@
 	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
-{\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}
 
@@
 		\begin{enumerate}
-			\item $\mathbb{E}\left[\xi_j(\omega)\right] = 0$
-			\item $Var\left(\xi_j(\omega)\right) = \lambda_i$
-			\item $Cov\left(\xi_j(\omega), \xi_k(\omega)\right) = 0$ if $j \neq k$
+			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
+			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
+			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
 		\end{enumerate}
@@
 	\begin{equation}
-		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
+		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
 	\end{equation}

### 2022-02-01 Paper/main.tex
Small correction

@@
 	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
-A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
+{\color{orange} How about hereby restricting the $\mathbb{F} = \mathbb{R}$, otherwise we would need to put something additional at 4.}A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
 
@@
 	\begin{equation}
-		\lvert \lvert f \rvert \rvert^2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
+		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
 	\end{equation}
@@
 	\subsection{Approximation and Smoothing via Basis Truncation}
-	{\color{red} Write something about how to approximate functions by truncating the basis.}
 	As above-mentioned, the realized curves can be estimated with basis functions.
@@
 Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g.
-$Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m > n$).
+$Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$).
 Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
+The proofs are provided at \ref{Proof1} and \ref{Proof2}.
 
@@
 
-	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.
-The proofs are provided at \ref{Proof1} and \ref{Proof2}.
+	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.
 

### 2022-02-01 Paper/main.tex
merge

--- 2022-02-01 Paper/main.tex
@@
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
-To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.
+To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.\\
 	Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
@@
 	\begin{equation}
-		\lvert \lvert f \rvert \rvert^2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
+		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
 	\end{equation}
@@
 	All functions $f$ satisfying the above condition are called square-integrable functions.
-Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.
+Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.\\
 	Its inner product is defined as
@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
-We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
+	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.
 
@@
 For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
+
+	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
 
@@
 	\begin{equation}
-		x(t) = \sum_{i \in \mathcal{I}} c_i(t -w)^{i}
+		x(t) = \sum_{i = 0, i \in \mathcal{I}} c_i(t -w)^{i}
 	\end{equation}
@@
 
-		A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
-
-	\begin{equation}
-		Y = \begin{pmatrix}
-			y_1 \\ \vdots \\ y_n
-		\end{pmatrix}, \quad
-		Z = \begin{pmatrix}
-			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
-			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
-		\end{pmatrix}
-	\end{equation}
-
-	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
-
-	\begin{equation}
-		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
-	\end{equation}
+	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.
 
@@
 		\end{split}
-	\end{equation}
-
-	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
-
-	\begin{equation}
-		Y = \begin{pmatrix}
-			y_1 \\ \vdots \\ y_n
-		\end{pmatrix}, \quad
-		Z = \begin{pmatrix}
-			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
-			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
-		\end{pmatrix}
-	\end{equation}
-
-	We can then derive the following estimators.
-
-	\begin{equation}
-		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
 	\end{equation}

### 2022-02-02 Code/Application_Functions.R
bspline fpcr nharm 4 sim

@@ -176,3 +176,387 @@ bspline_appl_function <- function(rep, fold_size, seed, debug = FALSE) {
   # return object containing averaged cv_scores
   return(CV_container)
 }
+
+### fourier Application function
+fourier_appl_function <- function(rep, fold_size, seed, even_basis = FALSE, debug = FALSE) {
+  set.seed(seed)
+  
+  # load NIR data
+  data(gasoline)
+  NIR <- as.matrix(gasoline$NIR)
+  octane <- gasoline$octane
+  
+  # calculate number of folds
+  n_folds <- 60 %/% fold_size
+  
+  # set up grid
+  grid <- seq(0, 1, length.out = 401)
+  
+  # specify number of basis functions that should be considered
+  n_basis <- seq(from = 4, to = 15, by = 1)
+  
+  # set up container for averaged cross validation scores
+  CV_container <- as.data.frame(
+    matrix(data = 0, nrow = length(n_basis), ncol = 5)
+  )
+  
+  colnames(CV_container) <- c(
+    "CV_score", "n_basis", "fold_size", "n_folds", "success_count"
+  )
+  
+  CV_container$n_basis <- n_basis
+  CV_container$fold_size <- fold_size
+  CV_container$n_folds <- n_folds
+  CV_container$success_count <- rep(x = 0, times = length(n_basis))
+  
+  # create basis functions
+  if (even_basis == TRUE) {
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) {
+        if (j %% 2 == 1) {
+          return(create.fourier.basis(rangeval = c(0, 1), nbasis = j))
+        } else {
+          return(create.fourier.basis(rangeval = c(0, 1), nbasis = j, dropind = j))
+        }
+      }
+    )
+  } else {
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) create.fourier.basis(rangeval = c(0, 1), nbasis = j)
+    )
+  }
+  
+  # prepare objects for functional linear regression
+  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
+  
+  betafdPar2_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) fdPar(basis_functions[[i]])
+  )
+  
+  betalist_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) {
+      list(
+        const = betafdPar1,
[…]

### 2022-02-02 Code/Main_Application.R

@@ -16,16 +16,16 @@ bspline_appl <- bspline_appl_function(fold_size = 5, rep = 250, seed = 100, debu
 saveRDS(object = bspline_appl, file = 'Results/Paper/Application/bspline_appl.RDS')
 write_csv(x = bspline_appl, file = 'Results/Paper/Application/bspline_appl.csv')
 
+fourier_appl <- fourier_appl_function(fold_size = 5, rep = 250, seed = 100, even_basis = FALSE, debug = TRUE)
+saveRDS(object = fourier_appl, file = 'Results/Paper/Application/fourier_appl.RDS')
+write_csv(x = fourier_appl, file = 'Results/Paper/Application/fourier_appl.csv')
+
+monomial_appl <- monomial_appl_function(fold_size = 5, rep = 250, seed = 100, debug = TRUE)
+saveRDS(object = monomial_appl, file = 'Results/Paper/Application/monomial_appl.RDS')
+write_csv(x = monomial_appl, file = 'Results/Paper/Application/monomial_appl.csv')
+
 ### Not yet implemented only for structure
 
-# fourier_appl <- fourier_appl_function(fold_size = 5, rep = 250, seed = 100, even_basis = FALSE, debug = TRUE)
-# saveRDS(object = fourier_appl, file = 'Results/Paper/Application/fourier_appl.RDS')
-# write_csv(x = fourier_appl, file = 'Results/Paper/Application/fourier_appl.csv')
-# 
-# monomial_appl <- monomial_appl_function(fold_size = 5, rep = 250, seed = 100, debug = TRUE)
-# saveRDS(object = monomial_appl, file = 'Results/Paper/Application/monomial_appl.RDS')
-# write_csv(x = monomial_appl, file = 'Results/Paper/Application/monomial_appl.csv')
-# 
 # ### Run Application for fpcr
 # bspline_fpcr_appl <- bspline_fpcr_appl_function(fold_size = 5, rep = 250, seed = 100, debug = TRUE)
 # saveRDS(object = bspline_fpcr_appl, file = 'Results/Paper/Application/bspline_fpcr_appl.RDS')

### 2022-02-02 Paper/main.tex

--- 2022-02-01 Paper/main.tex
@@
 \cite[S.~17]{kokoszka_introduction_2017}).\\
-	 Consider the case of a dataset which is containing observations of an underlying continuous process, measured at some discrete points $t_{j,i}$:
-
-\begin{equation}
-	x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]
-\end{equation}
 
@@
 
-	\subsection{Bases of $\mathbb{L}^2$} % Maybe change title due to monomial and bspline basis not ful;filling this property
+	\subsection{Bases of $\mathbb{L}^2$} 
+	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
 	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
@@
 	\paragraph{Monomial Basis}
+	{\color{red} No shift parameter in implementation in fda.}
 This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
@@
 	A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
-Let $S_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
+Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
 
@@
 	\subsection{Functional Data Sets}
+
+	Consider the case of a dataset which is containing observations of an underlying continuous process, measured at some discrete points $t_{j,i}$:
+
+	\begin{equation}
+		x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]
+	\end{equation}
+
 	In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions.
@@
 	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. 
-To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
+	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
 Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$.
@@
 
-	This decomposition can be used to express the random vector $V(\omega)$ in the following way.
-
-	\begin{equation}
-		V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
-	\end{equation}
-
-	where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\
+	%This decomposition can be used to express the random vector $V(\omega)$ in the following way.
+
+	%\begin{equation}
+	%	V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
+	%\end{equation}
+
+	%where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\
 
@@
 	\end{equation}
-	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+	%where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
 Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
-	\begin{equation}
-		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
-	\end{equation}
+	%\begin{equation}
+%		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
+%	\end{equation}
 
@@
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(t)
+		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t)
 	\end{equation}
@@
 
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: i \in \mathcal{M}\}$ as the solutions of the following equation.
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
 {\color{red} I think the number of principal components has to be smaller then the number of observations.
@@
 			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
-			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
+			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
 		\end{split}

### 2022-02-02 Paper/main.tex
Random function

@@
 	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
-{\color{orange} How about hereby restricting the $\mathbb{F} = \mathbb{R}$, otherwise we would need to put something additional at 4.}A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
+In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
+A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
 
@@
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
+	The inner product naturally defines a norm and an associated distance on the vector space as follows.
 
@@
 
-	\subsection{Hilbert Space of Square-Integrable Functions}
+	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} $\mathbb{L}^2[0,1]$ space and Random Function}}
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
@@
 	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
-We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
-
+We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
+	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
+The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process.
+The collection of such sample curves constitutes a functional data set.
 	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
@@
 
-	\begin{equation}
-	\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
-	\end{equation}
-
-	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
-
-	\subsection{Bases of $\mathbb{L}^2$} 
+	%\begin{equation}
+	%\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
+	%\end{equation}
+
+	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
 	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
@@
 	\paragraph{Monomial Basis}
-	{\color{red} No shift parameter in implementation in fda.}
-This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
-The polynomial of the form
+	{\color{red} No shift parameter in implementation in fda.} Every result of monomial basis expansion is the Taylor series of some function. 
+	This is the basis that is needed to build polynomials, one of the best-known ways to expand a function. The polynomial of the form
 
@@
 	\end{equation}
-	%where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
 Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
-	%\begin{equation}
-%		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
-%	\end{equation}
+	\begin{equation}
+		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
+	\end{equation}
 
@@
 				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
+				= & \int_{0}^{1} \int_{\Omega} F(t) dP(\omega) \nu_{j}(t) dt\\
 				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
@@
 				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
-				= & \int_{0}^{1} \left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right) \nu_{k}(t) dt \\
-				= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
+				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
+				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
+				= & \int_{0}^{1}{\color{red}[K\nu_{j}](t)}\nu_{k}(t)dt\\
 				= & \langle K \nu_{j}, \nu_{k} \rangle\\

### 2022-02-02 Paper/main.tex
deltas in basis expansion estimation

@@
 	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
+For the sake of clarity the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
 
@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right] \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right]
+			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
+			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
 		\end{split}
@@
 	\begin{equation}\label{score_approx}
-		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
+		\begin{split}
+			\hat{\xi}_{i}^m & = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
+			& \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] =: \tilde{\xi}^{m,L}_{i}
+		\end{split}
 	\end{equation}
@@
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
-Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
-
-	\begin{equation}
-		\beta(t) = \sum_{j = 1}^{\infty} b_j \phi_j(t)
+Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
+
+	\begin{equation}
+		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
 	\end{equation}
@@
 	\begin{equation}
-			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} b_j Z_j(\omega) + \epsilon(\omega)
+		\begin{split}
+			Y(\omega) & = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) X(\omega)(s) \mathrm{d}s +  \int_{0}^{1} \delta_{\beta}^{J}(s) X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
+		\end{split}
 	\end{equation}
@@
 			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
-			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega) 
-			\approx \alpha + \sum_{j = 1}^{J} \left[b_j \sum_{k = 1}^{K}  d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega)
+			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} a_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j  \phi_j(s) + \delta_{\beta}^{J}(s)\right)} {\color{red}\left(\sum_{k = 1}^K a_k(\omega)  \psi_k(s) + \delta_{X}^{K}(\omega)(s)\right)} \right]\mathrm{d}s + \epsilon(\omega)\\
+			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s
+			 + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
 		\end{split}
@@
 	\begin{equation}
-			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[a_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 	\end{equation}
@@
 	\begin{equation}\label{simplified_model_basis_equation}
-		Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
+		\begin{split}
+			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
+			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
+		\end{split}
 	\end{equation}

### 2022-02-02 Paper/main.tex
Truncation errors in fpca estimation

@@
 	\begin{equation}\label{score_approx}
-		\begin{split}
-			\hat{\xi}_{i}^m & = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
-			& \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] =: \tilde{\xi}^{m,L}_{i}
+			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
+	\end{equation}
+
+	And we can define the following objects:
+
+	\begin{equation}
+		\begin{split}
+			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] \\
+			\delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} = \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
+			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) \quad \quad \quad
+			\delta_{\nu, m}^L(t) := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
 		\end{split}
@@
 			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j  \phi_j(s) + \delta_{\beta}^{J}(s)\right)} {\color{red}\left(\sum_{k = 1}^K a_k(\omega)  \psi_k(s) + \delta_{X}^{K}(\omega)(s)\right)} \right]\mathrm{d}s + \epsilon(\omega)\\
-			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s
-			 + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
+			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K a_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s\\
+			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
 		\end{split}
@@
 			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
-			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
+			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
 		\end{split}
@@
 
+	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
+
+	\begin{equation}\label{fpcr_reg_both_expansions}
+		\begin{split}
+			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
+		\end{split}
+	\end{equation}
+
 	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following.
@@
 Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
+
+	For convenience, define the following notation:
+
+	\begin{equation}
+		\tilde{\alpha}^L = \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{L}(s) \hat{\mu}(s) \mathrm{d}s
+	\end{equation}
+
+	Then Equation \ref{fpcr_reg_both_expansions} can be expressed as follows.
+
+	\begin{equation}
+		\begin{split}
+			y_i & = \tilde{\alpha}^L
+			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
+			+ \epsilon_i \\
+			& = \tilde{\alpha}^L
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
+			+ \epsilon_i \\
+			& \approx \tilde{\alpha}^L
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+		\end{split}
+	\end{equation}
+
 	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
-
-	\begin{equation}
-		\begin{split}
-			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
-			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
-			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon_i
-			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon_i
-		\end{split}
-	\end{equation}
 

### 2022-02-02 Paper/main.tex
Proofs

@@
 	\subsection{Lemma} \label{Proof1}
-	{\color{orange} We might put the below theorems for KL.
-The deterministic basis expansions are pretty clear about why we can use the truncation version by itself.
-In contrast, I feel like that for the case of KL it does not.
-And in the centered case?}
-	The coefficients $\xi_{j}$ satisfy the following:
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu_j\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi_{j}$ of basis functions satisfy the following properties:
 	\begin{enumerate}
@@
 	\begin{proof}
-		To obtain the first result, we can show that
-		\begin{equation}
-			\begin{split}
-				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
-				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
-				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
-				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
-				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
-			\end{split}
-		\end{equation}
-		where the constant function is always an eigenfunction of the operater $K$.
-It leads the inner product to 0 due to orthonormality of eigenfunctions.
-{\color{red} Another way to prove or use centered mean}
-		For the case of centered process
+		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
 		\begin{equation}\label{Lemma1}
@@
 				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} \int_{\Omega} F(t) dP(\omega) \nu_{j}(t) dt\\
-				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
+				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu_{j}(t) dt\\
+				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu_{j}(t) dt = 0
 			\end{split}
@@
 		\end{equation}
-		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
+		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
 		\begin{equation}\label{Lemma3}
@@
 		\end{equation}
+		The original process also has the same properties as the centered one since
+		\begin{equation}
+			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{j=1}^{\infty}\xi_{j}\nu_{j}(t)
+		\end{equation}
 	\end{proof}
 
-	\subsection{Karhunen-Lo\'{e}ve expansion} \label{Proof2}
-	Let $F : [0,1]  \rightarrow \mathbb{R}$ be a centered mean-square continuous stochastic process with $F \in \mathbb{L}^{2}[0,1]$.
-Then there exists a basis ${\xi_{i}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
-	\begin{equation}
-		F(t) = \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
-	\end{equation}
-	where coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} F(t)(\omega) \nu_{j}(t)dt$ and satisfy the following conditions.
+	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
+	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$.
+Then there exists a basis ${\xi_{j}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
+	\begin{equation}
+		X(t) = \mu(t) + \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
+	\end{equation}
+	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} X(t)(\omega) \nu_{j}(t)dt$. These coefficients satisfy the following conditions.
 	\begin{enumerate}
@@
 		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$.
-With the fact that $\xi_{j}(\omega) = \int_{0}^{1} F(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma.
-We prove it by considering
-		\begin{equation}
-			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
-		\end{equation}
-
+With the solution that $\xi_{j}(\omega) = \int_{0}^{1} X(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma \ref{Proof1}, We prove this expansion by considering
+		\begin{equation}
+			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
+			= \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
+		\end{equation}
+		where $F(t)$ is the centered process of $X(t)$.
 		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
@@
 
-		Now, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}),
+		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since F(t) is the centered process. Now, take the second term
 		\begin{equation}\label{Thr2}
 			\begin{split}
-				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} \xi_{j}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} \bigg(\int_{0}^{1} F_{s}\nu_{i}(s)ds\bigg) \xi_{j}(t) \right]\\
-				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} \mathbb{E}[F(t)F(s)]\nu_{j}(s)ds\bigg)\nu_{j}\\
-				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} c(t,s) \nu_{j}(s)ds\bigg)\nu_{j}\\
-				= & \sum_{j=1}^{n}[K\nu_{j}](t)\nu_{j} = \sum_{j=1}^{n}\lambda_{j}\nu_{j}^{2}
+				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} {\color{red}\xi_{j}}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} {\color{red}\bigg(\int_{0}^{1} F(s)\nu_{j}(s)ds\bigg)} \nu_{j}(t) \right]\\
+				= & \mathbb{E} \left[ \sum_{j=1}^{n} \bigg(\int_{0}^{1} F(t)F(s)\nu_{j}(s)ds\bigg) \nu_{j}(t) \right]\\
+				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu_{j}(s)ds\bigg)\nu_{j}(t)\\
+				= & \sum_{j=1}^{n} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu_{j}(s)ds\bigg)}\nu_{j}(t)\\
+				= & \sum_{j=1}^{n}{\color{teal}[K\nu_{j}](t)}\nu_{j}(t) \\
+				= &\sum_{j=1}^{n}{\color{teal}\lambda_{j}\nu_{j}(t)}\nu_{j}(t) = \sum_{j=1}^{n}\lambda_{j}\nu_{j}(t)^{2}
 			\end{split}

### 2022-02-02 Paper/main.tex
Small correction

@@
 	\begin{equation}
-		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
-	\end{equation}
-
-	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator.
+		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
+	\end{equation}
+
+	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator(cf.
+\cite{alexanderian_KLexpansion_2015}).
 Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index.
@@
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t)
+		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
 	\end{equation}
@@
 	\end{equation}
-	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} X(t)(\omega) \nu_{j}(t)dt$. These coefficients satisfy the following conditions.
+	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} (X(t)(\omega) - \mu(t)) \nu_{j}(t)dt$.
+These coefficients satisfy the following conditions.
 	\begin{enumerate}
@@
 		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$.
-With the solution that $\xi_{j}(\omega) = \int_{0}^{1} X(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma \ref{Proof1}, We prove this expansion by considering
+With the reminder that $\xi_{j}(\omega)$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
 		\begin{equation}

### 2022-02-02 Paper/main.tex
Note on the geneartion of similar curves. Has to be more detailed.

@@
 These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:
+
+		 {\color{blue} We should mention how we derived the original principal components.
+(bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set.
+As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}
 

### 2022-02-02 Paper/main.tex
Rewriting motivation, small introduction on roughness penalties, literature reveiw

--- 2022-02-02 Paper/main.tex
@@
 	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
-In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
-A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
+{\color{orange} How about hereby restricting the $\mathbb{F} = \mathbb{R}$, otherwise we would need to put something additional at 4.}A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
 
@@
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space as follows.
+	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
 
@@
 
-	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} $\mathbb{L}^2[0,1]$ space and Random Function}}
+	\subsection{Hilbert Space of Square-Integrable Functions}
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
@@
 	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
-We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
-	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
-The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process.
-The collection of such sample curves constitutes a functional data set.
+We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
+
 	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
@@
 
-	%\begin{equation}
-	%\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
-	%\end{equation}
-
-	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
+	\begin{equation}
+	\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
+	\end{equation}
+
+	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
+
+	\subsection{Bases of $\mathbb{L}^2$} 
 	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
@@
 	\paragraph{Monomial Basis}
-	{\color{red} No shift parameter in implementation in fda.} Every result of monomial basis expansion is the Taylor series of some function. 
-	This is the basis that is needed to build polynomials, one of the best-known ways to expand a function. The polynomial of the form
+	{\color{red} No shift parameter in implementation in fda.}
+This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
+The polynomial of the form
 
@@
 	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
-For the sake of clarity the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
 
@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
-			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
+			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right] \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right]
 		\end{split}
@@
 	\begin{equation}\label{score_approx}
-			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
-	\end{equation}
-
-	And we can define the following objects:
-
-	\begin{equation}
-		\begin{split}
-			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] \\
-			\delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} = \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
-			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) \quad \quad \quad
-			\delta_{\nu, m}^L(t) := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
-		\end{split}
+		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
 	\end{equation}
@@
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
-Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
-
-	\begin{equation}
-		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
+Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
+
+	\begin{equation}
+		\beta(t) = \sum_{j = 1}^{\infty} b_j \phi_j(t)
 	\end{equation}
@@
 	\begin{equation}
-		\begin{split}
-			Y(\omega) & = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) X(\omega)(s) \mathrm{d}s +  \int_{0}^{1} \delta_{\beta}^{J}(s) X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
-		\end{split}
+			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} b_j Z_j(\omega) + \epsilon(\omega)
 	\end{equation}
@@
 			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
-			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} a_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
-			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j  \phi_j(s) + \delta_{\beta}^{J}(s)\right)} {\color{red}\left(\sum_{k = 1}^K a_k(\omega)  \psi_k(s) + \delta_{X}^{K}(\omega)(s)\right)} \right]\mathrm{d}s + \epsilon(\omega)\\
-			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K a_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s\\
-			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
+			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
+			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega) 
+			\approx \alpha + \sum_{j = 1}^{J} \left[b_j \sum_{k = 1}^{K}  d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega)
 		\end{split}
@@
 	\begin{equation}
-			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[a_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
+			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
 	\end{equation}
@@
 	\begin{equation}\label{simplified_model_basis_equation}
-		\begin{split}
-			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
-			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
-		\end{split}
+		Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
 	\end{equation}
@@
 			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
-			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
-			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
+			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
+			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
 		\end{split}
@@
 
-	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
-
-	\begin{equation}\label{fpcr_reg_both_expansions}
-		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
-		\end{split}
-	\end{equation}
-
 	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following.
@@
 Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
-
-	For convenience, define the following notation:
-
-	\begin{equation}
-		\tilde{\alpha}^L = \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{L}(s) \hat{\mu}(s) \mathrm{d}s
-	\end{equation}
-
-	Then Equation \ref{fpcr_reg_both_expansions} can be expressed as follows.
-
-	\begin{equation}
-		\begin{split}
-			y_i & = \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
-			+ \epsilon_i \\
-			& = \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
-			+ \epsilon_i \\
-			& \approx \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
-		\end{split}
-	\end{equation}
-
 The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+
+	\begin{equation}
+		\begin{split}
+			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
+			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
+			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon_i
+			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon_i
+		\end{split}
+	\end{equation}
 
@@
 	\subsection{Motivation}
-	For the simulation study, we deviate from the standard simulation setting.
+
+	In the simulation study, we deviate from the standard simulation setting.
 Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
-NIR- spectroscopy allows to analyse samples of gasoline much faster, cheaper and with the same reproducibility as standard tests while not destroying the sample (cf.
-\cite{Bohacs_Ovadi_Salgo1998}).
+We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
+
+	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $\mathcal{K}$ for the estimation in SECTION HERE.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation.
+While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction \cite{Jolliffe_1982}.
+
+	 This setup is opposing to the often used penalized functional regression as described by \citep{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
+This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation.
+To provide intuition in this approach, let
+	 \begin{equation}
+	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
+	 \end{equation}
+	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
+A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty.
+The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}
+
+	%While this paper and its simulation does not touch upon the topic of roughness penalties in estimation and their selection, other simulations focus e.g.
+on choosing the knots of penalized splines (David Ruppert 2000) or the important choice of the smoothing parameter selection method (Thomas C.M.
+Lee, 2002).
+An overview about other variable selections methods for functional regression with an origin in the multivariate regression setting can be found in( G.
+Aneiros, S.
+Novo and P.
+Vieu)
+
+	%In the simulation study, we deviate from the standard simulation setting.
+Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
 We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
@@
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu_j\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi_{j}$ of basis functions satisfy the following properties:
+	{\color{orange} We might put the below theorems for KL.
+The deterministic basis expansions are pretty clear about why we can use the truncation version by itself.
+In contrast, I feel like that for the case of KL it does not.
+And in the centered case?}
+	The coefficients $\xi_{j}$ satisfy the following:
 	\begin{enumerate}
@@
 	\begin{proof}
-		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
+		To obtain the first result, we can show that
+		\begin{equation}
+			\begin{split}
+				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
+				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
+				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
+				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
+				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
+				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
+			\end{split}
+		\end{equation}
+		where the constant function is always an eigenfunction of the operater $K$.
+It leads the inner product to 0 due to orthonormality of eigenfunctions.
+{\color{red} Another way to prove or use centered mean}
+		For the case of centered process
 		\begin{equation}\label{Lemma1}
@@
 				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu_{j}(t) dt\\
-				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu_{j}(t) dt = 0
+				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
 			\end{split}
@@
 				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
-				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
-				= & \int_{0}^{1}{\color{red}[K\nu_{j}](t)}\nu_{k}(t)dt\\
+				= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
+				= & \int_{0}^{1} \left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right) \nu_{k}(t) dt \\
+				= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
 				= & \langle K \nu_{j}, \nu_{k} \rangle\\
@@
 		\end{equation}
-		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
+		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
 		\begin{equation}\label{Lemma3}
@@
 		\end{equation}
-		The original process also has the same properties as the centered one since
-		\begin{equation}
-			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{j=1}^{\infty}\xi_{j}\nu_{j}(t)
-		\end{equation}
 	\end{proof}
 
-	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
-	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$.
-Then there exists a basis ${\xi_{j}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
-	\begin{equation}
-		X(t) = \mu(t) + \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
-	\end{equation}
-	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} X(t)(\omega) \nu_{j}(t)dt$. These coefficients satisfy the following conditions.
+	\subsection{Karhunen-Lo\'{e}ve expansion} \label{Proof2}
+	Let $F : [0,1]  \rightarrow \mathbb{R}$ be a centered mean-square continuous stochastic process with $F \in \mathbb{L}^{2}[0,1]$.
+Then there exists a basis ${\xi_{i}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
+	\begin{equation}
+		F(t) = \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
+	\end{equation}
+	where coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} F(t)(\omega) \nu_{j}(t)dt$ and satisfy the following conditions.
 	\begin{enumerate}
@@
 		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$.
-With the solution that $\xi_{j}(\omega) = \int_{0}^{1} X(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma \ref{Proof1}, We prove this expansion by considering
-		\begin{equation}
-			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
-			= \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
-		\end{equation}
-		where $F(t)$ is the centered process of $X(t)$.
+With the fact that $\xi_{j}(\omega) = \int_{0}^{1} F(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma.
+We prove it by considering
+		\begin{equation}
+			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
+		\end{equation}
+
 		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
@@
 
-		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since F(t) is the centered process. Now, take the second term
+		Now, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}),
 		\begin{equation}\label{Thr2}
 			\begin{split}
-				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} {\color{red}\xi_{j}}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} {\color{red}\bigg(\int_{0}^{1} F(s)\nu_{j}(s)ds\bigg)} \nu_{j}(t) \right]\\
-				= & \mathbb{E} \left[ \sum_{j=1}^{n} \bigg(\int_{0}^{1} F(t)F(s)\nu_{j}(s)ds\bigg) \nu_{j}(t) \right]\\
-				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu_{j}(s)ds\bigg)\nu_{j}(t)\\
-				= & \sum_{j=1}^{n} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu_{j}(s)ds\bigg)}\nu_{j}(t)\\
-				= & \sum_{j=1}^{n}{\color{teal}[K\nu_{j}](t)}\nu_{j}(t) \\
-				= &\sum_{j=1}^{n}{\color{teal}\lambda_{j}\nu_{j}(t)}\nu_{j}(t) = \sum_{j=1}^{n}\lambda_{j}\nu_{j}(t)^{2}
+				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} \xi_{j}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} \bigg(\int_{0}^{1} F_{s}\nu_{i}(s)ds\bigg) \xi_{j}(t) \right]\\
+				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} \mathbb{E}[F(t)F(s)]\nu_{j}(s)ds\bigg)\nu_{j}\\
+				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} c(t,s) \nu_{j}(s)ds\bigg)\nu_{j}\\
+				= & \sum_{j=1}^{n}[K\nu_{j}](t)\nu_{j} = \sum_{j=1}^{n}\lambda_{j}\nu_{j}^{2}
 			\end{split}

### 2022-02-02 Paper/main.tex
Small correction to previous push

--- 2022-02-02 Paper/main.tex
@@
 For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation.
-While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction \cite{Jolliffe_1982}.
-
-	 This setup is opposing to the often used penalized functional regression as described by \citep{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
+While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+
+	 This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
 This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation.
@@
 A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty.
-The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}
+The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
 

### 2022-02-02 Paper/main.tex
Rendering

--- 2022-02-02 Paper/main.tex
@@
 
-	 This setup is opposing to the often used penalized functional regression as described by \citep{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
+	 This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
 This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation.

### 2022-02-02 Paper/main.tex
Repeating previous correction push

--- 2022-02-02 Paper/main.tex
@@
 
-	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $\mathcal{K}$ for the estimation in SECTION HERE.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation.
-While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $K$ for the estimation in SECTION HERE.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation.
+While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra (SEE APPENDIX
 

### 2022-02-02 Paper/main.tex

--- 2022-02-02 Paper/main.tex
@@
 
-	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $\mathcal{K}$ for the estimation in SECTION HERE.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation.
-While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction \cite{Jolliffe_1982}.
+	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $K$ for the estimation in SECTION HERE.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation.
+While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra (SEE APPENDIX
 

### 2022-02-02 Paper/main.tex

@@
 	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf.
-\cite[S.~17]{kokoszka_introduction_2017}).\\
-
-			 This measurement set can be viewed as set of discretized approximations of the underlying true process which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application.
+\cite[S.~17]{kokoszka_introduction_2017}).
+
+	 In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application.
 NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other.
 {\color{green} For more details refer to the appendix SECTION ??!??!}.
-This continuous underlying process for which
- $x_i(t)$ exists $\forall t \in [T_1, T_2]$ is only observed at the discrete measurement points.
 This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable.
@@
 	As above-mentioned, the realized curves can be estimated with basis functions.
-For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$.
-On the one hand, this way is not efficient since the technique with too many basis functions can even approximate a noise of the sample curves which possibly interrupts the analysis.
-On the other hand, the important information on the curves would be missed with a too-small number of basis functions.
-This discussion challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, maintain significant fluctuation.
-The basis expansion with truncation is by:
+For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$ to fit an completely unbiased estimate.
+This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis.
+On the other hand, the important information on the curves could be missed with a too-small number of basis functions.
+This discussion is subject to the Bias-Variance Tradeoff and challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, do not introduce to much bias by maintaining significant fluctuations of the curves.
+The basis expansion with truncation is defined by
 	\begin{equation}
@@
 	where $\delta(t)$ is the truncation error.
-The number $L$ is subjectively chosen but we can fix the nubmer through a more reasonable method, Cross-Validation, which minimizes Mean Squared Error (MSE).
+The number $L$ can be chosen subjectively, but also trough the application of a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or another criteria.
+The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is subject of the simulation study.
 
@@
 
-	In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions.
+	This measurement set can be viewed as set of discretized approximations of the underlying functional process:
+ $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at the discrete measurement points. 
+As in the finite dimensional setting, the concept of identically distributed and independent data is important.
+This concept generalizes intuitively to the case of functional data using the concepts for general random variables which is needed to conduct inference.
+{\color{red} Explain this better!}\\  The introduced concept of basis expansion of functions allow to express each observation $x_1$ as a realization of $X_1$, a random function of $\mathbb{L}^2[0,1]$.
+
+	%In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions.
 In the following, all random functions are assumed to realize in $\mathbb{L}^2$.
-As in the finite dimensional setting the concept of identically distributed and independent data is important.
-This concept generalizes intuitively to the case of functional data using the concepts for general random variables.
-{\color{red} Explain this better!}\\
-	An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process.
+
+	An example of such a dataset could be the dataset of 60 NIR-spectra of gasoline samples.
+Together with a set of responses, this then can be used to perform FLR, as will be subject of the simulation and application.
+
+	% COMMENT: Maybe mention both NIR and WienerProcess? 
+	%An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process.
 A definition and a plotted example for the Wiener process are given in \ref{Wiener}.
@@
 
-	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $K$ for the estimation in SECTION HERE.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation.
+	 To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation using the prediction mean-squared error.
 While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
-This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra (SEE APPENDIX
+This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra {\color{green} Link to NIR}.
 

### 2022-02-02 Paper/main.tex
Reconstitution of KL

@@
 	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
+To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$.
+Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
+Then the mean and covariance functions of $X$ are defined as follows.
 	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
@@
 
-	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$.
-Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
-	Then the mean and covariance functions of $X$ are defined as follows.
-
 	\begin{equation}\label{MeanFunction}
@@
 Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
-	\begin{equation}
+	\begin{equation}\label{HSKernal}
 		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
@@
 
-	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator(cf.
+	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf.
 \cite{alexanderian_KLexpansion_2015}).
@@
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
-	\end{equation}
-
-	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.
-
-	\begin{equation}
-		{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
-	\end{equation}
-
-	The $\xi_j(\omega)$ are then given as 
-	\begin{equation}
-		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
-	\end{equation} 
-	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
-
+		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
+	\end{equation}
+
+	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of ({\ref{HSKernal}}).
+The $\xi^{m}(\omega)$ satisfy following properties.
+%of the following equation.
+
+	%\begin{equation}
+	%	{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
+	%\end{equation}
+
+	%The $\xi_j(\omega)$ are then given as 
+	%\begin{equation}
+	%	\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - %\mu(s)\right) \nu^m(s) \mathrm{d}s
+	%\end{equation} 
+	%and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
 	\begin{multicols}{2}

### 2022-02-02 Paper/main.tex
FB

@@
 	\paragraph{Fourier Basis}
-	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
+	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric funtions.
+Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing.
+As the series was originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula.
+That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
 	\begin{equation}
@@
 	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.
-Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthogonal when the values $t_j$ are equally spaced within $T$.
+Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$.
 This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
@@
 	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of ({\ref{HSKernal}}).
-The $\xi^{m}(\omega)$ satisfy following properties.
+The random variables $\xi^{m}(\omega)$ satisfy following properties.
 %of the following equation.

### 2022-02-02 Paper/main.tex
MB

@@
 	\paragraph{Monomial Basis}
-	{\color{red} No shift parameter in implementation in fda.} Every result of monomial basis expansion is the Taylor series of some function. 
-	This is the basis that is needed to build polynomials, one of the best-known ways to expand a function. The polynomial of the form
-
-	\begin{equation}
-		x(t) = \sum_{i \in \mathcal{I}} c_i(t -w)^{i}
-	\end{equation}
-	can be expressed as a finite linear combination of the monomials $(t - w)^{i}$ with coefficient $c_i$ which form the basis
-
-	\begin{equation}
-		\phi_{i}^{M}(t) = (t-w)^k \quad i \in \mathcal{I}
-	\end{equation}
-	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
-	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
-	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase.
-This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails.
+	{\color{red} No shift parameter in implementation in fda.}  Monomial bases are trivially decompositions of every polynomial function.
+The class of non-polynomial but enough many differentiable functions can be apporximated by Taylor series, a special type of power series.
+From these concepts, a function can be smooth by a power series.
+The bases construct
+
+	\begin{equation}
+		x(t) = \sum_{i \in \mathcal{I}} c_i(t - \alpha)^{i}
+	\end{equation}
+	 which forms the basis
+
+	\begin{equation}
+		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
+	\end{equation}
+	The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
+	The shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
+	 There exists problems of collinearity of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation.
+This restricts the number of basis functions.
+Therefore, regarding the use, this may be useful for relatively simple functions.
+However, the small number of degrees makes it impossible to capture pronounced local peculiarities {\color{orange} (Isn't it good as thinking of the Taylor?
+The use of MB for local expansion?
+Need to check.)} and leads to undesirable behaviour at the tails such as Taylor expansion.
 (cf.
@@
 Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing.
-As the series was originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula.
+As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions.
 That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.

### 2022-02-02 Paper/main.tex
Some corrections

@@
 
-	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} $\mathbb{L}^2[0,1]$ space and Random Function}}
+	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} Random Function in $\mathbb{L}^2[0,1]$ space}}
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
@@
 			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
+			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$%0$ if $m \neq n$
 			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
-			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
 		\end{enumerate}
 	\end{multicols}
-
+	where $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
 	In the typical scalar setting, a similar consideration leads to the concept of principal components.
@@
 	\begin{enumerate}
-		\item $\mathbb{E}[\xi_{j}] = 0$
-		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
-		\item Var[$\xi_{j}$] = $\lambda_{j}$
+		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
+		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$% if $m \neq n$
+		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
 	\end{enumerate}
-
+	Remind that $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
 	\begin{proof}
@@
 	\begin{enumerate}
-		\item $\mathbb{E}[\xi_{j}] = 0$
-		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
-		\item Var[$\xi_{j}$] = $\lambda_{j}$
+		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
+		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$ %if $m \neq n$
+		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
 	\end{enumerate}
-
 	\begin{proof}
@@
 
-		We derive from (\ref{Lemma2}) that
+		where the covariance function $c(t,s)$ has the Hilbert-Shmidt operator as in (\ref{HSKernal}).
+It turns out the product of the eigenfunction and the corresponding eigenvalue.
+For the last term, we derive from (\ref{Lemma2}) that
 		\begin{equation}\label{Thr3}

### 2022-02-02 Code/Application_Functions.R
Application Modifications

@@ -192,8 +192,12 @@ fourier_appl_function <- function(rep, fold_size, seed, even_basis = FALSE, debu
   # set up grid
   grid <- seq(0, 1, length.out = 401)
   
-  # specify number of basis functions that should be considered
-  n_basis <- seq(from = 4, to = 15, by = 1)
+  # specfiy number of basis functions that should be considered
+  if (even_basis == TRUE) {
+    n_basis <- seq(from = 1, to = 19, by = 1)
+  } else {
+    n_basis <- seq(from = 1, to = 19, by = 2)
+  }
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -356,7 +360,7 @@ fourier_appl_function <- function(rep, fold_size, seed, even_basis = FALSE, debu
         error = function(cond) {
           # in Case an error occurs issue a warning with the corresponding message
           warning(paste0(
-            "Problem occured in run ", i, " for ", n_basis[j], " b-spline basis functions.",
+            "Problem occured in run ", i, " for ", n_basis[j], " fourier basis functions.",
             " Error message: ", cond
           ))
         }
@@ -384,7 +388,7 @@ monomial_appl_function <- function(rep, fold_size, seed, debug = FALSE) {
   grid <- seq(0, 1, length.out = 401)
   
   # specify number of basis functions that should be considered
-  n_basis <- seq(from = 4, to = 15, by = 1)
+  n_basis <- seq(from = 1, to = 6, by = 1)
   
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(
@@ -534,7 +538,7 @@ monomial_appl_function <- function(rep, fold_size, seed, debug = FALSE) {
         error = function(cond) {
           # in Case an error occurs issue a warning with the corresponding message
           warning(paste0(
-            "Problem occured in run ", i, " for ", n_basis[j], " b-spline basis functions.",
+            "Problem occured in run ", i, " for ", n_basis[j], " monomial functions.",
             " Error message: ", cond
           ))
         }

### 2022-02-02 Code/Main_Application.R

@@ -12,15 +12,15 @@ suppressMessages(library(caret))
 source("Application_Functions.R")
 
 ### Run Application for basis expansion
-bspline_appl <- bspline_appl_function(fold_size = 5, rep = 250, seed = 100, debug = TRUE)
+bspline_appl <- bspline_appl_function(fold_size = 5, rep = 1000, seed = 100, debug = TRUE)
 saveRDS(object = bspline_appl, file = 'Results/Paper/Application/bspline_appl.RDS')
 write_csv(x = bspline_appl, file = 'Results/Paper/Application/bspline_appl.csv')
 
-fourier_appl <- fourier_appl_function(fold_size = 5, rep = 250, seed = 100, even_basis = FALSE, debug = TRUE)
+fourier_appl <- fourier_appl_function(fold_size = 5, rep = 1000, seed = 100, even_basis = FALSE, debug = TRUE)
 saveRDS(object = fourier_appl, file = 'Results/Paper/Application/fourier_appl.RDS')
 write_csv(x = fourier_appl, file = 'Results/Paper/Application/fourier_appl.csv')
 
-monomial_appl <- monomial_appl_function(fold_size = 5, rep = 250, seed = 100, debug = TRUE)
+monomial_appl <- monomial_appl_function(fold_size = 5, rep = 1000, seed = 100, debug = TRUE)
 saveRDS(object = monomial_appl, file = 'Results/Paper/Application/monomial_appl.RDS')
 write_csv(x = monomial_appl, file = 'Results/Paper/Application/monomial_appl.csv')
 

### 2022-02-03 Paper/main.tex
small correction

@@
 				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
+				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s)} \nu_{k}(t) {\color{red}ds} dt\\
 				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
@@
 				= & \langle K \nu_{j}, \nu_{k} \rangle\\
-				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
-			\end{split}
-		\end{equation}
-		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
+				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \delta_{j,k}\lambda_{j}
+			\end{split}
+		\end{equation}
+		where $\delta_{j,k} = 1$ if $j = k$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
 		\begin{equation}\label{Lemma3}

### 2022-02-03 Paper/main.tex
Small questions

@@
 These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
+For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
 		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve.
@@
 
+		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}
 		 {\color{blue} We should mention how we derived the original principal components.
@@
 	\paragraph{Monomial Basis}
-	Due to the high collinearity of these basis, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
+	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order?
+Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
 For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.

### 2022-02-03 Code/Main_Simulation.R
Monomial nharm4

@@ -82,7 +82,7 @@ for (j in 2:4) {
 }
 
 # Jonghun
-for (j in 2:4) {
+for (j in 4:4) {
   for (i in 100:149) {
     test_monomial_fpcr <- fpcr_monomial_function(
       rep = 100, my_data = NULL, n_obs = 200, nharm = j, seed = i, debug = TRUE

### 2022-02-03 Paper/main.tex
Small corrections

@@
 	As above-mentioned, the realized curves can be estimated with basis functions.
-For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$ to fit an completely unbiased estimate.
+For the basis expansion, it is technically possible to use all basis functions $\phi_{j \in \mathcal{I}}$ to fit an completely unbiased estimate.
 This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis.
 On the other hand, the important information on the curves could be missed with a too-small number of basis functions.
-This discussion is subject to the Bias-Variance Tradeoff and challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, do not introduce to much bias by maintaining significant fluctuations of the curves.
+In that sense, this discussion is subject to the Bias-Variance Tradeoff.
+It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves.
 The basis expansion with truncation is defined by
@@
 	\end{equation}
-	where $\delta(t)$ is the truncation error.
-The number $L$ can be chosen subjectively, but also trough the application of a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or another criteria.
-The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is subject of the simulation study.
+	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
+The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria.
+The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.
 

### 2022-02-03 Code/Application_Functions.R
FPCA Application Functions

@@ -734,10 +734,379 @@ bspline_fpcr_appl_function <- function(rep, fold_size, nharm, seed, debug = FALS
   
 ### fourier fpcr Application function
 fourier_fpcr_appl_function <- function(rep, fold_size, nharm, seed, even_basis = FALSE, debug = FALSE){
+  set.seed(seed)
   
+  # load NIR data
+  data(gasoline)
+  NIR <- as.matrix(gasoline$NIR)
+  octane <- gasoline$octane
+  
+  # calculate number of folds
+  n_folds <- 60 %/% fold_size
+  
+  # set up grid
+  grid <- seq(0, 1, length.out = 401)
+  
+  # specfiy number of basis functions that should be considered
+  if (even_basis == TRUE) {
+    n_basis <- seq(from = 1, to = 19, by = 1)
+  } else {
+    n_basis <- seq(from = 1, to = 19, by = 2)
+  }
+  
+  # set up container for averaged cross validation scores
+  CV_container <- as.data.frame(
+    matrix(data = 0, nrow = length(n_basis), ncol = 5)
+  )
+  
+  colnames(CV_container) <- c(
+    "CV_score", "n_basis", "fold_size", "n_folds", "success_count"
+  )
+  
+  CV_container$n_basis <- n_basis
+  CV_container$fold_size <- fold_size
+  CV_container$n_folds <- n_folds
+  CV_container$success_count <- rep(x = 0, times = length(n_basis))
+  
+  # create basis functions
+  if (even_basis == TRUE) {
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) {
+        if (j %% 2 == 1) {
+          return(create.fourier.basis(rangeval = c(0, 1), nbasis = j))
+        } else {
+          return(create.fourier.basis(rangeval = c(0, 1), nbasis = j, dropind = j))
+        }
+      }
+    )
+  } else {
+    basis_functions <- map(
+      .x = n_basis,
+      .f = function(j) create.fourier.basis(rangeval = c(0, 1), nbasis = j)
+    )
+  }
+  
+  # prepare objects for functional linear regression
+  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
+  
+  betafdPar2_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) fdPar(basis_functions[[i]])
+  )
+  
+  betalist_list <- map(
+    .x = 1:length(n_basis),
+    .f = function(i) {
[…]

### 2022-02-03 Paper/main.tex
Notation change of prf

@@
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu_j\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi_{j}$ of basis functions satisfy the following properties:
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ of basis functions satisfy the following properties:
 	\begin{enumerate}
@@
 			\begin{split}
-				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
-				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
-				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu_{j}(t) dt\\
-				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu_{j}(t) dt = 0
+				\mathbb{E}[\xi^m] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
+				= & \int_{\Omega} \int_{0}^{1} F(t) \nu^m(t) dt dP(\omega)\\
+				= & \int_{0}^{1} \int_{\Omega} F(t) \nu^m(t) dP(\omega) dt \quad \text{(Fubini)}\\
+				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu^m(t) dt\\
+				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu^m(t) dt = 0
 			\end{split}
@@
 			\begin{split}
-				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
-				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s)} \nu_{k}(t) {\color{red}ds} dt\\
-				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
-				= & \int_{0}^{1}{\color{red}[K\nu_{j}](t)}\nu_{k}(t)dt\\
-				= & \langle K \nu_{j}, \nu_{k} \rangle\\
-				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \delta_{j,k}\lambda_{j}
-			\end{split}
-		\end{equation}
-		where $\delta_{j,k} = 1$ if $j = k$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
+				\mathbb{E} [\xi^m \xi^n] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu^m(s)ds \int_{0}^{1} F(t) \nu^n(t)dt  \biggr\rbrack\\
+				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu^m(s) F(t) \nu^n(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
+				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu^m(s)} \nu^n(t) {\color{red}ds} dt\\
+				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu^m(s)ds \right)} \nu^n(t) dt \\
+				= & \int_{0}^{1}{\color{red}[K\nu^m](t)}\nu^n(t)dt\\
+				= & \langle K \nu^m, \nu^n \rangle\\
+				= & \langle \lambda^m \nu^m, \nu^n \rangle = \delta^{m,n}\lambda^{m}
+			\end{split}
+		\end{equation}
+		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions.
+		\begin{equation}
+			Cov\left(\xi^m, \xi^n\right) = \mathbb{E}[\xi^m \xi^n] - \mathbb{E}[\xi^m]\mathbb{E}[\xi^n] = \delta^{m,n}\lambda^{m}
+		\end{equation}
+		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as the first property.
+		The last assertion is confirmed from the above two properties.
 		\begin{equation}\label{Lemma3}
-			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
+			Var[\xi^m] = \mathbb{E}\left[(\xi^m - \mathbb{E}[\xi^m])^{2}\right] = \mathbb{E}[(\xi^m)^{2}] =\lambda^m
 		\end{equation}
@@
 		\begin{equation}
-			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{j=1}^{\infty}\xi_{j}\nu_{j}(t)
+			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{m=1}^{\infty}\xi^m\nu^m(t)
 		\end{equation}
@@
 	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$.
-Then there exists a basis ${\xi_{j}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
-	\begin{equation}
-		X(t) = \mu(t) + \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
-	\end{equation}
-	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} (X(t)(\omega) - \mu(t)) \nu_{j}(t)dt$.
-These coefficients satisfy the following conditions.
+Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
+	\begin{equation}
+		X(t) = \mu(t) + \sum_{m=1}^{\infty} \xi^m \nu^m(t),
+	\end{equation}
+	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)dt$. These coefficients satisfy the following conditions.
 	\begin{enumerate}
@@
 	\begin{proof}
-		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$.
-With the reminder that $\xi_{j}(\omega)$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
-		\begin{equation}
-			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
-			= \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
+		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda^m$.
+With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
+		\begin{equation}
+			\epsilon_{N}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
+			= \mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
 		\end{equation}
 		where $F(t)$ is the centered process of $X(t)$.
-		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
+		Once it is shown that $\lim\limits_{N \rightarrow \infty} \epsilon_{N}(t) = 0$ uniformly in [0,1], the proof is completed.
 		\begin{equation}\label{Thr1}
 			\begin{split}
-				\epsilon_{n}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} 	\nu_{j}(t)\bigg)^2 \right]\\
-				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{j=1}^{n}\xi_{j}\nu_{j}(t)\bigg] + \mathbb{E}\bigg[\sum_{j=1}^{n}\sum_{k=1}^{n}\xi_{j}\xi_{k}\nu_{j}(t)\nu_{k}(t)\bigg]
+				\epsilon_{N}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m 	\nu^m(t)\bigg)^2 \right]\\
+				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{m=1}^{N}\xi^m\nu^m(t)\bigg] + \mathbb{E}\bigg[\sum_{m=1}^{N}\sum_{n=1}^{N}\xi^m\xi^n\nu^m(t)\nu^n(t)\bigg]
 			\end{split}
@@
 			\begin{split}
-				\mathbb{E} \bigg[ F(t) \sum_{j=1}^{n} {\color{red}\xi_{j}}\nu_{j}(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{j=1}^{n} {\color{red}\bigg(\int_{0}^{1} F(s)\nu_{j}(s)ds\bigg)} \nu_{j}(t) \right]\\
-				= & \mathbb{E} \left[ \sum_{j=1}^{n} \bigg(\int_{0}^{1} F(t)F(s)\nu_{j}(s)ds\bigg) \nu_{j}(t) \right]\\
-				= & \sum_{j=1}^{n} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu_{j}(s)ds\bigg)\nu_{j}(t)\\
-				= & \sum_{j=1}^{n} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu_{j}(s)ds\bigg)}\nu_{j}(t)\\
-				= & \sum_{j=1}^{n}{\color{teal}[K\nu_{j}](t)}\nu_{j}(t) \\
-				= &\sum_{j=1}^{n}{\color{teal}\lambda_{j}\nu_{j}(t)}\nu_{j}(t) = \sum_{j=1}^{n}\lambda_{j}\nu_{j}(t)^{2}
+				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)ds\bigg)} \nu^m(t) \right]\\
+				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)ds\bigg) \nu^m(t) \right]\\
+				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)ds\bigg)\nu^m(t)\\
+				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)ds\bigg)}\nu^m(t)\\
+				= & \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\
+				= &\sum_{m=1}^{N}{\color{teal}\lambda^m\nu^m(t)}\nu^m(t) = \sum_{m=1}^{N}\lambda^m\nu^m(t)^{2}
 			\end{split}
@@
 			\begin{split}
-				\mathbb{E}\bigg[\sum_{j=1}^{n} \sum_{k=1}^{n} \xi_{j} \xi_{k} \nu_{j}(t) \nu_{k}(t)\bigg] = & \sum_{j=1}^{n} \sum_{k=1}^{n} \mathbb{E}[\xi_{j} \xi_{k}] \nu_{j}(t) \nu_{k}(t)\\
-				= & \sum_{j=1}^{n} \sum_{k=1}^{n} \delta_{jk} \lambda_{j} \nu_{j}(t) \nu_{k}(t) = 		\sum_{j=1}^{n} \lambda_{j} \nu_{j}(t)^{2}
-			\end{split}	
-		\end{equation}
-		where $\delta_{jk} = 1$ if $j=k$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain
-		\begin{equation}
-			\epsilon_{n}(t) = c(t,t) - \sum_{j=1}^{n} \lambda_{j} \nu_{j}(t) \nu_{j}(t)
+				\mathbb{E}\bigg[\sum_{m=1}^{N} \sum_{m=1}^{N} \xi^m \xi^m \nu^m(t) \nu^n(t)\bigg] = & \sum_{m=1}^{N} \sum_{m=1}^{N} \mathbb{E}[\xi^m \xi_{k}] \nu^m(t) \nu^n(t)\\
+				= & \sum_{m=1}^{N} \sum_{n=1}^{N} \delta^{m,n} \lambda^m \nu^m(t) \nu^n(t) = 		\sum_{m=1}^{N} \lambda^m \nu^m(t)^{2}
+			\end{split}	
+		\end{equation}
+		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain
+		\begin{equation}
+			\epsilon_{N}(t) = c(t,t) - \sum_{m=1}^{N} \lambda^m \nu^m(t) \nu^m(t)
 		\end{equation}
@@
 		\begin{equation}
-			\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = \lim\limits_{n \rightarrow \infty} \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right] = 0
+			\lim\limits_{N \rightarrow \infty} \epsilon_{N}(t) = \lim\limits_{n \rightarrow \infty} \mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right] = 0
 		\end{equation}

### 2022-02-03 Code/Main_Application.R
Main_Application fpcr specs added

@@ -13,29 +13,42 @@ source("Application_Functions.R")
 
 ### Run Application for basis expansion
 bspline_appl <- bspline_appl_function(fold_size = 5, rep = 1000, seed = 100, debug = TRUE)
-saveRDS(object = bspline_appl, file = 'Results/Paper/Application/bspline_appl.RDS')
-write_csv(x = bspline_appl, file = 'Results/Paper/Application/bspline_appl.csv')
+saveRDS(object = bspline_appl, file = "Results/Paper/Application/bspline_appl.RDS")
+write_csv(x = bspline_appl, file = "Results/Paper/Application/bspline_appl.csv")
 
 fourier_appl <- fourier_appl_function(fold_size = 5, rep = 1000, seed = 100, even_basis = FALSE, debug = TRUE)
-saveRDS(object = fourier_appl, file = 'Results/Paper/Application/fourier_appl.RDS')
-write_csv(x = fourier_appl, file = 'Results/Paper/Application/fourier_appl.csv')
+saveRDS(object = fourier_appl, file = "Results/Paper/Application/fourier_appl.RDS")
+write_csv(x = fourier_appl, file = "Results/Paper/Application/fourier_appl.csv")
 
 monomial_appl <- monomial_appl_function(fold_size = 5, rep = 1000, seed = 100, debug = TRUE)
-saveRDS(object = monomial_appl, file = 'Results/Paper/Application/monomial_appl.RDS')
-write_csv(x = monomial_appl, file = 'Results/Paper/Application/monomial_appl.csv')
+saveRDS(object = monomial_appl, file = "Results/Paper/Application/monomial_appl.RDS")
+write_csv(x = monomial_appl, file = "Results/Paper/Application/monomial_appl.csv")
 
-### Not yet implemented only for structure
+### Run Application for fpcr
+for (j in 2:4) {
+  bspline_fpcr_appl <- bspline_fpcr_appl_function(
+    fold_size = 5, rep = 1000,
+    seed = 100, nharm = j, debug = TRUE
+  )
+  saveRDS(object = bspline_fpcr_appl, file = paste0("Results/Paper/Application/bspline_fpcr_nharm", j, "_appl.RDS"))
[…]

### 2022-02-03 Paper/main.tex
Adding tables in seperat .tex, Further interpretation of results

--- 2022-02-03 Paper/main.tex
@@
 These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
+For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
 		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve.
@@
 
-		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}
 		 {\color{blue} We should mention how we derived the original principal components.
@@
 	\paragraph{Monomial Basis}
-	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order?
-Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
-For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
+	Due to the high collinearity of these basis, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
+As outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance in the simulations than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
-This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
+The outlined weakness due to collinearity is especially pronounced in $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
 
@@
 	Simulations with bspline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happend here exactly?}
-The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low)-signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$.
+The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$.
 For $f_2$, 11(6) bspline basis functions are needed for the high(low) signal-to-noise ratios.
@@
 	\subsubsection{Functional Principal Component Regression}
-	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
+	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}.
+Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC´s adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
 
 	\paragraph{Monomial Basis}
+	TBD
 	\paragraph{Bspline Basis}
+	For $f_1,Y_1$, the CV suggests a better model the more FPC´s are used.
+While the number of basis functions stays at 5 for two and three used FPC, it increases to 6 basis functions for $nharm$ = 4.
+In $f_1,Y_1$, the cross-validated MSE is only slightly affected by the number of FPC´s, but lowest for $nharm$ = 3, indicating the possibility of over-fitting for four FPC´s.
+$f_2,Y_1$ shows the strongest decrease of MSE in increasing FPC´s of all FPCR models fitted with BSplines (0.69614, 0.42504, 0.09497 for 2,3,4 FPC´s).
+For $f_2,Y_2$ the same holds true as in the setup with $f_2$ and the high signal-to-noise ration, but less pronounced.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions is increasing in the number of FPC´s (4,6,8 for 2,3,4 FPC´s)\\
+	The results overall might indicate that a higher number of FPC´s has a strong effect in the setup with high signal-to-noise ratio, while not reducing as much error in the setting with the higher noise.
+
 	\paragraph{Fourier Basis}
+	We observe similar behaviour as for the FPCR using BSplines.
+In $f_1,Y_1$, the MSE is deceasing in the number of FPC´s while the results in $f_1,Y_2$ might again indicate over fitting when using 4 FPC´s.
+Since it was not possible to calculate the cross-validated MSE for 3 basis functions for 4 FPC´s, the increasing number of basis functions as seen in the FPCR with BSplines can not be observed here.
+$f_2,Y_1$ displays again the greatest decline of MSE in the increasing number of FPC´s.
+The same behaviour can be seen in $f_2,Y_2$, but less pronounced.
+Both configurations of $f_2$ a re using 5,15,7 basis functions for 2,3,4 FPC´s: This behaviour is opposing to the previous reported increasing nature of basis functions in the number of FPC`s.
 
@@
 
-	\subsection{Literature}
-	\begin{itemize}
-		\item \cite{shonkwiler_explorations_2009}
-		\item R-packages: fda, refund, mgcv
-	\end{itemize}
+	%\subsection{Literature}
+	%\begin{itemize}
+	%	\item \cite{shonkwiler_explorations_2009}
+	%	\item R-packages: fda, refund, mgcv
+	%\end{itemize}
 
@@
 	\section{Application}
-		The application uses the insights from the previous sections to predict the octane ratings of the introduced gasoline dataset. Following the results from the simulation study,... 
+		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset.
+The simulation study will contribute towards the reading of the results.
 		\begin{itemize}
@@
 \newpage
-	\subsection{Simulation Study Results}
-
-	\begin{table}[htb]
-			\centering
-			\caption{Monomial Basis Expansion Regression}
-				\begin{tabular}{lllllll}
-					\cline{1-5}
-					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
-7.177234352026647                        & 131.92716520680838                        & 0.8936725847175324                         & 2.5839516380614462                        & 2       &  \\
-4.170391190343292                        & {\color[HTML]{FE0000} 129.64258934345224} & 0.8122408608804015                         & 2.511772278865247                         & 3       &  \\
-3.912749103345826                        & 130.1170783435205                         & 0.3807927171910713                         & 2.090474762002978                         & 4       &  \\
-{\color[HTML]{FE0000} 3.638501968909747} & 130.59817144950233                        & {\color[HTML]{FE0000} 0.09216751463887264} & {\color[HTML]{FE0000} 1.8134256416939782} & 5       &  \\
-6.016442343989896                        & 201.15534584991525                        & 0.7620805051836907                         & 3.3937342332820926                        & 6       & 
-\end{tabular}
-\end{table}
-
-\vspace{2cm}
-
-	\begin{table}[htb]
-			\centering
-			\caption{BSpline Basis Expansion Regression}
-				\begin{tabular}{lllllll}
-					\cline{1-5}
-					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
-3.9127490963955247                        & {\color[HTML]{FE0000} 130.1170783090359} & 0.3807927168700936                          & 2.090474761101881                         & 4       &  \\
-{\color[HTML]{FE0000} 3.6430480624640396} & 130.61094959896604                       & 0.09511820431115069                         & 1.8164314387816713                        & 5       &  \\
-3.6542611008674575                        & 131.35354539843397                       & 0.07775281510299467                         & {\color[HTML]{FE0000} 1.8091346529425483} & 6       &  \\
-3.6770545937377634                        & 132.14205183557064                       & 0.07518488287219192                         & 1.8168036577708813                        & 7       &  \\
-3.710740869697218                         & 133.3653658811635                        & 0.05810108378740701                         & 1.8164984632128844                        & 8       &  \\
-3.7192146351418724                        & 133.6814928169343                        & 0.05640282340664383                         & 1.8193083539013821                        & 9       &  \\
-3.742010447810594                         & 134.5121710907784                        & 0.0521785231194299                          & 1.8257576297312081                        & 10      &  \\
-3.7643964092462974                        & 135.29727347111702                       & {\color[HTML]{FE0000} 0.051902252769905684} & 1.8360966075573522                        & 11      &  \\
-3.80109308638683                          & 136.5758146586355                        & 0.052040315671138586                        & 1.8531479959118535                        & 12      &  \\
-3.834360204971099                         & 137.78406681481994                       & 0.052706573106132304                        & 1.869969847032031                         & 13      &  \\
-3.862166917165765                         & 138.73431326927349                       & 0.053068654178390816                        & 1.8826933364948355                        & 14      &  \\
-3.8685638723557956                        & 138.97427074660192                       & 0.0525955164519272                          & 1.8848221385552892                        & 15      &  \\
-3.88505750612787                          & 139.57418873526626                       & 0.05283448721173191                         & 1.8933474257957223                        & 16      &  \\
-3.912671952971778                         & 140.51490301138338                       & 0.053220205231306356                        & 1.9061942087104604                        & 17      &  \\
-3.948125713522542                         & 141.80885020010606                       & 0.053584434348457485                        & 1.9231184762987383                        & 18      & 
-\end{tabular}
-\end{table}
-
-\vspace{2cm}
-
-	\begin{table}[htb]
-			\centering
-			\caption{Fourier Basis Expansion Regression}
-				\begin{tabular}{lllllll}
-					\cline{1-5}
-					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
-3.6975216821108177                        & {\color[HTML]{FE0000} 129.19133735032568} & 0.6952364931614831                         & 2.394399533437222                         & 3       \\
-{\color[HTML]{FE0000} 3.6347035142043147} & 130.59281554182246                        & 0.07418129892625985                        & 1.795816800944426                         & 5       \\
-3.6762259845089287                        & 132.0824820138016                         & 0.05147130962678385                        & {\color[HTML]{FE0000} 1.7934269021325526} & 7       \\
-3.718852537544315                         & 133.67575428625497                        & {\color[HTML]{FE0000} 0.05104970622270979} & 1.812908100982769                         & 9       \\
-3.764506721475903                         & 135.26218648523314                        & 0.05146451789575423                        & 1.8346302450265894                        & 11      \\
-3.810949927900835                         & 136.90281800923086                        & 0.05197380387819929                        & 1.8572425102431276                        & 13      \\
-3.8567441840723165                        & 138.57257529224665                        & 0.05252120988973837                        & 1.8802107534919845                        & 15      \\
-3.9061852571557436                        & 140.29178124765565                        & 0.05304327165297495                        & 1.9028253007284568                        & 17      \\
-3.9551703628111876                        & 142.057266882177                          & 0.053647142499864804                       & 1.9271845824346567                        & 19     
-\end{tabular}
-\end{table}
+\include{tables.tex}
 
@@
 				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s)} \nu_{k}(t) {\color{red}ds} dt\\
+				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
 				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
@@
 				= & \langle K \nu_{j}, \nu_{k} \rangle\\
-				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \delta_{j,k}\lambda_{j}
-			\end{split}
-		\end{equation}
-		where $\delta_{j,k} = 1$ if $j = k$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
+				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
+			\end{split}
+		\end{equation}
+		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
 		\begin{equation}\label{Lemma3}

### 2022-02-03 Paper/main.tex

--- 2022-02-03 Paper/main.tex
@@
 Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
-For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
+For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.

### 2022-02-03 Paper/main.tex
Small correction

@@
 
-	\begin{itemize}
-		\item Describe the idea of regressing a scalar on functional data
-		\item Describing the difference to multiple linear regression intuitively
-		\item Giving an intuitive example
-	\end{itemize}	
 	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.

### 2022-02-03 Paper/main.tex
Some language changes + appl_fpcr_bspline_nharm2

@@
 
-	All functions $f$ satisfying the above condition are called square-integrable functions.
-Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.
-Its inner product is defined as
+	%All functions $f$ satisfying the above condition are called square-integrable functions. 
+	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined as
 
@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality.
-We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
-	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
+	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis but analogous constructions can be made for every closed interval of $\mathbb{R}$.
+	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
+	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
 The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process.
@@
 
-	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
-	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
+	\subsection{Representing a Function in terms of a Basis} 
 	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
-Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.
+Three examples of bases that are often used in practice to approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.
 
@@
 The use of MB for local expansion?
-Need to check.)} and leads to undesirable behaviour at the tails such as Taylor expansion.
+Need to check.)} and leads to undesirable behavior at the tails such as Taylor expansion.
 (cf.
@@
 	\paragraph{Fourier Basis}
-	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric funtions.
+	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric functions.
 Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing.
@@
 
-	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.
+	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.
 Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$.
 This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
-{\color{blue} Motivate from fourier series}
+{\color{blue} Motivate from Fourier series}
 
@@
 
-	Consider the case of a dataset which is containing observations of an underlying continuous process, measured at some discrete points $t_{j,i}$:
+	Consider the case of a data set containing observations $X_i(t)$ of a random function $X(\omega)(t)$, measured at discrete points $t_{j,i}$:
 
@@
 
-	This measurement set can be viewed as set of discretized approximations of the underlying functional process:
- $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at the discrete measurement points. 
+ 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
+Therefore, this can be seen as set of discretized approximations of the realizations of a random function.
 	As in the finite dimensional setting, the concept of identically distributed and independent data is important.
-This concept generalizes intuitively to the case of functional data using the concepts for general random variables which is needed to conduct inference.
-{\color{red} Explain this better!}\\  The introduced concept of basis expansion of functions allow to express each observation $x_1$ as a realization of $X_1$, a random function of $\mathbb{L}^2[0,1]$.
-
-	%In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions.
-In the following, all random functions are assumed to realize in $\mathbb{L}^2$.
-
-	An example of such a dataset could be the dataset of 60 NIR-spectra of gasoline samples.
-Together with a set of responses, this then can be used to perform FLR, as will be subject of the simulation and application.
-
-	% COMMENT: Maybe mention both NIR and WienerProcess? 
-	%An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process.
-A definition and a plotted example for the Wiener process are given in \ref{Wiener}.
+This concept generalizes to the case of functional data using the concepts for general random variables.
+
+	An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples.
+Together with a set of responses, this then can be used to perform functional linear regression, as will be subject of the simulation and application.
 
@@
 
+	\newpage
+
 	\subsection{Basis Plots}
@@
 \include{tables.tex}
-
-\subsection{Wiener Process}\label{Wiener}
-A Wiener process $W_t$ is a real-valued continuous-time stochastic process {\color{red} ... This is wikipedia, look for right citation!}
-It is characterized by the following properties.
-
-\begin{multicols}{2}
-	\begin{enumerate}
-		\item $W_0 = 0$
-		\item $\forall t > 0 W_{t+u} - W_t \perp\!\!\!\perp W_s \forall s \leq t$
-		\item $W_{t+u} - W_t \sim \mathcal{N}(0,u)$
-		\item $W_t$ is continuous in $t$
-	\end{enumerate}
-\end{multicols}
-
-\begin{figure}[H]\label{Wiener_plot}
-	\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
-	\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
-\end{figure}
 

### 2022-02-03 Paper/main.tex
Equation Structure Improvements

@@
 Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
-	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
+	A typical case known to every undergraduate student of economics is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
 As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
@@
 
-	\begin{equation}
-		\begin{split}
-			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] \\
-			\delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} = \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
-			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) \quad \quad \quad
-			\delta_{\nu, m}^L(t) := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
-		\end{split}
-	\end{equation}
+		\begin{align}
+			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] 
+			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
+			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) 
+			& \delta_{\nu, m}^L(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
+		\end{align}
 

### 2022-02-03 Paper/main.tex
merging files to pull changes

--- 2022-02-03 Paper/main.tex
@@
 
+	\begin{itemize}
+		\item Describe the idea of regressing a scalar on functional data
+		\item Describing the difference to multiple linear regression intuitively
+		\item Giving an intuitive example
+	\end{itemize}	
 	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.
@@
 	\section{Theory}
-	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
-However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space.
+	In multivariate regression, data is often observed in the form of elements from the Euclidean space, $\mathbb{R}^p$.
 To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
@@
 As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
+However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space.
 A formalization of this idea makes some more theoretical considerations necessary.
@@
 For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve.
-These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:
-
-		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}
+		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the first $nharm$ FPC´s for $nharm \in \{2,3,4\}$ of the trainig-set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification.
+The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
+
+		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}{\color{green} Adressed }
 		 {\color{blue} We should mention how we derived the original principal components.
 (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set.
-As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}
+As we explain the approximations for the estimation, this question could come up, so we have to make it specific.
+}{\color{green} Adressed }
 
@@
 	\end{equation}
+	with truncation parameter $m$.
 	\vspace{	0.2cm}
@@
 	\paragraph{Monomial Basis}
-	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order?
-Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
+	Due to the in the number of basis functions increasing collinearity of these basis{(\color{orange} How about stressing the higher order?
+Are they already highly correlated at lower orders?)}{\color{green} Adressed }, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
 For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.

### 2022-02-03 Code/Application_Functions.R
Reviewing Code for Application

@@ -588,24 +588,6 @@ bspline_fpcr_appl_function <- function(rep, fold_size, nharm, seed, debug = FALS
     .f = function(j) create.bspline.basis(rangeval = c(0, 1), nbasis = j, norder = 4)
   )
   
-  # prepare objects for functional linear regression
-  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
-  
-  betafdPar2_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) fdPar(basis_functions[[i]])
-  )
-  
-  betalist_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) {
-      list(
-        const = betafdPar1,
-        smooth_basis = betafdPar2_list[[i]]
-      )
-    }
-  )
-  
   # loop over repetitions
   for (i in 1:rep) {
     if (debug) {
@@ -787,24 +769,6 @@ fourier_fpcr_appl_function <- function(rep, fold_size, nharm, seed, even_basis =
     )
   }
   
-  # prepare objects for functional linear regression
-  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
-  
-  betafdPar2_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) fdPar(basis_functions[[i]])
-  )
-  
-  betalist_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) {
-      list(
-        const = betafdPar1,
-        smooth_basis = betafdPar2_list[[i]]
-      )
-    }
-  )
-  
   # loop over repetitions
   for (i in 1:rep) {
     if (debug) {
@@ -966,24 +930,6 @@ monomial_fpcr_appl_function <- function(rep, fold_size, nharm, seed, debug = FAL
   basis_functions <- map(
     .x = n_basis,
     .f = function(j) create.monomial.basis(rangeval = c(0, 1), nbasis = j)
-  )
-  
-  # prepare objects for functional linear regression
-  betafdPar1 <- fdPar(fd(0, create.constant.basis(c(0, 1))))
-  
-  betafdPar2_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) fdPar(basis_functions[[i]])
-  )
-  
-  betalist_list <- map(
-    .x = 1:length(n_basis),
-    .f = function(i) {
-      list(
-        const = betafdPar1,
-        smooth_basis = betafdPar2_list[[i]]
-      )
-    }
   )
   
   # loop over repetitions

### 2022-02-03 Paper/main.tex
Functional data set

@@
 
+	\subsection{Functional Data Set}
+	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:
+
+	\begin{equation}
+		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
+	\end{equation}
+
+	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
+As it can be seen, the measurmant points can be differentiated through each sample.
+However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$.
+In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable.
+The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
+	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis.
+The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible.
+An example of such a data set could be the data set of 60 N
+
 	\subsection{Representing a Function in terms of a Basis} 
@@
 	\subsection{Functional Data Sets}
-
-	Consider the case of a data set containing observations $X_i(t)$ of a random function $X(\omega)(t)$, measured at discrete points $t_{j,i}$:
-
-	\begin{equation}
-		x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]
+	{\color{orange} Move this part below 3.2?}
+	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:
+
+	\begin{equation}
+		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
 	\end{equation}
@@
 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
-Therefore, this can be seen as set of discretized approximations of the realizations of a random function.
-	As in the finite dimensional setting, the concept of identically distributed and independent data is important.
-This concept generalizes to the case of functional data using the concepts for general random variables.
-
-	An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples.
-Together with a set of responses, this then can be used to perform functional linear regression, as will be subject of the simulation and application.
+As it can be seen, the measurmant points can be differentiated through each sample.
+However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$.
+In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable.
+The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
+	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis.
+The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible.
+An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.
 

### 2022-02-03 Paper/main.tex
correction
Small correction

@@
 The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible.
-An example of such a data set could be the data set of 60 N
+An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.
 
@@
 	\end{equation}
-	The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
-	The shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
-	 There exists problems of collinearity of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation.
+	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
+The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf.
+\cite{horvath_inference_2012}).
+There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation.
 This restricts the number of basis functions.
 Therefore, regarding the use, this may be useful for relatively simple functions.
-However, the small number of degrees makes it impossible to capture pronounced local peculiarities {\color{orange} (Isn't it good as thinking of the Taylor?
-The use of MB for local expansion?
-Need to check.)} and leads to undesirable behavior at the tails such as Taylor expansion.
+However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities.
+Moreover, it leads to an undesirable behavior at the tails such as Taylor expansion.
 (cf.

### 2022-02-03 Paper/main.tex
small corrections

@@
 In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable.
-The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
+It causes necessities to represent the functional data with respect to some expansion technique.
+The several techniques to make the functional data smooth is introduced on the following sub-chapters.\\
 	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis.
@@
 	\begin{equation}
-		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
+		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
 	\end{equation}
@@
 This restricts the number of basis functions.
+However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities.
+It finally leads to an undesirable behavior at the tails such as Taylor expansion (cf.
+\cite{ramsay_functional_2005}).
 Therefore, regarding the use, this may be useful for relatively simple functions.
-However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities.
-Moreover, it leads to an undesirable behavior at the tails such as Taylor expansion.
-(cf.
-\cite{ramsay_functional_2005})
 
@@
 This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
-{\color{blue} Motivate from Fourier series}
 

### 2022-02-04 Paper/main.tex
Grammarly First Run

@@
 	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.
-Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf.
+Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf.
 \cite{levitin_introduction_2007}).
@@
 
-	 In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions which could be the absorption of the Near-infrared (NIR) spectrum which will be used for the simulation and application.
-NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyse the interaction of each other.
+	In functional data analysis, the concept of a data set can include not only realizations of scalar random variables but also realizations of random functions.
+These could be the absorption of the Near-infrared (NIR) spectrum, which will be used for the simulation and application.
+NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyze the interaction of each other.
 {\color{green} For more details refer to the appendix SECTION ??!??!}.
 This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable.
-To conduct functional linear regression, several new concepts and methods need to be considered and explained that distinguish it multivariate linear regression.
+To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
 %	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
 \cite{Das_2019}).\\
-The focus of this paper is to introduce FLR in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:
+	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as follows:
 
@@
 
-	 where the $X_{i}$ are realizations of a random function $\mathbf{X}$, $Y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function.
+	 where the $x_{i}$ are realizations of a random function $X(\omega)$, $y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function.
 The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation.
-As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction.
-For instance, fluctuation in $X_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0.
-\\
-	 Estimation of $\beta(s)$ is inherently an infinite-dimensional problem.
+As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference.
+	 %For instance, fluctuation in $x_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
+	 The estimation of $\beta(s)$ is inherently an infinite-dimensional problem.
 In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion.
@@
 Finally, in Section 4, we test the prediction of FLR in a real-world setting.
-{\color{red} (We may put some simple descriptions of results about each of MC and Application)}
 
@@
 	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
-However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space.
-To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
-One integral concept in inferential statistics are random variables.
+However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
+Therefore, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
+One integral concept in inferential statistics is random variables.
 Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
@@
 	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space as follows.
+	The inner product naturally defines a norm and an associated distance on the vector space.
 
@@
 \\
-	It is called an orthonormal basis, if in addition the following properties hold.
+	It is called an orthonormal basis if, in addition, the following properties hold.
 
@@
 
-	As can be seen, differing from the case of a Banach space, these representations can be limits of series as previously hinted at by using the closed span of the basis.
-As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space, is to use a truncated series.
+	As can be seen, differing from the case of Banach spaces, these representations can be limits of series as previously hinted at by using the closed span of the basis.
+As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space is to use a truncated series.
 
@@
 
-	%All functions $f$ satisfying the above condition are called square-integrable functions. 
-	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined as
+	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined.
 
@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis but analogous constructions can be made for every closed interval of $\mathbb{R}$.
+	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis, but analogous constructions can be made for every closed interval of $\mathbb{R}$.
 	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
@@
 The collection of such sample curves constitutes a functional data set.
-	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations.
-For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.
 
@@
 
-	\subsection{Functional Data Set}
+	\subsection{Functional Data Sets}
 	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:
@@
 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
-As it can be seen, the measurmant points can be differentiated through each sample.
-However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$.
-In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable.
+The measurement points can be different for each sample.
+However, this is not a primary interest of this paper, and, therefore, we consider the case where curves are observed at a shared set of measuring points.
+In principle, these measurements can be seen as a discretized approximation of a realization of a random function.
 It causes necessities to represent the functional data with respect to some expansion technique.
-The several techniques to make the functional data smooth is introduced on the following sub-chapters.\\
-	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis.
-The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible.
-An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.
+One technique to make the functional data smooth, truncated basis expansion, is introduced in the following sections.\\
+	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis, such as, for example, many inferential procedures.
+One example could be a set of NIR absorption spectra of gasoline samples in which curves are observed at a shared set of wavelengths and each sample stemming from the same production can be seen as a realization of the same random process.
 
@@
 
-	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
+	Both of these can be used to express or in the case of the B-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
 Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.
@@
 
+	{\color{red}We should give a reference for how to obtain these coefficients and say that for the purpose of this paper we will treat this as a black box.}
+
 	\paragraph{Monomial Basis}
-	{\color{red} No shift parameter in implementation in fda.}  Monomial bases are trivially decompositions of every polynomial function.
-The class of non-polynomial but enough many differentiable functions can be apporximated by Taylor series, a special type of power series.
+	{\color{red} No shift parameter in implementation in fda.} The Monomial basis are trivially decompositions of every polynomial function.
+The class of non-polynomial but enough many differentiable functions can be approximated by Taylor series, a special type of power series.
 From these concepts, a function can be smooth by a power series.
@@
 	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
-The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf.
+The first order function within the monomial basis system, for $k=0$, is called the constant basis (cf.
 \cite{horvath_inference_2012}).
@@
 	\paragraph{Fourier Basis}
-	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric functions.
-Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing.
+	Fourier series decomposes a periodic function with a weighted sum of trigonometric functions.
+Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between $0$ and $1$, and we can then apply the Fourier series to approximate the function for smoothing.
 As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions.
@@
 	\end{equation}
-
-	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$.
+	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$.
 Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$.
-This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
+This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
 
@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$.
-	A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
+Additionally, at each $\tau_l$ the polynomials on neighboring subintervals must match derivatives up to order $m-2$.
+	A B-spline is a specific type of spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
 Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
@@
 
-	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+	However, a finite set of B-spline functions does not constitute a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
 To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
@@
 	\subsection{Approximation and Smoothing via Basis Truncation}
-	As above-mentioned, the realized curves can be estimated with basis functions.
-For the basis expansion, it is technically possible to use all basis functions $\phi_{j \in \mathcal{I}}$ to fit an completely unbiased estimate.
-This is not efficient since the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis.
-On the other hand, the important information on the curves could be missed with a too-small number of basis functions.
-In that sense, this discussion is subject to the Bias-Variance Tradeoff.
+	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis.
+For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$.
+In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis.
+{\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small.
+In that sense, this discussion is subject to the Bias-Variance tradeoff.
 It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves.
@@
 
-	\subsection{Functional Data Sets}
-	{\color{orange} Move this part below 3.2?}
-	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:
-
-	\begin{equation}
-		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
-	\end{equation}
-
-	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
-As it can be seen, the measurmant points can be differentiated through each sample.
-However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$.
-In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable.
-The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
-	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis.
-The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible.
-An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.
-
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
-	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
-To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$.
-Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
-Then the mean and covariance functions of $X$ are defined as follows.
-	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.
-Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$.
-Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\
-
-	%This decomposition can be used to express the random vector $V(\omega)$ in the following way.
-
-	%\begin{equation}
-	%	V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
-	%\end{equation}
-
-	%where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\
+	Given a realization of a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
+To do so, it is necessary to define the mean and covariance functions of $X(\omega)$.
 
@@
 	\end{equation}
-	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+
+	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
 Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+
 	\begin{equation}\label{HSKernal}
@@
 			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
-			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$%0$ if $m \neq n$
+			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
 			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
@@
 	\end{multicols}
-	where $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
-	In the typical scalar setting, a similar consideration leads to the concept of principal components.
-This is also possible in a functional setting.
+
+	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting.
 Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d.
 realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
-	Define the following sample analogues for the mean and covariance functions.
+	Define the following sample analogs for the mean and covariance functions.
 
@@
 
-	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
-For the sake of clarity the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
+	In reality, these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
+For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
 
@@
 	\subsection{Scalar-on-Function Regression}
-	In the simple scalar setting one of the most important tools in econometrics is the linear regression.
+	In the simple scalar setting, one of the most important tools in econometrics is linear regression.
 Its goal is to predict the value of a dependent variable given a set of associated variables.
-For reference assume a data generating process as follows.
-{\color{red} Structure is bad...
-This will be changed.}
+For reference, assume a data generating process as follows.
 
@@
 The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
-{\color{red}List Assumptions?
-Then we need to list the assumptions for functional linear regression as well I think.}
 
@@
 	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
-	A general data generating process in this functional scenario could look like the following equation.
-
-	\begin{equation}
-		Y(\omega) = \alpha + \Psi\left(X(\omega)\right) + \epsilon(\omega)
-	\end{equation}
-
-	Here $\Psi$ is a functional that maps a realization of a random function in $\mathbb{L}^2[0,1]$ into $\mathbb{R}$.
-One simple example to illustrate the principle is the maximum $\Psi(f) = \max_{x \in [0,1]}f(x)$.
-	However, the typical setup is often as follows mimicking the structure of the multivariate linear model extended from summation to integration.
-This structure is crucial for the extension of linear regression to the case of functional regressors.
-Therefore, in this paper we always implicitly assume that a data generating process has the following structure.
-{\color{red} maybe a better motivation is the one Jona gave: from very dense observations that run into problems of colinearity when using the original OLS estimator}
+	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
+Therefore, we will always assume a data generating process as follows in this paper.
 
@@
 
-	Where $x(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
-	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
-However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible.
+	Where $\beta(t)$ is an unknown coefficient function.
+Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
+However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible.
 Therefore, other options have to be considered.
@@
 
-	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogues is more interesting as a representation of an observation.
+	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
 
@@
 
-	This, however, is a simplification for the purposes of real-world estimation as in most implementations the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely.
+	This, however, is a simplification for the purposes of real-world estimation as in most implementations, the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely.
 Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
@@
 
-	%\subsection{Detailed Draft}
-	%\begin{itemize}
-	%	\item Motivate random functions from introduction and the general concept of random variables
-	%	\item Formalize random function in this context as random variables realizing in a Hilbert space
-	%	\item Introduce $\mathbb{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
-	%	\item Specialize to Hilbert space being $\mathbb{L}^2[0,1]$ for this context
-	%	\item Define mean and covariance function of a random function realizing in $\mathbb{L}^2[0,1]$
-	%	\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbb{L}^2[0,1]$
-	%	\item Introduce b-spline and Fourier bases
-	%	\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
-	%	\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
-	%	\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbb{L}^2[0,1]$
-	%	\item Explain the concept of iid data in a functional setting		
-	%	\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
-	%	\item Explain approximations of functional observations using truncated basis representations
-	%	\item Introduce linear operator $L_1$ and sufficient condition associated with it
-	%	\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
-	%\end{itemize}
-
-%There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation.
-Without it, there might be prediction, but the increase in understanding of the underlying question will be minimal.
-One aspect of a useful interpretation is that the estimate $\beta(s)$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.
-
-	%A common setting in non-functional regression is akin to the following. Assume a model as follows:
-
-	%\begin{equation}
-	%	Y = X'\beta + \epsilon
-	%\end{equation}
-
-	%where $X \in \mathbb{R}^{n\times J}$ is a matrix containing the regressors, $\beta \in \mathbb{R}^J$ is a coefficient vector and $epsilon$ is a vector containing the error term.
-For simplicity, assume that the data generating process fulfills the Markov assumptions.
-Then the famous OLS-estimator is given by:
-
-	%\begin{equation}
-	%	\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
-	%\end{equation}
-
-	%A naive approach to FLR would be to try to generalize this to the functional setting.
-	%Assuming a data generating process of the form:
-
-	%\begin{equation}
-   % 	 Y =  \int \beta(s)X(s) \,\mathrm{d}t \ +\epsilon
-    %\end{equation}
-
-    %it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects.
-Where in the finite dimensional setting the OLS estimator can be derived as a method of moments estimator by solving a system of equations of sample moment restrictions, this leads to a system of infinitely many equations in the functional setting.
-    %In practice, functional observations are never truly continuously observed.
-If we assume that the functional observations are observed at a finite set of points $\{t_1, \dots, t_J\}$ this makes the derivation of an OLS estimator possible as before.
-
-    %\begin{equation}\label{discrete_time_model}
-    %	Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{i},
-    %\end{equation}
-
-    %However, this often still results in a large and difficult to solve system of equations.
-Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions.
-Another reason why estimation is not feasible using this approach is colinearity.
-    %Looking at equation \ref{discrete_time_model} and assuming continuous functions $X_i$ it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$.
-Thereby, there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances of $\beta$.
-(cf.
-~\cite{kokoszka_introduction_2017})\\
-
 	\subsection{Literature}
@@
 
-	%\subsection{Draft-Overview}
-	%\begin{itemize}
-	%	\item Motivate Simulation for some data generating process from application
-	%	\item Describe Simulation Setting from technical standpoint (DGP, set-up for replication, ...)
-	%			\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
-	%	\item Present Results
-	%	\item Explain relevance for application
-	%\end{itemize}
-
 	\subsection{Motivation}
@@
 	In the simulation study, we deviate from the standard simulation setting.
-Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
+Instead of generating data from scratch, we use the gasoline data, which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
 We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
@@
 	To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation using the prediction mean-squared error.
-While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
-This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra {\color{green} Link to NIR}.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
+While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+This might apply to this simulation too since certain eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.
 
 	This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
-This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation.
+This would avoid the heavy computing of validating the best value for $K$, which we will conduct in the simulation.
 To provide intuition in this approach, let
+
 	 \begin{equation}
@@
 	 \end{equation}
+
 	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
@@
 	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots.
+First, the initial curves are expressed in terms of a generated B-spline basis which is created using 50 knots.
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
@@
 
-		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$
-
-		where
-			$\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
-
-    %{\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
-    %Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other.
-Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience...
-No theoretical reasoning)}
+	\begin{equation}
+		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)
+	\end{equation}
+
+	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
 
@@
 		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $.
-The error variations represent different signal-to-noise ratios to test the methods both with a low and a high amount of noise.
+The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise.
 They are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
-The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
+The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
 
@@
 In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses.
-These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
+These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
 For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the first $nharm$ FPC´s for $nharm \in \{2,3,4\}$ of the trainig-set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification.
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification.
 The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
-
-		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}{\color{green} Adressed }
-		 {\color{blue} We should mention how we derived the original principal components.
-(bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set.
-As we explain the approximations for the estimation, this question could come up, so we have to make it specific.
-}{\color{green} Adressed }
 
@@
 		with truncation parameter $m$.
-	\vspace{	0.2cm}
+		\vspace{0.2cm}
 
@@
 	\paragraph{Monomial Basis}
-	Due to the in the number of basis functions increasing collinearity of these basis{(\color{orange} How about stressing the higher order?
-Are they already highly correlated at lower orders?)}{\color{green} Adressed }, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant.
-For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
+	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis.
+For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than B-splines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
-This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
-
-	\paragraph{Bspline Basis}
-	Simulations with bspline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happend here exactly?}
-The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$.
-For $f_2$, 11(6) bspline basis functions are needed for the high(low) signal-to-noise ratios.
-For $f_2$, the bspline basis functions outperform the monomial basis, but come second to the fourier basis.
+This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less pronounced.
+
+	\paragraph{B-spline Basis}
+	Simulations with B-spline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happened here exactly?}
+	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
+For $f_2$, 11(6) B-spline basis functions are needed for the high(low) signal-to-noise ratios.
+For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis.
 
 	\paragraph{Fourier Basis}
-	For $f_1$, the simulation chooses a smaller number of fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
+	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
 With the low signal-to-noise ratio, the simulation chooses a smaller number to account for the higher noise in the response variable.
-The fourier basis functions performs the best in each setup for the basis expansion regression.
-When recalling $f_1$ and $f_2$, both, but especially $f_1$ shows similar curvature order across the domain which contributes to the strong performance of this basis.
-	\\
-
-	For all specifications, the effect of the Bias-Variance tradeoff can be observed:: The function $f_1$ is rather smooth and not much bias is introduced here when choosing a small number of basis functions since $f_1$ lacks pronounced peculiarities.
-For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$: We can choose a higher number of basis functions since the amount of bias is deceasing much faster in the number of basis functions than the variance is increasing, compared to $f_1$.
+The Fourier basis functions perform the best in each setup for the basis expansion regression.
+When recalling $f_1$ and $f_2$, both, but especially $f_1$ shows similar curvature order across the domain which contributes to the strong performance of this basis.	\\
+
+	For all specifications, the effect of the Bias-Variance tradeoff can be observed: The function $f_1$ is rather smooth and little bias introduced when choosing a small number of basis functions.
+For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$.
+We can choose a higher number of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
 
@@
 	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}.
-Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC´s adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
+Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
 
@@
 	TBD
-	\paragraph{Bspline Basis}
-	For $f_1,Y_1$, the CV suggests a better model the more FPC´s are used.
-While the number of basis functions stays at 5 for two and three used FPC, it increases to 6 basis functions for $nharm$ = 4.
-In $f_1,Y_1$, the cross-validated MSE is only slightly affected by the number of FPC´s, but lowest for $nharm$ = 3, indicating the possibility of over-fitting for four FPC´s.
-$f_2,Y_1$ shows the strongest decrease of MSE in increasing FPC´s of all FPCR models fitted with BSplines (0.69614, 0.42504, 0.09497 for 2,3,4 FPC´s).
-For $f_2,Y_2$ the same holds true as in the setup with $f_2$ and the high signal-to-noise ration, but less pronounced.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions is increasing in the number of FPC´s (4,6,8 for 2,3,4 FPC´s)\\
-	The results overall might indicate that a higher number of FPC´s has a strong effect in the setup with high signal-to-noise ratio, while not reducing as much error in the setting with the higher noise.
+	\paragraph{B-spline Basis}
+	For $f_1,Y_1$, the CV suggests a better model with a higher number of FPC's.
+While the number of basis functions stays at five for two and three used FPC, it increases to six basis functions for $nharm$ = 4.
+In $f_1,Y_1$, the cross-validated MSE is only slightly affected by the number of FPC's, but lowest for $nharm$ = 3, indicating the possibility of over-fitting for four FPC's.
+$f_2,Y_1$ shows the strongest decrease of MSE in increasing FPC's of all FPCR models fitted with B-splines (0.69614, 0.42504, 0.09497 for 2,3,4 FPC's).
+For $f_2,Y_2$ the same holds true as in the setup with $f_2$ and the high signal-to-noise ratio, but less pronounced.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions is increasing in the number of FPC's (4,6,8 for 2,3,4 FPC's)\\
+	The results overall might indicate that a higher number of FPC's has a strong effect in the setup with a high signal-to-noise ratio while not reducing as much error in the setting with the higher noise.
 
 	\paragraph{Fourier Basis}
-	We observe similar behaviour as for the FPCR using BSplines.
-In $f_1,Y_1$, the MSE is deceasing in the number of FPC´s while the results in $f_1,Y_2$ might again indicate over fitting when using 4 FPC´s.
-Since it was not possible to calculate the cross-validated MSE for 3 basis functions for 4 FPC´s, the increasing number of basis functions as seen in the FPCR with BSplines can not be observed here.
-$f_2,Y_1$ displays again the greatest decline of MSE in the increasing number of FPC´s.
-The same behaviour can be seen in $f_2,Y_2$, but less pronounced.
-Both configurations of $f_2$ a re using 5,15,7 basis functions for 2,3,4 FPC´s: This behaviour is opposing to the previous reported increasing nature of basis functions in the number of FPC`s.
+	We observe similar behavior as for the FPCR using B-splines.
+In $f_1,Y_1$, the MSE is decreasing in the number of FPC's while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
+Since it was not possible to calculate the cross-validated MSE for three basis functions for four FPC's, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here.
+$f_2,Y_1$ displays the greatest decline of MSE in the increasing number of FPC's.
+The same behavior can be seen in $f_2,Y_2$, but less pronounced.
+Both configurations of $f_2$ are using 5,15,7 basis functions for 2,3,4 FPC's: This behavior opposes to the previously reported increasing nature of basis functions in the number of FPC's.
 
@@
 	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
-It therefore measures the absorption and interaction of this spectrum of radiation with the sample.
-NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another big advantage is that it does not need a reagent and thus does not destroy the sample.
-It is used for analysis in different sectors and fields, like the agrochemical industry but also in healthcare.
-Its non-invasive nature makes it also to an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy is able to detect the worsening of the blood glucose metabolic dysfunction (cf .
+It, therefore, measures the absorption and interaction of this spectrum of radiation with the sample.
+NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample.
+It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare.
+Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf .
 \cite{FR_li_et_al_2020}).
 In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy.
-According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (eg.: carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).
+According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).
 While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al.
-1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characktersitics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
+1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
 
@@
 
-	\begin{figure}[H]\label{fourier_basis}
+	\begin{figure}[H]\label{Fourier_basis}
 		\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
@@
 
-	\begin{figure}[H]\label{bspline_basis}
+	\begin{figure}[H]\label{B-spline_basis}
 		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
@@
 
-		where the covariance function $c(t,s)$ has the Hilbert-Shmidt operator as in (\ref{HSKernal}).
+		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in (\ref{HSKernal}).
 It turns out the product of the eigenfunction and the corresponding eigenvalue.

### 2022-02-04 Paper/main.tex
Added picture of NIR spectroscope in Appendix

@@
 \cite{FR_li_et_al_2020}).
+\\
 	In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy.
@@
 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width = \textwidth]{../Graphics/FinderSD.jpg}
+			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
+			(source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
+		\end{center}
+	\end{figure}
 

### 2022-02-04 Paper/main.tex
Cleaned up bibliography

@@
 			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
-			(source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
+			(Source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
 		\end{center}

### 2022-02-04 Paper/main.tex

@@
 \begin{document}
-	\title{{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
+	\title{{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
 	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
@@
 
+	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}.
+Therefore, it is interesting to think about when the approximation error is small...
+{\color{red}Continue Here Jakob!!!}
+
 	\subsubsection{Estimation using Functional Principal Components}
@@
 	\end{equation}
+
+	As in the previous case, the performance of this estimation depends the quality of the approximation made during the derivation of this estimator.
+Therefore, it is interesting to think about when these errors are small...
+{\color{red}Continue Here Jakob!!!}
 

### 2022-02-04 Paper/main.tex
B-spline

@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-Additionally, at each $\tau_l$ the polynomials on neighboring subintervals must match derivatives up to order $m-2$.
-	A B-spline is a specific type of spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
+In general, every single knot is equally spaced on the interval but inequally placing knots is needed when the input data is not equally observed.
+Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with single knot at each boundary.
+However, it is possible that placing multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure.
+A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
 Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
@@
 
-	However, a finite set of B-spline functions does not constitute a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
 To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
@@
 
-	{\color{red}Explain what happens when $l+m+1 > L$ !!!\\
-		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.}
+	{\color{red}Explain what happens when $l+m+1 > L$ !!!(I don't get it)\\
+		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.(adressed)}
 

### 2022-02-04 Paper/main.tex
Corrections

@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-In general, every single knot is equally spaced on the interval but inequally placing knots is needed when the input data is not equally observed.
-Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with single knot at each boundary.
-However, it is possible that placing multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure.
+In general, every single knot is equally spaced on the interval, but inequally placing knots is needed when the input data is not equally observed.
+Additionally, at each $\tau_l$, the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with a single knot at each boundary.
+However, it is sensible to place multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure.
 A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.

### 2022-02-04 Paper/main.tex
Small correction to b-spline basis

@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-In general, every single knot is equally spaced on the interval, but inequally placing knots is needed when the input data is not equally observed.
-Additionally, at each $\tau_l$, the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with a single knot at each boundary.
-However, it is sensible to place multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure.
+Typically, knots are placed on an equidistant grid, but deviations from this principle can prove advantageous in atypical settings.
+Additionally, at each $\tau_l$, the polynomials on neighboring subintervals must match derivatives up to order $m-2$ at the boundary.
+However, it is sensible to place multiple knots at the same value to replicate specific properties of the data structure.
 A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
@@
 
-	This, however, does not really yield a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
-To really obtain a basis of $\mathbb{L}^2[0,1]$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made.
-As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen B-spline basis.
+	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions.
 	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

### 2022-02-04 Paper/main.tex
Some introduction stuff

@@
 \cite{levitin_introduction_2007}).
-	As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf.
-\cite[S.~17]{kokoszka_introduction_2017}).
-
-	In functional data analysis, the concept of a data set can include not only realizations of scalar random variables but also realizations of random functions.
-These could be the absorption of the Near-infrared (NIR) spectrum, which will be used for the simulation and application.
-NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyze the interaction of each other.
-{\color{green} For more details refer to the appendix SECTION ??!??!}.
-This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable.
+	As \cite{kokoszka_introduction_2017} {\color{red}(page ca.
+17)} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves .
+
+	In functional data analysis, the concept of a data set includes both realizations of scalar random variables and realizations of random functions.
+These could be the absorption of the Near-infrared (NIR) spectrum, which will be used in later parts of this paper.
+NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of light at different wavelengths in a sample.
+\footnote{For more details, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  This dataset can then be used, for example, to predict a scalar response variable.
 To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
-%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf.
-\cite{Das_2019}).\\
-	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as follows:
-
-	 \begin{equation}
+	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.
+
+	 \begin{equation}\label{DGP1}
 	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
@@
 
-	 where the $x_{i}$ are realizations of a random function $X(\omega)$, $y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function.
-The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation.
+	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function.
+The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional.
 As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference.
-	 %For instance, fluctuation in $x_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
-	 The estimation of $\beta(s)$ is inherently an infinite-dimensional problem.
+\\
+
+	 {\color{red} This has to be updated.}
 	 In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion.

### 2022-02-04 Paper/main.tex
Slight wording changes for Fourier basis

@@
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional.
-As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference.
+As in the framework of scalar linear regression, estimating $\beta(t)$ is particularly interesting for prediction or inference.
 \\
@@
 	\paragraph{Fourier Basis}
-	Fourier series decomposes a periodic function with a weighted sum of trigonometric functions.
-Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between $0$ and $1$, and we can then apply the Fourier series to approximate the function for smoothing.
-As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions.
-That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
+	In the same way the monomial basis corresponds to the Taylor expansion, the Fourier basis corresponds to the Fourier series.
+The Fourier series can be used to decompose a periodic function into a weighted sum of trigonometric functions.
+Equation \ref{Fourier_Series} shows an example for a periodic function $s(x)$ defined on the interval $[0,1]$.
+
+	\begin{equation}\label{Fourier_Series}
+		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
+	\end{equation}
+
+	In its classical form, the series is represented in the so called amplitude-phase form.
+This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift.
+Therefore, rewriting the series in the sine-cosine form through a simple trigonometry formula as shown above is necessary.
+Due to this origin of the Fourier basis it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
+	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
+
 	\begin{equation}
@@
 	\end{equation}
+
 	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$.
@@
 	 \begin{equation}
-	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
+	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
 	 \end{equation}

### 2022-02-04 Paper/main.tex
Wording in the basis part

@@
 	\subsection{Representing a Function in terms of a Basis} 
-	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion.
-Three examples of bases that are often used in practice to approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.
-
-	Both of these can be used to express or in the case of the B-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions.
-Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.
-
-	\begin{equation}
-		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_{j}(\omega_0) \phi_j(t)
-	\end{equation}
-
-	{\color{red}We should give a reference for how to obtain these coefficients and say that for the purpose of this paper we will treat this as a black box.}
+	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion.
+Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express or approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.
+Then the following equation shows how a basis can be used to express a function as a weighted sum of its elements.
+
+	\begin{equation}
+		x(t) = \sum_{j \in \mathcal{I}} a_j \phi_j(t) 
+	\end{equation}
+
+	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$.
+For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
+	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
 
@@
 
-	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$.
-Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$.
-This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
+	Its elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$.
+Additionally, the Fourier basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
+
+	{\color{blue}I don't get this...
+Isn't the basis defined independently from the data set?
+Why is this dependent on the measuring points?
+"rephrasing \cite{ramsay_functional_2005}, the Fourier basis is orthonormal when the values $t_j$ are equally spaced within $T$."}
 

### 2022-02-04 Paper/main.tex
Introduction Stuff

@@
 
-	 {\color{red} This has to be updated.}
-	 In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion.
-We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3.
-Finally, in Section 4, we test the prediction of FLR in a real-world setting.
-
-	\section{Theory}
+	 In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using using two different approaches.
+Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis for the previously mentioned methods.
+The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
+In section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
+
+	\section{Theory}\label{Theory}
 	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
@@
 
-	\newpage
-	\section{Simulation Study}
+	\section{Simulation Study}\label{Simulation}
 
@@
 
-	\newpage
-	\section{Application}
+	\section{Application}\label{Application}
 		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset.
@@
 
-	\section{Outlook}
+	\section{Outlook}\label{Outlook}
 

### 2022-02-04 Paper/main.tex
Monomial Basis stuff

@@
 
-	 In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using using two different approaches.
+	 In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis.
 Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis for the previously mentioned methods.
@@
 
-	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} Random Function in $\mathbb{L}^2[0,1]$ space}}
+	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
@@
 	{\color{red} No shift parameter in implementation in fda.} The Monomial basis are trivially decompositions of every polynomial function.
-The class of non-polynomial but enough many differentiable functions can be approximated by Taylor series, a special type of power series.
-From these concepts, a function can be smooth by a power series.
-The bases construct
-
-	\begin{equation}
-		x(t) = \sum_{i \in \mathcal{I}} c_i(t - \alpha)^{i}
-	\end{equation}
-	 which forms the basis
+
+	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials.
+Let $f(t)$ be an entire function, e.g.
+the exponential function or a trigonometric function, then we can write the following.
+
+	\begin{equation}\label{Taylor_expansion}
+		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}}{i!}
+	\end{equation}
+
+	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can oftenlead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole.
+From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$.
+As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter.
+This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
 
@@
 	\end{equation}
-	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
-The first order function within the monomial basis system, for $k=0$, is called the constant basis (cf.
-\cite{horvath_inference_2012}).
+
+	Due to the chosen implementation for our simulation, we will limit our paper to the case of $\alpha = 0$.
+However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
 	There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation.

### 2022-02-04 Paper/main.tex
Small change, structure

@@
 	\paragraph{Monomial Basis}
-	{\color{red} No shift parameter in implementation in fda.} The Monomial basis are trivially decompositions of every polynomial function.
-
+	The Monomial basis are trivially decompositions of every polynomial function. {\color{red} Continue Work here!}	
 	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials.

### 2022-02-04 Code/Plot_Generators/f_functions.R
ggplot replacements for function plots

@@ -1,0 +1,43 @@
+library(tidyverse)
+
+f1 <- function(t){
+  return(2*sin(0.5*pi*t) + 4*sin(1.5*pi*t) + 5*sin(2.5*pi*t))
+}
+
+f2 <- function(t){
+  return(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2))
+}
+
+grid <- seq(0, 1, length.out = 1000)
+
+plot_tibble_1 <- tibble(x = grid,
+                        y = f1(grid))
+
+plot_tibble_2 <- tibble(x = grid,
+                        y = f2(grid))
+
+f1_plot <- ggplot(data = plot_tibble_1) +
+  geom_line(aes(x = x, y = y), col = 'red') +
+  theme_light() +
+  theme(legend.position = "none",
+        axis.title = element_text(size = 40),
+        axis.text = element_text(size = 40),
+        legend.title = element_text(size = 48),
+        legend.text = element_text(size = 40))
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/f1_plot.pdf', plot = f1_plot,
+       width = 20, height = 12, units = "in", dpi = 600)
+
+f2_plot <- ggplot(data = plot_tibble_2) +
+  geom_line(aes(x = x, y = y), col = 'red') +
+  theme_light() +
+  theme(legend.position = "none",
+        axis.title = element_text(size = 40),
+        axis.text = element_text(size = 40),
+        legend.title = element_text(size = 48),
+        legend.text = element_text(size = 40))
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/f2_plot.pdf', plot = f2_plot,
+       width = 20, height = 12, units = "in", dpi = 600)

### 2022-02-04 Paper/main.tex
ggplot replacements for function plots
Comment for new curves

@@
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
+It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
 Finally, we obtain the generated curves $NIR_{sim}$
+
+	{\color{blue} This has to be more precise. We don't really use $\hat{\nu}_j(t)$ but $\tilde{\nu}^{m,L}(t)$ for a large $L$.}
 
@@
 				\centering
-  				\includegraphics[width=\textwidth]{../Graphics/smooth_function.png}
+  				\includegraphics[width=\textwidth]{../Graphics/f1_plot.pdf}
   				\caption{$f_1(t)$, smooth function}
@@
 	  			\centering
-  				\includegraphics[width=\textwidth]{../Graphics/bumpy_function.png}
+  				\includegraphics[width=\textwidth]{../Graphics/f2_plot.pdf}
   				\caption{$f_2(t)$, bumpy function}

### 2022-02-05 Paper/main.tex
Small corrections

@@
 	\begin{equation}\label{Taylor_expansion}
-		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}}{i!}
-	\end{equation}
-
-	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can oftenlead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole.
+		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
+	\end{equation}
+
+	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can often lead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole.
 From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$.

### 2022-02-05 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R
Coefficient function estimate plots for chosen specifications

@@ -1,0 +1,918 @@
+##### Load packages #####
+library(tidyverse)
+library(fda)
+library(refund)
+library(rlist)
+
+###### load auxiliary files #####
+source("data_generator.R")
+
+###### original functions #####
+f_1 <- function(t) {
+  return(2 * sin(0.5 * pi * t) + 4 * sin(1.5 * pi * t) + 5 * sin(2.5 * pi * t))
+}
+
+f_2 <- function(t) {
+  return(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2))
+}
+
+# grid for plotting
+plot_grid <- seq(0, 1, length.out = 1000)
+
+###### generate response variables #####
+grid <- seq(0, 1, length.out = 401)
+f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
+
+data(gasoline)
+NIR <- gasoline$NIR
+
+sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
+sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
+sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
+sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
+
+generated_curves <- NIR_curve_generator(n = 200, n_harmonics = 30)
+my_data <- as.matrix(generated_curves[, -1])
+
+Y1_1 <- as.numeric(my_data %*% f1 + rnorm(200, 0, 1) * sigma_eps_squared1_1)
[…]

### 2022-02-05 Code/Simulation_Functions.R

@@ -144,7 +144,7 @@ bspline_function <- function(rep, my_data = NULL, n_obs, seed, debug = FALSE) {
             
             # multiply
             coefficient_matrix_1_1 <- map(.x = 1:n_elem_fold,
-                    .f = function(i) est_coef_1_1 %*% obs_test_coefs[,i])
+                                          .f = function(i) est_coef_1_1 %*% obs_test_coefs[,i])
             coefficient_matrix_1_2 <- map(.x = 1:n_elem_fold,
                                           .f = function(i) est_coef_1_2 %*% obs_test_coefs[,i])
             coefficient_matrix_2_1 <- map(.x = 1:n_elem_fold,

### 2022-02-05 Paper/main.tex
Added plots to tex doc with caption Placeholder

@@
 
+	\subsection{Curve Estimates for Chosen Specifications}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+		\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+		\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_1.pdf}
+			\caption{Placeholder}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_2.pdf}
+			\caption{Placeholder}
+		\end{minipage}
+	\end{figure}
+
 	\section{Proofs}

### 2022-02-05 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R
Improved text size in plots

@@ -648,9 +648,9 @@ basis_expansion_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
   theme_light() +
   theme(
     legend.position = "bottom",
-    axis.title = element_text(size = 20),
-    axis.text = element_text(size = 20),
-    legend.title = element_text(size = 24),
+    axis.title = element_text(size = 40),
+    axis.text = element_text(size = 40),
+    legend.title = element_text(size = 48),
     legend.text = element_text(size = 20)
   )
 
@@ -665,9 +665,9 @@ basis_expansion_plot_1_2 <- ggplot(data = plot_tibble_1_2 %>%
   theme_light() +
   theme(
     legend.position = "bottom",
-    axis.title = element_text(size = 20),
-    axis.text = element_text(size = 20),
-    legend.title = element_text(size = 24),
+    axis.title = element_text(size = 40),
+    axis.text = element_text(size = 40),
+    legend.title = element_text(size = 48),
     legend.text = element_text(size = 20)
   )
 
@@ -682,9 +682,9 @@ basis_expansion_plot_2_1 <- ggplot(data = plot_tibble_2_1 %>%
   theme_light() +
   theme(
     legend.position = "bottom",
-    axis.title = element_text(size = 20),
-    axis.text = element_text(size = 20),
-    legend.title = element_text(size = 24),
+    axis.title = element_text(size = 40),
+    axis.text = element_text(size = 40),
+    legend.title = element_text(size = 48),
     legend.text = element_text(size = 20)
   )
 
@@ -699,9 +699,9 @@ basis_expansion_plot_2_2 <- ggplot(data = plot_tibble_2_2 %>%
   theme_light() +
   theme(
     legend.position = "bottom",
-    axis.title = element_text(size = 20),
-    axis.text = element_text(size = 20),
-    legend.title = element_text(size = 24),
+    axis.title = element_text(size = 40),
+    axis.text = element_text(size = 40),
+    legend.title = element_text(size = 48),
     legend.text = element_text(size = 20)
   )
 
@@ -717,9 +717,9 @@ fpcr_nharm2_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
   theme_light() +
   theme(
     legend.position = "bottom",
-    axis.title = element_text(size = 20),
-    axis.text = element_text(size = 20),
-    legend.title = element_text(size = 24),
+    axis.title = element_text(size = 40),
[…]

### 2022-02-05 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R
Small Correction for Legends

@@ -612,14 +612,14 @@ plot_tibble_1_2 <- cbind(
 plot_tibble_2_1 <- cbind(
   tibble(
     x = plot_grid,
-    f1 = f_2(plot_grid)
+    f2 = f_2(plot_grid)
   ),
   beta_hat_2_1,
   pca_beta_est_2_1
 ) %>%
   pivot_longer(cols = !x, names_to = "Curve", values_to = "y") %>%
   mutate(Curve = factor(Curve, levels = c(
-    "f1", "B-Spline", "Monomial", "Fourier",
+    "f2", "B-Spline", "Monomial", "Fourier",
     "bspline_nharm2", "bspline_nharm3", "bspline_nharm4",
     "monomial_nharm2", "monomial_nharm3", "monomial_nharm4",
     "fourier_nharm2", "fourier_nharm3", "fourier_nharm4"
@@ -628,14 +628,14 @@ plot_tibble_2_1 <- cbind(
 plot_tibble_2_2 <- cbind(
   tibble(
     x = plot_grid,
-    f1 = f_2(plot_grid)
+    f2 = f_2(plot_grid)
   ),
   beta_hat_2_2,
   pca_beta_est_2_2
 ) %>%
   pivot_longer(cols = !x, names_to = "Curve", values_to = "y") %>%
   mutate(Curve = factor(Curve, levels = c(
-    "f1", "B-Spline", "Monomial", "Fourier",
+    "f2", "B-Spline", "Monomial", "Fourier",
     "bspline_nharm2", "bspline_nharm3", "bspline_nharm4",
     "monomial_nharm2", "monomial_nharm3", "monomial_nharm4",
     "fourier_nharm2", "fourier_nharm3", "fourier_nharm4"
@@ -651,7 +651,7 @@ basis_expansion_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
     axis.title = element_text(size = 40),
     axis.text = element_text(size = 40),
     legend.title = element_text(size = 48),
-    legend.text = element_text(size = 20)
+    legend.text = element_text(size = 40)
   )
 
 ggsave(
@@ -668,7 +668,7 @@ basis_expansion_plot_1_2 <- ggplot(data = plot_tibble_1_2 %>%
     axis.title = element_text(size = 40),
     axis.text = element_text(size = 40),
     legend.title = element_text(size = 48),
-    legend.text = element_text(size = 20)
[…]

### 2022-02-05 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R
Legend linewidth improvements

@@ -652,11 +652,12 @@ basis_expansion_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
     axis.text = element_text(size = 40),
     legend.title = element_text(size = 48),
     legend.text = element_text(size = 40)
-  )
+  ) +
+  guides(color = guide_legend(override.aes = list(lwd = 5)))
 
 ggsave(
   filename = "../Graphics/Curve_Estimates/basis_expansion_1_1.pdf", plot = basis_expansion_plot_1_1,
-  width = 20, height = 8, units = "in", dpi = 600
+  width = 20, height = 12, units = "in", dpi = 600
 )
 
 basis_expansion_plot_1_2 <- ggplot(data = plot_tibble_1_2 %>%
@@ -669,11 +670,12 @@ basis_expansion_plot_1_2 <- ggplot(data = plot_tibble_1_2 %>%
     axis.text = element_text(size = 40),
     legend.title = element_text(size = 48),
     legend.text = element_text(size = 40)
-  )
+  ) +
+  guides(color = guide_legend(override.aes = list(lwd = 5)))
 
 ggsave(
   filename = "../Graphics/Curve_Estimates/basis_expansion_1_2.pdf", plot = basis_expansion_plot_1_2,
-  width = 20, height = 8, units = "in", dpi = 600
+  width = 20, height = 12, units = "in", dpi = 600
 )
 
 basis_expansion_plot_2_1 <- ggplot(data = plot_tibble_2_1 %>%
@@ -686,11 +688,12 @@ basis_expansion_plot_2_1 <- ggplot(data = plot_tibble_2_1 %>%
     axis.text = element_text(size = 40),
     legend.title = element_text(size = 48),
     legend.text = element_text(size = 40)
-  )
+  ) +
+  guides(color = guide_legend(override.aes = list(lwd = 5)))
 
 ggsave(
   filename = "../Graphics/Curve_Estimates/basis_expansion_2_1.pdf", plot = basis_expansion_plot_2_1,
-  width = 20, height = 8, units = "in", dpi = 600
+  width = 20, height = 12, units = "in", dpi = 600
 )
 
 basis_expansion_plot_2_2 <- ggplot(data = plot_tibble_2_2 %>%
@@ -703,11 +706,12 @@ basis_expansion_plot_2_2 <- ggplot(data = plot_tibble_2_2 %>%
[…]

### 2022-02-05 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R
Correction of  Coefficient Functions in Simulation
Due to the Numeric Approximation, we were actually using this function. (Just the original ones multiplied by 401) This might be an artifact of changing the interval to [0,1], where in Reiss & Ogden the authors might have used [0, 401]

@@ -9,11 +9,11 @@ source("data_generator.R")
 
 ###### original functions #####
 f_1 <- function(t) {
-  return(2 * sin(0.5 * pi * t) + 4 * sin(1.5 * pi * t) + 5 * sin(2.5 * pi * t))
+  return(401*(2 * sin(0.5 * pi * t) + 4 * sin(1.5 * pi * t) + 5 * sin(2.5 * pi * t)))
 }
 
 f_2 <- function(t) {
-  return(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2))
+  return(401*(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2)))
 }
 
 # grid for plotting
@@ -303,22 +303,22 @@ fReg_coef_2_2 <- map(
 ##### and bind to data.frame #####
 beta_hat_1_1 <- as_tibble(list.cbind(map(
   .x = 1:3,
-  .f = function(i) (eval_bases_1_1[[i]] %*% fReg_coef_1_1[[i]]) / 401
+  .f = function(i) (eval_bases_1_1[[i]] %*% fReg_coef_1_1[[i]]) # / 401
 )))
 
 beta_hat_1_2 <- as_tibble(list.cbind(map(
   .x = 1:3,
-  .f = function(i) (eval_bases_1_2[[i]] %*% fReg_coef_1_2[[i]]) / 401
+  .f = function(i) (eval_bases_1_2[[i]] %*% fReg_coef_1_2[[i]]) # / 401
 )))
 
 beta_hat_2_1 <- as_tibble(list.cbind(map(
   .x = 1:3,
-  .f = function(i) (eval_bases_2_1[[i]] %*% fReg_coef_2_1[[i]]) / 401
+  .f = function(i) (eval_bases_2_1[[i]] %*% fReg_coef_2_1[[i]]) # / 401
 )))
 
 beta_hat_2_2 <- as_tibble(list.cbind(map(
   .x = 1:3,
[…]

### 2022-02-05 Code/Plot_Generators/f_functions.R

@@ -1,11 +1,11 @@
 library(tidyverse)
 
 f1 <- function(t){
-  return(2*sin(0.5*pi*t) + 4*sin(1.5*pi*t) + 5*sin(2.5*pi*t))
+  return(401*(2*sin(0.5*pi*t) + 4*sin(1.5*pi*t) + 5*sin(2.5*pi*t)))
 }
 
 f2 <- function(t){
-  return(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2))
+  return(401*(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2)))
 }
 
 grid <- seq(0, 1, length.out = 1000)

### 2022-02-06 Paper/main.tex
Correction of  Coefficient Functions in Simulation
Due to the Numeric Approximation, we were actually using this function. (Just the original ones multiplied by 401) This might be an artifact of changing the interval to [0,1], where in Reiss & Ogden the authors might have used [0, 401]
Added useful captions
Introduction work + added plot to basis truncation

@@
 
-	\section{Colour Guide}
-		\begin{itemize}
-			\item {\color{red} RED}: is for general comments for your own text
-			\item {\color{green} GREEN}: is for Jona's comments
-			\item {\color{orange} ORANGE}: is for Jonghun's comments
-			\item {\color{blue} BLUE}: is for Jakob's comments
-		\end{itemize}
+%	\section{Colour Guide}
+%		\begin{itemize}
+%			\item {\color{red} RED}: is for general comments for your own text
+%			\item {\color{green} GREEN}: is for Jona's comments
+%			\item {\color{orange} ORANGE}: is for Jonghun's comments
+%			\item {\color{blue} BLUE}: is for Jakob's comments
+%		\end{itemize}
 
@@
 
-	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.
-Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf.
-\cite{levitin_introduction_2007}).
-	As \cite{kokoszka_introduction_2017} {\color{red}(page ca.
-17)} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves .
-
-	In functional data analysis, the concept of a data set includes both realizations of scalar random variables and realizations of random functions.
-These could be the absorption of the Near-infrared (NIR) spectrum, which will be used in later parts of this paper.
-NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of light at different wavelengths in a sample.
-\footnote{For more details, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  This dataset can then be used, for example, to predict a scalar response variable.
-To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
+	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature.
+Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf.
+\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variables or units of a given data set can be seen as smooth curves or functions.
+	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
+Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples, an example which will be used in later parts of this paper.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}
 	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.
@@
 
-	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function.
+	Here, $X(\omega)$ is a random function, $Y(\omega)$ is a scalar response variable and $\beta(t)$ is a coefficient function.
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional.
-As in the framework of scalar linear regression, estimating $\beta(t)$ is particularly interesting for prediction or inference.
-\\
+This paper then introduces two distinct ways of estimating $\beta(t)$ using approximations dependent on a parameter choice and explores the selection of these parameters using cross validation.\\
 
 	In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis.
-Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis for the previously mentioned methods.
+Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods.
 The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
-In section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
+In Section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
 
@@
 
-	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can often lead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole.
+	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can often lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
 From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$.
@@
 
-	{\color{blue}I don't get this...
+	%{\color{blue}I don't get this...
 Isn't the basis defined independently from the data set?
@@
 The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.
+
+	\begin{figure}[H]
+		\includegraphics[width=\textwidth]{../Graphics/basis_expansions.pdf}
+		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
+	\end{figure}
 
@@
 	\begin{equation}
-    	f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
-    \end{equation}
-
-    \begin{equation}
-    	\begin{split}
-    		f_2(t) = & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
-    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)}
+    	f_1(t) = 401 \left[ 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) \right]
+    \end{equation}
+
+    \begin{equation}
+    	\begin{split}
+    		f_2(t) = 401  \Bigg[ & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
+    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)} \Bigg]
     	\end{split}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_1.pdf}
-			\caption{Placeholder}
+			\caption{Basis Expansion Regression - $f_1, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_2.pdf}
-			\caption{Placeholder}
+			\caption{Basis Expansion Regression - $f_1, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_1.pdf}
-			\caption{Placeholder}
+			\caption{Basis Expansion Regression - $f_2, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_2.pdf}
-			\caption{Placeholder}
+			\caption{Basis Expansion Regression - $f_2, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 2 harmonics - $f_1, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 2 harmonics - $f_1, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 2 harmonics - $f_2, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 2 harmonics - $f_2, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 3 harmonics - $f_1, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 3 harmonics - $f_1, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 3 harmonics - $f_2, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 3 harmonics - $f_2, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 4 harmonics - $f_1, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 4 harmonics - $f_1, Y_2$}
 		\end{minipage}
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_1.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 4 harmonics - $f_2, Y_1$}
 		\end{minipage}%
@@
 			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_2.pdf}
-			\caption{Placeholder}
+			\caption{FPC Regression, 4 harmonics - $f_2, Y_2$}
 		\end{minipage}

### 2022-02-06 Paper/main.tex
Limit to the number of Eigenfunctions added

@@
 	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
-	 	\qquad i = 1, ..., n
+	 	\qquad i = 1, ..., N
 	 \end{equation}
@@
 	\begin{equation}\label{Fourier_Series}
-		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
+		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
 	\end{equation}
@@
 	\begin{equation}
-		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
-	\end{equation}
-
-	\begin{equation}
-		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
-	\end{equation}
-
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
-{\color{red} I think the number of principal components has to be smaller then the number of observations.
-So I can give more information about $\mathcal{M}$.}
+		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
+	\end{equation}
+
+	\begin{equation}
+		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
+	\end{equation}
+
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1, \dots, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
+As in the case of ordinary principal components, the number of eigenfunctions corresponding to non-zero eigenvalues is limited (cf.
+chapter 8.2.3 \cite{ramsay_functional_2005}).
+As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality.
+However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
 
@@
 	\begin{equation}
-		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
+		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
 	\end{equation}
@@
 			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
+			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
 		\end{pmatrix}
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
-			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
+			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
 		\end{split}
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
-			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
+			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 			y_i & = \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& = \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& \approx \tilde{\alpha}^L
-			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
+			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
 		\end{pmatrix}
@@
 		\end{equation}
-		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions.
+		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.
 		\begin{equation}

### 2022-02-06 Paper/main.tex
Small text changes

@@
 Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf.
-\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variables or units of a given data set can be seen as smooth curves or functions.
+\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.
 	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
@@
 
+	This method of deriving or approximating the eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
+The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.
+
 	\subsection{Scalar-on-Function Regression}

### 2022-02-06 Paper/main.tex
reference for proof

@@
 
-	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+	where the $c(t,s)$ are \textit{Hilbert-Schmidt Kernels} defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+Let $K$ be a \textit{Hilberst-Shmidt operator} on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
 
@@
 	\section{Proofs}
+	\cite{alexanderian_KLexpansion_2015} was referred for the following proofs.
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ of basis functions satisfy the following properties:
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}).
+The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:
 	\begin{enumerate}
@@
 		\end{equation}
-		The original process also has the same properties as the centered one since
+		The original process $X(t)$ also has the same properties as the centered one since
 		\begin{equation}
@@
 	\begin{proof}
-		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda^m$.
+		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

### 2022-02-06 Paper/main.tex
Auto stash before merge of "main" and "origin/main"

@@
 	\subsection{Inner Products and Hilbert Spaces}
-	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
-In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
-A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
+	In the following we restrict our analysis to vector spaces over $\mathbb{R}$ but more a general formalization including other fields is possible.
+Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.
+Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
 

### 2022-02-06 Paper/main.tex
Proof

@@
 
-	where the $c(t,s)$ are \textit{Hilbert-Schmidt Kernels} defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be a \textit{Hilberst-Shmidt operator} on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+Let $K$ be a Hilberst-Shmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
 
@@
 	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
-	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$.
+	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process, namely, $\lim\limits_{\epsilon \rightarrow 0} \mathbb{E}[(X(t+\epsilon) - X(t))^2]$ = 0, such that $X \in \mathbb{L}^{2}[0,1]$.
 Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
@@
 	\begin{proof}
-		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
+		Let $K$ be a Hilbert-Schmidt operator as in \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
@@
 
-		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since F(t) is the centered process. Now, take the second term
+		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since $F(t)$ is the centered process. Now, take the second term
 		\begin{equation}\label{Thr2}

### 2022-02-06 Paper/main.tex
Bspline correction

--- 2022-02-06 Paper/main.tex
@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-Typically, knots are placed on an equidistant grid, but deviations from this principle can prove advantageous in atypical settings.
-Additionally, at each $\tau_l$, the polynomials on neighboring subintervals must match derivatives up to order $m-2$ at the boundary.
-However, it is sensible to place multiple knots at the same value to replicate specific properties of the data structure.
-A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
-Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
+Typically, knots are placed on an equidistant grid leading to polynomials on neighboring subintervals matching derivatives up to order $m-2$ at the boundary knot $\tau_l$.
+However, in some settings it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure.
+This allows for a reduced number of matching derivatives at the corresponding knots.
+For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\
+
+	B-splines were developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure.
+Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
 
@@
 
+	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times.
+This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\
+
 	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
@@
 	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
-
-	{\color{red}Explain what happens when $l+m+1 > L$ !!!(I don't get it)\\
-		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.(adressed)}
 

### 2022-02-06 Paper/main.tex
One reference corrected

@@
 
-	\subsubsection{Estimation using Basis-Representation}
+	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
@@
 
-	\begin{equation}\label{basis_exp_transf}
+	\begin{equation}
 		\begin{split}
@@
 
-	\subsubsection{Estimation using Functional Principal Components}
+	\subsubsection{Estimation using Functional Principal Components}\label{fpc_exp_transf}
 

### 2022-02-06 Paper/main.tex
Simulation results, Appliaction

--- 2022-02-06 Paper/main.tex
@@
 
-%	\section{Colour Guide}
-%		\begin{itemize}
-%			\item {\color{red} RED}: is for general comments for your own text
-%			\item {\color{green} GREEN}: is for Jona's comments
-%			\item {\color{orange} ORANGE}: is for Jonghun's comments
-%			\item {\color{blue} BLUE}: is for Jakob's comments
-%		\end{itemize}
+	\section{Colour Guide}
+		\begin{itemize}
+			\item {\color{red} RED}: is for general comments for your own text
+			\item {\color{green} GREEN}: is for Jona's comments
+			\item {\color{orange} ORANGE}: is for Jonghun's comments
+			\item {\color{blue} BLUE}: is for Jakob's comments
+		\end{itemize}
 
@@
 
-	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature.
-Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf.
-\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.
-	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
-Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples, an example which will be used in later parts of this paper.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}
+	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature.
+Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf.
+\cite{levitin_introduction_2007}).
+	As \cite{kokoszka_introduction_2017} {\color{red}(page ca.
+17)} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves .
+
+	In functional data analysis, the concept of a data set includes both realizations of scalar random variables and realizations of random functions.
+These could be the absorption of the Near-infrared (NIR) spectrum, which will be used in later parts of this paper.
+NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of light at different wavelengths in a sample.
+\footnote{For more details, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  This dataset can then be used, for example, to predict a scalar response variable.
+To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
 	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.
@@
 	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
-	 	\qquad i = 1, ..., N
-	 \end{equation}
-
-	Here, $X(\omega)$ is a random function, $Y(\omega)$ is a scalar response variable and $\beta(t)$ is a coefficient function.
+	 	\qquad i = 1, ..., n
+	 \end{equation}
+
+	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function.
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional.
-This paper then introduces two distinct ways of estimating $\beta(t)$ using approximations dependent on a parameter choice and explores the selection of these parameters using cross validation.\\
+As in the framework of scalar linear regression, estimating $\beta(t)$ is particularly interesting for prediction or inference.
+\\
 
 	 In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis.
-Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods.
+Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis for the previously mentioned methods.
 The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
-In Section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
+In section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
 
@@
 	\subsection{Inner Products and Hilbert Spaces}
-	In the following we restrict our analysis to vector spaces over $\mathbb{R}$ but more a general formalization including other fields is possible.
-Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.
-Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
+	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$.
+In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
+A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
 
@@
 
-	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can often lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
+	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can often lead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole.
 From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$.
@@
 	\begin{equation}\label{Fourier_Series}
-		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
+		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
 	\end{equation}
@@
 
-	%{\color{blue}I don't get this...
+	{\color{blue}I don't get this...
 Isn't the basis defined independently from the data set?
@@
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-Typically, knots are placed on an equidistant grid leading to polynomials on neighboring subintervals matching derivatives up to order $m-2$ at the boundary knot $\tau_l$.
-However, in some settings it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure.
-This allows for a reduced number of matching derivatives at the corresponding knots.
-For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\
-
-	B-splines were developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure.
-Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
+Typically, knots are placed on an equidistant grid, but deviations from this principle can prove advantageous in atypical settings.
+Additionally, at each $\tau_l$, the polynomials on neighboring subintervals must match derivatives up to order $m-2$ at the boundary.
+However, it is sensible to place multiple knots at the same value to replicate specific properties of the data structure.
+A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}.
+Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
 
@@
 
-	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times.
-This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\
-
 	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
@@
 	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
+
+	{\color{red}Explain what happens when $l+m+1 > L$ !!!(I don't get it)\\
+		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.(adressed)}
 
@@
 
-	\begin{figure}[H]
-		\includegraphics[width=\textwidth]{../Graphics/basis_expansions.pdf}
-		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
-	\end{figure}
-
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
@@
 
-	where the $c(t,s)$ are \textit{Hilbert-Schmidt Kernels} defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be a \textit{Hilberst-Shmidt operator} on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
+Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
 
@@
 	\begin{equation}
-		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
-	\end{equation}
-
-	\begin{equation}
-		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
-	\end{equation}
-
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1, \dots, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
-As in the case of ordinary principal components, the number of eigenfunctions corresponding to non-zero eigenvalues is limited (cf.
-chapter 8.2.3 \cite{ramsay_functional_2005}).
-As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality.
-However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
+		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
+	\end{equation}
+
+	\begin{equation}
+		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
+	\end{equation}
+
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
+{\color{red} I think the number of principal components has to be smaller then the number of observations.
+So I can give more information about $\mathcal{M}$.}
 
@@
 	\begin{equation}
-		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
+		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
 	\end{equation}
@@
 
-	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
+	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the curves for both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
 This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
@@
 
-	This method of deriving or approximating the eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
-The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.
-
 	\subsection{Scalar-on-Function Regression}
@@
 			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
+			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
 		\end{pmatrix}
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
-			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
+			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
 		\end{split}
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
-			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
+			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 			y_i & = \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& = \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& \approx \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 			\vdots & \vdots & \ddots & \vdots \\
-			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
+			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
 		\end{pmatrix}
@@
 	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-First, the initial curves are expressed in terms of a generated B-spline basis which is created using 50 knots.
+First, the initial curves are expressed in terms of a generated cubic B-spline basis which is created using 50 knots.
+In the R implementation of the fda package that is used, these 50 knots account for 52 basis functions (50+4-2).
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$.
+It is assumed that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
 Finally, we obtain the generated curves $NIR_{sim}$
 
-	{\color{blue} This has to be more precise. We don't really use $\hat{\nu}_j(t)$ but $\tilde{\nu}^{m,L}(t)$ for a large $L$.}
-
-	\begin{equation}
-		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)
-	\end{equation}
-
-	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
+	\begin{equation}
+		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{m = 1}^{M} \tilde{\xi}_m(\omega) \tilde{\nu}^{m,L}(t)
+	\end{equation}
+
+	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\tilde{\nu}^{m,L}(t)$  are approximated as vectors in $\mathbb{R}^{401}$ for $L =$ 30 eigenfunctions.
 
@@
 	\subsection{Results}	
-
+	The discussed results and figures of $\hat{\beta}$ for the simulation can be found in the appendix. 
 	\subsubsection{Basis Expansion Regression}
@@
 	\paragraph{Monomial Basis}
-	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis.
-For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than B-splines for this coefficient function, but show the weakest performance for the coefficient function $f_2$.
+	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability.
+For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$.
+The monomial basis shows a better performance than B-splines for this coefficient function.
+A hypothesis for this could be that $f_1$ resembles an entire function, which can be well approximated with a power series.
+In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in figure 9 and 10, where it seems like $\hat{\beta}$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
-This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less pronounced.
+This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.
 
@@
 	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
-For $f_2$, 11(6) B-spline basis functions are needed for the high(low) signal-to-noise ratios.
+An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (figure 7 and 8), which is especially pronounced for the higher noise responses.
+For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios.
 For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis.
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (figure 9 and 10).
 
 	\paragraph{Fourier Basis}
-	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
-With the low signal-to-noise ratio, the simulation chooses a smaller number to account for the higher noise in the response variable.
-The Fourier basis functions perform the best in each setup for the basis expansion regression.
-When recalling $f_1$ and $f_2$, both, but especially $f_1$ shows similar curvature order across the domain which contributes to the strong performance of this basis.	\\
-
-	For all specifications, the effect of the Bias-Variance tradeoff can be observed: The function $f_1$ is rather smooth and little bias introduced when choosing a small number of basis functions.
-For $f_2$, higher number of basis functions are needed, resulting from the inherent peculiarities of $f_2$.
-We can choose a higher number of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
+	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
+With the low signal-to-noise ratio, the simulation chooses a smaller number of basis functions, which could be to account for the higher noise in the response variable.
+The Fourier basis functions perform the best for each setup for the basis expansion regression.
+Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$, while changing, does not display any eradic jumps.
+Second, both functions feature periodic behaviour.
+Third, $f_2$ does have the same value at the start- and the end of the interval.	\\
+
+	A possible explanation applicable for all the specifications might be the effect of the Bias-Variance tradeoff and the following hypothesis: The function $f_1$ is rather simple.
+meaning that little bias is introduced when choosing a small number of basis functions.
+For $f_2$, a higher number of basis functions is needed, resulting from the inherent peculiarities of $f_2$.
+This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
 
 	\subsubsection{Functional Principal Component Regression}
-	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}.
+	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
 Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
+But since the FPCR is ultimately estimated with a linear model with the FPC´s as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC´s $n_{FPC} \in \{2, 3, 4 \}$.
 
 	\paragraph{Monomial Basis}
-	TBD
+	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC´s and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behaviour of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC.
+This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC´s.
+The monomial basis shows the weakest performance for all three basis functions in each setting.
 	\paragraph{B-spline Basis}
@@
 While the number of basis functions stays at five for two and three used FPC, it increases to six basis functions for $nharm$ = 4.
-In $f_1,Y_1$, the cross-validated MSE is only slightly affected by the number of FPC's, but lowest for $nharm$ = 3, indicating the possibility of over-fitting for four FPC's.
-$f_2,Y_1$ shows the strongest decrease of MSE in increasing FPC's of all FPCR models fitted with B-splines (0.69614, 0.42504, 0.09497 for 2,3,4 FPC's).
-For $f_2,Y_2$ the same holds true as in the setup with $f_2$ and the high signal-to-noise ratio, but less pronounced.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions is increasing in the number of FPC's (4,6,8 for 2,3,4 FPC's)\\
-	The results overall might indicate that a higher number of FPC's has a strong effect in the setup with a high signal-to-noise ratio while not reducing as much error in the setting with the higher noise.
+In $f_1,Y_1$, the cross-validated MSE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4.
+$f_2,Y_1$ shows a decrease of MSE in increasing $n_{FPC}$.
+The same holds true in the setup with $f_2$ and the high signal-to-noise ratio with the decrease being similar in absolute terms.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,8 for $n_{FPC} \in \{2, 3, 4 \}$)\\
 
 	\paragraph{Fourier Basis}
-	We observe similar behavior as for the FPCR using B-splines.
-In $f_1,Y_1$, the MSE is decreasing in the number of FPC's while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
-Since it was not possible to calculate the cross-validated MSE for three basis functions for four FPC's, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here.
-$f_2,Y_1$ displays the greatest decline of MSE in the increasing number of FPC's.
-The same behavior can be seen in $f_2,Y_2$, but less pronounced.
-Both configurations of $f_2$ are using 5,15,7 basis functions for 2,3,4 FPC's: This behavior opposes to the previously reported increasing nature of basis functions in the number of FPC's.
+	We observe similar behaviour as for the FPCR using B-splines.
+In $f_1,Y_1$, the MSE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
+Since it is not possible to calculate the cross-validated MSE for three basis functions for $n_{FPC}$ = 4, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here for sure.
+$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolut values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline if MSE is similar to the decline observed for $f_2,Y_2$.
+Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$: This behaviour in increasing $n_{FPC}$ opposes the previously reported behaviour of the monomial basis and the increasing nature of the B-splines basis functions.
 
 	\subsubsection{Interpretation and Relevance for Application}
+
+	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \citep{Dattoli_2001})
+
+	Adress numerical instability?
+
+	maybee both in paragraph under results instead of here?
 
@@
 		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset.
-The simulation study will contribute towards the reading of the results.
+		Although the simulation study granted valuable insights in the different methods in the four different settings, it is not enough for determining the method and choice of basis of the application since there is still too much uncertainty involved.
+To point out some sources of uncertainty: First, we do not know the true coefficient function.
+The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion.
+Second, we do not know anything about the signal-to-noise ratios of the octane rating.
+Third, we made assumptions about the distribution of $\tilde{\xi}$ that are not relate-able to this real-life application where we not know this distribution.
+We will run all specification again for the gasoline dataset, but the results from the simulation study will contribute towards the reading of the results.
+The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 10 fold cross-validation.
+In total, we conducted 1000 repetitions for each setting.
 		\begin{itemize}
@@
 		\end{itemize}
+	\subsection{Interpretation of Results}
 
@@
 	\section{Proofs}
-	\cite{alexanderian_KLexpansion_2015} was referred for the following proofs.
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}).
-The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ of basis functions satisfy the following properties:
 	\begin{enumerate}
@@
 		\end{equation}
-		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.
+		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormaility of the eigenfunctions.
 		\begin{equation}
@@
 		\end{equation}
-		The original process $X(t)$ also has the same properties as the centered one since
+		The original process also has the same properties as the centered one since
 		\begin{equation}
@@
 	\begin{proof}
-		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
+		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda^m$.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

### 2022-02-06 Paper/main.tex
Reference added
Rendering

@@
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
+Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
 
@@
 
-	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \citep{Dattoli_2001})
+	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001})
 
@@
 
-	\subsection{Basis Plots}
+	\subsection{Basis Plots}\label{Basis_Plots}
 

### 2022-02-06 Paper/main.tex
Added multicols in proof section

@@
 	\subsubsection{Functional Principal Component Regression}
-	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
+	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}.
 Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
-But since the FPCR is ultimately estimated with a linear model with the FPC´s as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC´s $n_{FPC} \in \{2, 3, 4 \}$.
+But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
 
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC´s and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC's and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
 In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behaviour of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC.
-This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC´s.
+This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC's.
 The monomial basis shows the weakest performance for all three basis functions in each setting.
@@
 	\section{Proofs}
+
 	\cite{alexanderian_KLexpansion_2015} was referred for the following proofs.
+
 	\subsection{Lemma} \label{Proof1}
@@
 The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:
+
+	\begin{multicols}{2}
 		\begin{enumerate}
@@
 		\end{enumerate}
+	\end{multicols}
+
 	Remind that $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
+
 	\begin{proof}
 		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
+
 		\begin{equation}\label{Lemma1}
@@
 		\end{equation}
+
 		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
 		The second claim is proved as:
+
 		\begin{equation}\label{Lemma2}
@@
 		\end{equation}
+
 		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.
+
 		\begin{equation}
@@
 		\end{equation}
+
 		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as the first property.
 		The last assertion is confirmed from the above two properties.
+
 		\begin{equation}\label{Lemma3}
@@
 		\end{equation}
+
 		The original process $X(t)$ also has the same properties as the centered one since
+
 		\begin{equation}
@@
 		\end{equation}
+
 	\end{proof}
@@
 	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
+
 	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process, namely, $\lim\limits_{\epsilon \rightarrow 0} \mathbb{E}[(X(t+\epsilon) - X(t))^2]$ = 0, such that $X \in \mathbb{L}^{2}[0,1]$.
 Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
+
 	\begin{equation}
@@
 	\end{equation}
+
 	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)dt$. These coefficients satisfy the following conditions.
+
+	\begin{multicols}{2}
 		\begin{enumerate}
@@
 		\end{enumerate}
+	\end{multicols}
+
 	\begin{proof}
+
 		Let $K$ be a Hilbert-Schmidt operator as in \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
+
 		\begin{equation}
@@
 		\end{equation}
+
 		where $F(t)$ is the centered process of $X(t)$.
 		Once it is shown that $\lim\limits_{N \rightarrow \infty} \epsilon_{N}(t) = 0$ uniformly in [0,1], the proof is completed.
+
 		\begin{equation}\label{Thr1}
@@
 		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since $F(t)$ is the centered process. Now, take the second term
+
 		\begin{equation}\label{Thr2}
@@
 For the last term, we derive from (\ref{Lemma2}) that
+
 		\begin{equation}\label{Thr3}
@@
 		\end{equation}
+
 		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain
+
 		\begin{equation}
@@
 		implementing Mercer's Theorem this proof is concluded by
+
 		\begin{equation}

### 2022-02-06 Paper/main.tex
Added Structure to Outlook
Equaiton Coherences in proof

@@
 
+	\subsection{Limitations}
+
+	\subsection{Possible Extensions}
+
 	\subsection{Literature}
@@
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}).
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}.
 The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:
@@
 
-		Let $K$ be a Hilbert-Schmidt operator as in \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
+		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
@@
 
-		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since $F(t)$ is the centered process. Now, take the second term
+		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in Equation \ref{CovarianceFunction} since $F(t)$ is the centered process. Now, take the second term
 
@@
 
-		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in (\ref{HSKernal}).
+		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}.
 It turns out the product of the eigenfunction and the corresponding eigenvalue.
-For the last term, we derive from (\ref{Lemma2}) that
+For the last term, we derive from Equation \ref{Lemma2} that
 
@@
 
-		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain
+		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by Equations \ref{Thr1}, \ref{Thr2}, and \ref{Thr3} we obtain
 

### 2022-02-06 Paper/main.tex
Small correction for b-splines
Changes for additional runs for application

@@
 	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times.
-This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\
+This padding of the knot vector then allows to calculate every object that is needed for the definition of the basis over the original set of knots.\\
 
@@
 The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria.
-The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.
+The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study.
 

### 2022-02-06 Code/Main_Application.R

@@ -30,8 +30,8 @@ for (j in 2:4) {
     fold_size = 5, rep = 1000,
     seed = 100, nharm = j, debug = TRUE
   )
-  saveRDS(object = bspline_fpcr_appl, file = paste0("Results/Paper/Application/bspline_fpcr_nharm", j, "_appl.RDS"))
-  write_csv(x = bspline_fpcr_appl, file = paste0("Results/Paper/Application/bspline_fpcr_nharm", j, "_appl.csv"))
+  saveRDS(object = bspline_fpcr_appl, file = paste0("Results/Paper/Application/bspline_fpcr_nharm", j, "_appl_additional.RDS"))
+  write_csv(x = bspline_fpcr_appl, file = paste0("Results/Paper/Application/bspline_fpcr_nharm", j, "_appl_additional.csv"))
 }
 
 for (j in 2:4) {
@@ -40,8 +40,8 @@ for (j in 2:4) {
     seed = 100, nharm = j,
     even_basis = FALSE, debug = TRUE
   )
-  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl.RDS"))
-  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl.csv"))
+  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS.RDS"))
+  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS.csv"))
 }
 
 for (j in 2:4) {
@@ -49,6 +49,6 @@ for (j in 2:4) {
     fold_size = 5, rep = 1000,
     seed = 100, nharm = j, debug = TRUE
   )
-  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl.RDS"))
-  write_csv(x = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl.csv"))
+  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.RDS.RDS"))
[…]

### 2022-02-06 Code/Main_Application.R
Small correction

@@ -40,8 +40,8 @@ for (j in 2:4) {
     seed = 100, nharm = j,
     even_basis = FALSE, debug = TRUE
   )
-  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS.RDS"))
-  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS.csv"))
+  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS"))
+  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.csv"))
 }
 
 for (j in 2:4) {
@@ -49,6 +49,6 @@ for (j in 2:4) {
     fold_size = 5, rep = 1000,
     seed = 100, nharm = j, debug = TRUE
   )
-  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.RDS.RDS"))
-  write_csv(x = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.RDS.csv"))
+  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.RDS"))
+  write_csv(x = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.csv"))
 }

### 2022-02-06 Paper/main.tex
Rearranging simulation tables, starting application tables, stuff on interpretation

--- 2022-02-06 Paper/main.tex
@@
 	\begin{center}
+		University of Bonn \\
 		Research Module in Econometrics and Statistics \\
@@
 	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability.
+This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001}.
 For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$.
@@
 	\section{Application}\label{Application}
-		The application uses the methods from the previous sections to predict the octane ratings of the introduced gasoline dataset.
-		Although the simulation study granted valuable insights in the different methods in the four different settings, it is not enough for determining the method and choice of basis of the application since there is still too much uncertainty involved.
-To point out some sources of uncertainty: First, we do not know the true coefficient function.
+		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
+		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application from those insights, since there is still too much uncertainty involved.
+To point out some sources of uncertainty: First, opposing to the simulations study, we do not know the true coefficient function.
 The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion.
-Second, we do not know anything about the signal-to-noise ratios of the octane rating.
-Third, we made assumptions about the distribution of $\tilde{\xi}$ that are not relate-able to this real-life application where we not know this distribution.
+Second, we do not know anything about the signal-to-noise ratios of the measured octane numbers.
+Third, we made assumptions about the distribution of $\xi$ that are not relateable to this real-life application where we not know this distribution, neither can we infer something about it.
 We will run all specification again for the gasoline dataset, but the results from the simulation study will contribute towards the reading of the results.
@@
 In total, we conducted 1000 repetitions for each setting.
-		\begin{itemize}
-			\item {\color{green} incorporate results of simulation study: 					number of basis, components, etc...}
-			\item point out difficulties estimating sderror
-			\item describe setup and results
-		\end{itemize}
 	\subsection{Interpretation of Results}
@@
 \newpage
-\include{tables.tex}
+\include{tables_simulation.tex}
 
@@
 	\end{figure}
+
+\newpage
+\include{tables_application.tex}
 

### 2022-02-06 Paper/main.tex
Some Bullet Points for Outlook Section

@@
 
+	\paragraph{Insights from Simulation cannot be Extended to More General Functions}
+
+	\paragraph{Collinearity Problems in Basis Expansion Regression}
+
+	\paragraph{Low Number of Basis Functions in FPCR Regression}
+
 	\subsection{Possible Extensions}
+
+	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}
+
+	\paragraph{Comparison to Penalty Based Smoothing Procedures}
 

### 2022-02-06 Paper/main.tex
Replaced Literature Sections by \nocites
Small corrections

@@
 	\paragraph{Fourier Basis}
-	In the same way the monomial basis corresponds to the Taylor expansion, the Fourier basis corresponds to the Fourier series.
+	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series.
 The Fourier series can be used to decompose a periodic function into a weighted sum of trigonometric functions.
-Equation \ref{Fourier_Series} shows an example for a periodic function $s(x)$ defined on the interval $[0,1]$.
+Equation \ref{Fourier_Series} shows an example for a periodic function with a period of 1.
 
@@
 Therefore, rewriting the series in the sine-cosine form through a simple trigonometry formula as shown above is necessary.
-Due to this origin of the Fourier basis it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
+Due to this origin of the Fourier basis it is reasonable to restrict the number of Fourier basis functions to odd numbered values to stay true to the expansion in amplitude-phase form.
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
@@
 
-	Its elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$.
-Additionally, the Fourier basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
-
-	%{\color{blue}I don't get this...
-Isn't the basis defined independently from the data set?
-Why is this dependent on the measuring points?
-"rephrasing \cite{ramsay_functional_2005}, the Fourier basis is orthonormal when the values $t_j$ are equally spaced within $T$."}
-
-	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
+	Its elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
+Additionally, the Fourier basis is especially suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
+
+	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
 On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-Typically, knots are placed on an equidistant grid leading to polynomials on neighboring subintervals matching derivatives up to order $m-2$ at the boundary knot $\tau_l$.
-However, in some settings it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure.
-This allows for a reduced number of matching derivatives at the corresponding knots.
+If there are no multiplicities in the set of these knots, the polynomials on neighboring subintervals are matching derivatives up to order $m-2$ at the boundary knot $\tau_l$.
+A typical case of this that is often used in practive is an equidistant grid of knots.
+In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure allowing for a reduced number of matching derivatives at the corresponding knots.
 For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\
 
-	B-splines were developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure.
+	B-splines are a specific system of spline functions developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure.
 Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
@@
 
-	\subsection{Literature}
-	\begin{itemize}
-		\item \cite{alexanderian_KLexpansion_2015}
-		\item \cite{kokoszka_introduction_2017}
-		\item \cite{hsing_theoretical_2015}
-		\item \cite{ramsay_functional_2005}
-		\item \cite{horvath_inference_2012}
-		\item \cite{cai_prediction_2006}
-		\item \cite{levitin_introduction_2007}
-	\end{itemize}
+	\nocite{alexanderian_KLexpansion_2015}
+	\nocite{kokoszka_introduction_2017}
+	\nocite{hsing_theoretical_2015}
+	\nocite{ramsay_functional_2005}
+	\nocite{horvath_inference_2012}
+	\nocite{cai_prediction_2006}
+	\nocite{levitin_introduction_2007}
 
@@
 
-	\subsection{Literature}
-	\begin{itemize}
-		\item \cite{carey_life_2002}
-	\end{itemize}
+	\nocite{carey_life_2002}
 
@@
 
-	\subsection{Literature}
-	\begin{itemize}
-		\item \cite{James.2009} (shape-restrictions)
-	\end{itemize}
+	\nocite{James.2009} %(shape-restrictions)
 
@@
 
-	\newpage
 	\section{Affidavit}

### 2022-02-07 Code/Main_Application.R
Code updates

@@ -40,8 +40,8 @@ for (j in 2:4) {
     seed = 100, nharm = j,
     even_basis = FALSE, debug = TRUE
   )
-  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.RDS"))
-  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl_additional.csv"))
+  saveRDS(object = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl.RDS"))
+  write_csv(x = fourier_fpcr_appl, file = paste0("Results/Paper/Application/fourier_fpcr_nharm", j, "_appl.csv"))
 }
 
 for (j in 2:4) {
@@ -49,6 +49,6 @@ for (j in 2:4) {
     fold_size = 5, rep = 1000,
     seed = 100, nharm = j, debug = TRUE
   )
-  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.RDS"))
-  write_csv(x = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl_additional.csv"))
+  saveRDS(object = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl.RDS"))
+  write_csv(x = monomial_fpcr_appl, file = paste0("Results/Paper/Application/monomial_fpcr_nharm", j, "_appl.csv"))
 }

### 2022-02-07 Paper/main.tex
Two added outlook points
Adiing bspline_fpcr results, structuring application

@@
 		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
-		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application from those insights, since there is still too much uncertainty involved.
-To point out some sources of uncertainty: First, opposing to the simulations study, we do not know the true coefficient function.
+		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved.
+To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function.
 The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion.
-Second, we do not know anything about the signal-to-noise ratios of the measured octane numbers.
+Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
 Third, we made assumptions about the distribution of $\xi$ that are not relateable to this real-life application where we not know this distribution, neither can we infer something about it.
-We will run all specification again for the gasoline dataset, but the results from the simulation study will contribute towards the reading of the results.
-The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 10 fold cross-validation.
+		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results.
+The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold.
 In total, we conducted 1000 repetitions for each setting.
+
 	\subsection{Interpretation of Results}
-
-	\nocite{carey_life_2002}
+		\subsubsection{Basis Expansion Regression}
+		\subsubsection{Functional Principal Component Regression}
+
+	%\nocite{carey_life_2002}
 

### 2022-02-07 Paper/main.tex
Changes from meetings

@@
 	\section{Theory}\label{Theory}
-	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
+	{\color{red} Introductory Sentence Here!} In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
 However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
@@
 One integral concept in inferential statistics is random variables.
-Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
-	A typical case known to every undergraduate student of economics is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
+Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.
+	A typical case is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
 As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
@@
 	\paragraph{Monomial Basis}
-	The Monomial basis are trivially decompositions of every polynomial function. {\color{red} Continue Work here!}	
 	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials.
 Let $f(t)$ be an entire function, e.g.
-the exponential function or a trigonometric function, then we can write the following.
+a polynomial, the exponential function or a trigonometric function, then we can write the following.
 
@@
 However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
-	There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation.
-This restricts the number of basis functions.
-However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities.
-It finally leads to an undesirable behavior at the tails such as Taylor expansion (cf.
+	Collinearity problems arise since the monomials become more correlated to each other as their degree increases, which can result in numerically unstable calculations.
+This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities.
+It can also lead to undesirable behavior away from the point of evaluation of the monomials (cf.
 \cite{ramsay_functional_2005}).
-Therefore, regarding the use, this may be useful for relatively simple functions.
 
@@
 Additionally, the Fourier basis is especially suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
+{\color{red} Citation}
 
@@
 The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study.
+{\color{red} Add text for figure}
 
@@
 	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+{\color{red} Write equation with limited number of principal components.
+Truncation parameter M instead of N-1}
 
@@
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
+It is assumed that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}_{1},\: \dots \:, \mathring{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
 Finally, we obtain the generated curves $NIR_{sim}$
@@
 	\begin{equation}
-		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{m = 1}^{M} \tilde{\xi}_m(\omega) \tilde{\nu}^{m,L}(t)
-	\end{equation}
-
-	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\tilde{\nu}^{m,L}(t)$  are approximated as vectors in $\mathbb{R}^{401}$ for $L =$ 30 eigenfunctions.
+		\mathring{X}(\omega)(t) = \hat{\mu}(t) + \sum_{m = 1}^{M} \mathring{\xi}^m(\omega) \tilde{\nu}^{m,L}(t)
+	\end{equation}
+
+	where $\mathring{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\tilde{\nu}^{m,L}(t)$  are approximated as vectors in $\mathbb{R}^{401}$ for $M =$ 30 FPC's.
 
@@
 The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise.
-They are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
+They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
 The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
@@
 			\begin{split}
-				\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
-			    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^{m, \mathcal{T}} \psi_{k}(s)\right)} \mathrm{d}s \\
-				 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}^{\mathcal{H}}\sum_{k \in \mathcal{L}}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+				\hat{\xi}_{i}^{m, \mathcal{H}} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
+			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
+				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
 			\end{split}
@@
 	\subsection{Results}	
-	The discussed results and figures of $\hat{\beta}$ for the simulation can be found in the appendix. 
+	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in the appendix. 
 	\subsubsection{Basis Expansion Regression}
@@
 
+	\paragraph{Larger Range for the Number of Basis Functions for FPCR}
+
+	\paragraph{Larger Range for the Number of Principal Components}
+
+	\paragraph{Input from Physics Analysis}
+
 	\nocite{James.2009} %(shape-restrictions)

### 2022-02-07 Paper/main.tex
Small changes

@@
 	\section{Theory}\label{Theory}
-	{\color{red} Introductory Sentence Here!} In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$.
-However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
-Therefore, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects.
-One integral concept in inferential statistics is random variables.
+	To allow for scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
+One integral concept that has to be defined is a random function as a special case of a random variable.
 Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.
-	A typical case is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
-As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
-A formalization of this idea makes some more theoretical considerations necessary.
-The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.
+	The typical case for a random variable realizing i $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
+As a first intuition for the concept of a random function, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
+A formalization of this idea makes some more in-depth considerations necessary.
+The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015} and chapters 4.4 and 4.6 from \cite{kokoszka_introduction_2017}.
 
@@
 It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves.
-The basis expansion with truncation is defined by
-	\begin{equation}
+The basis expansion with truncation is given by Equation \ref{basis_exp}.
+
+	\begin{equation}\label{basis_exp}
 		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
 	\end{equation}
+
 	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
-The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria.
+The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation.
 The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study.

### 2022-02-07 Paper/main.tex
Some text changes

@@
 The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation.
-The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study.
-{\color{red} Add text for figure}
+Figure \ref{Different_Expansions} shows the effect of choosing different truncation parameters for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.
 
@@
 		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
+		\label{Different_Expansions}
 	\end{figure}
@@
 	In the simple scalar setting, one of the most important tools in econometrics is linear regression.
-Its goal is to predict the value of a dependent variable given a set of associated variables.
-For reference, assume a data generating process as follows.
+Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction.
+To motivate the jump from multivariate regression to scalar-on-function regression, assume first a data generating process as follows.
 
@@
 
-	Where $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
+	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
 	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$.
@@
 
-	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is supposed to be predicted from a functional variable. 
+	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent of a functional regressor. 
 	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
@@
 
-	Where $\beta(t)$ is an unknown coefficient function.
+	Here, $\beta(t)$ is an unknown coefficient function.
 Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
@@
 	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors.
-Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.
+Using a truncation of the basis at some parameter $J$ can be used to make this problem tractable if we assume that the approximation error created by this truncation is small.
 
@@
 
-	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
+	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
 

### 2022-02-07 Paper/main.tex
Making Bspline truncation more precise.

@@
 	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
+\\
+
+	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases have, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
+For the sake of keeping the notation reasonably concise, we will still keep this notation.
+However, by convention, this shall mean using a B-spline basis consisting of $L$ functions from this point on.
 
@@
 The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation.
-Figure \ref{Different_Expansions} shows the effect of choosing different truncation parameters for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.
+Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.
 

### 2022-02-07 Paper/main.tex
Small correction

@@
 
-	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases have, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
+	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
 For the sake of keeping the notation reasonably concise, we will still keep this notation.
-However, by convention, this shall mean using a B-spline basis consisting of $L$ functions from this point on.
+However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.
 

### 2022-02-07 Paper/main.tex
Shortened Introduction

@@
 	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
-Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples, an example which will be used in later parts of this paper.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}
-	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.
-
-	 \begin{equation}\label{DGP1}
-	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
-	 	\qquad i = 1, ..., N
-	 \end{equation}
-
-	Here, $X(\omega)$ is a random function, $Y(\omega)$ is a scalar response variable and $\beta(t)$ is a coefficient function.
-The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional.
-This paper then introduces two distinct ways of estimating $\beta(t)$ using approximations dependent on a parameter choice and explores the selection of these parameters using cross validation.\\
-
-	In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis.
-Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods.
+Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}
+
+	This paper introduces Functional Linear Regression in a scalar-on-function setting.
+The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional.
+	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can addressed using theory from multivariate regression.
+First, a so-called basis expansion of the coefficient function and second, functional principal component regression.
+Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis and this paper focuses on exploring the selection of these parameters using cross validation.\\
+
+	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures and address the theoretical importance of the truncation parameter.
+Section \ref{Simulation} contains a description of structure and results of our Monte-Carlo Simulation which is aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods.
 The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
-In Section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.
+In Section \ref{Outlook} we give an outlook on possible extensions for this paper and describe limitations of our approach.
 

### 2022-02-07 Paper/main.tex
added def

@@
 	\end{equation}
-
+	More exact definitions are provided at \ref{def_HS}.
 Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf.
@@
 
-	\section{Proofs}
-
-	\cite{alexanderian_KLexpansion_2015} was referred for the following proofs.
+	\section{Definition and Proofs}
+	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.
+
+	\subsection{Definition (Hilbert-Schmidt Operator)}\label{def_HS}
+	Given a bounded domain $\mathcal{A} \subset \mathbb{R}^n$, we call a function $c : \mathcal{A} \times \mathcal{A} \rightarrow \mathbb{R}$ a Hilbert-Schmidt kernel if
+	\begin{equation}
+		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 dx dy < \infty
+	\end{equation}
+	where $c \in \mathbb{L}^2(\mathcal{A} \times \mathcal{A})$.
+Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, by
+
+	\begin{equation}
+		[K\nu](x) = \int_{\mathcal{A}} c(x,y) \nu(y) dy
+	\end{equation}
+	When an integral operator $K$ is linear and bounded, it is called a Hilbert-Schmidt operator.
+The linearity of the operator $K$ is simply proved.
+Additionaly assume that $\alpha, \beta \in \mathbb{R}$ and $\theta \in \mathbb{L}^2(\mathcal{A})$.
+	\begin{equation}
+		\begin{split}
+			[K (\alpha \nu + \beta \theta)](x) =& \int_{\mathcal{A}} c(x,y)(\alpha \nu(y) + \beta \theta(y)) dy\\
+			= & \int_{\mathcal{A}} c(x,y) \alpha \nu(y) dy + \int_{\mathcal{A}} c(x,y) \beta \theta(y) dy\\
+			= & \alpha\int_{\mathcal{A}} c(x,y) \nu (y) dy + \beta\int_{\mathcal{A}} c(x,y) \theta (y) dy\\
+			= & \alpha[K\nu](x) + \beta[K\theta](x)
+		\end{split}
+	\end{equation}
+	For boundedness of the oprator $K$,
+	\begin{equation}
+		\begin{split}
+			\Vert K\nu \Vert^{2}_{\mathbb{L}^2(\mathcal{A})} = & \int_{\mathcal{A}} \biggl\vert [K\nu](x) \biggr\vert^2 dx\\
+			= &\int_{\mathcal{A}} \biggl\vert \int_{\mathcal{A}}c(x,y)\nu(y)dy \biggr\vert^2dx\\
+			\leq & \int_{\mathcal{A}}\biggl(\int_{\mathcal{A}}\vert c(x,y) \vert^2dy\biggr) \biggl(\int_{\mathcal{A}}\vert \nu(y) \vert ^2 dy \biggr)dx \quad \text{(Cauchy-Schwarz)}\\
+			= & \Vert c \Vert_{\mathbb{L}^2(\mathcal{A} \times \mathcal{A})}\Vert \nu \Vert_{\mathbb{L}^2} < \infty
+		\end{split}
+	\end{equation}
 

### 2022-02-07 Paper/main.tex
some outlook text

@@
 
-	\begin{equation}
+	\begin{equation}\label{regressor_mat_1}
 		Y = \begin{pmatrix}
@@
 	\paragraph{Collinearity Problems in Basis Expansion Regression}
+	As already described in the section on the simulation study, the basis expansion regression was in part limited by the numerical instability of the estimation procedure.
+This is mainly due to an increase in collinearity of the derived regressor matrix shown in Definition \ref{regressor_mat_1}.
+This problem is inherent to basis systems whose functions are not pairwise orthogonal, such as the monomial or B-splines bases, but gets more pronounced the more functions we add to the basis system and the higher the correlation between those functions.
+\\
+	The numeric instability of the inversion of this matrix makes the estimates unreliable and therefore can make this approach infeasible for non-orthogonal bases in settings where the characteristics of the data set demand a higher number of basis functions than is feasible due to the properties of the estimation procedure.
 
 	\paragraph{Low Number of Basis Functions in FPCR Regression}
+	Another limitation of the exploration into functional principal component regression is the low number of principal component specifications used in this paper.
+As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of this method as long as an appropriately high number of basis functions is provided.
+	A more significant factor seems to be the number of principal components available for the linear regression which in itself could be subject to choice according to cross validation.
 

### 2022-02-07 Paper/main.tex
Added plot for Legendre Polynomials

@@
 Let $f(t)$ be an entire function, e.g.
-a polynomial, the exponential function or a trigonometric function, then we can write the following.
+a polynomial, the exponential function or a trigonometric function, then we can express it in the following form.
 
@@
 However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
-	Collinearity problems arise since the monomials become more correlated to each other as their degree increases, which can result in numerically unstable calculations.
+	As the monomials are not pariwise orthogonal, this basis is also prone to Collinearity problems, which can result in numerically unstable estimates.
 This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities.
@@
 	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be a Hilberst-Shmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+Let $K$ be a Hilberst-Schmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
 
@@
 	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}
+	To address the collinearity problems described earlier, one possible idea would be to use a system of pair-wise orthogonal polynomials as a basis instead of the monomial basis.
+One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials.
+Due to their orthogonality the problems of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.
+The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.
 
@@
 
-\newpage
+	\begin{figure}[H]\label{Legendre_basis}
+		\includegraphics[width = \textwidth]{../Graphics/Legendre_Plot.pdf}
+		\caption{Legendre Polynomials of degree 0 to 7}
+	\end{figure}
+
 \include{tables_simulation.tex}
@@
 
-	\section{Affidavit}
+	\section*{Affidavit}
 

### 2022-02-07 Code/Plot_Generators/Legendre_Polynomials.R

@@ -1,0 +1,41 @@
+# Load packages
+library(tidyverse)
+
+# define polynomial functions
+Legendre <- function(degree, x){
+  if(degree == 0){return(1)}
+  if(degree == 1){return(x)}
+  if(degree == 2){return(1/2 * (3*x^2 - 1))}
+  if(degree == 3){return(1/2 * (5*x^3 - 3*x))}
+  if(degree == 4){return(1/8 * (35*x^4 - 30*x^2 + 3))}
+  if(degree == 5){return(1/8 * (63*x^5 - 70*x^3 + 15*x))}
+  if(degree == 6){return(1/16 * (231*x^6 - 315*x^4 + 105*x^2 - 5))}
+  if(degree == 7){return(1/16 * (429*x^7 - 693*x^5 + 315*x^3 - 35*x))}
+  else{stop('Higher degrees than 7 not implemented.')}
+}
+
+# create plotting tibble
+plotting <- tibble(x = seq(0,1, length.out = 1000),
+                   P_0 = Legendre(degree = 0, x = x),
+                   P_1 = Legendre(degree = 1, x = x),
+                   P_2 = Legendre(degree = 2, x = x),
+                   P_3 = Legendre(degree = 3, x = x),
+                   P_4 = Legendre(degree = 4, x = x),
+                   P_5 = Legendre(degree = 5, x = x),
+                   P_6 = Legendre(degree = 6, x = x),
+                   P_7 = Legendre(degree = 7, x = x)) %>% 
+  pivot_longer(cols = !x, names_to = 'Polynomial', values_to = 'y')
+
+
+Legendre_plot <- ggplot(data = plotting) +
+  geom_line(aes(x = x, y = y, col = Polynomial)) +
+  theme_light() +
+  theme(legend.position = "none",
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 20),
+        legend.title = element_text(size = 24),
+        legend.text = element_text(size = 20))
+
+# save plot in appropriate folder
+ggsave(filename = '../Graphics/Legendre_plot.pdf', plot = Legendre_plot,
+       width = 20, height = 8, units = "in", dpi = 600)

### 2022-02-07 Paper/main.tex
IMproved Spacing between \paragraph environments

@@
 	\subsubsection{Basis Expansion Regression}
-	The following results origin from the \hyperref[basis_exp_transf]{\textbf{Estimation using Basis-Representation}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
+	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
 
@@
 This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.
+	\vspace{-0.2cm}
 
@@
 While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (figure 9 and 10).
+	\vspace{-0.2cm}
 
@@
 	\subsubsection{Functional Principal Component Regression}
-	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{\textbf{Estimation using Functional Principal Components}}.
+	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
 Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
@@
 The monomial basis shows the weakest performance for all three basis functions in each setting.
+	\vspace{-0.2cm}
+
 	\paragraph{B-spline Basis}
@@
 The same holds true in the setup with $f_2$ and the high signal-to-noise ratio with the decrease being similar in absolute terms.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,8 for $n_{FPC} \in \{2, 3, 4 \}$)\\
+Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,8 for $n_{FPC} \in \{2, 3, 4 \}$)
+	\vspace{-0.2cm}
 
@@
 Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$: This behaviour in increasing $n_{FPC}$ opposes the previously reported behaviour of the monomial basis and the increasing nature of the B-splines basis functions.
+	\vspace{-0.2cm}
 
@@
 	\paragraph{Insights from Simulation cannot be Extended to More General Functions}
+	\vspace{-0.2cm}
 
@@
 	The numeric instability of the inversion of this matrix makes the estimates unreliable and therefore can make this approach infeasible for non-orthogonal bases in settings where the characteristics of the data set demand a higher number of basis functions than is feasible due to the properties of the estimation procedure.
+	\vspace{-0.2cm}
 
@@
 	A more significant factor seems to be the number of principal components available for the linear regression which in itself could be subject to choice according to cross validation.
+	\vspace{-0.2cm}
 
@@
 The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.
+	\vspace{-0.2cm}
 

### 2022-02-07 Paper/main.tex
Equation Spacing
Spacing
Appendix Spacing
Some fpcr estimation stuff.

@@
 
-%	\section{Colour Guide}
-%		\begin{itemize}
-%			\item {\color{red} RED}: is for general comments for your own text
-%			\item {\color{green} GREEN}: is for Jona's comments
-%			\item {\color{orange} ORANGE}: is for Jonghun's comments
-%			\item {\color{blue} BLUE}: is for Jakob's comments
-%		\end{itemize}
+	\setlength{\abovedisplayskip}{0.4cm}
+	\setlength{\belowdisplayskip}{0.4cm}
+
+	\setlength{\abovedisplayshortskip}{0.2cm}
+	\setlength{\belowdisplayshortskip}{0.4cm}
 
@@
 	The inner product naturally defines a norm and an associated distance on the vector space.
-
-	\begin{equation}
-		\lvert \lvert v \rvert \rvert = {\langle v, v \rangle}^{\frac{1}{2}}
-	\end{equation}
-
-	\begin{equation}
+	\begin{equation}
+		\lvert \lvert v \rvert \rvert = {\langle v, v \rangle}^{\frac{1}{2}} \quad \text{and} \quad 
 		d(v_1, v_2) = {\langle v_2 - v_1, v_2 - v_1 \rangle}^{\frac{1}{2}}
@@
 Recall that the span of a set of vectors $S \subseteq \mathbb{R}^P$ is given by
-
 	\begin{equation}
@@
 a basis $S = \{s_n\}$ as follows.
-
 	\begin{equation}
@@
 As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space is to use a truncated series.
-
 	\begin{equation}
@@
 Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
-
 	\begin{equation}
@@
 	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined.
-
 	\begin{equation}
@@
 
-	%\begin{equation}
-	%\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
-	%\end{equation}
-
 	\subsection{Functional Data Sets}
 	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$: 
-
 	\begin{equation}
@@
 Then the following equation shows how a basis can be used to express a function as a weighted sum of its elements.
-
 	\begin{equation}
@@
 a polynomial, the exponential function or a trigonometric function, then we can express it in the following form.
-
 	\begin{equation}\label{Taylor_expansion}
@@
 This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
-
 	\begin{equation}
@@
 \cite{ramsay_functional_2005}).
+	\vspace{-0.2cm}
 
@@
 Equation \ref{Fourier_Series} shows an example for a periodic function with a period of 1.
-
 	\begin{equation}\label{Fourier_Series}
@@
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
-
 	\begin{equation}
@@
 {\color{red} Citation}
+	\vspace{-0.2cm}
 
@@
 Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
-
 	\begin{equation}
@@
 The basis expansion with truncation is given by Equation \ref{basis_exp}.
-
 	\begin{equation}\label{basis_exp}
@@
 To do so, it is necessary to define the mean and covariance functions of $X(\omega)$.
-
 	\begin{equation}\label{MeanFunction}
@@
 	\end{equation}
-
 	\begin{equation}\label{CovarianceFunction}
@@
 Let $K$ be a Hilberst-Schmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
-
 	\begin{equation}\label{HSKernal}
@@
 	Define the following sample analogs for the mean and covariance functions.
-
 	\begin{equation}
@@
 	\end{equation}
-
 	\begin{equation}
@@
 However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
-
 	\begin{equation}
@@
 	This naturally leads to the following representation.
-
 	\begin{equation}
@@
 	\end{equation}
+
 	where the $\hat{\xi}_{i}^m$ are derived as 
-
 	\begin{equation}
@@
 For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
-
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
-
 	\begin{equation}\label{score_approx}
@@
 	And we can define the following objects:
-
 		\begin{align}
@@
 To motivate the jump from multivariate regression to scalar-on-function regression, assume first a data generating process as follows.
-
 	\begin{equation}
@@
 The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
-
 	\begin{equation}
@@
 Therefore, we will always assume a data generating process as follows in this paper.
-
 	\begin{equation}\label{DGP}
@@
 Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
-
 	\begin{equation}
@@
 	This enables us to write equation \ref{DGP} with $\beta(t)$ represented in this way to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
-
 	\begin{equation}
@@
 Using a truncation of the basis at some parameter $J$ can be used to make this problem tractable if we assume that the approximation error created by this truncation is small.
-
 	\begin{equation}
@@
 This leads to the following representation.
-
 	\begin{equation}
@@
 Defining the following notation
-
 	\begin{equation}
@@
 	This leads to a considerable simplification of Equation \ref{basis_exp_transf}.
-
 	\begin{equation}\label{simplified_model_basis_equation}
@@
 	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
-
 	\begin{equation}\label{regressor_mat_1}
@@
 	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
-
 	\begin{equation}
@@
 	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.
-
 	\begin{equation}
@@
 	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
-
 	\begin{equation}
@@
 Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
-
 	\begin{equation}
@@
 	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
-
 	\begin{equation}\label{fpcr_reg_both_expansions}
@@
 	For convenience, define the following notation:
-
 	\begin{equation}
@@
 	Then Equation \ref{fpcr_reg_both_expansions} can be expressed as follows.
-
 	\begin{equation}
@@
 	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
-{\color{red} Write equation with limited number of principal components.
-Truncation parameter M instead of N-1}
+Using only $M$ functional principal components therefore leads to the following approximation.
+	\begin{equation}
+		y_i \approx \tilde{\alpha}^L
+		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
+		= \tilde{\alpha}^L
+		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
+	\end{equation}
 
 	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
-
 	\begin{equation}
@@
 
-	We can then derive the following estimators.
-
-	\begin{equation}
-		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
+	We can then derive the following estimator for $\tilde{\alpha}^L$ and $\bar{b}^{m,L} \quad m = 1, \dots, M$
+	\begin{equation}
+		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1}
 	\end{equation}
@@
 To provide intuition in this approach, let
-
 	 \begin{equation}
@@
 Finally, we obtain the generated curves $NIR_{sim}$
-
 	\begin{equation}
@@
 Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the introduced methods with differing true coefficient functions:
-
 	\begin{equation}
@@
     \end{equation}
-
     \begin{equation}
@@
     \end{equation}
-    \vspace{0.2cm}\\
 
@@
 
-		\vspace{0.1cm}
 		\begin{figure}
@@
 The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
-
 		\begin{equation}
@@
 The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
-
 		\begin{equation}
@@
 		\end{equation}
+
 		with truncation parameter $m$.
@@
 This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
+	\vspace{-0.2cm}
 
@@
 One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials.
-Due to their orthogonality the problems of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.
+Due to their orthogonality, the problem of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.
 The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.
@@
 	\paragraph{Comparison to Penalty Based Smoothing Procedures}
+	In contrast to the more typical approach of using a large but often arbitrary number of basis functions and smoothing using a penalty term involving for example the second derivative of the curve, this paper focuses on smoothing by using a smaller number of basis functions.
+As a next step to the analysis of this paper, it would be interesting to compare both methods to see in which settings different approaches to smoothing perform better and if a possible combination of both approaches could be advantageous.
+	\vspace{-0.2cm}
 
 	\paragraph{Larger Range for the Number of Basis Functions for FPCR}
+	\vspace{-0.2cm}
 
 	\paragraph{Larger Range for the Number of Principal Components}
+	\vspace{-0.2cm}
 
 	\paragraph{Input from Physics Analysis}
+	\vspace{-0.2cm}
 
@@
 
-\include{tables_simulation.tex}
-
+	\input{tables_simulation.tex}
+
+	\newpage
 	\subsection{Curve Estimates for Chosen Specifications}
@@
 \newpage
-\include{tables_application.tex}
-
+\input{tables_application.tex}
+
+	\newpage
 	\section{Definition and Proofs}

### 2022-02-07 Paper/main.tex
Additional Simulation Code

@@
 
-	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
 Using only $M$ functional principal components therefore leads to the following approximation.
@@
 
-	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
+	As in the previous section, this equation lends itself for estimation with OLS and we can define the following objects.
 	\begin{equation}
@@
 	\newpage
-	\section{Definition and Proofs}
+	\section{Definitions and Proofs}
 	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.

### 2022-02-07 Code/Simulation_Functions.R

@@ -744,7 +744,7 @@ fpcr_function <- function(rep, my_data = NULL, n_obs, nharm, seed, debug = FALSE
   }
   
   # specfiy number of basis functions that should be considered
-  n_basis <- seq(from = 4, to = 25, by = 1)
+  n_basis <- c(50, 70) #seq(from = 4, to = 25, by = 1)
 
   # set up container for averaged cross validation scores
   CV_container <- as.data.frame(

### 2022-02-07 Paper/main.tex
some correction, interpretation cont.

--- 2022-02-07 Paper/main.tex
@@
 
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{7pt}
+
+\setlength{\abovedisplayshortskip}{3pt}
+\setlength{\belowdisplayshortskip}{7pt}
+
 \newcommand{\independent}{\perp\!\!\!\!\perp}
@@
 For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
-
+	\vspace{-0.1cm}
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
-
+	\vspace{-0.1cm}
 	\begin{equation}\label{fpcr_reg_both_expansions}
@@
 	\subsection{Generating Similar Curves}
-	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline dataset, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 First, the initial curves are expressed in terms of a generated cubic B-spline basis which is created using 50 knots.
@@
 			\begin{split}
-				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\biggr\rbrack \\
-				Y_{2,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\biggr\rbrack
+				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
+				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
 			\end{split}
@@
 			\begin{split}
-				\hat{\xi}_{i}^{m, \mathcal{H}} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
+				\hat{\xi}_{i}^{m, \mathcal{H},L} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
 			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
@@
 		\end{equation}
-		with truncation parameter $m$.
+
+		with truncation parameter $L$.
 		\vspace{0.2cm}
@@
 	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
+examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.
 
@@
 
-	A possible explanation applicable for all the specifications might be the effect of the Bias-Variance tradeoff and the following hypothesis: The function $f_1$ is rather simple.
-meaning that little bias is introduced when choosing a small number of basis functions.
-For $f_2$, a higher number of basis functions is needed, resulting from the inherent peculiarities of $f_2$.
-This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
-
 	\subsubsection{Functional Principal Component Regression}
@@
 But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+As will be described, it seems that neither a convex behaviour of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
 
@@
 	\subsubsection{Interpretation and Relevance for Application}
-
-	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001})
-
-	Adress numerical instability?
-
-	maybee both in paragraph under results instead of here?
+	A possible explanation applicable for all setups using Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For the function $f_1$ it might be that little bias is introduced when choosing a small number of basis functions.
+For $f_2$, a higher number of basis functions is needed, resulting from the inherent peculiarities of $f_2$.
+This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
+The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.
+This could not be observed for the FPCR where no clear relationship between the basis functions and the number of FPC was observed.
+An hypothesis for this would be that the results for the FPCR are mostly driven by the selected FPC´s.
+To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L$ for $n_{FPC} \in \{2, 3, 4 \}$, which seem to support this claim (LINK TO APPENDIX).
+
+	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)
+
+	%Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001})
+
+	%Adress numerical instability?
+
+	%maybee both in paragraph under results instead of here?
 
@@
 		\subsubsection{Functional Principal Component Regression}
+		As for the simulation study, the
 
@@
 	\paragraph{Comparison to Penalty Based Smoothing Procedures}
+	\vspace{-0.2cm}
 
 	\paragraph{Larger Range for the Number of Basis Functions for FPCR}
+	\vspace{-0.2cm}
 
 	\paragraph{Larger Range for the Number of Principal Components}
+	\vspace{-0.2cm}
 
 	\paragraph{Input from Physics Analysis}
+	\vspace{-0.2cm}
 

### 2022-02-07 Paper/main.tex

@@
 
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{7pt}
-
-\setlength{\abovedisplayshortskip}{3pt}
-\setlength{\belowdisplayshortskip}{7pt}
-
 \newcommand{\independent}{\perp\!\!\!\!\perp}
@@
 For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
-	\vspace{-0.1cm}
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
-	\vspace{-0.1cm}
 	\begin{equation}\label{fpcr_reg_both_expansions}
@@
 
-	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
-{\color{red} Write equation with limited number of principal components.
-Truncation parameter M instead of N-1}
-
-	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
-
+	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+Using only $M$ functional principal components therefore leads to the following approximation.
+	\begin{equation}
+		y_i \approx \tilde{\alpha}^L
+		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
+		= \tilde{\alpha}^L
+		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
+	\end{equation}
+
+	As in the previous section, this equation lends itself for estimation with OLS and we can define the following objects.
 	\begin{equation}
@@
 Third, $f_2$ does have the same value at the start- and the end of the interval.	\\
-
-	\subsubsection{Functional Principal Component Regression}
-	The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
-But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
-As will be described, it seems that neither a convex behaviour of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
 
@@
 	\paragraph{Comparison to Penalty Based Smoothing Procedures}
+	In contrast to the more typical approach of using a large but often arbitrary number of basis functions and smoothing using a penalty term involving for example the second derivative of the curve, this paper focuses on smoothing by using a smaller number of basis functions.
+As a next step to the analysis of this paper, it would be interesting to compare both methods to see in which settings different approaches to smoothing perform better and if a possible combination of both approaches could be advantageous.
 	\vspace{-0.2cm}
@@
 \newpage
-\include{tables_application.tex}
-
-	\section{Definition and Proofs}
+\input{tables_application.tex}
+
+	\newpage
+	\section{Definitions and Proofs}
 	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.

### 2022-02-07 Paper/main.tex
started wording application

@@
 To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function.
-The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion.
+Visual inspection fuels the hypothesis that $NIR$ looks closer to $f_2$ than to $f_1$ but the insights from two functions are not enough to draw any conclusion.
 Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
@@
 		\subsubsection{Basis Expansion Regression}
+		\paragraph{Monomial Basis} 
+		The cross-validated MSPE selects 5 basis functions, as three out of the four setups in the simulation study.
+However, we must exercise caution since the results from $L$=6 onwards appear to display signs of numerical instability.
+
+		\paragraph{B-Spline Basis}
+		The lowest MSPE is reported for 10 basis functions, most similar to $f_2,Y_1$.
+Although no convex behaviour can be observed, as for $f_2,Y_1$ the MSPE stays relatively small from 8 basis functions onwards.
+
+		\paragraph{Fourier Basis}
 		\subsubsection{Functional Principal Component Regression}

### 2022-02-07 Paper/main.tex
Appl_Coef_Func_Ests

@@
 	\newpage
-	\subsection{Curve Estimates for Chosen Specifications}
+	\subsection{Simulation - Coefficient Function Estimates}
 
@@
 	\newpage
+
+	\subsection{Application - Coefficient Function Estimates}
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
+			\caption{Basis Expansion Regression}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm2.pdf}
+			\caption{2 Functional Principal Components}
+		\end{minipage}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm3.pdf}
+			\caption{3 Functional Principal Components}
+		\end{minipage}%
+		\begin{minipage}{.5\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm4.pdf}
+			\caption{4 Functional Principal Components}
+		\end{minipage}
+	\end{figure}
+
 	\section{Definitions and Proofs}

### 2022-02-07 Paper/main.tex
revert changes

@@
 
+	\subsubsection{Functional Principal Component Regression}
+		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
+Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
+But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+As will be described, it seems that neither a convex behaviour of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
+
 	\paragraph{Monomial Basis}

### 2022-02-07 Code/Plot_Generators/Application_Function_Estimates.R
FPC plot update

@@ -201,8 +201,8 @@ ggsave(
 )
 
 ##### generate plots for fpcr nharm = 2 #####
-fpcr_nharm2_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
-                                 filter(Curve %in% c("f1", "bspline_nharm2", "monomial_nharm2", "fourier_nharm2"))) +
+fpcr_nharm2_plot <- ggplot(data = plot_tibble %>%
+                                 filter(Curve %in% c("bspline_nharm2", "monomial_nharm2", "fourier_nharm2"))) +
   geom_line(aes(x = x, y = y, col = Curve)) +
   theme_light() +
   theme(
@@ -215,13 +215,13 @@ fpcr_nharm2_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
   guides(color = guide_legend(override.aes = list(lwd = 10)))
 
 ggsave(
-  filename = "../Graphics/Curve_Estimates/fpcr_nharm2_1_1.pdf", plot = fpcr_nharm2_plot_1_1,
+  filename = "../Graphics/Appl_Curve_Estimates/fpcr_nharm2.pdf", plot = fpcr_nharm2_plot,
   width = 20, height = 12, units = "in", dpi = 600
 )
 
 ##### generate plots for fpcr nharm = 3 #####
-fpcr_nharm3_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
-                                 filter(Curve %in% c("f1", "bspline_nharm3", "monomial_nharm3", "fourier_nharm3"))) +
+fpcr_nharm3_plot <- ggplot(data = plot_tibble %>%
+                                 filter(Curve %in% c("bspline_nharm3", "monomial_nharm3", "fourier_nharm3"))) +
   geom_line(aes(x = x, y = y, col = Curve)) +
   theme_light() +
   theme(
@@ -234,13 +234,13 @@ fpcr_nharm3_plot_1_1 <- ggplot(data = plot_tibble_1_1 %>%
   guides(color = guide_legend(override.aes = list(lwd = 10)))
 
 ggsave(
-  filename = "../Graphics/Curve_Estimates/fpcr_nharm3_1_1.pdf", plot = fpcr_nharm3_plot_1_1,
+  filename = "../Graphics/Appl_Curve_Estimates/fpcr_nharm3.pdf", plot = fpcr_nharm3_plot,
   width = 20, height = 12, units = "in", dpi = 600
[…]

### 2022-02-07 Code/Plot_Generators/Optimal_Specification_Function_Estimates.R

@@ -256,7 +256,6 @@ fReg_2_2 <- map(
 )
 
 ##### extract intercepts parameters from basis expansion models #####
-
 fReg_interc_1_1 <- map(
   .x = fReg_1_1,
   .f = function(model) model$betaestlist$const$fd$coefs[1]
@@ -278,7 +277,6 @@ fReg_interc_2_2 <- map(
 )
 
 ##### extract coefficients from basis expansion models #####
-
 fReg_coef_1_1 <- map(
   .x = fReg_1_1,
   .f = function(model) model$betaestlist$smooth_basis$fd$coefs

### 2022-02-07 Code/Plot_Generators/Principal_Components_NIR.R

@@ -17,7 +17,7 @@ NIR <- as.matrix(gasoline$NIR)
 # set up parameters
 n_basis_fun <- 20
 n_order <- 4
-n_harm <- 5
+n_harm <- 6
 stepsize <- 0.1
 
 # generate fitting functional basis (b-spline basis)

### 2022-02-08 Paper/main.tex

@@
 			\centering
-			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm2.pdf}
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm2.pdf}
 			\caption{2 Functional Principal Components}
@@
 			\centering
-			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm3.pdf}
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm3.pdf}
 			\caption{3 Functional Principal Components}
@@
 			\centering
-			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm4.pdf}
+			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm4.pdf}
 			\caption{4 Functional Principal Components}

### 2022-02-08 Paper/main.tex
Meeting changes

@@
 	\subsubsection{Basis Expansion Regression}
-	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.
+	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform regression of a scalar on a finite sequence of regressors, which is then tractable with typical multivariate regression theory.
 examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.
@@
 The monomial basis shows a better performance than B-splines for this coefficient function.
-A hypothesis for this could be that $f_1$ resembles an entire function, which can be well approximated with a power series.
+A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
 In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in figure 9 and 10, where it seems like $\hat{\beta}$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
+This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
-This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.
 	\vspace{-0.2cm}
@@
 	\paragraph{B-spline Basis}
-	Simulations with B-spline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happened here exactly?}
+	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
 	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
@@
 The Fourier basis functions perform the best for each setup for the basis expansion regression.
-Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$, while changing, does not display any eradic jumps.
-Second, both functions feature periodic behaviour.
+Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$, while changing, does not display any erratic jumps.
+Second, both functions feature periodic behavior.
 Third, $f_2$ does have the same value at the start- and the end of the interval.	\\
@@
 		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
-But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degree of freedom of these models is not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
-As will be described, it seems that neither a convex behaviour of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
+Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
+But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+As will be described, it seems that neither a convex behavior of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
 
@@
 	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC's and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
-In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behaviour of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC.
+In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behavior of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC.
 This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC's.
@@
 Since it is not possible to calculate the cross-validated MSE for three basis functions for $n_{FPC}$ = 4, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here for sure.
-$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolut values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline if MSE is similar to the decline observed for $f_2,Y_2$.
+$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline if MSE is similar to the decline observed for $f_2,Y_2$.
 Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$: This behaviour in increasing $n_{FPC}$ opposes the previously reported behaviour of the monomial basis and the increasing nature of the B-splines basis functions.
@@
 To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function.
-Visual inspection fuels the hypothesis that $NIR$ looks closer to $f_2$ than to $f_1$ but the insights from two functions are not enough to draw any conclusion.
+Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not enough to draw any conclusion.
 Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
-Third, we made assumptions about the distribution of $\xi$ that are not relateable to this real-life application where we not know this distribution, neither can we infer something about it.
+Third, we made assumptions about the distribution of $\xi$ that are not relatable to this real-life application where we not know this distribution.
 		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results.

### 2022-02-08 Paper/main.tex
Rewriting Interpretation, correcting things, starting application interpretation for basis expansion

@@
 	\subsubsection{Basis Expansion Regression}
-	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform regression of a scalar on a finite sequence of regressors, which is then tractable with typical multivariate regression theory.
-examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.
+	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR.
+Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.
 
@@
 	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability.
-This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001}.
 For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$.
@@
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in figure 9 and 10, where it seems like $\hat{\beta}$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
-This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.
+In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10}, where it seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
+This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
 For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
@@
 	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
-	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
-An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (figure 7 and 8), which is especially pronounced for the higher noise responses.
+	Function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
+An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the higher noise responses.
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios.
-For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis.
-While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (figure 9 and 10).
+For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis.
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
 	\vspace{-0.2cm}
@@
 	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
-With the low signal-to-noise ratio, the simulation chooses a smaller number of basis functions, which could be to account for the higher noise in the response variable.
+With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise into $\hat{\beta}(t)$.
 The Fourier basis functions perform the best for each setup for the basis expansion regression.
-Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$, while changing, does not display any erratic jumps.
+Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps.
 Second, both functions feature periodic behavior.
@@
 		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function.
-But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to approximate the function.
+But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
 As will be described, it seems that neither a convex behavior of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
+This might be since the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description, The results indicate that the FPCR in this simulation seems to not take into account the differing signal-to-noise ratios of the responses since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.
 
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC's and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
-In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behavior of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC.
-This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC's.
+	For $f_1$, the cross-validated MSPE is decreasing in the increasing number of FPC's and chosen basis functions for both the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the choosen basis functions.
 The monomial basis shows the weakest performance for all three basis functions in each setting.
@@
 	\paragraph{B-spline Basis}
-	For $f_1,Y_1$, the CV suggests a better model with a higher number of FPC's.
-While the number of basis functions stays at five for two and three used FPC, it increases to six basis functions for $nharm$ = 4.
-In $f_1,Y_1$, the cross-validated MSE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4.
-$f_2,Y_1$ shows a decrease of MSE in increasing $n_{FPC}$.
-The same holds true in the setup with $f_2$ and the high signal-to-noise ratio with the decrease being similar in absolute terms.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,8 for $n_{FPC} \in \{2, 3, 4 \}$)
+	For $f_1,Y_1$, the MSPE suggests a better model with a higher number of FPC's.
+While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$.
+In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,23 for $n_{FPC} \in \{2, 3, 4 \}$)
 	\vspace{-0.2cm}
@@
 	\paragraph{Fourier Basis}
-	We observe similar behaviour as for the FPCR using B-splines.
-In $f_1,Y_1$, the MSE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
-Since it is not possible to calculate the cross-validated MSE for three basis functions for $n_{FPC}$ = 4, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here for sure.
-$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline if MSE is similar to the decline observed for $f_2,Y_2$.
-Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$: This behaviour in increasing $n_{FPC}$ opposes the previously reported behaviour of the monomial basis and the increasing nature of the B-splines basis functions.
+	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
+$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
+Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
 	\vspace{-0.2cm}
@@
 	\subsubsection{Interpretation and Relevance for Application}
-	A possible explanation applicable for all setups using Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For the function $f_1$ it might be that little bias is introduced when choosing a small number of basis functions.
-For $f_2$, a higher number of basis functions is needed, resulting from the inherent peculiarities of $f_2$.
+	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ it might be that little bias is introduced when choosing a small number of basis functions.
+For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$.
 This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
 The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.
-This could not be observed for the FPCR where no clear relationship between the basis functions and the number of FPC was observed.
-An hypothesis for this would be that the results for the FPCR are mostly driven by the selected FPC´s.
-To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L$ for $n_{FPC} \in \{2, 3, 4 \}$, which seem to support this claim (LINK TO APPENDIX).
+This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered.
+An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture here.
+Following this, it appears that the results for the FPCR are mostly driven by the selected FPC´s and less by the choice of basis.
+To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$, which seem to support this claim (LINK TO APPENDIX).
 
@@
 To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function.
-Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not enough to draw any conclusion.
+Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
 Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
-Third, we made assumptions about the distribution of $\xi$ that are not relatable to this real-life application where we not know this distribution.
+Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not relatable to this real-life application where we not know this distribution.
 		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results.
@@
 		\paragraph{Monomial Basis} 
-		The cross-validated MSPE selects 5 basis functions, as three out of the four setups in the simulation study.
-However, we must exercise caution since the results from $L$=6 onwards appear to display signs of numerical instability.
-
-		\paragraph{B-Spline Basis}
-		The lowest MSPE is reported for 10 basis functions, most similar to $f_2,Y_1$.
-Although no convex behaviour can be observed, as for $f_2,Y_1$ the MSPE stays relatively small from 8 basis functions onwards.
-
-		\paragraph{Fourier Basis}
+		The cross-validated MSPE selects 5 basis functions for the monomial basis, as three out of the four setups in the simulation study.
+For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the fourier basis.
+Comparing the estimates in \hyperref[basis_expansion_estimate_appl]{ADD}, apart from the boundaries, B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributed by the lower basis functions.
+However, we must exercise caution since from $L$=6 onwards, we were not able to calculate stable results for the monomial basis.
+Especially at the lower boundary, the monomial basis shows a strong exaggerated bahavior.
+The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while it is clearly knocked for the monomial basis (0.24181) by a factor of 5.
+In contrast to our hypothesis from the simulation study in which we partly attributed the weaker performance of the B-splines to its attributes at the boundaries, it manages to outperform the fourier basis.
+It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by a similar high signal-to-noise ratio of the octane numbers, but also other factors should be considered.
+
 		\subsubsection{Functional Principal Component Regression}
-		As for the simulation study, the
+		As for the simulation study, the interpretation of the results with respect to the choosen basis is difficult.
+Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behaviour of the estimate $\hat{\beta}(t)$ can be observed.
+Opposing to the simulation study, the number of basis functions is steadily increasing for the monomial basis.
+The bevahiour for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
+In contrast to the simulation study, no evidence of overfitting was found for any of the three bases.
 
@@
 			\caption{Basis Expansion Regression - $f_1, Y_1$}
+			\label{basis_expansion_1_1}
 		\end{minipage}%
@@
 			\caption{Basis Expansion Regression - $f_1, Y_2$}
+			\label{basis_expansion_1_2}
 		\end{minipage}
@@
 			\caption{Basis Expansion Regression - $f_2, Y_1$}
+			\label{basis_expansion_2_1}
 		\end{minipage}%
@@
 			\caption{Basis Expansion Regression - $f_2, Y_2$}
+			\label{basis_expansion_2_2}
 		\end{minipage}
@@
 			\caption{FPC Regression, 2 harmonics - $f_1, Y_1$}
+			\label{fpcr_nharm2_1_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 2 harmonics - $f_1, Y_2$}
+			\label{fpcr_nharm2_1_2}
+
 		\end{minipage}
@@
 			\caption{FPC Regression, 2 harmonics - $f_2, Y_1$}
+			\label{fpcr_nharm2_2_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 2 harmonics - $f_2, Y_2$}
+			\label{fpcr_nharm2_2_2}
 		\end{minipage}
@@
 			\caption{FPC Regression, 3 harmonics - $f_1, Y_1$}
+			\label{fpcr_nharm3_1_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 3 harmonics - $f_1, Y_2$}
+			\label{fpcr_nharm3_1_2}
 		\end{minipage}
@@
 			\caption{FPC Regression, 3 harmonics - $f_2, Y_1$}
+			\label{fpcr_nharm3_2_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 3 harmonics - $f_2, Y_2$}
+			\label{fpcr_nharm3_2_2}
 		\end{minipage}
@@
 			\caption{FPC Regression, 4 harmonics - $f_1, Y_1$}
+			\label{fpcr_nharm4_1_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 4 harmonics - $f_1, Y_2$}
+			\label{fpcr_nharm4_1_2}
 		\end{minipage}
@@
 			\caption{FPC Regression, 4 harmonics - $f_2, Y_1$}
+			\label{fpcr_nharm4_2_1}
 		\end{minipage}%
@@
 			\caption{FPC Regression, 4 harmonics - $f_2, Y_2$}
+			\label{fpcr_nharm4_2_2}
 		\end{minipage}
@@
 			\caption{Basis Expansion Regression}
+			\label{basis_expansion_estimate_appl}
 		\end{minipage}%
@@
 			\caption{2 Functional Principal Components}
+			\label{FPCR2_estimate_appl}			
 		\end{minipage}
@@
 			\caption{3 Functional Principal Components}
+			\label{FPCR3_estimate_appl}	
 		\end{minipage}%
@@
 			\caption{4 Functional Principal Components}
+			\label{FPCR4_estimate_appl}	
 		\end{minipage}

### 2022-02-08 Code/Stitch_Additional.R
Summaries for Higher Order Runs

@@ -1,0 +1,43 @@
+# import libraries
+library(stringr)
+library(tidyverse)
+
+# import stitching functions
+source("Simulation_Stitch_Functions.R")
+
+# get subfolders of Results/partial
+sbfldrs <- list.files(path = "Results/Paper/High_Num_bsplines_fpcr_partial/")
+
+# create paths to subfolders
+sbfldr_paths <- map(
+  .x = sbfldrs,
+  .f = function(fldr) paste0("Results/Paper/High_Num_bsplines_fpcr_partial/", fldr)
+)
+
+# create names for summary objects
+output_names <- map(
+  .x = sbfldrs,
+  .f = function(fldr) str_split(string = fldr, pattern = "_partial")[[1]][1]
+)
+
+# summarize partial results
+summary_results <- map(
+  .x = 1:length(sbfldr_paths),
+  .f = function(p) {
+    try(simulation_stitch(path = sbfldr_paths[[p]]))
+  }
+)
+
+# save in summaries folder
+for (i in 1:length(sbfldrs)) {
+  if(length(summary_results[[i]]) != 1){
+    saveRDS(
+      object = summary_results[[i]],
+      file = paste0("Results/Paper/Summaries_additional/", output_names[[i]], ".RDS")
+    )
+    write_csv(
+      x = summary_results[[i]], 
+      file = paste0("Results/Paper/Summaries_additional/", output_names[[i]], ".csv")
+    )
+  }
+}

### 2022-02-08 Code/Plot_Generators/large_basis_fpcr_estimates.R
Higher number basis functions fpcr graphics

@@ -1,0 +1,727 @@
+##### Load packages #####
+library(tidyverse)
+library(fda)
+library(refund)
+library(rlist)
+
+###### load auxiliary files #####
+source("data_generator.R")
+
+###### original functions #####
+f_1 <- function(t) {
+  return(401*(2 * sin(0.5 * pi * t) + 4 * sin(1.5 * pi * t) + 5 * sin(2.5 * pi * t)))
+}
+
+f_2 <- function(t) {
+  return(401*(1.5 * exp(-0.5 * (t - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (t - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (t - 0.6)^2 / 0.02^2) - exp(-0.5 * (t - 0.8)^2 / 0.03^2)))
+}
+
+# grid for plotting
+plot_grid <- seq(0, 1, length.out = 1000)
+
+###### generate response variables #####
+grid <- seq(0, 1, length.out = 401)
+f1 <- 2 * sin(0.5 * pi * grid) + 4 * sin(1.5 * pi * grid) + 5 * sin(2.5 * pi * grid)
+f2 <- 1.5 * exp(-0.5 * (grid - 0.3)^2 / 0.02^2) - 4 * exp(-0.5 * (grid - 0.45)^2 / 0.015^2) + 8 * exp(-0.5 * (grid - 0.6)^2 / 0.02^2) - exp(-0.5 * (grid - 0.8)^2 / 0.03^2)
+
+data(gasoline)
+NIR <- gasoline$NIR
+
+sigma_eps_squared1_1 <- as.numeric((var(NIR %*% f1) / 0.9) - var(NIR %*% f1))
+sigma_eps_squared1_2 <- as.numeric((var(NIR %*% f1) / 0.6) - var(NIR %*% f1))
+sigma_eps_squared2_1 <- as.numeric((var(NIR %*% f2) / 0.9) - var(NIR %*% f2))
+sigma_eps_squared2_2 <- as.numeric((var(NIR %*% f2) / 0.6) - var(NIR %*% f2))
+
+generated_curves <- NIR_curve_generator(n = 200, n_harmonics = 30)
+my_data <- as.matrix(generated_curves[, -1])
+
+Y1_1 <- as.numeric(my_data %*% f1 + rnorm(200, 0, 1) * sigma_eps_squared1_1)
[…]

### 2022-02-08 Paper/main.tex
Correction
Some grammarly improvements and shortenings in theory

@@
 	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
-Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}
+Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the Section on Near-Infrared-Spectroscopy in the Appendix.}
 
@@
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional.
-	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can addressed using theory from multivariate regression.
-First, a so-called basis expansion of the coefficient function and second, functional principal component regression.
-Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis and this paper focuses on exploring the selection of these parameters using cross validation.\\
-
-	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures and address the theoretical importance of the truncation parameter.
-Section \ref{Simulation} contains a description of structure and results of our Monte-Carlo Simulation which is aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods.
+	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression.
+Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\
+
+	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures, and address the theoretical importance of the truncation parameter.
+Section \ref{Simulation} contains a description of our Monte-Carlo Simulation, which aims to provide information on how to choose an appropriate functional basis and truncation parameter for the aforementioned methods.
 The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
-In Section \ref{Outlook} we give an outlook on possible extensions for this paper and describe limitations of our approach.
+In Section \ref{Outlook}, we give an outlook on possible extensions for this paper and describe the limitations of our approach.
 
@@
 	To allow for scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
-One integral concept that has to be defined is a random function as a special case of a random variable.
+One integral concept that must be defined is random functions as a special case of random variables.
 Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.
-	The typical case for a random variable realizing i $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
+	The typical case for a random variable realizing in $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
 As a first intuition for the concept of a random function, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
@@
 	\subsection{Inner Products and Hilbert Spaces}
-	In the following we restrict our analysis to vector spaces over $\mathbb{R}$ but more a general formalization including other fields is possible.
+	The first concept we will introduce is the concept of Hilbert spaces.
+To do so, we start from inner product spaces but restrict our analysis to vector spaces over $\mathbb{R}$ for the sake of clarity.
 Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.
@@
 
-	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
-	The inner product naturally defines a norm and an associated distance on the vector space.
+	A vector space with an associated inner product is called an inner product space and the inner product defines a norm and an associated distance on the vector space.
 	\begin{equation}
@@
 	If the inner product space is complete with respect to the induced distance, it is called a Hilbert space, denoted $\mathbb{H}$ in the following.
-To extend the known concept of a basis in a finite dimensional space to the potentially infinite Hilbert spaces, it is necessary to define the closed span of a sequence of elements of $\mathbb{H}$.
+To extend the known concept of a basis in a finite dimensional space to potentially infinite Hilbert spaces, it is necessary to define the closed span of a sequence of elements of $\mathbb{H}$.
 Recall that the span of a set of vectors $S \subseteq \mathbb{R}^P$ is given by
@@
 
-	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm.
-$S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$.
-\\
-	It is called an orthonormal basis if, in addition, the following properties hold.
+	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm and $S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$.	It is called an orthonormal basis if, in addition, the following properties hold.
 
@@
 
-	As can be seen, differing from the case of Banach spaces, these representations can be limits of series as previously hinted at by using the closed span of the basis.
-As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space is to use a truncated series.
+	Differing from the case of Banach spaces, these representations can be limits of series.
+As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements in a Hilbert space is to use a truncated series.
 	\begin{equation}
@@
 	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
-	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$.
-To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.
-Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
+	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$.
+Denoted by $\mathbb{L}^2[0,1]$, this space is consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
 	\begin{equation}
@@
 
-	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined.
-	\begin{equation}
+	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined.
+The inner product of $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
+	\begin{equation}\label{inner_prod}
 		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis, but analogous constructions can be made for every closed interval of $\mathbb{R}$.
-	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
-	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
-The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process.
+	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
+	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
+%The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve of the random function.
 The collection of such sample curves constitutes a functional data set.
@@
 			\begin{split}
-				\mathbb{E}\bigg[\sum_{m=1}^{N} \sum_{m=1}^{N} \xi^m \xi^m \nu^m(t) \nu^n(t)\bigg] = & \sum_{m=1}^{N} \sum_{m=1}^{N} \mathbb{E}[\xi^m \xi_{k}] \nu^m(t) \nu^n(t)\\
+				\mathbb{E}\bigg[\sum_{m=1}^{N} \sum_{n=1}^{N} \xi^m \xi^n \nu^m(t) \nu^n(t)\bigg] = & \sum_{m=1}^{N} \sum_{n=1}^{N} \mathbb{E}[\xi^m \xi^n] \nu^m(t) \nu^n(t)\\
 				= & \sum_{m=1}^{N} \sum_{n=1}^{N} \delta^{m,n} \lambda^m \nu^m(t) \nu^n(t) = 		\sum_{m=1}^{N} \lambda^m \nu^m(t)^{2}

### 2022-02-08 Paper/main.tex
Some changes in functional data set

@@
 	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
-%The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve of the random function.
-The collection of such sample curves constitutes a functional data set.
 
 	\subsection{Functional Data Sets}
-	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$: 
+	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function.
+The presence of functional observations in a data set is what defines functional data sets.
+However, in reality realizations of random functions are not typically observed in their functional form.
+Instead, each curve is observed at a discrete and typically large set of measurements points.
+Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
 	\begin{equation}
@@
 
-	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points.
-The measurement points can be different for each sample.
-However, this is not a primary interest of this paper, and, therefore, we consider the case where curves are observed at a shared set of measuring points.
-In principle, these measurements can be seen as a discretized approximation of a realization of a random function.
-It causes necessities to represent the functional data with respect to some expansion technique.
-One technique to make the functional data smooth, truncated basis expansion, is introduced in the following sections.\\
-	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis, such as, for example, many inferential procedures.
-One example could be a set of NIR absorption spectra of gasoline samples in which curves are observed at a shared set of wavelengths and each sample stemming from the same production can be seen as a realization of the same random process.
+	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$.
+These measurement points can be different for each sample curve.
+However, in this paper, we only consider the case where curves share their measuring points.
+	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure.
+Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\
+
+	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis.
+One example of i.i.d.
+curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d.
+random process itself.
 

### 2022-02-08 Paper/main.tex
Finishing up first take on results

--- 2022-02-08 Paper/main.tex
@@
 	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability.
-For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$.
-The monomial basis shows a better performance than B-splines for this coefficient function.
+For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10}, where it seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
+In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence: It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
 This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
-For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios.
+For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio.
 	\vspace{-0.2cm}
@@
 	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
-	Function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
+	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
 An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the higher noise responses.
-For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios.
+For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
 For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis.
@@
 		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to approximate the function.
+Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
 But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
-As will be described, it seems that neither a convex behavior of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.
-This might be since the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description, The results indicate that the FPCR in this simulation seems to not take into account the differing signal-to-noise ratios of the responses since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.
+As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's.
+This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description.
+In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.
 
@@
 	For $f_1$, the cross-validated MSPE is decreasing in the increasing number of FPC's and chosen basis functions for both the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
-In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the choosen basis functions.
-The monomial basis shows the weakest performance for all three basis functions in each setting.
+In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the chosen basis functions.
+The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
 	\vspace{-0.2cm}
@@
 	\paragraph{B-spline Basis}
-	For $f_1,Y_1$, the MSPE suggests a better model with a higher number of FPC's.
+	For $f_1,Y_1$, the MSPE suggests better models with a higher number of FPC's.
 While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$.
-In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,23 for $n_{FPC} \in \{2, 3, 4 \}$)
+In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting using $n_{FPC}$ = 4.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4 ,6 ,23 for $n_{FPC} \in \{2, 3, 4 \}$)
 	\vspace{-0.2cm}
@@
 	\paragraph{Fourier Basis}
-	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's.
-$f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
-Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
+	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC}$ = 4.
+$f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
+Both configurations of $f_2$ are using 5, 15, 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
 	\vspace{-0.2cm}
@@
 	\subsubsection{Interpretation and Relevance for Application}
-	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ it might be that little bias is introduced when choosing a small number of basis functions.
-For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$.
+	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems introduced when choosing a small number of basis functions.
+For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with lower $L$.
 This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
 The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.
+
 	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered.
-An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture here.
-Following this, it appears that the results for the FPCR are mostly driven by the selected FPC´s and less by the choice of basis.
-To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$, which seem to support this claim (LINK TO APPENDIX).
+An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture in our setting.
+To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX).
+As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$.
+The additional simulations revealed evidence that there exists a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower than for 70 basis functions which might be a first sign of a too high $K$ and subsequent undersmoothing.
+Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better on a lower truncated smoothed curve (here $L$ = 50).
+Importantly, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ration of the responses is not affecting the construction of the FPC's which might indicate benefiting attributes of the lower basis functions used in the main simulation.
 
 	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)
-
-	%Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001})
-
-	%Adress numerical instability?
-
-	%maybee both in paragraph under results instead of here?
-
-	%\subsection{Literature}
-	%\begin{itemize}
-	%	\item \cite{shonkwiler_explorations_2009}
-	%	\item R-packages: fda, refund, mgcv
-	%\end{itemize}
 
@@
 		\subsubsection{Basis Expansion Regression}
-		\paragraph{Monomial Basis} 
-		The cross-validated MSPE selects 5 basis functions for the monomial basis, as three out of the four setups in the simulation study.
+		The cross-validated MSPE selects 5 basis functions for the monomial basis.
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the fourier basis.
-Comparing the estimates in \hyperref[basis_expansion_estimate_appl]{ADD}, apart from the boundaries, B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributed by the lower basis functions.
+Comparing the estimates in \hyperref[basis_expansion_estimate_appl]{ADD}, apart from the boundaries, B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributed by the lower amount of used basis functions.
+Especially at the lower boundary, the monomial basis shows a strong exaggerated bahavior.
 However, we must exercise caution since from $L$=6 onwards, we were not able to calculate stable results for the monomial basis.
-Especially at the lower boundary, the monomial basis shows a strong exaggerated bahavior.
-The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while it is clearly knocked for the monomial basis (0.24181) by a factor of 5.
-In contrast to our hypothesis from the simulation study in which we partly attributed the weaker performance of the B-splines to its attributes at the boundaries, it manages to outperform the fourier basis.
-It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by a similar high signal-to-noise ratio of the octane numbers, but also other factors should be considered.
+The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while it is clearly knocked of for the monomial basis (0.24181).
+In contrast to the simulation study, the B-splines basis manages to outperform the fourier basis.
+Driving factors for this better performance could be that first, we do not assume a periodic true coefficient function with the same start- and end value and second, the Fourier basis tries to force the same start- and endvalue on $NIR$ (confirmed in unreported visual inspection).
+It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the mentioned similarities between $NIR$ and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
 
 		\subsubsection{Functional Principal Component Regression}
-		As for the simulation study, the interpretation of the results with respect to the choosen basis is difficult.
-Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behaviour of the estimate $\hat{\beta}(t)$ can be observed.
+		The best performance for all numbers of FPC's was achieved with the Fourier Basis, as for the FPCR in the simulation study.
+In contrast to the simulation study, no evidence of overfitting was found for the best basis choices in any of the three bases.
+The MSPE appears to be strictly decreasing in the number of FPC´s for its best basis choice.
+As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behaviour of the estimate $\hat{\beta}(t)$ can be observed.
 Opposing to the simulation study, the number of basis functions is steadily increasing for the monomial basis.
-The bevahiour for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
-In contrast to the simulation study, no evidence of overfitting was found for any of the three bases.
+The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
 

### 2022-02-08 Paper/main.tex

@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis, but analogous constructions can be made for every closed interval of $\mathbb{R}$.
-	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
-	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
-The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process.
-The collection of such sample curves constitutes a functional data set.
+	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
+	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
 
 	\subsection{Functional Data Sets}
-	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$: 
+	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function.
+The presence of functional observations in a data set is what defines functional data sets.
+However, in reality realizations of random functions are not typically observed in their functional form.
+Instead, each curve is observed at a discrete and typically large set of measurements points.
+Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
 	\begin{equation}

### 2022-02-08 Paper/main.tex
Monomial and Fourier Basis parts

@@
 	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion.
-Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express or approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.
+Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express or approximate a realization $x(t)$ of $X(\omega)$.
 Then the following equation shows how a basis can be used to express a function as a weighted sum of its elements.
@@
 	\paragraph{Monomial Basis}
-	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials.
-Let $f(t)$ be an entire function, e.g.
-a polynomial, the exponential function or a trigonometric function, then we can express it in the following form.
+	A very simple idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis.
+For entire functions $f(t)$, e.g.
+polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, converging sum of weighted monomials.
 	\begin{equation}\label{Taylor_expansion}
@@
 
-	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can often lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
-From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$.
+	However, the monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$.
+But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
+From this idea, it is natural to use the monomials as a potential basis for approximation.
+\\
 	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter.
@@
 
-	Due to the chosen implementation for our simulation, we will limit our paper to the case of $\alpha = 0$.
-However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
-	As the monomials are not pariwise orthogonal, this basis is also prone to Collinearity problems, which can result in numerically unstable estimates.
+	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$.
+However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis.
+	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates.
 This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities.
-It can also lead to undesirable behavior away from the point of evaluation of the monomials (cf.
+These problems will be addressed in more detail in later parts of this paper.
+The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf.
 \cite{ramsay_functional_2005}).
@@
 	In its classical form, the series is represented in the so called amplitude-phase form.
-This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift.
-Therefore, rewriting the series in the sine-cosine form through a simple trigonometry formula as shown above is necessary.
-Due to this origin of the Fourier basis it is reasonable to restrict the number of Fourier basis functions to odd numbered values to stay true to the expansion in amplitude-phase form.
+This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter.
+Therefore, rewriting the series in the sine-cosine form as shown above is necessary.
+
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
@@
 
-	Its elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
+	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
+The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
 Additionally, the Fourier basis is especially suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

### 2022-02-08 Paper/main.tex
Small cut from bspline basis

@@
 For entire functions $f(t)$, e.g.
-polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, converging sum of weighted monomials.
+polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, but converging sum of weighted monomials.
 	\begin{equation}\label{Taylor_expansion}
@@
 	\paragraph{Fourier Basis}
-	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series.
-The Fourier series can be used to decompose a periodic function into a weighted sum of trigonometric functions.
-Equation \ref{Fourier_Series} shows an example for a periodic function with a period of 1.
+	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions.
+Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
 	\begin{equation}\label{Fourier_Series}
@@
 
-	In its classical form, the series is represented in the so called amplitude-phase form.
+	Typically, the series is represented in the so called amplitude-phase form.
 This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter.
 Therefore, rewriting the series in the sine-cosine form as shown above is necessary.
-
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
@@
 	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
-On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree.
-If there are no multiplicities in the set of these knots, the polynomials on neighboring subintervals are matching derivatives up to order $m-2$ at the boundary knot $\tau_l$.
-A typical case of this that is often used in practive is an equidistant grid of knots.
+On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree.
+If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_l$.
+A typical case that is often used in practice is an equidistant grid of knots.
 In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure allowing for a reduced number of matching derivatives at the corresponding knots.
@@
 
-	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
 To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions.
-	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.
-\\
-
-	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
+
+	As the B-spline basis does not have infinitely many elements as the full monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
 For the sake of keeping the notation reasonably concise, we will still keep this notation.

### 2022-02-08 Paper/main.tex
Basis truncation text

@@
 	\subsection{Approximation and Smoothing via Basis Truncation}
-	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis.
-For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$.
-In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis.
-{\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small.
-In that sense, this discussion is subject to the Bias-Variance tradeoff.
-It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves.
-The basis expansion with truncation is given by Equation \ref{basis_exp}.
+	Realized curves from a data set can be expressed in terms of a chosen functional basis.
+For this expansion, it is  possible to use a complete basis of $\mathbb{L}^2[0,1]$.
+In many cases this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting.
+To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves.
+On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information.
+This is a typical occurence of the Bias-Variance tradeoff.\\
+
+	A different approach that is atypical in practice, is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects.
+Here, the parameter of choice is not a weighting term for the penalty, but the number of basis functions.
+Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper.
+A truncated basis expansion as described above is given in Equation \ref{basis_exp}.
 	\begin{equation}\label{basis_exp}
@@
 	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
-The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation.
-Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.
+$L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
+Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
 
@@
 The proofs are provided at \ref{Proof1} and \ref{Proof2}.
-
-	%\begin{enumerate}
-	%\item The eigenspaces corresponding to distinct eigenvalues are mutually orthogonal.
-	%\item The eigenspaces corresponding to non-zero eigenvalues are finite-dimentsional.
-	%\item The eigenvalues can be ordered in nonincreasing order as follows $\lambda_{1} \geq \lambda_{2} \geq \dots \geq 0$.
-	%\end{enumerate}
-	%Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g.
-$Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$).
-Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
-{\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}
-
 	\begin{equation}\label{KarhunenLoeve}
@@
 The random variables $\xi^{m}(\omega)$ satisfy following properties.
-%of the following equation.
-
-	%\begin{equation}
-	%	{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
-	%\end{equation}
-
-	%The $\xi_j(\omega)$ are then given as 
-	%\begin{equation}
-	%	\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - %\mu(s)\right) \nu^m(s) \mathrm{d}s
-	%\end{equation} 
-	%and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
 	\begin{multicols}{2}

### 2022-02-08 Paper/main.tex
Overlapping Plots NIR data appendix

@@
 \usepackage{hyperref}
+\usepackage{overpic}
 \usepackage[font=small,skip=2pt]{caption}
@@
 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
+	\vspace{0.5cm}
 
@@
 		\begin{center}
-			\includegraphics[width = \textwidth]{../Graphics/FinderSD.jpg}
-			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
+			\begin{overpic}[width = \textwidth]{../Graphics/NIR_data.pdf}
+				\put(7, 30){
+					\frame{\includegraphics[width = 0.4\textwidth]{../Graphics/FinderSD.jpg}}
+				}
+			\end{overpic}
+			\caption{NIR Data Set and Finder SD (a Near-Infrared-Spectroscope built by HiperScan GmbH) \\
 			(Source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}

### 2022-02-08 Code/Plot_Generators/NIR_data.R

@@ -1,0 +1,41 @@
+# Clear Workspace
+rm(list = ls())
+
+# load libraries
+library(fda)
+library(refund)
+library(tidyverse)
+
+data(gasoline)
+NIR <- gasoline$NIR
+
+my_basis <- create.bspline.basis(rangeval = c(0,1), nbasis = 50, norder = 4)
+
+NIR_func <- smooth.basis(argvals = seq(0, 1, length.out = 401), 
+                         y = t(NIR), fdParobj = my_basis)
+
+plot_grid <- seq(0, 1, length.out = 1000)
+NIR_plot_tibble <- cbind(
+  tibble(x = plot_grid),
+  as_tibble(eval.fd(evalarg = plot_grid, fdobj = NIR_func$fd)))
+
+colnames(NIR_plot_tibble) <- c('x', paste0('Observation_', 1:60))
+
+NIR_plot_tibble <- NIR_plot_tibble %>% 
+  pivot_longer(cols = !x, names_to = 'Observation', values_to = 'y')
+
+NIR_plot <- ggplot(data = NIR_plot_tibble) +
+  geom_line(aes(x = x, y = y, col = Observation), alpha = 0.5) +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    plot.title = element_text(size = 30),
+    axis.title = element_text(size = 20),
+    axis.text = element_text(size = 20),
+  )
+
+# save plot in appropriate folder
+ggsave(
+  filename = "../Graphics/NIR_data.pdf", plot = NIR_plot,
+  width = 20, height = 12, units = "in", dpi = 600
+)

### 2022-02-08 Code/Plot_Generators/Tradeoff_plot.R

@@ -82,7 +82,7 @@ NIR_data = rbind(NIR,NIR_plot5,NIR_plot10,NIR_plot30,NIR_plot50,NIR_plot100)
 label <- paste0("K=",c(0,5,10,30,50,100))
 label[1] <- "Real Line"
 
-basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength,color=K)) +
+basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength, color=K)) +
   geom_line()+
   xlab('Wavelength in nm') +
   ylab('Absorption') +
@@ -97,7 +97,8 @@ basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength,color=K)) +
     axis.text = element_text(size = 20),
     legend.title = element_text(size = 24),
     legend.text = element_text(size = 20)
-  )
+  ) +
+  guides(color = guide_legend(override.aes = list(lwd = 10)))
 
 # save plot in appropriate folder
 ggsave(

### 2022-02-08 Code/Plot_Generators/NIR_data.R
Increased number of basis functions for plot

@@ -9,7 +9,7 @@ library(tidyverse)
 data(gasoline)
 NIR <- gasoline$NIR
 
-my_basis <- create.bspline.basis(rangeval = c(0,1), nbasis = 50, norder = 4)
+my_basis <- create.bspline.basis(rangeval = c(0,1), nbasis = 100, norder = 4)
 
 NIR_func <- smooth.basis(argvals = seq(0, 1, length.out = 401), 
                          y = t(NIR), fdParobj = my_basis)

### 2022-02-08 Paper/main.tex
Karhunen Loeve Wording

@@
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
-	Given a realization of a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process.
-To do so, it is necessary to define the mean and covariance functions of $X(\omega)$.
+	Given a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent its realizations in terms of the stochastic process.
+To do so, we define the mean and covariance functions of $X(\omega)$.
 	\begin{equation}\label{MeanFunction}
@@
 
-	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$.
-Let $K$ be a Hilberst-Schmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
+	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt operator\footnote{Definitions of Hilbert-Schmidt Kernels and Operators are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
 	\begin{equation}\label{HSKernal}
@@
 	\end{equation}
-	More exact definitions are provided at \ref{def_HS}.
-Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf.
+
+	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
 \cite{alexanderian_KLexpansion_2015}).
-Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index.
-Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g.
-$Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$).
-Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.
-The proofs are provided at \ref{Proof1} and \ref{Proof2}.
+	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.}
 	\begin{equation}\label{KarhunenLoeve}
-		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
-	\end{equation}
-
-	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of ({\ref{HSKernal}}).
-The random variables $\xi^{m}(\omega)$ satisfy following properties.
+		X(\omega)(t) = \mu(t) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
+	\end{equation}
+
+	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of Equation \ref{HSKernal} and the random variables $\xi^{m}(\omega)$ satisfy the following properties.
 	\begin{multicols}{2}
@@
 
+	As in the well known setting of principal component analysis, the eigenvalues correspond to the variance in the random function that is explained by the corresponding eigenfunction. 
+	Therefore, ordering the the eigenfunctions according to their their corresponding eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
+Due to this property a functional observation can often be approximated well by using a limited number of the eigenfunctions of its generating random process.\\
+
 	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting.
@@
 
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1, \dots, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation.
-As in the case of ordinary principal components, the number of eigenfunctions corresponding to non-zero eigenvalues is limited (cf.
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1,\: \dots\:, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m = 1, 2, \:\dots\}$ as the solutions of the following equation.
+	\begin{equation}
+		\int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t)
+	\end{equation}
+
+	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical eigenfunctions $\nu^m(s)$.
+As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero eigenvalues is limited (cf.
 chapter 8.2.3 \cite{ramsay_functional_2005}).
 As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality.
-However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
-	\begin{equation}
-		\int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t)
-	\end{equation}
-
-	This naturally leads to the following representation.
+However, the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
+	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
 	\begin{equation}

### 2022-02-08 Paper/main.tex
KL def

@@
 
-	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt operator\footnote{Definitions of Hilbert-Schmidt Kernels and Operators are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
+	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
 	\begin{equation}\label{HSKernal}
@@
 
-	\subsection{Definition (Hilbert-Schmidt Operator)}\label{def_HS}
+	\subsection{Definition (Hilbert-Schmidt Integral Operator)}\label{def_HS}
 	Given a bounded domain $\mathcal{A} \subset \mathbb{R}^n$, we call a function $c : \mathcal{A} \times \mathcal{A} \rightarrow \mathbb{R}$ a Hilbert-Schmidt kernel if

### 2022-02-08 Paper/main.tex
Auto stash before merge of "main" and "origin/main"

@@
 
-	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
+	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
 \cite{alexanderian_KLexpansion_2015}).
@@
 
-	As in the well known setting of principal component analysis, the eigenvalues correspond to the variance in the random function that is explained by the corresponding eigenfunction. 
-	Therefore, ordering the the eigenfunctions according to their their corresponding eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
-Due to this property a functional observation can often be approximated well by using a limited number of the eigenfunctions of its generating random process.\\
+	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
+	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
+Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.\\
 
@@
 
-	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical eigenfunctions $\nu^m(s)$.
-As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero eigenvalues is limited (cf.
+	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(s)$.
+As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf.
 chapter 8.2.3 \cite{ramsay_functional_2005}).
 As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality.
-However, the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
+However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
 	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
@@
 
-	In reality, these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
+	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
 For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
@@
 
-	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the curves for both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
+	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
 This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
@@
 
-	This method of deriving or approximating the eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
+	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
 The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.
@@
 Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction.
-To motivate the jump from multivariate regression to scalar-on-function regression, assume first a data generating process as follows.
+To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
 	\begin{equation}
@@
 
-	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent of a functional regressor. 
+	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
 	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
@@
 
-	Here, $\beta(t)$ is an unknown coefficient function.
-Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
+	Similar to the finite-dimensional setting, an interesting question is how to estimate the unknown coefficient function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
 However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible.
-Therefore, other options have to be considered.
+Therefore, other options have to be considered, two of which will be explained in the following.
 
@@
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
-Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
+Therefore, let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
 	\begin{equation}
@@
 
-	This enables us to write equation \ref{DGP} with $\beta(t)$ represented in this way to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
+	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
 	\begin{equation}
@@
 	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations.
-Defining the following notation
+Using the following notation
 	\begin{equation}
@@
 
-	This leads to a considerable simplification of Equation \ref{basis_exp_transf}.
+	this leads to a considerable simplification of Equation \ref{basis_exp_transf}.
 	\begin{equation}\label{simplified_model_basis_equation}
@@
 
-	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.
+	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)(t)$.
 	\begin{equation}
@@
 To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
-Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
+Additionally, the following approximation truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
 
@@
 	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
-Using only $M$ functional principal components therefore leads to the following approximation.
+Using only $M$ functional principal components leads to the following approximation.
 	\begin{equation}
@@
 For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
-While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
-This might apply to this simulation too since certain eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.
+While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.
 
@@
 		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification.
-The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
+The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
 		\begin{equation}
@@
 		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
+Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
 But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
@@
 	\subsection{Lemma} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}.
-The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:
+	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}.
+The coefficients $\xi^{m}$ corresponding to Eigenfunctions $\nu^m$ satisfy the following properties:
 
@@
 
-		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.
+		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the Eigenfunctions.
 
@@
 
-		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
+		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of Eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative Eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator.
 With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
@@
 		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}.
-It turns out the product of the eigenfunction and the corresponding eigenvalue.
+It turns out the product of the Eigenfunction and the corresponding Eigenvalue.
 For the last term, we derive from Equation \ref{Lemma2} that

### 2022-02-09 Paper/main.tex
Small language things

@@
 
-	\subsection{Representing a Function in terms of a Basis} 
+	\subsection{Representing a Function in terms of a Basis}\label{bases}
 	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion.
@@
 $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
-Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
+Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
 
@@
 
-	\subsection{Scalar-on-Function Regression}
+	\subsection{Scalar-on-Function Regression}\label{Scalar_on_function_regression}
 	In the simple scalar setting, one of the most important tools in econometrics is linear regression.
@@
 	In the simulation study, we deviate from the standard simulation setting.
-Instead of generating data from scratch, we use the gasoline data, which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
-We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
-
-	To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
-While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
-This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.
+Instead of generating data from scratch, we use the gasoline data, which consists of 60 samples of Near-infrared (NIR) absorption spectra measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane rating.
+We chose this setup to improve the approach towards the application in which we predict the octane ratings from the gasoline data set.
+
+	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
+{\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\
 
@@
 Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
-We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.
+We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline data set.
 
 	\subsection{Generating Similar Curves}
-	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline dataset, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 First, the initial curves are expressed in terms of a generated cubic B-spline basis which is created using 50 knots.
@@
     The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}.
-The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline dataset.
+The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.
 
@@
 	\section{Application}\label{Application}
-		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
+		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline data set.
 		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved.
@@
 Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not relatable to this real-life application where we not know this distribution.
-		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results.
-The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold.
+		Therefore, we will run all specification again for the gasoline data set and use the results of the simulation study towards the reading of the results.
+The application is designed similar to the simulation study: The 60 spectra of the gasoline data set will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold.
 In total, we conducted 1000 repetitions for each setting.
@@
 
-	\subsection{Near-infrared (NIR) Spectroscopy}
+	\subsection{Near-infrared (NIR) Spectroscopy}\label{NIR}
 	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
@@
 \\
-	In the context of this paper, the gasoline dataset which is used for the simulation and the application is constructed using NIR spectroscopy.
+	In the context of this paper, the gasoline data set which is used for the simulation and the application is constructed using NIR spectroscopy.
 According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).

### 2022-02-09 Paper/main.tex
Small correction

@@
 For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
-{\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}).
+{\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability (cf.
+\cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf.
+\cite{Jolliffe_1982}).
 This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

### 2022-02-09 Paper/main.tex
fortomorrow

@@
 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$.
-These measurement points can be different for each sample curve.
+{\color{orange} May we put the link to the figure 4 by footnote?} These measurement points can be different for each sample curve.
 However, in this paper, we only consider the case where curves share their measuring points.
@@
 For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
-	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
-Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
+	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper {\color{orange} link with specify?} are explained in the following.
+{\color{orange}or Each unique feature of the basis systems is used to interpret results of simulation study and application of this study.
+with link} Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
 
@@
 	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
-$L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
+{\color{orange} The theoretical progress is also precisely shown at one eqution(link).} $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
 Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
@@
 	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
-Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.\\
+Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.
+{\color{orange} Moreover, our data generating process is also based on this property.}\\
 
@@
 
-	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
+	{\color{orange} For the last equation, shouldn't it be approx including following equations regarding truncation error term?
+or delta times delta is so small that we can neglect(maybe not true)..?} In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
 This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.

### 2022-02-09 Paper/main.tex
Missing term in Equations added

@@
 			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
-			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
-			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
-		\end{split}
-	\end{equation}
-
-	{\color{orange} For the last equation, shouldn't it be approx including following equations regarding truncation error term?
-or delta times delta is so small that we can neglect(maybe not true)..?} In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
+			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
+			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
+			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
+			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\beta}^K(s) \mathrm{d}s
+		\end{split}
+	\end{equation}
+
+	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
 This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
 	\begin{equation}\label{score_approx}
-			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
+		\begin{split}
+			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s \\
+			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
+		\end{split}
 	\end{equation}
@@
 			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
-			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) 
+			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} d_{k}^m \phi_{k}(t) 
 			& \delta_{\nu, m}^L(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)

### 2022-02-09 Paper/main.tex
More Equation Corrections

@@
 		\begin{split}
-			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s \\
+			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \phi_{k}(s) \mathrm{d}s \\
 			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
@@
 		\begin{align}
-			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] 
+			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] 
 			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
@@
 			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K a_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s\\
-			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
+			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{J}(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s
 		\end{split}
@@
 		\begin{split}
-			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
+			Y(\omega) &= \alpha + \sum_{j = 1}^{L} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{L} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s\\
+			& \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
 			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)

### 2022-02-09 Paper/main.tex
More corrections

@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
+			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu, m}^K(s)\right)} \mathrm{d}s \\
 			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
-			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\beta}^K(s) \mathrm{d}s
+			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu, m}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu, m}^K(s) \mathrm{d}s
 		\end{split}
@@
 	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
-The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.
+The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.
 
@@
 			Y(\omega) &= \alpha + \sum_{j = 1}^{L} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{L} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s\\
-			& \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
+			& \quad \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
 			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)

### 2022-02-09 Paper/main.tex
Unifying Notation

@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
-			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu, m}^K(s)\right)} \mathrm{d}s \\
+			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu}^{m,K}(s)\right)} \mathrm{d}s \\
 			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
-			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu, m}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu, m}^K(s) \mathrm{d}s
+			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s
 		\end{split}
@@
 			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} d_{k}^m \phi_{k}(t) 
-			& \delta_{\nu, m}^L(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
+			& \delta_{\nu}^{m, L}(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
 		\end{align}
@@
 			y_i & = \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu}^{m,L}(s) \right) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
@@
 			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
+			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] \\
 			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\

### 2022-02-09 Paper/main.tex
Small changes before meeting

@@
 	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
-Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the Section on Near-Infrared-Spectroscopy in the Appendix.}
+Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the \hyperref[NIR]{Section on Near-Infrared-Spectroscopy in the Appendix.}}
 
@@
 While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$.
-In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting using $n_{FPC}$ = 4.
+In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of over-fitting using $n_{FPC} = 4$.
 Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4 ,6 ,23 for $n_{FPC} \in \{2, 3, 4 \}$)
@@
 	\paragraph{Fourier Basis}
-	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC}$ = 4.
+	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
 $f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
@@
 The additional simulations revealed evidence that there exists a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower than for 70 basis functions which might be a first sign of a too high $K$ and subsequent undersmoothing.
-Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better on a lower truncated smoothed curve (here $L$ = 50).
+Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better on a lower truncated smoothed curve (here $L = 50$).
 Importantly, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ration of the responses is not affecting the construction of the FPC's which might indicate benefiting attributes of the lower basis functions used in the main simulation.

### 2022-02-09 Paper/main.tex
Changes before meeting

@@
 
-	This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
-This would avoid the heavy computing of validating the best value for $K$, which we will conduct in the simulation.
+	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
+This would avoid the heavy computations of validating the best value for $K$, which we will conduct in the simulation.
 To provide intuition in this approach, let
@@
 	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
-A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty.
+A typical choice is the second derivative as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
 The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
@@
 	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-First, the initial curves are expressed in terms of a generated cubic B-spline basis which is created using 50 knots.
-In the R implementation of the fda package that is used, these 50 knots account for 52 basis functions (50+4-2).
+First, the initial curves are expressed in terms of a  cubic B-spline basis which is created using 50 knots.
+In the R implementation of the fda package, these 50 knots account for 52 basis functions (50+4-2).
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-It is assumed that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}_{1},\: \dots \:, \mathring{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
-Finally, we obtain the generated curves $NIR_{sim}$
+We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}_{1},\: \dots \:, \mathring{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
+Finally, we obtain the generated curves $NIR_{sim}$ as
 
@@
 
-		\begin{figure}
+		\begin{figure}[H]
 			\centering
@@
 		where $Z \sim \mathcal{N}(0,1)$.
-In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses.
+In total, we created four combinations, using the two true coefficient functions and the two error terms.
 These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
 For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification.
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification.
 The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
@@
 
-		with truncation parameter $L$.
-		\vspace{0.2cm}
-
-		The simulation was done with R (version...). In total, 5000 repetitions were done for each set of simulations.
+		with truncation parameter $L$. In total, 5000 repetitions were conducted for each set of simulations.
 
@@
 	\section{Application}\label{Application}
-		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline data set.
-		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved.
-To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function.
-Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
+		Our application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline data set.
+		Although the simulation study granted valuable insights into the different methods in our four different settings, it is not enough to determine the optimal method and choice of basis for the application, since there is too much uncertainty involved.
+To point out some sources of uncertainty: First, differing from the simulation setup, we do not know the true coefficient function.
+Visual inspection of the the estimated coefficient functions shwon in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be closer to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
 Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
-Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not relatable to this real-life application where we not know this distribution.
-		Therefore, we will run all specification again for the gasoline data set and use the results of the simulation study towards the reading of the results.
-The application is designed similar to the simulation study: The 60 spectra of the gasoline data set will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold.
+Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not applicable to this real-life application where we do not know their distribution.
+
+		Therefore, we will run all specification again for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
+The application is designed similar to the simulation study: The 60 spectra of the gasoline data set will be used as regressors to estimate a coefficient function, predict the reported octane numbers and evaluate the results via prediction MSE using 12 fold cross-validation with 5 elements per fold.
 In total, we conducted 1000 repetitions for each setting.
@@
 		The cross-validated MSPE selects 5 basis functions for the monomial basis.
-For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the fourier basis.
-Comparing the estimates in \hyperref[basis_expansion_estimate_appl]{ADD}, apart from the boundaries, B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributed by the lower amount of used basis functions.
-Especially at the lower boundary, the monomial basis shows a strong exaggerated bahavior.
+For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
+Comparing the estimates in Appendix \ref{Estimates_Appl}, apart from the boundaries, the B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributable to the lower number of basis functions.
+Especially at the lower boundary, the monomial basis shows an exaggerated behavior.
 However, we must exercise caution since from $L$=6 onwards, we were not able to calculate stable results for the monomial basis.
-The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while it is clearly knocked of for the monomial basis (0.24181).
-In contrast to the simulation study, the B-splines basis manages to outperform the fourier basis.
-Driving factors for this better performance could be that first, we do not assume a periodic true coefficient function with the same start- and end value and second, the Fourier basis tries to force the same start- and endvalue on $NIR$ (confirmed in unreported visual inspection).
-It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the mentioned similarities between $NIR$ and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
+The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while the monomial basis (0.24181) shows distinctly worse properties.
+In contrast to the simulation study, the B-splines basis manages to outperform the Fourier basis.
+Driving factors for this better performance could be that, first, we do not assume a periodic true coefficient function with the same start- and end value and second, the Fourier basis tries to force the same start- and endvalue on $NIR$.
+It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the hypothesized similarities between the true coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
 
@@
 The MSPE appears to be strictly decreasing in the number of FPC´s for its best basis choice.
-As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behaviour of the estimate $\hat{\beta}(t)$ can be observed.
-Opposing to the simulation study, the number of basis functions is steadily increasing for the monomial basis.
+As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
+Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis.
 The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
@@
 
-	\subsection{Application - Coefficient Function Estimates}
+	\subsection{Application - Coefficient Function Estimates}\label{Estimates_Appl}
 	\begin{figure}[H]

### 2022-02-09 Paper/main.tex
Meeting State

@@
 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$.
-{\color{orange} May we put the link to the figure 4 by footnote?} These measurement points can be different for each sample curve.
+These measurement points can be different for each sample curve.
 However, in this paper, we only consider the case where curves share their measuring points.
@@
 random process itself.
+More information about this example can be found in Appendix \ref{NIR}.
 
@@
 For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
-	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper {\color{orange} link with specify?} are explained in the following.
-{\color{orange}or Each unique feature of the basis systems is used to interpret results of simulation study and application of this study.
-with link} Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
-
-	\paragraph{Monomial Basis}
+	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
+Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
+
+	\paragraph{Monomial Basis}\label{Monomial_basis}
 	A very simple idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis.
@@
 	\begin{equation}\label{Fourier_Series}
-		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
+		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_i \cos(2\pi i x - \phi_i) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
 	\end{equation}
@@
 The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
-Additionally, the Fourier basis is especially suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.
-{\color{red} Citation}
+The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions.
+(cf.
+\cite{ramsay_functional_2005})
 	\vspace{-0.2cm}
@@
 	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
-{\color{orange} The theoretical progress is also precisely shown at one eqution(link).} $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
+In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations.
+$L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
 Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
@@
 Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.
-{\color{orange} Moreover, our data generating process is also based on this property.}\\
+Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
 
@@
 
-	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
+	The parameter $M \in \{1,\: \dots \:, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
 Using only $M$ functional principal components leads to the following approximation.
@@
 For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
-{\color{red} This is incorrect, nearly nobody does this.} While cross-validation is common for selecting $K$, the number of FPC's is in practice chosen by using the lowest number of FPC's that explain a specified amount of variability (cf.
+The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf.
 \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf.
@@
 
-	\subsection{Generating Similar Curves}
+	\subsection{Generating Similar Curves}\label{similar_curves}
 	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 First, the initial curves are expressed in terms of a  cubic B-spline basis which is created using 50 knots.
-In the R implementation of the fda package, these 50 knots account for 52 basis functions (50+4-2).
+In the R implementation of the fda package, these 50 knots account for 52 basis functions ($50+4-2$).
 These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}_{1},\: \dots \:, \mathring{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$.
+We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}^{1},\: \dots \:, \mathring{\xi}^{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}^1,\: \dots\:, \hat{\lambda}^M))$.
 Finally, we obtain the generated curves $NIR_{sim}$ as
@@
 
-		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $.
+		 Two different error-terms $\epsilon$ were created by first generating an i.i.d.
+standard normal error term and then multiplying it by two error variations $\sigma_e $.
 The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise.
@@
 			\begin{split}
-				\hat{\xi}_{i}^{m, \mathcal{H},L} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
-			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
-				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+				\hat{\xi}_{i}^{m, \mathcal{H},L} & =  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} }\mathrm{d}s) 
+			    \approx \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
+				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
 			\end{split}
@@
 	\subsection{Results}	
-	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in the appendix. 
+	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in Appendix \ref{Tables_sim} and \ref{Estimates_sim}. 
 	\subsubsection{Basis Expansion Regression}
@@
 	\paragraph{Monomial Basis}
-	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability.
-For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function.
+	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
+For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence: It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
+In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence.
+It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
 This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
@@
 	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
-	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$.
-An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the higher noise responses.
+	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis.
+It still performs the worst for $f_1$.
+An explanation might be its exaggerated behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the lower signal-to-noise ratios.
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
@@
 	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
-With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise into $\hat{\beta}(t)$.
+With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
 The Fourier basis functions perform the best for each setup for the basis expansion regression.
@@
 Second, both functions feature periodic behavior.
-Third, $f_2$ does have the same value at the start- and the end of the interval.	\\
+Third, $f_2$ does have the same value at the start- and the end of the interval lending itself to a periodic representation.	\\
 
 	\subsubsection{Functional Principal Component Regression}
-		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
-But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+		The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
+In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
+But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
 As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's.
@@
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSPE is decreasing in the increasing number of FPC's and chosen basis functions for both the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
-In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the chosen basis functions.
+	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
 The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
@@
 	\paragraph{B-spline Basis}
-	For $f_1,Y_1$, the MSPE suggests better models with a higher number of FPC's.
+	For $f_1,Y_1$, the MSPE suggests that models with a higher number of FPC's perform better.
 While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$.
-In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of over-fitting using $n_{FPC} = 4$.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4 ,6 ,23 for $n_{FPC} \in \{2, 3, 4 \}$)
+In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting using $n_{FPC} = 4$.
+Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} \in \{2, 3, 4 \}$)
 	\vspace{-0.2cm}
@@
 $f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
-Both configurations of $f_2$ are using 5, 15, 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
+Both configurations of $f_2$ are using 5, 15 and 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
 	\vspace{-0.2cm}
@@
 	\subsubsection{Interpretation and Relevance for Application}
-	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems introduced when choosing a small number of basis functions.
-For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with lower $L$.
-This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$.
+	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems to be introduced when choosing a small number of basis functions.
+For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$.
+This results in higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$.
 The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.
@@
 	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered.
-An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture in our setting.
+An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
 To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX).
 As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$.
-The additional simulations revealed evidence that there exists a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower than for 70 basis functions which might be a first sign of a too high $K$ and subsequent undersmoothing.
-Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better on a lower truncated smoothed curve (here $L = 50$).
-Importantly, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ration of the responses is not affecting the construction of the FPC's which might indicate benefiting attributes of the lower basis functions used in the main simulation.
+The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be a first sign of a too high $L$ and subsequent undersmoothing.
+Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$).
+The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's which might indicate beneficial attributes of the lower truncation parameters used in the main simulation.
 
@@
 	\section{Application}\label{Application}
-		Our application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline data set.
+		Our application uses the methods and insights from the previous sections to predict the octane ratings of the  gasoline data set.
 		Although the simulation study granted valuable insights into the different methods in our four different settings, it is not enough to determine the optimal method and choice of basis for the application, since there is too much uncertainty involved.
 To point out some sources of uncertainty: First, differing from the simulation setup, we do not know the true coefficient function.
-Visual inspection of the the estimated coefficient functions shwon in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be closer to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
-Second, we have no information about the signal-to-noise ratios of the measured octane numbers.
-Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not applicable to this real-life application where we do not know their distribution.
-
-		Therefore, we will run all specification again for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
-The application is designed similar to the simulation study: The 60 spectra of the gasoline data set will be used as regressors to estimate a coefficient function, predict the reported octane numbers and evaluate the results via prediction MSE using 12 fold cross-validation with 5 elements per fold.
+Visual inspection of the the estimated coefficient functions shown in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be more similar to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
+Second, we have no information about the signal-to-noise ratio of the measured octane numbers.
+Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not applicable in this application where we do not know their distribution.
+
+		Therefore, we will rerun all specification for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
+The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set will be used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via prediction MSE using 12 fold cross-validation with 5 elements per fold.
 In total, we conducted 1000 repetitions for each setting.
@@
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
-Comparing the estimates in Appendix \ref{Estimates_Appl}, apart from the boundaries, the B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributable to the lower number of basis functions.
+Comparing the estimates in Appendix \ref{Estimates_Appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the monomial estimate which might be attributable to the lower number of basis functions.
 Especially at the lower boundary, the monomial basis shows an exaggerated behavior.
-However, we must exercise caution since from $L$=6 onwards, we were not able to calculate stable results for the monomial basis.
+However, we must exercise caution since from $L=6$ onwards, we were not able to calculate stable results for the monomial basis.
 The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while the monomial basis (0.24181) shows distinctly worse properties.
 In contrast to the simulation study, the B-splines basis manages to outperform the Fourier basis.
-Driving factors for this better performance could be that, first, we do not assume a periodic true coefficient function with the same start- and end value and second, the Fourier basis tries to force the same start- and endvalue on $NIR$.
+Driving factors for this better performance could be that, first, we do not assume a periodic true coefficient function with the same start- and end value and second, that the Fourier basis enforces identical start and end value on $NIR$.
 It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the hypothesized similarities between the true coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
@@
 In contrast to the simulation study, no evidence of overfitting was found for the best basis choices in any of the three bases.
-The MSPE appears to be strictly decreasing in the number of FPC´s for its best basis choice.
-As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
+The MSPE for the optimal specification appears to be strictly decreasing in the number of FPC's.
+As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
 Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis.
@@
 
-	\paragraph{Larger Range for the Number of Basis Functions for FPCR}
-	\vspace{-0.2cm}
-
-	\paragraph{Larger Range for the Number of Principal Components}
+	\paragraph{Larger Range for the Number of Specifications for FPCR}
 	\vspace{-0.2cm}
@@
 			\end{overpic}
-			\caption{NIR Data Set and Finder SD (a Near-Infrared-Spectroscope built by HiperScan GmbH) \\
+			\caption{NIR absorption spectra from the Gasoline Data Set and Finder SD (a Near-Infrared-Spectroscope built by HiperScan GmbH)	\\
 			(Source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
@@
 	\newpage
-	\subsection{Simulation - Coefficient Function Estimates}
+	\subsection{Simulation - Coefficient Function Estimates}\label{Estimates_sim}
 
@@
 
+	\newpage
 	\section*{Affidavit}

### 2022-02-09 Code/Plot_Generators/Tradeoff_plot.R

@@ -68,25 +68,25 @@ NIR_plot100 <- as.data.frame(NIR_plot100)
 
 NIR <- cbind(as.data.frame(NIR[,1]),NIR_seq)
 colnames(NIR) = c('wavelength','time')
-plot(NIR[,wavelength])
+#plot(NIR[,wavelength])
 
-NIR$'K' = 'K=0'
-NIR_plot5$'K' = 'K=5'
-NIR_plot10$'K' = 'K=10'
-NIR_plot30$'K' = 'K=30'
-NIR_plot50$'K' = 'K=50'
-NIR_plot100$'K' = 'K=100'
+NIR$'L' = 'L=0'
+NIR_plot5$'L' = 'L=5'
+NIR_plot10$'L' = 'L=10'
+NIR_plot30$'L' = 'L=30'
+NIR_plot50$'L' = 'L=50'
+NIR_plot100$'L' = 'L=100'
 
 NIR_data = rbind(NIR,NIR_plot5,NIR_plot10,NIR_plot30,NIR_plot50,NIR_plot100)
 
-label <- paste0("K=",c(0,5,10,30,50,100))
+label <- paste0("L=",c(0,5,10,30,50,100))
 label[1] <- "Real Line"
 
-basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength, color=K)) +
+basis_exp_plot <- ggplot(data = NIR_data, aes(x=time, y=wavelength, color=L)) +
   geom_line()+
   xlab('Wavelength in nm') +
   ylab('Absorption') +
-  scale_color_discrete(breaks=c('K=0','K=5','K=10','K=30','K=50','K=100'), 
+  scale_color_discrete(breaks=c('L=0','L=5','L=10','L=30','L=50','L=100'), 
                        labels=label)+
   #ggtitle('Basis expansions according to the different number of B-spline basis functions') +
   theme_light() +

### 2022-02-09 Paper/main.tex
Physics Paragraph

@@
 	\paragraph{Input from Physics Analysis}
+	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
+For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value.
+This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.
+Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex
Added citation for blackbox

@@
 	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$.
-For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
+For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.

### 2022-02-09 Paper/main.tex
Paragraph for higher number of specifications in the outlook

@@
 	\paragraph{Larger Range for the Number of Specifications for FPCR}
+	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation.
+It would therefore be interesting to focus more attention on this aspect of the paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex
Slight equation spacing adjustment

@@
 
-	\setlength{\abovedisplayskip}{0.4cm}
-	\setlength{\belowdisplayskip}{0.4cm}
+	\setlength{\abovedisplayskip}{0.35cm}
+	\setlength{\belowdisplayskip}{0.35cm}
 
 	\setlength{\abovedisplayshortskip}{0.2cm}
-	\setlength{\belowdisplayshortskip}{0.4cm}
+	\setlength{\belowdisplayshortskip}{0.35cm}
 
@@
 
-	\paragraph{Input from Physics Analysis}
+	\paragraph{Input from Physics}
 	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.

### 2022-02-09 Paper/main.tex
proofreading simulation and application part 1

--- 2022-02-09 Paper/main.tex
@@
 	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$.
-For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
+For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
@@
 	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error.
+For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $L$ as well as the number of FPC's, which is possibly affected by $L$, by ten-fold cross-validation using the prediction mean-squared error.
 The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf.
@@
 
-	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high.
-This would avoid the heavy computations of validating the best value for $K$, which we will conduct in the simulation.
+	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high.
+This would avoid the heavy computations of validating the best value for $L$, which we will conduct in the simulation.
 To provide intuition in this approach, let
@@
 	The simulation study follows \cite{Reiss_2007b} as a guideline.
-Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the introduced methods with differing true coefficient functions:
+Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness are created to compare the introduced methods with differing true coefficient functions:
 	\begin{equation}
@@
 
-    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}.
-The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.
+    The function $f_2(t)$ was generated by referring to \cite{cardot_bumpyfunction_2002} while function $f_1(t)$ directly follows \cite{Reiss_2007b}. 
+    %and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.
 
@@
 standard normal error term and then multiplying it by two error variations $\sigma_e $.
-The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise.
+The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses.
 They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
@@
 These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification.
+		% For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was prior smoothed with the respective basis function specification.
 The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
@@
 
-		with truncation parameter $L$. In total, 5000 repetitions were conducted for each set of simulations.
+		with truncation parameter $L$.
+In total, 5000 repetitions were conducted for each specified model, basis system and basis function.
+The models are denoted as a combination of the function $f \in \{f_1(t), f_2(t)\}$	and created responses $Y \in \{Y_1, Y_2\}$.
 
@@
 	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in Appendix \ref{Tables_sim} and \ref{Estimates_sim}.
+
 	\subsubsection{Basis Expansion Regression}
-	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR.
-Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.
+	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
+Examining the results, it appears that the cross-validated MSPE inherits a convex nature in the increasing basis functions.
 
 	\paragraph{Monomial Basis}
-	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
-For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function.
+	Due to the in the number of monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
+For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence.
+In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
 It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
@@
 	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
-	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis.
-It still performs the worst for $f_1$.
-An explanation might be its exaggerated behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the lower signal-to-noise ratios.
+	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis.
+An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ ( figure \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio.
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
-For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis.
-While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
+The B-spline basis outperforms the monomial basis in $f_2$, but comes second to the Fourier basis.
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ( figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
+With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
 	\vspace{-0.2cm}
@@
 	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
-With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
+As for the B-splines basis functions, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses.
 The Fourier basis functions perform the best for each setup for the basis expansion regression.
@@
 As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's.
-This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description.
-In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.
+This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions regarding this within this simulation study.
+Therefore, we will limit ourself to a brief description.
+In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios).
+A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses at all.
 
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
 In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
-The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
+The monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
 	\vspace{-0.2cm}
@@
 An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
-To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX).
+To examine this further, additional simulations ( section \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
 As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$.
@@
 Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$).
-The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's which might indicate beneficial attributes of the lower truncation parameters used in the main simulation.
+The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's.
+This might indicate beneficial attributes of the lower truncation parameters in settings with low signal-to-noise responses.
 
@@
 The MSPE for the optimal specification appears to be strictly decreasing in the number of FPC's.
-As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
+As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in figure  \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
 Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis.
@@
 	\paragraph{Insights from Simulation cannot be Extended to More General Functions}
+	As described, the properties of the two used functions $f \in \{f_1(t), f_2(t)\}$ influence the results.
+Although the resulting MSPE and visual inspection provided some evidence to support the hypothesis that the true coefficient function of $NIR$ might be similar to $f_2$, several other factors that were not asserted could also have caused this.
+Therefore, this simulation is not sufficient to base a reasonable claim concerning more general true coefficient functions on it.
 	\vspace{-0.2cm}
@@
 	\paragraph{Input from Physics Analysis}
-	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
-For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value.
-This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.
-Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex

@@
 	\paragraph{Larger Range for the Number of Specifications for FPCR}
+	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation.
+It would therefore be interesting to focus more attention on this aspect of the paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
 	\vspace{-0.2cm}
 
-	\paragraph{Input from Physics Analysis}
+	\paragraph{Input from Physics}
+	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
+For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value.
+This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.
+Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex
Take out subsections from Outlook to reduce Contents Length
Adjusted Capitalization of Monomial basis

@@
 	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$.
-However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis.
+However, a different choice of $\alpha$ could lead to improvements in performance of the Monomial basis.
 	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates.
@@
 	\paragraph{Fourier Basis}
-	In the same way the monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions.
+	In the same way the Monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions.
 Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
@@
 
-	As the B-spline basis does not have infinitely many elements as the full monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
+	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
 For the sake of keeping the notation reasonably concise, we will still keep this notation.
@@
 In total, we created four combinations, using the two true coefficient functions and the two error terms.
-These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
+These four combinations are then used with a different number of Monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
 		% For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
@@
 	\paragraph{Monomial Basis}
-	Due to the in the number of monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
+	Due to the in the number of Monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
 For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function.
@@
 This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
-For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio.
+For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high(low) signal-to-noise ratio.
 	\vspace{-0.2cm}
@@
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
-The B-spline basis outperforms the monomial basis in $f_2$, but comes second to the Fourier basis.
+The B-spline basis outperforms the Monomial basis in $f_2$, but comes second to the Fourier basis.
 While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ( figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
@@
 In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
-The monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
+The Monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
 	\vspace{-0.2cm}
@@
 		\subsubsection{Basis Expansion Regression}
-		The cross-validated MSPE selects 5 basis functions for the monomial basis.
+		The cross-validated MSPE selects 5 basis functions for the Monomial basis.
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
-Comparing the estimates in Appendix \ref{Estimates_Appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the monomial estimate which might be attributable to the lower number of basis functions.
-Especially at the lower boundary, the monomial basis shows an exaggerated behavior.
-However, we must exercise caution since from $L=6$ onwards, we were not able to calculate stable results for the monomial basis.
-The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while the monomial basis (0.24181) shows distinctly worse properties.
+Comparing the estimates in Appendix \ref{Estimates_Appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate which might be attributable to the lower number of basis functions.
+Especially at the lower boundary, the Monomial basis shows an exaggerated behavior.
+However, we must exercise caution since from $L=6$ onwards, we were not able to calculate stable results for the Monomial basis.
+The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while the Monomial basis (0.24181) shows distinctly worse properties.
 In contrast to the simulation study, the B-splines basis manages to outperform the Fourier basis.
@@
 As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in figure  \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
-Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis.
+Differing from the simulation study, the number of basis functions is steadily increasing for the Monomial basis.
 The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
@@
 
-	\subsection{Limitations}
+	%\subsection{Limitations}
 
@@
 This is mainly due to an increase in collinearity of the derived regressor matrix shown in Definition \ref{regressor_mat_1}.
-This problem is inherent to basis systems whose functions are not pairwise orthogonal, such as the monomial or B-splines bases, but gets more pronounced the more functions we add to the basis system and the higher the correlation between those functions.
+This problem is inherent to basis systems whose functions are not pairwise orthogonal, such as the Monomial or B-splines bases, but gets more pronounced the more functions we add to the basis system and the higher the correlation between those functions.
 \\
@@
 
-	\subsection{Possible Extensions}
+	%\subsection{Possible Extensions}
 
 	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}
-	To address the collinearity problems described earlier, one possible idea would be to use a system of pair-wise orthogonal polynomials as a basis instead of the monomial basis.
+	To address the collinearity problems described earlier, one possible idea would be to use a system of pair-wise orthogonal polynomials as a basis instead of the Monomial basis.
 One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials.

### 2022-02-09 Paper/main.tex
Better Outlook Structure
Slight spacing changes

@@
 Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\
-
 	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis.
@@
 Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
+	\vspace{-0.2cm}
 
@@
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
+
 	\begin{equation}
@@
 	\end{equation}
-
 	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
@@
 This padding of the knot vector then allows to calculate every object that is needed for the definition of the basis over the original set of knots.\\
-
 	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
 To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions.
-
 	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
@@
 Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
-
 	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting.
@@
 	\end{equation}
-
 	where the $\hat{\xi}_{i}^m$ are derived as 
@@
 	\end{equation}
-
 	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
@@
 	\end{equation}
-
 	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
@@
 	\end{equation}
-
 	And we can define the following objects:
@@
 	\end{equation}
-
 	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
+
 	\begin{equation}
@@
 
-	%\subsection{Limitations}
+	\subsection*{Limitations}
 
@@
 
-	%\subsection{Possible Extensions}
+	\subsection*{Possible Extensions}
 

### 2022-02-09 Paper/main.tex
Score Estimation Equation

@@
 		% For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was prior smoothed with the respective basis function specification.
-The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
-		\begin{equation}
-			\begin{split}
-				\hat{\xi}_{i}^{m, \mathcal{H},L} & =  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} }\mathrm{d}s) 
-			    \approx \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
-				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculated the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was prior smoothed with the respective basis function specification.
+The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$  by the equation
+		\begin{equation}
+			\check{\xi}_{i}^{m, \mathcal{H},L}
+			= \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, L, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s
+		    \approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+		\end{equation}
+		where 
+		\begin{equation}
+			\begin{split}
+				{\color{red} \left(X_{i}^{\mathcal{H}}(t) - \hat{\mu}^{\mathcal{T}}(t)\right)} 
+				&= {\color{red}\sum_{j \in \mathcal{L}} a_{i,j}^{\mathcal{H}} \phi_j(t)}
+				= {\color{red}\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(t) + \delta_{i}^{L, \mathcal{H}}(t)}
+				\approx {\color{red}\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(t)} \\
+				{\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} } &= {\color{blue}\sum_{k = 1}^{L} d_{k}^{m, L, \mathcal{T}} \phi_{k}(s)}
 			\end{split}

### 2022-02-09 Paper/main.tex
removing page number from title
Slight proofreading from start. but switch to local pdf proofreading

@@
 \begin{document}
+\begin{titlepage}
+
 	\title{{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
@@
 	\maketitle
+	\thispagestyle{empty}
 	\vspace{1.5 cm}
@@
 	\end{center}
-
+\end{titlepage}
 	\newpage
@@
 Section \ref{Simulation} contains a description of our Monte-Carlo Simulation, which aims to provide information on how to choose an appropriate functional basis and truncation parameter for the aforementioned methods.
-The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves.
+The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of octane numbers of gasoline samples based on Near-Infrared absorption curves.
 In Section \ref{Outlook}, we give an outlook on possible extensions for this paper and describe the limitations of our approach.
@@
 		\begin{enumerate}
-			\item $\langle v_i, v_j \rangle = 0 \quad \forall v_i, v_j \in S \quad i \neq j$
+			\item $\langle v_i, v_j \rangle = 0 \quad \forall v_i, v_j \in S $ for $i \neq j$
 			\item $\lvert \lvert v \rvert \rvert = 1 \quad \forall v \in S$
@@
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$.
-Denoted by $\mathbb{L}^2[0,1]$, this space is consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
+Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
 	\begin{equation}
@@
 The presence of functional observations in a data set is what defines functional data sets.
-However, in reality realizations of random functions are not typically observed in their functional form.
+In reality however,  realizations of random functions are not typically observed in their functional form.
 Instead, each curve is observed at a discrete and typically large set of measurements points.
@@
 These measurement points can be different for each sample curve.
-However, in this paper, we only consider the case where curves share their measuring points.
+In this paper, we only consider the case where curves share their measuring points.
 	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure.
-Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\
+Therefore, methods such as basis representations will be introduced in the following parts of the Theory Section.\\
 	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis.
@@
 	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion.
-Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express or approximate a realization $x(t)$ of $X(\omega)$.
-Then the following equation shows how a basis can be used to express a function as a weighted sum of its elements.
+Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express or approximate a realization $x(t)$ of $X(\omega)$.
+The following equation shows how a basis can be used to express a function as a weighted sum of its elements.
 	\begin{equation}
@@
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
-Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.
+Diagrams showing a number of basis functions from these bases are found in Section \ref{Basis_Plots} of the Appendix.
 	\vspace{-0.2cm}
@@
 
-	However, the monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$.
+	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$.
 But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
@@
 Although the resulting MSPE and visual inspection provided some evidence to support the hypothesis that the true coefficient function of $NIR$ might be similar to $f_2$, several other factors that were not asserted could also have caused this.
-Therefore, this simulation is not sufficient to base a reasonable claim concerning more general true coefficient functions on it.
+Therefore, this simulation is not sufficient to base a reasonable claim concerning more general true coefficient functions, as we would assume them in other applications, on it.
 	\vspace{-0.2cm}
@@
 	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
-It, therefore, measures the absorption and interaction of this spectrum of radiation with the sample.
+It measures the absorption and interaction of this spectrum of radiation with the sample.
 NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample.

### 2022-02-09 Paper/main.tex
Slight language correction

@@
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
+In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
 It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
@@
 	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis.
-An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ ( figure \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio.
+An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (Figures \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio.
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
 The B-spline basis outperforms the Monomial basis in $f_2$, but comes second to the Fourier basis.
-While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ( figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
 With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.

### 2022-02-09 Paper/main.tex
part two proofreading before switching to pdf

--- 2022-02-09 Paper/main.tex
@@
 	\subsection{Motivation}
+	\label{sim_motivation}
 
@@
 An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
-To examine this further, additional simulations ( section \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
+To examine this further, additional simulations ( Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
 As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$.
@@
 The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's.
-This might indicate beneficial attributes of the lower truncation parameters in settings with low signal-to-noise responses.
+This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.
 
@@
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
-Comparing the estimates in Appendix \ref{Estimates_Appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate which might be attributable to the lower number of basis functions.
+Comparing $\hat{\beta}(t)$ for the different bases in figure \ref{basis_expansion_estimate_appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate which might be attributable to the lower number of basis functions.
 Especially at the lower boundary, the Monomial basis shows an exaggerated behavior.
@@
 	\paragraph{Low Number of Basis Functions in FPCR Regression}
-	Another limitation of the exploration into functional principal component regression is the low number of principal component specifications used in this paper.
-As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of this method as long as an appropriately high number of basis functions is provided.
-	A more significant factor seems to be the number of principal components available for the linear regression which in itself could be subject to choice according to cross validation.
+	As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of FPCR, apart from the additional simulations which reported signs of undersmoothing for larger values of $L$.
+A more significant factor seems to be the number of FPC's available for the linear regression.
+This paper selects these components in order of their explanatory power of the variability around the mean function.
+For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC´s subject to some criteria such as cross validation or base their choice on insights and expertise from the respective field.
 	\vspace{-0.2cm}
@@
 	To address the collinearity problems described earlier, one possible idea would be to use a system of pair-wise orthogonal polynomials as a basis instead of the Monomial basis.
-One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials.
+One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials (cf.
+\citep{Dattoli_2001}).
 Due to their orthogonality, the problem of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.
@@
 	\paragraph{Larger Range for the Number of Specifications for FPCR}
-	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation.
-It would therefore be interesting to focus more attention on this aspect of the paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
+	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient and limited to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation.
+It would therefore be interesting to focus more attention on this limitation of this paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
 	\vspace{-0.2cm}
@@
 	\paragraph{Input from Physics}
-	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
+	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models, and be conducive to a more meaningful interpretation of estimates.
 For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value.
 This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.
-Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
+Alternatively, it could be used to link specific principal components to chemical compounds which would be useful for the model selection and interesting for the interpretation of estimates.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex
Slight changes

@@
 	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
-Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the \hyperref[NIR]{Section on Near-Infrared-Spectroscopy in the Appendix.}}
+Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to Appendix \ref{NIR}.}
 
@@
 
-	A vector space with an associated inner product is called an inner product space and the inner product defines a norm and an associated distance on the vector space.
+	A vector space with an associated inner product is called an inner product space, and the inner product defines a norm and an associated distance on the vector space.
 	\begin{equation}
@@
 	The closed span $\overline{span}(S)$ of a sequence $S$ in $\mathbb{H}$ is defined as the closure of the span with respect to the distance induced by the norm and $S$ is called a basis of $\mathbb{H}$ if $\overline{span}(S) = \mathbb{H}$.	It is called an orthonormal basis if, in addition, the following properties hold.
-
 	\begin{multicols}{2}
@@
 	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function.
-The presence of functional observations in a data set is what defines functional data sets.
-In reality however,  realizations of random functions are not typically observed in their functional form.
+The presence of functional observations in a data set defines functional data sets.
+However,  realizations of random functions are not typically observed in their functional form.
 Instead, each curve is observed at a discrete and typically large set of measurements points.
@@
 In this paper, we only consider the case where curves share their measuring points.
-	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure.
+	To use the unique capabilities of functional data analysis with functional data obtained in this form, it is necessary to restore its functional structure.
 Therefore, methods such as basis representations will be introduced in the following parts of the Theory Section.\\
@@
 	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$.
-For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
+For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
@@
 	\paragraph{Monomial Basis}\label{Monomial_basis}
-	A very simple idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis.
+	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis.
 For entire functions $f(t)$, e.g.
@@
 In total, we created four combinations, using the two true coefficient functions and the two error terms.
-These four combinations are then used with a different number of Monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
-		% For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
-		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculated the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was prior smoothed with the respective basis function specification.
+These four combinations are then used with a different number of Monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.\\
+
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculated the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification.
 The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$  by the equation
@@
 			= \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, L, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s
-		    \approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+		    = \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
 		\end{equation}
@@
 	\subsubsection{Basis Expansion Regression}
-	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
-Examining the results, it appears that the cross-validated MSPE inherits a convex nature in the increasing basis functions.
+	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
+Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions.
 
@@
 This paper selects these components in order of their explanatory power of the variability around the mean function.
-For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC´s subject to some criteria such as cross validation or base their choice on insights and expertise from the respective field.
+For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC's subject to some criteria such as cross validation or base their choice on insights and expertise from the respective field.
 	\vspace{-0.2cm}
@@
 One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials (cf.
-\citep{Dattoli_2001}).
+\cite{Dattoli_2001}).
 Due to their orthogonality, the problem of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.

### 2022-02-09 Paper/main.tex
Grammarly Run

@@
 	\paragraph{Monomial Basis}\label{Monomial_basis}
-	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis.
-For entire functions $f(t)$, e.g.
-polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, but converging sum of weighted monomials.
+	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use monomials of increasing degree as a basis.
+For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
 	\begin{equation}\label{Taylor_expansion}
@@
 	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$.
-But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
+Nevertheless, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
 From this idea, it is natural to use the monomials as a potential basis for approximation.
 \\
-	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter.
+	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero, as shown above.
+Instead, one can introduce a shift parameter.
 This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
@@
 	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$.
-However, a different choice of $\alpha$ could lead to improvements in performance of the Monomial basis.
+However, a different choice of $\alpha$ could lead to improvements in the performance of the Monomial basis.
 	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates.
@@
 
-	Typically, the series is represented in the so called amplitude-phase form.
+	Typically, the series is represented in the so-called amplitude-phase form.
 This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter.
-Therefore, rewriting the series in the sine-cosine form as shown above is necessary.
+Therefore, rewriting the series in the sine-cosine form, as shown above, is necessary.
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
@@
 	\end{equation}
-	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
+	To stay true to the original amplitude-phase form, it is reasonable to restrict the number of Fourier basis functions to odd-numbered values.
 The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
@@
 A typical case that is often used in practice is an equidistant grid of knots.
-In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure allowing for a reduced number of matching derivatives at the corresponding knots.
+In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure, allowing for a reduced number of matching derivatives at the corresponding knots.
 For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\
@@
 
-	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times.
-This padding of the knot vector then allows to calculate every object that is needed for the definition of the basis over the original set of knots.\\
+	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$, an additional $m$ times.
+This padding of the knot vector then allows calculating every object that is needed for the definition of the basis over the original set of knots.\\
 	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
@@
 For this expansion, it is possible to use a complete basis of $\mathbb{L}^2[0,1]$.
-In many cases this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting.
+In many cases, this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting.
 To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves.
 On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information.
-This is a typical occurence of the Bias-Variance tradeoff.\\
-
-	A different approach that is atypical in practice, is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects.
-Here, the parameter of choice is not a weighting term for the penalty, but the number of basis functions.
+This is a typical occurrence of the Bias-Variance tradeoff.\\
+
+	A different approach that is atypical in practice is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects.
+Here, the parameter of choice is not a weighting term for the penalty but the number of basis functions.
 Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper.
@@
 $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
-Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.
+Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set, which is used in the later parts of this paper and exemplifies the tradeoffs at the core of the truncation parameter choice.
 
@@
 
-	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
+	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$, each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
 \cite{alexanderian_KLexpansion_2015}).
@@
 
-	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
-	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
-Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.
+	As in the well-known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function explained by the corresponding Eigenfunction. 
+	Therefore, ordering the Eigenfunctions according to their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes.
+Due to this property, a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.
 Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
@@
 chapter 8.2.3 \cite{ramsay_functional_2005}).
-As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality.
+As each curve is infinite-dimensional, there is no upper limit to this number due to the dimensionality.
 However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
@@
 	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
-For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
+For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are proper bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
-The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.
+The following considerations and results of the simulation study might serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.
 
 	\subsection{Scalar-on-Function Regression}\label{Scalar_on_function_regression}
-	In the simple scalar setting, one of the most important tools in econometrics is linear regression.
-Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction.
+	In the simple scalar setting, one of the essential tools in econometrics is linear regression.
+Its goal is twofold: to gain information about the dependency between variables and allow for prediction.
 To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
@@
 
-	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
-	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$.
-The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
+	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns, and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
+	In this finite-dimensional setting, one important question is how to estimate the unknown coefficients $\beta$.
+The most famous estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
 	\begin{equation}
@@
 
-	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
+	The concept of linear regression can be extended to the setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
 	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
@@
 	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
-
 	\begin{equation}
@@
 
-	In practice it is common to not only express the coefficient function in terms of a basis but also the observations.
+	In practice, it is common to not only express the coefficient function in terms of a basis but also the observations.
 Therefore two bases ($\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and $\left(\psi_k(t)\right)_{k \in \mathcal{L}}$) and two corresponding truncation parameters ($J$ and $K$) can be chosen.
@@
 
-	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
+	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$, and an estimate of the coefficient function can be derived accordingly.
 	\begin{equation}
@@
 
-	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following.
+	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx}, we obtain the following.
 To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
@@
 	\begin{equation}
-		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1}
+		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\beta}(t) = \sum_{m = 1}^{M} \tilde{b}_{m + 1}^{L,M} \tilde{\nu}^{m,L}(t)
 	\end{equation}
@@
 
-	\subsection{Motivation}
-	\label{sim_motivation}
+	\subsection{Motivation}\label{sim_motivation}
 
@@
 The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf.
-\cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf.
+\cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have a more significant influence on the prediction (cf.
 \cite{Jolliffe_1982}).
@@
 	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
-A typical choice is the second derivative as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
+A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
 The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
@@
 	\subsection{Generating Similar Curves}\label{similar_curves}
+
 	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
@@
 In the R implementation of the fda package, these 50 knots account for 52 basis functions ($50+4-2$).
-These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+These smooth curves are then centered before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
 We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}^{1},\: \dots \:, \mathring{\xi}^{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}^1,\: \dots\:, \hat{\lambda}^M))$.
 Finally, we obtain the generated curves $NIR_{sim}$ as
-
 	\begin{equation}
@@
 		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculated the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification.
-The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$  by the equation
-		\begin{equation}
+The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$  by Equation \ref{Score_est}.
+		\begin{equation}\label{Score_est}
 			\check{\xi}_{i}^{m, \mathcal{H},L}
 			= \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, L, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s
-		    = \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
+		    = \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
 		\end{equation}
@@
 
-		with truncation parameter $L$.
 		In total, 5000 repetitions were conducted for each specified model, basis system and basis function.
@@
 	\paragraph{Monomial Basis}
-	Due to the in the number of Monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
-For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function.
+	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
+For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines for this coefficient function.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
-It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries.
+In the case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
+It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behavior at the boundaries.
 This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
@@
 	\paragraph{B-spline Basis}
-	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
-	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis.
+	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onwards, the simulations were running into problems of numerical instability.
+	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three bases.
 An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (Figures \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio.
 For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
-The B-spline basis outperforms the Monomial basis in $f_2$, but comes second to the Fourier basis.
-While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
-With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
+The B-spline basis outperforms the Monomial basis in $f_2$ but comes second to the Fourier basis.
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
+With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could prevent fitting this scalar noise using $\hat{\beta}(t)$.
 	\vspace{-0.2cm}
@@
 Second, both functions feature periodic behavior.
-Third, $f_2$ does have the same value at the start- and the end of the interval lending itself to a periodic representation.	\\
+Third, $f_2$ does have the same value at the start- and the end of the interval, lending itself to a periodic representation.
+	\vspace{-0.2cm}
 
@@
 But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
-As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's.
-This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions regarding this within this simulation study.
-Therefore, we will limit ourself to a brief description.
+As will be described, it seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's.
+This might be because the dependency {\color{red} Reformulate this in the meeting!!!} (FPCA is performed on the smoothed curves) is too complex to draw conclusions regarding this within this simulation study.
+Therefore, we will limit ourselves to a brief description.
 In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios).
-A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses at all.
+A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses.
 
@@
 	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
-In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
+In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
 The Monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
@@
 	\paragraph{Fourier Basis}
-	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
+	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
 $f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
-Both configurations of $f_2$ are using 5, 15 and 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
+Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
 	\vspace{-0.2cm}
@@
 	\subsubsection{Interpretation and Relevance for Application}
-	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ only little bias seems to be introduced when choosing a small number of basis functions.
+	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$, only little bias seems to be introduced when choosing a small number of basis functions.
 For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$.
 This results in higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$.
-The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff.
+The described convex behavior of the MSPE might also be partially attributable to the bias-variance tradeoff.
 
 	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered.
-An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
+A hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
 To examine this further, additional simulations ( Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
-As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$.
-The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be a first sign of a too high $L$ and subsequent undersmoothing.
+As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$.
+The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing.
 Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$).
@@
 		Our application uses the methods and insights from the previous sections to predict the octane ratings of the gasoline data set.
-		Although the simulation study granted valuable insights into the different methods in our four different settings, it is not enough to determine the optimal method and choice of basis for the application, since there is too much uncertainty involved.
+		Although the simulation study granted valuable insights into the different methods in our four different settings, it is not enough to determine the optimal method and choice of basis for the application since there is too much uncertainty involved.
 To point out some sources of uncertainty: First, differing from the simulation setup, we do not know the true coefficient function.
-Visual inspection of the the estimated coefficient functions shown in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be more similar to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion.
+Visual inspection of the estimated coefficient functions shown in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be more similar to $f_2$ than to $f_1$, but the insights from the two functions are not sufficient to draw any conclusion.
 Second, we have no information about the signal-to-noise ratio of the measured octane numbers.
@@
 
-		Therefore, we will rerun all specification for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
+		Therefore, we will rerun all specifications for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
 The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set will be used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via prediction MSE using 12 fold cross-validation with 5 elements per fold.
@@
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
-Comparing $\hat{\beta}(t)$ for the different bases in figure \ref{basis_expansion_estimate_appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate which might be attributable to the lower number of basis functions.
+Comparing $\hat{\beta}(t)$ for the different bases in figure \ref{basis_expansion_estimate_appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate, which might be attributable to the lower number of basis functions.
 Especially at the lower boundary, the Monomial basis shows an exaggerated behavior.
-However, we must exercise caution since from $L=6$ onwards, we were not able to calculate stable results for the Monomial basis.
-The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while the Monomial basis (0.24181) shows distinctly worse properties.
-In contrast to the simulation study, the B-splines basis manages to outperform the Fourier basis.
-Driving factors for this better performance could be that, first, we do not assume a periodic true coefficient function with the same start- and end value and second, that the Fourier basis enforces identical start and end value on $NIR$.
-It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the hypothesized similarities between the true coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
+However, we must exercise caution since from $L=6$ onwards, we could not calculate stable results for the Monomial basis.
+The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar, while the Monomial basis (0.24181) shows distinctly worse properties.
+		In contrast to the simulation study, the B-splines basis outperforms the Fourier basis.
+Driving factors for this improved performance could be that we do not assume a periodic coefficient function with the same start- and end value and second, that the Fourier basis enforces identical start and end value on NIR.
+It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the hypothesized similarities between the actual coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
 
@@
 As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in figure  \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
-Differing from the simulation study, the number of basis functions is steadily increasing for the Monomial basis.
+Differing from the simulation study, the number of basis functions steadily increases for the Monomial basis.
 The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).
@@
 	\paragraph{Low Number of Basis Functions in FPCR Regression}
-	As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of FPCR, apart from the additional simulations which reported signs of undersmoothing for larger values of $L$.
+	As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of FPCR, apart from the additional simulations, which reported signs of undersmoothing for larger values of $L$.
 A more significant factor seems to be the number of FPC's available for the linear regression.
-This paper selects these components in order of their explanatory power of the variability around the mean function.
-For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC's subject to some criteria such as cross validation or base their choice on insights and expertise from the respective field.
+This paper selects these components by their corresponding Eigenvalues.
+For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC's subject to some criteria such as cross-validation or base their choice on insights and expertise from the respective field.
 	\vspace{-0.2cm}
@@
 \cite{Dattoli_2001}).
-Due to their orthogonality, the problem of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach.
+Due to their orthogonality, the problem of collinearity in the regressor matrix is greatly reduced, which could allow for larger numbers of basis functions in the basis expansion regression approach.
 The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.
@@
 	\paragraph{Comparison to Penalty Based Smoothing Procedures}
-	In contrast to the more typical approach of using a large but often arbitrary number of basis functions and smoothing using a penalty term involving for example the second derivative of the curve, this paper focuses on smoothing by using a smaller number of basis functions.
+	In contrast to the more typical approach of using a large but often arbitrary number of basis functions and smoothing using a penalty term involving, for example, the second derivative of the curve, this paper focuses on smoothing by using a smaller number of basis functions.
 As a next step to the analysis of this paper, it would be interesting to compare both methods to see in which settings different approaches to smoothing perform better and if a possible combination of both approaches could be advantageous.
@@
 	\paragraph{Larger Range for the Number of Specifications for FPCR}
-	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient and limited to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation.
+	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions used for FPCR might be insufficient to obtain a complete picture of the performance of this procedure when combined with smoothing using basis truncation.
 It would therefore be interesting to focus more attention on this limitation of this paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
@@
 	\paragraph{Input from Physics}
-	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models, and be conducive to a more meaningful interpretation of estimates.
-For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value.
+	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics, as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
+For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with high predictive power for the octane value.
 This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.
-Alternatively, it could be used to link specific principal components to chemical compounds which would be useful for the model selection and interesting for the interpretation of estimates.
+Alternatively, it could be used to link specific principal components to chemical compounds, which would be useful for the model selection and interesting for the interpretation of estimates.
 	\vspace{-0.2cm}

### 2022-02-09 Paper/main.tex
Small Equation correction
Small correction
small corrections

@@
 			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \phi_{k}(s) \mathrm{d}s \\
-			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
+			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu}^{m,L}(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\nu}^{m,L}(s) \mathrm{d}s
 		\end{split}
@@
 		\begin{align}
-			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] 
+			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] 
 			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
@@
 For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $L$ as well as the number of FPC's, which is possibly affected by $L$, by ten-fold cross-validation using the prediction mean-squared error.
-The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf.
+The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified proportion of variance (cf.
 \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have a more significant influence on the prediction (cf.
@@
 			\begin{split}
-				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
+				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
 				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
@@
 	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
-Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions.
+Examining the results, it appears that the cross-validated mean squared prediction error (MSPE) exhibits a convex behavior in the number of basis functions.
 
@@
 	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
-For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines for this coefficient function.
+For reasons outlined in \ref{Monomial_basis} {\color{orange} This is not explained anymore in 2.4}, they seem suited for $f_1$, where it shows a better performance than B-splines for this coefficient function.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
@@
 	\paragraph{B-spline Basis}
-	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onwards, the simulations were running into problems of numerical instability.
+	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onwards, the simulations were running into problems of numerical instability {\color{orange} since the functions are inherently not orthogonal to each other}.
 	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three bases.
@@
 		Therefore, we will rerun all specifications for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
-The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set will be used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via prediction MSE using 12 fold cross-validation with 5 elements per fold.
+The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set will be used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via MSPE using 12 fold cross-validation with 5 elements per fold.
 In total, we conducted 1000 repetitions for each setting.

### 2022-02-09 Paper/main.tex
Addressed Approximation in Basis expansion Regression

@@
 	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}.
-Therefore, it is interesting to think about when the approximation error is small...
-{\color{red}Continue Here Jakob!!!}
+Therefore, it is interesting to think about when the approximation error is small.
+Due to the nature of a basis representation, the approximation error can only decrease with an increasing number of basis functions.
+However, contrary to this effect are the potential benefits of introducing some amount of smoothing into the procedure, making it not intuitively clear, what the effects of different choices for the number of basis functions might be.
 
@@
 
-	This, however, is a simplification for the purposes of real-world estimation as in most implementations, the coefficient function and the principal components are also expressed or derived in terms of a basis that can be chosen freely.
+	This, however, is a simplification as in most implementations, the coefficient function and the principal components are also expressed or derived in terms of a basis.
 Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
@@
 
-	As in the previous case, the performance of this estimation depends the quality of the approximation made during the derivation of this estimator.
-Therefore, it is interesting to think about when these errors are small...
-{\color{red}Continue Here Jakob!!!}
+	As in the previous case, the performance of this estimation depends in parts on the quality of the approximation made during the derivation of this estimator. {\color{red}Continue Here Jakob!!!}
 
@@
 
-	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
+	\subsection{Theorem (Karhunen-Lo\'{e}ve Expansion)} \label{Proof2}
 

### 2022-02-09 Paper/main.tex
Something on the approximation error in FPCR

@@
 
-	As in the previous case, the performance of this estimation depends in parts on the quality of the approximation made during the derivation of this estimator. {\color{red}Continue Here Jakob!!!}
+	As in the previous case, the performance of this estimation depends in parts on the quality of the approximation made during the derivation of this estimator.
+Here, the interactions are even more complicated.
+Even though the approximations exhibit smaller errors when a larger number of basis functions is used, the interplay of smoothing in the construction of the functional principal components and the choice of a number of FPC's to be used in the linear regression makes the behavior of this estimator difficult to predict.
 
@@
 	\paragraph{B-spline Basis}
-	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onwards, the simulations were running into problems of numerical instability {\color{orange} since the functions are inherently not orthogonal to each other}.
+	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onward, the simulations were running into problems of numerical instability {\color{orange} since the functions are inherently not orthogonal to each other}.
 	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three bases.

### 2022-02-09 Paper/main.tex
Simul

@@
 In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
-But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
+{\color{orange} The selection of the truncation parameter $L$ is difficult since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
+In addition, the choice of the number of FPC's adds to the complexity of the model since some eigenfunctions, which hold important traits, corresponding to lower variances would be omitted for the model as described in 3.1.} But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
 As will be described, it seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's.
@@
 A hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
-To examine this further, additional simulations ( Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
+{\color{orange}redundant?} To examine this {\color{orange} unclear relationship between the basis functions and the number of FPC} further, additional simulations (Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
 As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$.
-The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing.
+The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing.
 Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$).
-The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's.
+The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's {\color{orange} we cannot compare the Y1 by the number of basis functions since we don't have the results of n=5,6,7.
+and I don't get the although part.
+The regressors are influenced by the noise so the fact fpc is not affected would not be important?
+How about putting 'The results of FPCR is relatively more stable thn basis expansion regression regarding the number of basis function.
+It seems like that the number of FPC's is rather significant.'}.
 This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.
-
 	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)

### 2022-02-09 Paper/main.tex
change d's

@@
 	\begin{equation}
-		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 dx dy < \infty
+		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 \mathrm{d}x \mathrm{d}y < \infty
 	\end{equation}
@@
 	\begin{equation}
-		[K\nu](x) = \int_{\mathcal{A}} c(x,y) \nu(y) dy
+		[K\nu](x) = \int_{\mathcal{A}} c(x,y) \nu(y) \mathrm{d}y
 	\end{equation}
@@
 		\begin{split}
-			[K (\alpha \nu + \beta \theta)](x) =& \int_{\mathcal{A}} c(x,y)(\alpha \nu(y) + \beta \theta(y)) dy\\
-			= & \int_{\mathcal{A}} c(x,y) \alpha \nu(y) dy + \int_{\mathcal{A}} c(x,y) \beta \theta(y) dy\\
-			= & \alpha\int_{\mathcal{A}} c(x,y) \nu (y) dy + \beta\int_{\mathcal{A}} c(x,y) \theta (y) dy\\
+			[K (\alpha \nu + \beta \theta)](x) =& \int_{\mathcal{A}} c(x,y)(\alpha \nu(y) + \beta \theta(y)) \mathrm{d}y\\
+			= & \int_{\mathcal{A}} c(x,y) \alpha \nu(y) \mathrm{d}y + \int_{\mathcal{A}} c(x,y) \beta \theta(y) \mathrm{d}y\\
+			= & \alpha\int_{\mathcal{A}} c(x,y) \nu (y) \mathrm{d}y + \beta\int_{\mathcal{A}} c(x,y) \theta (y) \mathrm{d}y\\
 			= & \alpha[K\nu](x) + \beta[K\theta](x)
@@
 		\begin{split}
-			\Vert K\nu \Vert^{2}_{\mathbb{L}^2(\mathcal{A})} = & \int_{\mathcal{A}} \biggl\vert [K\nu](x) \biggr\vert^2 dx\\
-			= &\int_{\mathcal{A}} \biggl\vert \int_{\mathcal{A}}c(x,y)\nu(y)dy \biggr\vert^2dx\\
-			\leq & \int_{\mathcal{A}}\biggl(\int_{\mathcal{A}}\vert c(x,y) \vert^2dy\biggr) \biggl(\int_{\mathcal{A}}\vert \nu(y) \vert ^2 dy \biggr)dx \quad \text{(Cauchy-Schwarz)}\\
+			\Vert K\nu \Vert^{2}_{\mathbb{L}^2(\mathcal{A})} = & \int_{\mathcal{A}} \biggl\vert [K\nu](x) \biggr\vert^2 \mathrm{d}x\\
+			= &\int_{\mathcal{A}} \biggl\vert \int_{\mathcal{A}}c(x,y)\nu(y)\mathrm{d}y \biggr\vert^2\mathrm{d}x\\
+			\leq & \int_{\mathcal{A}}\biggl(\int_{\mathcal{A}}\vert c(x,y) \vert^2\mathrm{d}y\biggr) \biggl(\int_{\mathcal{A}}\vert \nu(y) \vert ^2 \mathrm{d}y \biggr)\mathrm{d}x \quad \text{(Cauchy-Schwarz)}\\
 			= & \Vert c \Vert_{\mathbb{L}^2(\mathcal{A} \times \mathcal{A})}\Vert \nu \Vert_{\mathbb{L}^2} < \infty
@@
 
-	Remind that $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
+	where $\delta^{m,n} = 0$ if $m \neq n$, otherwise 1.
 
 	\begin{proof}
-		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
+		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)\mathrm{d}P(\omega)$. To obtain the first result, we can show that
 
@@
 			\begin{split}
-				\mathbb{E}[\xi^m] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
-				= & \int_{\Omega} \int_{0}^{1} F(t) \nu^m(t) dt dP(\omega)\\
-				= & \int_{0}^{1} \int_{\Omega} F(t) \nu^m(t) dP(\omega) dt \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu^m(t) dt\\
-				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu^m(t) dt = 0
+				\mathbb{E}[\xi^m] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)\mathrm{d}t\biggr\rbrack\\
+				= & \int_{\Omega} \int_{0}^{1} F(t) \nu^m(t) \mathrm{d}t \mathrm{d}P(\omega)\\
+				= & \int_{0}^{1} \int_{\Omega} F(t) \nu^m(t) \mathrm{d}P(\omega) \mathrm{d}t \quad
+				\text{(Fubini)}\\
+				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) \mathrm{d}P(\omega)} \nu^m(t) \mathrm{d}t\\
+				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu^m(t) \mathrm{d}t = 0
 			\end{split}
@@
 			\begin{split}
-				\mathbb{E} [\xi^m \xi^n] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu^m(s)ds \int_{0}^{1} F(t) \nu^n(t)dt  \biggr\rbrack\\
-				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu^m(s) F(t) \nu^n(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
-				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu^m(s)} \nu^n(t) {\color{red}ds} dt\\
-				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu^m(s)ds \right)} \nu^n(t) dt \\
-				= & \int_{0}^{1}{\color{red}[K\nu^m](t)}\nu^n(t)dt\\
+				\mathbb{E} [\xi^m \xi^n] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu^m(s)\mathrm{d}s \int_{0}^{1} F(t) \nu^n(t)\mathrm{d}t  \biggr\rbrack\\
+				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu^m(s) F(t) \nu^n(t) \mathrm{d}s \mathrm{d}t} \biggr\rbrack \quad \text{(Fubini)}\\
+				= & \int_{0}^{1} {\color{red}\int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu^m(s)} \nu^n(t) {\color{red}\mathrm{d}s} \mathrm{d}t\\
+				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu^m(s)\mathrm{d}s \right)} \nu^n(t) \mathrm{d}t \\
+				= & \int_{0}^{1}{\color{red}[K\nu^m](t)}\nu^n(t)\mathrm{d}t\\
 				= & \langle K \nu^m, \nu^n \rangle\\
@@
 
-	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)dt$. These coefficients satisfy the following conditions.
+	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)\mathrm{d}t$. These coefficients satisfy the following conditions.
 
@@
 			\begin{split}
-				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)ds\bigg)} \nu^m(t) \right]\\
-				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)ds\bigg) \nu^m(t) \right]\\
-				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)ds\bigg)\nu^m(t)\\
-				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)ds\bigg)}\nu^m(t)\\
+				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)\mathrm{d}s\bigg)} \nu^m(t) \right]\\
+				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)\mathrm{d}s\bigg) \nu^m(t) \right]\\
+				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)\mathrm{d}s\bigg)\nu^m(t)\\
+				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)\mathrm{d}s\bigg)}\nu^m(t)\\
 				= & \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\

### 2022-02-09 Paper/main.tex
naming

@@
 
-	\subsection{Lemma} \label{Proof1}
+	\subsection{Lemma (Three Traits of Scores)} \label{Proof1}
 	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}.

### 2022-02-10 Paper/main.tex
Meeting State 10.02.2022

@@
 		University of Bonn \\
+		\vspace{0.2cm}
 		Research Module in Econometrics and Statistics \\
+		Supervised by: Prof. Dr. Dominik Liebl and Dr. Christopher Walsh \\
+		\vspace{0.2cm}
 		Winter Semester 2021/2022
@@
 
+	\thispagestyle{empty}
 	\tableofcontents
@@
 
+	\pagenumbering{arabic}
 	\section{Introduction}
 
-	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature.
-Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf.
-\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.
-	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions.
+	Functional Data Analysis (FDA) has its roots in the work of Ulf Grenander and Kari Karhunen and is gaining traction as researchers from different fields collect data that is functional in nature.
+Although classical statistical methods can often process this data, FDA has advantages allowing it to extract information given by properties such as the smoothness of the underlying process or its derivatives (cf.
+\cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves.
 	Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to Appendix \ref{NIR}.}
@@
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional.
-	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression.
-Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\
+	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression.
+Both methods depend on a parameter called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\
 
@@
 Section \ref{Simulation} contains a description of our Monte-Carlo Simulation, which aims to provide information on how to choose an appropriate functional basis and truncation parameter for the aforementioned methods.
-The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of octane numbers of gasoline samples based on Near-Infrared absorption curves.
-In Section \ref{Outlook}, we give an outlook on possible extensions for this paper and describe the limitations of our approach.
+The application in Section \ref{Application} uses the insights from theory and simulation to choose an appropriate basis for the estimation of octane numbers of gasoline samples based on Near-Infrared absorption curves.
+In Section \ref{Outlook}, we describe the limitations of our approach and give an outlook on possible extensions for this paper.
 
 	\section{Theory}\label{Theory}
-	To allow for scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
-One integral concept that must be defined is random functions as a special case of random variables.
+	To introduce scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space.
+One integral concept that must be defined are random functions as a special case of random variables.
 Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.
 	The typical case for a random variable realizing in $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers.
-As a first intuition for the concept of a random function, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
+As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space.
 A formalization of this idea makes some more in-depth considerations necessary.
@@
 	The first concept we will introduce is the concept of Hilbert spaces.
-To do so, we start from inner product spaces but restrict our analysis to vector spaces over $\mathbb{R}$ for the sake of clarity.
+We start from inner product spaces but restrict our analysis to vector spaces over $\mathbb{R}$ for clarity.
 Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.
@@
 
-	A vector space with an associated inner product is called an inner product space, and the inner product defines a norm and an associated distance on the vector space.
+	A vector space with an associated inner product is called an inner product space. The inner product defines a norm and an associated distance on the vector space.
 	\begin{equation}
@@
 
-	As in the case of a Banach space, each element of a Hilbert space can be expressed in terms of a corresponding basis.
-This can be done using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t.
-a basis $S = \{s_n\}$ as follows.
+	Each element of a Hilbert space can be expressed in terms of a corresponding basis.
+Using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t.
+a basis $S = \{s_n\}$ leads to the following representation.
 	\begin{equation}
@@
 
-	Differing from the case of Banach spaces, these representations can be limits of series.
+	Differing from the finite-dimensional case, these representations can be limits of series.
 As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements in a Hilbert space is to use a truncated series.
@@
 
-	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
-	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$.
+	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}\label{L_2}
+	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$, but analogous constructions can be made for different domains.
 Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
@@
 	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined.
-The inner product of $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
+The inner product on $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
 	\begin{equation}\label{inner_prod}
@@
 
-	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
-	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
+	A random function on $\mathbb{L}^2[0,1]$ can now be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.
 
 	\subsection{Functional Data Sets}
-	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function.
-The presence of functional observations in a data set defines functional data sets.
+	If we take a random function $X(\omega)$ as defined in the previous section, then its realizations $x(t)$ are called sample curves of the random function.
+This presence of functional observations $x_i(t)$ in a data set defines functional data sets.
 However,  realizations of random functions are not typically observed in their functional form.
-Instead, each curve is observed at a discrete and typically large set of measurements points.
+Instead, each curve is observed at a set of discrete measurement points.
 Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
@@
 
-	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$.
+	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at measurement points $t_{i,j}$.
 These measurement points can be different for each sample curve.
@@
 	To use the unique capabilities of functional data analysis with functional data obtained in this form, it is necessary to restore its functional structure.
-Therefore, methods such as basis representations will be introduced in the following parts of the Theory Section.\\
-	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis.
+Therefore, we introduce methods such as basis representations in the following parts of the Theory Section.\\
+	As in the finite-dimensional setting, the concept of independent and identically distributed (i.i.d.) data is important for many aspects of functional data analysis.
 One example of i.i.d.
@@
 	\subsection{Representing a Function in terms of a Basis}\label{bases}
-	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion.
-Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express or approximate a realization $x(t)$ of $X(\omega)$.
-The following equation shows how a basis can be used to express a function as a weighted sum of its elements.
+	As previously described, a basis of a Hilbert space can be used to express its elements using a Fourier expansion.
+Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express a realization $x(t)$ of $X(\omega)$.
+The following equation shows how to use a basis to express a function as a weighted sum of its elements.
 	\begin{equation}
@@
 
-	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$.
+	One very important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$.
 For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
 	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
-Diagrams showing a number of basis functions from these bases are found in Section \ref{Basis_Plots} of the Appendix.
+Diagrams showing these bases are found in Section \ref{Basis_Plots} of the Appendix.
 	\vspace{-0.2cm}
@@
 	\paragraph{Monomial Basis}\label{Monomial_basis}
-	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use monomials of increasing degree as a basis.
+	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use the monomials as a basis.
 For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
@@
 	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$.
-Nevertheless, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
-From this idea, it is natural to use the monomials as a potential basis for approximation.
-\\
+However, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
 	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero, as shown above.
-Instead, one can introduce a shift parameter.
-This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
-	\begin{equation}
-		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
-	\end{equation}
-
-	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$.
-However, a different choice of $\alpha$ could lead to improvements in the performance of the Monomial basis.
+Instead, one can introduce a shift parameter $\alpha$.
+This leads to the following formalization of the Monomial basis.
+	\begin{equation}
+		\phi_{i}^{M}(t) = (t-\alpha)^i \quad i \in \mathbb{N}
+	\end{equation}
+
+	Due to the implementation of our simulation, we limit our paper to the case of $\alpha = 0$. A different choice of $\alpha$ could lead to performance improvements.
 	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates.
 This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities.
-These problems will be addressed in more detail in later parts of this paper.
+The effects of this problem will be addressed in more detail in later parts of this paper.
 The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf.
@@
 	In the same way the Monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions.
-Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
+Equation \ref{Fourier_Series} shows an example for a function $s(x)$ with a period of $T = 1$.
 	\begin{equation}\label{Fourier_Series}
@@
 This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter.
-Therefore, rewriting the series in the sine-cosine form, as shown above, is necessary.
+Rewriting the series in its sine-cosine form, as shown above, is necessary.
 	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.
@@
 	To stay true to the original amplitude-phase form, it is reasonable to restrict the number of Fourier basis functions to odd-numbered values.
-The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process.
-The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions.
+The Fourier basis' elements are cyclical which is useful to expand functions that represent a periodic or seasonal underlying process.
+Due to the nature of the trigonometric functions, it is especially suitable to expand functions with a similar curvature across their domain, resulting in uniformly smooth expansions.
 (cf.
@@
 
-	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots.
+	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_B]$ into $B$ subintervals of non-negative length bounded by a non-decreasing sequence of points $(\tau_b)_{b = 0, \: \dots \:, B}$ called knots.
 On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree.
-If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_l$.
+If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_b$.
 A typical case that is often used in practice is an equidistant grid of knots.
@@
 	B-splines are a specific system of spline functions developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure.
-Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
-	\begin{equation}
-		\begin{split}
-			\phi_{l,0}^{BS}(x) = &
+Let $\phi_{b,m}^{BS}(x)$ for $b \in \{1, \: \dots \:, B + m - 2\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_B]$ and knots $\{\tau_b \: \vert \: b = 0, \:\dots \:, B\}$, then it is defined by the Cox-de Boor recursion formula as follows.
+	\begin{equation}
+		\begin{split}
+			\phi_{b,0}^{BS}(x) = &
 			\begin{cases}
-				1 & \text{if} \quad x \in \left[\tau_l, \tau_{l+1}\right)\\
+				1 & \text{if} \quad x \in \left[\tau_b, \tau_{b+1}\right)\\
 				0 & \text{otherwise}
 			\end{cases}\\ \\
-			\phi_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} \phi_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} \phi_{l+1,m-1}^{BS}(x)
-		\end{split}
-	\end{equation}
-
-	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$, an additional $m$ times.
-This padding of the knot vector then allows calculating every object that is needed for the definition of the basis over the original set of knots.\\
-	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
-To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions.
-	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper.
-For the sake of keeping the notation reasonably concise, we will still keep this notation.
-However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.
+			\phi_{b,m}^{BS}(x) = &\frac{x - \tau_b}{\tau_{b+m} - \tau_b} \phi_{b,m-1}^{BS}(x) + \frac{\tau_{b+m+1} - x}{\tau_{b+m+1} - \tau_{b+1}} \phi_{b+1,m-1}^{BS}(x)
+		\end{split}
+	\end{equation}
+
+	As this equation references knots that are not defined by the original vector of knots, implementations typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_B$, an additional $m$ times.
+This padding of the knot vector allows calculating every object that is needed for the definition of the basis over the original set of knots.\\
+	This does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$.
+However, to focus on specific approximation errors in the later parts of this paper, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions.
+	As the B-spline basis does not have infinitely many elements, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$.
+For the sake of keeping the notation concise, we will still keep this notation.
+By convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.
 
@@
 In many cases, this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting.
-To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves.
-On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information.
+To combat this problem, smoothing methods such as acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves.
+On the other hand, important information on the curves could be missed by oversmoothing the data, giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information.
 This is a typical occurrence of the Bias-Variance tradeoff.\\
 
-	A different approach that is atypical in practice is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects.
+	A typical setup is described by \cite{Goldsmith_2011} in which an explicit smoothness term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high.
+To provide intuition for this approach, let
+	\begin{equation}
+		PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
+	\end{equation}
+
+	denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
+A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
+The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
+
+	A different approach is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects.
 Here, the parameter of choice is not a weighting term for the penalty but the number of basis functions.
@@
 	\begin{equation}\label{basis_exp}
-		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
-	\end{equation}
-
-	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
+		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} a_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} a_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} a_j(\omega_0) \phi_j(t)
+	\end{equation}
+
+	Here, $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.
 In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations.
-$L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation.
-Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set, which is used in the later parts of this paper and exemplifies the tradeoffs at the core of the truncation parameter choice.
+$L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation (CV).
+Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one NIR absorption curve from the gasoline data set, which exemplifies the tradeoffs at the core of the truncation parameter choice.
 
@@
 
-	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
+	Here, the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
 	\begin{equation}\label{HSKernal}
@@
 
-	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$, each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf.
-\cite{alexanderian_KLexpansion_2015}).
-	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.}
+	The operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$, each corresponding to an Eigenvalue $\lambda^{m}$ (cf. \cite{alexanderian_KLexpansion_2015}).
+	Theoretical considerations lead to the result that $X(\omega)$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.}
 	\begin{equation}\label{KarhunenLoeve}
@@
 
-	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of Equation \ref{HSKernal} and the random variables $\xi^{m}(\omega)$ satisfy the following properties.
+	Here, the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of Equation \ref{HSKernal} and the random variables $\xi^{m}(\omega)$, which are called scores, satisfy the following properties.
 	\begin{multicols}{2}
@@
 Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
-	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting.
-Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d.
-realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
-	Define the following sample analogs for the mean and covariance functions.
+	The concept of principal components, which can be extended to the functional setting.\\
+	Let $\{x_1(t),\: \dots, \: x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega)$.	Define the following sample analogs for the mean and covariance functions.
 	\begin{equation}
@@
 
-	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1,\: \dots\:, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m = 1, 2, \:\dots\}$ as the solutions of the following equation.
+	\newpage
+	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1,\: \dots\:, \mathcal{O}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m = 1, 2, \:\dots\}$ as the solutions of the following equation.
 	\begin{equation}
@@
 
-	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(s)$.
+	In the following, we will call the $\hat{\nu}^m(t)$ Functional Principal Components (FPC's) to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(t)$.
 As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf.
-chapter 8.2.3 \cite{ramsay_functional_2005}).
+\cite{ramsay_functional_2005}).
 As each curve is infinite-dimensional, there is no upper limit to this number due to the dimensionality.
 However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
+A second upper limit is given by the number $L$ of basis functions available in the derivation of the FPC's.
+Define therefore $\mathcal{O} := \min(N-1, L)$.
+	In case the number of FPC's is limited by $L$, an exact representation of the functional observations is impossible, introducing an approximation error.
+For the purposes of this paper, we will not address this error and assume that an exact representation is possible.
+Using this assumption, $\mathcal{O}$ is implicitly assumed to always equal $N-1$.
+
 	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
 	\begin{equation}
-		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
-	\end{equation}
-	where the $\hat{\xi}_{i}^m$ are derived as 
+		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{\mathcal{O}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
+	\end{equation}
+	Here, the $\hat{\xi}_{i}^m$ are derived as 
 	\begin{equation}
@@
 	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.
-For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are proper bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
+For clarity, we assume that the bases used for the expansion of both the observations and the coefficient function are proper bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
+The $\delta_i^J(s)$ denotes the approximation error of the demeaned observation due to the basis truncation and $\delta_{\nu}^{m,K}(s)$ denotes the corresponding error for the FPC.
 	\begin{equation}\label{FPCA_basis_expansion}
@@
 	\end{equation}
+
+	\newpage
 	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$.
@@
 	\end{equation}
-	And we can define the following objects:
+	We define the following objects
 		\begin{align}
@@
 
-	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda.
-The following considerations and results of the simulation study might serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.
+	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in chapter 8.4.2 of \cite{ramsay_functional_2005} and implemented in the R package \textit{fda}.
+The following considerations and results of the simulation study might provide information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.
 
@@
 	In the simple scalar setting, one of the essential tools in econometrics is linear regression.
-Its goal is twofold: to gain information about the dependency between variables and allow for prediction.
 To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
@@
 	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns, and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
-	In this finite-dimensional setting, one important question is how to estimate the unknown coefficients $\beta$.
-The most famous estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
+	In this finite-dimensional setting, one important question is how to estimate the unknown coefficients $\beta$. The most famous estimator, the Ordinary Least Squares estimator, fulfills this purpose.
 	\begin{equation}
@@
 	The concept of linear regression can be extended to the setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
-	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
+	Integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations.
+However, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects.
 Therefore, we will always assume a data generating process as follows in this paper.
@@
 
-	Similar to the finite-dimensional setting, an interesting question is how to estimate the unknown coefficient function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
-However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible.
-Therefore, other options have to be considered, two of which will be explained in the following.
+	\newpage
+	Similar to the finite-dimensional setting, a challenge is to estimate the unknown coefficient function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables.
+A simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible.
+Therefore, other options have to be considered, two of which are explained in the following.
 
@@
 	The most common way to make this problem tractable is via a basis representation of $\beta(t)$.
-Therefore, let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
+Let $\{\phi_j(t) \: \vert \: j \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
 	\begin{equation}
@@
 	In practice, it is common to not only express the coefficient function in terms of a basis but also the observations.
-Therefore two bases ($\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and $\left(\psi_k(t)\right)_{k \in \mathcal{L}}$) and two corresponding truncation parameters ($J$ and $K$) can be chosen.
+Therefore two bases, $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and $\left(\psi_k(t)\right)_{k \in \mathcal{L}}$, and two corresponding truncation parameters, $J$ and $K$, can be chosen.
 This leads to the following representation.
-	\begin{equation}
+	\begin{equation}\label{complicated_eq}
 		\begin{split}
@@
 			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K a_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s\\
-			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{J}(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s
-		\end{split}
-	\end{equation}
-
+			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\psi_k(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{J}(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s
+		\end{split}
+	\end{equation}
+
+	\newpage
 	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations.
@@
 
-	this leads to a considerable simplification of Equation \ref{basis_exp_transf}.
+	this leads to a considerable simplification of Equation \ref{complicated_eq} and an approximation by omitting the terms containing truncation errors.
 	\begin{equation}\label{simplified_model_basis_equation}
@@
 			Y(\omega) &= \alpha + \sum_{j = 1}^{L} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{L} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s\\
-			& \quad \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
+			& \quad \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_k(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
 			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
@@
 
-	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects
+	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression.
+
+	Define therefore the following objects
 	\begin{equation}\label{regressor_mat_1}
@@
 	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}.
-Therefore, it is interesting to think about when the approximation error is small.
-Due to the nature of a basis representation, the approximation error can only decrease with an increasing number of basis functions.
-However, contrary to this effect are the potential benefits of introducing some amount of smoothing into the procedure, making it not intuitively clear, what the effects of different choices for the number of basis functions might be.
+Due to the nature of basis representations, the approximation error can only decrease with an increasing number of basis functions.
+Contrary to this effect, we have the potential benefits of introducing some amount of smoothing into the procedure.
+Because of this tradeoff, it is intuitively unclear, what the effects of different choices for the number of basis functions might be.
 
@@
 
-	As these theoretical Eigenfunctions and Eigenvalues are typically unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
+	\newpage
+	As these theoretical Eigenfunctions and Eigenvalues are unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
 	\begin{equation}
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
-			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
-			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
-		\end{split}
-	\end{equation}
-
-	This, however, is a simplification as in most implementations, the coefficient function and the principal components are also expressed or derived in terms of a basis.
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
+			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
+			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
+		\end{split}
+	\end{equation}
+
+	This is a simplification as in most implementations, the coefficient function and the principal components are also expressed or derived in terms of a basis.
 Introducing both concepts one step at a time leads to the following complication if we first introduce an expansion of the coefficient function.
@@
 			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
-			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
-			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
-		\end{split}
-	\end{equation}
-
-	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.
+			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
+			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{\mathcal{O}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+		\end{split}
+	\end{equation}
+
+	Truncating the basis used for expansion of the coefficient function introduces an approximation error.
 	\begin{equation}\label{fpcr_reg_both_expansions}
 		\begin{split}
-			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
-			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
+			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
+			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{\mathcal{O}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad + \sum_{m = 1}^{\mathcal{O}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
 		\end{split}
@@
 	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx}, we obtain the following.
-To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
-Additionally, the following approximation truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.
-
-	For convenience, define the following notation:
+To not complicate things unnecessarily, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function.
+Additionally, the following approximation truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.\\
+	Defining the following notation
 	\begin{equation}
@@
 
-	Then Equation \ref{fpcr_reg_both_expansions} can be expressed as follows.
+	we can express Equation \ref{fpcr_reg_both_expansions} as follows.
 	\begin{equation}
@@
 			y_i & = \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu}^{m,L}(s) \right) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{\mathcal{O}} \left[ \left({\color{red}\tilde{\xi}^{m,L}_{i}} + {\color{blue}\delta_{\xi, i}^{m, L} }\right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left({\color{teal}\tilde{\nu}^{m,L}(s)} + {\color{violet}\delta_{\nu}^{m,L}(s)} \right) \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& = \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] \\
-			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
-			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right]
+			+ \sum_{m = 1}^{\mathcal{O}} \left[ {\color{red}\tilde{\xi}^{m,L}_{i}} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{teal}\tilde{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m = 1}^{\mathcal{O}} \left[ {\color{red}\tilde{\xi}^{m,L}_{i}} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{violet}\delta_{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] \\
+			& \quad \quad \: \: + \sum_{m = 1}^{\mathcal{O}} \left[ {\color{blue}\delta_{\xi, i}^{m, L}} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{teal}\tilde{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] 
+			+ \sum_{m = 1}^{\mathcal{O}} \left[ {\color{blue}\delta_{\xi, i}^{m, L}} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{violet}\delta_{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right]
 			+ \epsilon_i \\
 			& \approx \tilde{\alpha}^L
-			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
-		\end{split}
-	\end{equation}
-
-	The parameter $M \in \{1,\: \dots \:, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.
-Using only $M$ functional principal components leads to the following approximation.
+			+ \sum_{m = 1}^{\mathcal{O}} \left[ {\color{red}\tilde{\xi}^{m,L}_{i}} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{teal}\tilde{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i
+		\end{split}
+	\end{equation}
+
+	The parameter $M \in \{1,\: \dots \:, \mathcal{O}\}$ corresponds to the chosen number of principal components and constitutes another choice in the approximation.
+Using $M$ functional principal components leads to the following approximation.
 	\begin{equation}
@@
 
-	In the simulation study, we deviate from the standard simulation setting.
-Instead of generating data from scratch, we use the gasoline data, which consists of 60 samples of Near-infrared (NIR) absorption spectra measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane rating.
-We chose this setup to improve the approach towards the application in which we predict the octane ratings from the gasoline data set.
-
-	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}.
-For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $L$ as well as the number of FPC's, which is possibly affected by $L$, by ten-fold cross-validation using the prediction mean-squared error.
-The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified proportion of variance (cf.
-\cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have a more significant influence on the prediction (cf.
+	Instead of generating data from scratch, we use the gasoline data set from R package \textit{refund}, which consists of 60 samples of Near-infrared (NIR) absorption curves measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane number.
+We chose this setup to improve the approach towards the application in which we predict the octane numbers from the gasoline data set.
+	We introduced different bases in Section \ref{bases} and demonstrated the importance of the truncation parameter $L$ for the estimation in Section \ref{Scalar_on_function_regression}.
+For the simulation study, we rely on the estimation strategies with the introduced bases and focus on choosing the truncation parameter $L$ as well as the number of FPC's by ten-fold CV using the Mean-Squared Prediction Error (MSPE).
+
+	In practice, the number of FPC's is often chosen by using the lowest number that explains a specified proportion of variance of the smoothed curves (cf.
+\cite{kokoszka_introduction_2017}).
+This might not be optimal since FPC's with smaller Eigenvalues may have a more significant influence on the prediction (cf.
 \cite{Jolliffe_1982}).
-This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\
-
-	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high.
-This would avoid the heavy computations of validating the best value for $L$, which we will conduct in the simulation.
-To provide intuition in this approach, let
-	 \begin{equation}
-	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
-	 \end{equation}
-
-	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
-A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
-The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
-
-	%While this paper and its simulation does not touch upon the topic of roughness penalties in estimation and their selection, other simulations focus e.g.
-on choosing the knots of penalized splines (David Ruppert 2000) or the important choice of the smoothing parameter selection method (Thomas C.M.
-Lee, 2002).
-An overview about other variable selections methods for functional regression with an origin in the multivariate regression setting can be found in( G.
-Aneiros, S.
-Novo and P.
-Vieu)
-
-	%In the simulation study, we deviate from the standard simulation setting.
-Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating.
-We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline data set.
+In this simulation certain Eigenfunctions could correspond to certain chemical compounds and vibration overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.
 
@@
 
-	To avoid small sample problems, we generated 200 similar curves, $NIR_{sim}$, from the spectra of the gasoline data set, $NIR$, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-First, the initial curves are expressed in terms of a  cubic B-spline basis which is created using 50 knots.
-In the R implementation of the fda package, these 50 knots account for 52 basis functions ($50+4-2$).
-These smooth curves are then centered before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
-We assume that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}^{1},\: \dots \:, \mathring{\xi}^{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}^1,\: \dots\:, \hat{\lambda}^M))$.
-Finally, we obtain the generated curves $NIR_{sim}$ as
+	To avoid small sample problems, we generated 200 similar curves denoted by $NIR_{sim}$, from the absorption curves of the gasoline data set denoted $NIR_{orig}$.
+Our approach is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+First, the initial curves are mapped to the interval $[0,1]$ as described in Section \ref{L_2} and expressed in terms of a cubic B-spline basis which is created using 50 knots.
+In the implementation of the \textit{fda} package, these 50 knots account for 52 basis functions ($50+4-2$).
+These smoothed curves are centered before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}.
+For the purposes of data generation, we assume that the scores follow a multivariate normal distribution $\mathring{\xi} = \left(\mathring{\xi}^{1},\: \dots \:, \mathring{\xi}^{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}^1,\: \dots\:, \hat{\lambda}^M))$.
+Finally, we obtain the generated curves $NIR_{sim}$ as realizations of
 	\begin{equation}
@@
 	The simulation study follows \cite{Reiss_2007b} as a guideline.
-Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness are created to compare the introduced methods with differing true coefficient functions:
+Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness, are created to compare our methods with differing true coefficient functions.
 	\begin{equation}
@@
 
-    The function $f_2(t)$ was generated by referring to \cite{cardot_bumpyfunction_2002} while function $f_1(t)$ directly follows \cite{Reiss_2007b}. 
+    The function $f_2(t)$ was generated referring to \cite{cardot_bumpyfunction_2002} while function $f_1(t)$ directly follows \cite{Reiss_2007b}. 
     %and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.
@@
 
-		 Two different error-terms $\epsilon$ were created by first generating an i.i.d.
-standard normal error term and then multiplying it by two error variations $\sigma_e $.
+		 Two different error-terms were created by generating an i.i.d.
+standard normal error term and multiplying it by two error variations $\sigma_e $.
 The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses.
 They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6.
-The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$
-		\begin{equation}
-			\begin{split}
-				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
-				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
-			\end{split}
-		\end{equation}
-
-		where $Z \sim \mathcal{N}(0,1)$.
-In total, we created four combinations, using the two true coefficient functions and the two error terms.
-These four combinations are then used with a different number of Monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.\\
-
-		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculated the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification.
-The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$  by Equation \ref{Score_est}.
+The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.
+		\begin{equation}
+			\begin{split}
+				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.9} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack \\
+				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.6} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack
+			\end{split}
+		\end{equation}
+
+		Here, $Z \sim \mathcal{N}(0,1)$.
+In total, we created four combinations, using the two coefficient functions and the two error terms.
+These four combinations are then used with a different number of Monomial basis functions, cubic B-spline basis functions and Fourier basis functions to predict the generated responses using the basis expansion approach and the FPCR approach.\\
+
+		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we calculated the first $n_{FPC} \in \{2,3,4\}$ FPC's for the training set $\mathcal{T}$, which was smoothed with the respective basis specification.
+The approximated Eigenfunctions $\tilde{\nu}^{m, L, \mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\check{\xi}_{i}^{m, L, \mathcal{H}}$,  by Equation \ref{Score_est}.
 		\begin{equation}\label{Score_est}
@@
 		\end{equation}
-		where 
-		\begin{equation}
-			\begin{split}
-				{\color{red} \left(X_{i}^{\mathcal{H}}(t) - \hat{\mu}^{\mathcal{T}}(t)\right)} 
-				&= {\color{red}\sum_{j \in \mathcal{L}} a_{i,j}^{\mathcal{H}} \phi_j(t)}
+		Here we use the following basis expansions.
+		\begin{equation}
+			\begin{split}
+				{\color{red} X_{i}^{\mathcal{H}}(t) - \hat{\mu}^{\mathcal{T}}(t)} 
+				&= {\color{red}\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(t)}
 				= {\color{red}\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(t) + \delta_{i}^{L, \mathcal{H}}(t)}
@@
 
-		In total, 5000 repetitions were conducted for each specified model, basis system and basis function.
+		In total, we conducted 5000 repetitions for each specified model, basis system and basis function.
 The models are denoted as a combination of the function $f \in \{f_1(t), f_2(t)\}$	and created responses $Y \in \{Y_1, Y_2\}$.
@@
 	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
-Examining the results, it appears that the cross-validated mean squared prediction error (MSPE) exhibits a convex behavior in the number of basis functions.
+Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions.
 
@@
 	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
-For reasons outlined in \ref{Monomial_basis} {\color{orange} This is not explained anymore in 2.4}, they seem suited for $f_1$, where it shows a better performance than B-splines for this coefficient function.
+For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
-In the case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence.
+In the case of $f_2$, this basis shows the weakest performance out of all bases, for which Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide visual evidence.
 It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behavior at the boundaries.
@@
 	\paragraph{B-spline Basis}
-	Simulations with B-spline basis functions were possible from 4 to 18 since from 18 onward, the simulations were running into problems of numerical instability {\color{orange} since the functions are inherently not orthogonal to each other}.
-	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three bases.
-An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (Figures \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio.
-For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio.
+	Simulations with B-spline basis functions were possible from 4 to 18 basis functions.
+From 18 onward, the simulations  ran into problems of numerical instability.
+This might be caused by the fact, that the B-splines are not pairwise orthogonal.
+	Function $f_1$ chooses 5(4) B-spline basis functions for the high (low) signal-to-noise ratio to obtain the best fit and shows the worst performance of the three bases.
+An explanation might be its extreme behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (Figures \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}).
+This is especially pronounced for the lower signal-to-noise ratio.
+For $f_2$, 11(6) B-spline basis functions are chosen for the high (low) signal-to-noise ratio.
 The B-spline basis outperforms the Monomial basis in $f_2$ but comes second to the Fourier basis.
-While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
-With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could prevent fitting this scalar noise using $\hat{\beta}(t)$.
+While the basis seems to recognize the peculiarities in $f_2,Y_1$, it struggles for the noisy responses in $f_2,Y_2$ (Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}).
+With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could prevent overfitting the scalar noise using $\hat{\beta}(t)$.
 	\vspace{-0.2cm}
@@
 	\paragraph{Fourier Basis}
-	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio.
-As for the B-splines basis functions, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses.
-The Fourier basis functions perform the best for each setup for the basis expansion regression.
-Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps.
+	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high (low) signal-to-noise ratio.
+As for the B-splines basis, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses.
+The Fourier basis performs the best for each setup for the basis expansion regression.
+Several reasons could contribute to this.
+First, especially $f_1$ shows similar curvature across the domain while the curvature of $f_2$ does at least not display any erratic jumps.
 Second, both functions feature periodic behavior.
@@
 	The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
-In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
-{\color{orange} The selection of the truncation parameter $L$ is difficult since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function.
-In addition, the choice of the number of FPC's adds to the complexity of the model since some eigenfunctions, which hold important traits, corresponding to lower variances would be omitted for the model as described in 3.1.} But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$.
-As will be described, it seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's.
-This might be because the dependency {\color{red} Reformulate this in the meeting!!!} (FPCA is performed on the smoothed curves) is too complex to draw conclusions regarding this within this simulation study.
+The selection of the truncation parameter $L$ is difficult since the approximated Eigenfunctions from the decomposition are influenced by the choice of $L$.
+In addition, the choice of the number of FPC's adds to the complexity of the model.
+Some eigenfunctions, which might contain important information, could correspond to small Eigenvalues and, therefore, be omitted as described in Section \ref{sim_motivation}.
+But since the FPCR is ultimately estimated with a linear model containing the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by $n_{FPC} \in \{2, 3, 4 \}$.
+It seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's.
+This might be because this dependency is too complex to draw conclusions with this simulation study.
 Therefore, we will limit ourselves to a brief description.
-In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios).
-A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses.
+In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account.
+This is indicated by the fact that the same number of basis functions is chosen for the different signal-to-noise ratios.
+A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the responses.
 
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} \in \{2, 3, 4 \}$).
+	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$).
 In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
@@
 In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting using $n_{FPC} = 4$.
-Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} \in \{2, 3, 4 \}$)
+Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$)
 	\vspace{-0.2cm}
@@
 	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
-$f_2,Y_1$ displays the greatest relative decline of MPSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
-Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
+$f_2,Y_1$ displays the greatest relative decline of MSPE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
+Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} = 2, 3, 4$.
 	\vspace{-0.2cm}
@@
 	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$, only little bias seems to be introduced when choosing a small number of basis functions.
-For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$.
-This results in higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$.
+For $f_2$, a higher number of basis functions seems appropriate.
+This could result from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$, therefore choosing higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$.
 The described convex behavior of the MSPE might also be partially attributable to the bias-variance tradeoff.
 
-	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered.
-A hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting.
-{\color{orange}redundant?} To examine this {\color{orange} unclear relationship between the basis functions and the number of FPC} further, additional simulations (Appendix \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
+	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC's could be found.
+The MSPE of FPCR seems to be comparatively more stable when changing the number of basis functions than for basis expansion regression.
+It seems like the chosen number of FPC's is more significant.
+To examine this relationship further, we conducted additional simulations (Appendix \ref{Tables_sim_additional}) for B-spline basis specifications with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
 As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$.
-The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and subsequent undersmoothing.
-Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$).
-The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's {\color{orange} we cannot compare the Y1 by the number of basis functions since we don't have the results of n=5,6,7.
-and I don't get the although part.
-The regressors are influenced by the noise so the fact fpc is not affected would not be important?
-How about putting 'The results of FPCR is relatively more stable thn basis expansion regression regarding the number of basis function.
-It seems like that the number of FPC's is rather significant.'}.
+The additional simulations revealed evidence for a relationship from $n_{FPC} = 3$ onwards.
+For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and creates undersmoothing.
+Following this, it seems that once a sufficient number of basis functions is used to expand the curves, FPCR performs better using a lower number of basis functions.
+For $n_{FPC} \in \{2, 3, 4 \}$, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation.
+In contrast, $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's.
 This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.
-	%Keeping \cite{Jolliffe_1982} in mind, we ....(refer to problematic of missing insights in pysics / chemistry?)
 
 	\section{Application}\label{Application}
-		Our application uses the methods and insights from the previous sections to predict the octane ratings of the gasoline data set.
+		Our application uses the methods and insights from the previous sections to predict the octane numbers of the gasoline data set.
 		Although the simulation study granted valuable insights into the different methods in our four different settings, it is not enough to determine the optimal method and choice of basis for the application since there is too much uncertainty involved.
 To point out some sources of uncertainty: First, differing from the simulation setup, we do not know the true coefficient function.
-Visual inspection of the estimated coefficient functions shown in Appendix \ref{Estimates_Appl} fuels the hypothesis the real coefficient function might be more similar to $f_2$ than to $f_1$, but the insights from the two functions are not sufficient to draw any conclusion.
+Visual inspection of the estimated coefficient functions shown in Appendix \ref{Estimates_Appl} fuels the hypothesis that the real coefficient function might be more similar to $f_2$ than to $f_1$, but the insights from the two functions are not sufficient to draw any conclusion.
 Second, we have no information about the signal-to-noise ratio of the measured octane numbers.
@@
 
-		Therefore, we will rerun all specifications for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
-The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set will be used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via MSPE using 12 fold cross-validation with 5 elements per fold.
-In total, we conducted 1000 repetitions for each setting.
+		Therefore, we rerun all specifications for the gasoline data set and use the results of the simulation study to improve our understanding of the results.
+The application is designed analogously to the simulation study: The 60 spectra of the gasoline data set are used to estimate a coefficient function, predict the reported octane numbers, and evaluate the results via MSPE using 12 fold CV with 5 elements per fold.
+In total, we conducted 1000 repetitions for each setting, choosing different fold partitions for each run.
+Over all specifications, the best-performing model is FPCR using 4 FPC's built on 7 Fourier basis functions (0.0435), followed by basis expansion regression using 10 B-spline basis functions (0.04574).
 
@@
 For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the Fourier basis.
-Comparing $\hat{\beta}(t)$ for the different bases in figure \ref{basis_expansion_estimate_appl}, away from the boundaries, the B-spline and Fourier bases show similar behavior, opposing to the Monomial estimate, which might be attributable to the lower number of basis functions.
-Especially at the lower boundary, the Monomial basis shows an exaggerated behavior.
+Comparing $\hat{\beta}(t)$ for the different bases away from the boundaries (Figure \ref{basis_expansion_estimate_appl}), the B-spline and Fourier bases show similar behavior, differing from the Monomial estimate, which might be attributable to the lower number of basis functions.
+Especially at the lower boundary, the Monomial basis shows exaggerated behavior.
 However, we must exercise caution since from $L=6$ onwards, we could not calculate stable results for the Monomial basis.
@@
 		In contrast to the simulation study, the B-splines basis outperforms the Fourier basis.
-Driving factors for this improved performance could be that we do not assume a periodic coefficient function with the same start- and end value and second, that the Fourier basis enforces identical start and end value on NIR.
-It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by the hypothesized similarities between the actual coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
+Driving factors for this improved performance could be that, first, we do not assume a periodic coefficient function with the same start- and end value and second, that the Fourier basis enforces identical start and end values on the curves of NIR.
+Note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for $f_2,Y_1$, which might be caused by the hypothesized similarities between the actual coefficient function and $f_2$, but also by a similar high signal-to-noise ratio of the octane numbers.
 
@@
 The MSPE for the optimal specification appears to be strictly decreasing in the number of FPC's.
-As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in figure  \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed.
+As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ (Figures \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}), it appears to be the case that the higher $n_{FPC}$ is, the more similar the behavior of the corresponding estimates becomes.
 Differing from the simulation study, the number of basis functions steadily increases for the Monomial basis.
@@
 	As described, the properties of the two used functions $f \in \{f_1(t), f_2(t)\}$ influence the results.
-Although the resulting MSPE and visual inspection provided some evidence to support the hypothesis that the true coefficient function of $NIR$ might be similar to $f_2$, several other factors that were not asserted could also have caused this.
-Therefore, this simulation is not sufficient to base a reasonable claim concerning more general true coefficient functions, as we would assume them in other applications, on it.
+Although the resulting MSPE and visual inspection provided some evidence to support the hypothesis that the true coefficient function of the original gasoline data set might be similar to $f_2$, other factors that were not addressed could have caused this.
+Therefore, this simulation is not sufficient to base reasonable claims concerning more general coefficient functions on it.
 	\vspace{-0.2cm}
@@
 	\paragraph{Collinearity Problems in Basis Expansion Regression}
-	As already described in the section on the simulation study, the basis expansion regression was in part limited by the numerical instability of the estimation procedure.
+	Except for the Fourier basis, the basis expansion regression was in part limited by the numerical instability of the estimation procedure.
 This is mainly due to an increase in collinearity of the derived regressor matrix shown in Definition \ref{regressor_mat_1}.
 This problem is inherent to basis systems whose functions are not pairwise orthogonal, such as the Monomial or B-splines bases, but gets more pronounced the more functions we add to the basis system and the higher the correlation between those functions.
-\\
 	The numeric instability of the inversion of this matrix makes the estimates unreliable and therefore can make this approach infeasible for non-orthogonal bases in settings where the characteristics of the data set demand a higher number of basis functions than is feasible due to the properties of the estimation procedure.
-	\vspace{-0.2cm}
-
-	\paragraph{Low Number of Basis Functions in FPCR Regression}
-	As the simulation and application showed, the number of basis functions does not seem to be the deciding factor for the performance of FPCR, apart from the additional simulations, which reported signs of undersmoothing for larger values of $L$.
-A more significant factor seems to be the number of FPC's available for the linear regression.
-This paper selects these components by their corresponding Eigenvalues.
-For reasons outlined in Section \ref{sim_motivation} it might be better to make the selection of the FPC's subject to some criteria such as cross-validation or base their choice on insights and expertise from the respective field.
 	\vspace{-0.2cm}
@@
 Due to their orthogonality, the problem of collinearity in the regressor matrix is greatly reduced, which could allow for larger numbers of basis functions in the basis expansion regression approach.
-The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.
+The first eight Legendre polynomials are shown in Appendix \ref{Basis_Plots}.
 	\vspace{-0.2cm}
@@
 	\paragraph{Comparison to Penalty Based Smoothing Procedures}
-	In contrast to the more typical approach of using a large but often arbitrary number of basis functions and smoothing using a penalty term involving, for example, the second derivative of the curve, this paper focuses on smoothing by using a smaller number of basis functions.
-As a next step to the analysis of this paper, it would be interesting to compare both methods to see in which settings different approaches to smoothing perform better and if a possible combination of both approaches could be advantageous.
+	In contrast to the more typical approach of using a arbitrary, large number of basis functions and smoothing using a penalty term involving, e.g.
+the second derivative, this paper focuses on smoothing by using a smaller number of basis functions.
+As the next step to the analysis of this paper, we could compare both methods to see in which settings different approaches to smoothing perform better and if a possible combination of both approaches could be advantageous.
 	\vspace{-0.2cm}
@@
 	\paragraph{Larger Range for the Number of Specifications for FPCR}
-	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions used for FPCR might be insufficient to obtain a complete picture of the performance of this procedure when combined with smoothing using basis truncation.
+	The chosen specifications for the number of principal components and the number of basis functions used for FPCR might be insufficient to obtain a complete picture of the performance of this procedure when combined with smoothing using basis truncation.
 It would therefore be interesting to focus more attention on this limitation of this paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
@@
 	\paragraph{Input from Physics}
-	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics, as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates.
-For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with high predictive power for the octane value.
+	It could be exciting to combine the findings of this paper with theoretical expertise from the field of physics.
+This could inform the choice of models and be conducive to a more meaningful interpretation of the estimates.
+For example, specific parts of the NIR spectrum could possibly be linked to specific molecules associated with the octane number.
 This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise.

### 2022-02-11 Paper/main.tex
One passive voice removed
Changes to interpretation of results and indications

@@
 
-		 Two different error-terms were created by generating an i.i.d.
+		 We created two different error-terms by generating an i.i.d.
 standard normal error term and multiplying it by two error variations $\sigma_e $.
@@
 	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
-Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions.
+Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions for all bases.
 
@@
 	\paragraph{Monomial Basis}
-	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$).
+	For $f_1,Y_1$, the cross-validated MSPE seems to decrease in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$).
+For the noisy responses of $f_1,Y_2$ we find sign of overfitting for $n_{FPC}$ = 4.
 In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
-The Monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
+The Monomial basis shows the weakest performance for all three bases in each setting.
 	\vspace{-0.2cm}
@@
 While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$.
-In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting using $n_{FPC} = 4$.
+In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting for $n_{FPC} = 4$.
 Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$)
@@
 	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
+Both specifications using $f_1$ select the lowest number of basis  possible.
 $f_2,Y_1$ displays the greatest relative decline of MSPE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
 Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} = 2, 3, 4$.
+The basis shows the lowest MSPE for all four settings.
 	\vspace{-0.2cm}
@@
 The MSPE of FPCR seems to be comparatively more stable when changing the number of basis functions than for basis expansion regression.
-It seems like the chosen number of FPC's is more significant.
+It seems like the chosen number of FPC's is more significant, especially for the two high signal-to-noise ratio settings which display a higher relative decrease of MSPE in $n_{FPC}$.
 To examine this relationship further, we conducted additional simulations (Appendix \ref{Tables_sim_additional}) for B-spline basis specifications with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
-As in the simulation study, we can find potential signs of overfitting for all setups and both choices of $L$.
-The additional simulations revealed evidence for a relationship from $n_{FPC} = 3$ onwards.
+We can find potential signs of overfitting in all setups for $L = 70$.
+For $L = 50$, signs of overfitting can be observed for the setups with the noisy responses.
+The additional simulations revealed evidence for a relationship from $n_{FPC} = 3$ onwards for all setups.
 For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and creates undersmoothing.
-Following this, it seems that once a sufficient number of basis functions is used to expand the curves, FPCR performs better using a lower number of basis functions.
-For $n_{FPC} \in \{2, 3, 4 \}$, the settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation.
-In contrast, $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's.
-This might indicate beneficial attributes of a lower truncation parameter in settings with low signal-to-noise responses.
+Following this, it seems that once a sufficient number of basis functions is used to expand the curves, FPCR with B-splines performs better using a lower number of basis functions.
+While a higher number of $n_{FPC}$ decreases the MSPE of $f_1,Y_1$ and $f_2,Y_1$ for $L = 50$ compared to the main simulations, this holds not true for the two setups with noisy responses.
+This strengthens our hypothesis of the high significance of $n_{FPC}$ for the high signal-to-noise ratio setup.
+For $n_{FPC} \in \{2, 3, 4 \}$, the additional B-splines simulations perform worse for these high number of basis functions compared to the main simulation.
+This might indicate beneficial attributes of a lower truncation parameter in settings with a lower number of $n_{FPC}$.
 

### 2022-02-11 Paper/main.tex
Meeting Changes

@@
 The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional.
-	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression.
+	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, Functional Principal Component Regression (FPCR).
 Both methods depend on a parameter called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\
@@
 	Each element of a Hilbert space can be expressed in terms of a corresponding basis.
-Using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t.
-a basis $S = \{s_n\}$ leads to the following representation.
+Using a Fourier expansion of an element $x \in \mathbb{H}$ with respect to a basis $S = \{s_n\}$ leads to the following representation.
 	\begin{equation}
@@
 	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$, but analogous constructions can be made for different domains.
-Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
+Denoted by $\mathbb{L}^2[0,1]$, this space consists of all Lebesgue-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition.
 	\begin{equation}
@@
 
-	One very important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$.
-For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
-	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
-Diagrams showing these bases are found in Section \ref{Basis_Plots} of the Appendix.
-	\vspace{-0.2cm}
-
+	One important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$.
+In this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
+	Three examples of bases used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.
+Diagrams showing these bases are found in Appendix \ref{Basis_Plots}.
+
+	\newpage
 	\paragraph{Monomial Basis}\label{Monomial_basis}
@@
 
-	A typical setup is described by \cite{Goldsmith_2011} in which an explicit smoothness term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high.
+	\newpage
+	A usual setup is described by \cite{Goldsmith_2011} in which an explicit smoothing term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting setting the number of basis functions sufficiently high.
 To provide intuition for this approach, let
@@
 
-	denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$.
+	denote the penalized residual sum of squares for the derivative of order $m$.
 A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty.
-The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.
+The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be achieved by different criteria as shown in \cite{ThomasLee_2003}.
 
@@
 
+	\newpage
 	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
@@
 	\end{equation}
-	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
+	This enables us to write Equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
 	\begin{equation}
@@
 	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. 
-
-	Define therefore the following objects
+	Define therefore the following objects.
 	\begin{equation}\label{regressor_mat_1}
@@
 	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}.
-Due to the nature of basis representations, the approximation error can only decrease with an increasing number of basis functions.
-Contrary to this effect, we have the potential benefits of introducing some amount of smoothing into the procedure.
-Because of this tradeoff, it is intuitively unclear, what the effects of different choices for the number of basis functions might be.
+Due to the nature of basis representations, the overall approximation error $\delta(t)$ can only decrease with the number of basis functions.
+However, in specific points $t_0$ which might coincide with high predictive power for the response, the error $\delta(t_0)$ could increase, potentially increasing the prediction error.
+	In addition, we have the potential benefits of  smoothing such as reducing the potential of overfitting functional noise and reducing the degrees of freedom in the estimation.
+Because of this tradeoff between a reduction in the overall approximation error and beneficial smoothing properties, increasing the number of basis function and thereby decreasing the approximation error is not necessarily beneficial for the prediction accuracy.
+	Therefore, the behavior of the estimator when changing the truncation parameter $L$ is not intuitively clear even if we stay in the same basis system.
 
@@
 
-	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)(t)$.
+	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)$.
 	\begin{equation}
@@
 
-	\newpage
 	As these theoretical Eigenfunctions and Eigenvalues are unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
@@
 
-	As in the previous case, the performance of this estimation depends in parts on the quality of the approximation made during the derivation of this estimator.
-Here, the interactions are even more complicated.
-Even though the approximations exhibit smaller errors when a larger number of basis functions is used, the interplay of smoothing in the construction of the functional principal components and the choice of a number of FPC's to be used in the linear regression makes the behavior of this estimator difficult to predict.
+	As in the previous case, the performance of this estimation depends in parts on the quality of the approximations in the derivation of this estimator.
+The interactions are even more complex.
+Even though the approximations exhibit smaller errors when a larger number of basis functions is used, the interplay of the chosen way of smoothing in the construction of the FPC's and the choice of a number of FPC's used in the linear regression makes the behavior of this estimator difficult to predict.
 
@@
 
-	Instead of generating data from scratch, we use the gasoline data set from R package \textit{refund}, which consists of 60 samples of Near-infrared (NIR) absorption curves measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane number.
+	Instead of generating data from scratch, we use the gasoline data set from R package \textit{refund}, which consists of 60 samples of Near-infrared absorption curves measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane number.
 We chose this setup to improve the approach towards the application in which we predict the octane numbers from the gasoline data set.
 	We introduced different bases in Section \ref{bases} and demonstrated the importance of the truncation parameter $L$ for the estimation in Section \ref{Scalar_on_function_regression}.
-For the simulation study, we rely on the estimation strategies with the introduced bases and focus on choosing the truncation parameter $L$ as well as the number of FPC's by ten-fold CV using the Mean-Squared Prediction Error (MSPE).
+For the simulation study, we use Basis Expansion Regression and Functional Principal Component Regression (FPCR) with the introduced bases and focus on choosing the truncation parameter $L$ as well as the number of FPC's by ten-fold CV using the Mean-Squared Prediction Error (MSPE).
 
@@
 Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness, are created to compare our methods with differing true coefficient functions.
+
 	\begin{equation}
@@
 	\subsubsection{Basis Expansion Regression}
-	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression.
+	These results follow from the model introduced in Section \ref{basis_exp_transf}, in which we transform the smoothed curves to perform scalar-on-function regression.
 Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions for all bases.
@@
 	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability.
-For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines.
+For reasons outlined in Section \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines.
 A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series.
@@
 This weakness is especially pronounced in the MSPE for $f_2,Y_1$.
-For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high(low) signal-to-noise ratio.
+For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high (low) signal-to-noise ratio.
 	\vspace{-0.2cm}
@@
 As for the B-splines basis, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses.
-The Fourier basis performs the best for each setup for the basis expansion regression.
+The Fourier basis performs the best for each setup for the Basis Expansion Regression.
 Several reasons could contribute to this.
@@
 	\subsubsection{Functional Principal Component Regression}
-	The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}.
+	The model used for the FPCR is described in Section \ref{fpc_exp_transf}.
 The selection of the truncation parameter $L$ is difficult since the approximated Eigenfunctions from the decomposition are influenced by the choice of $L$.
@@
 	For $f_1,Y_1$, the cross-validated MSPE seems to decrease in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$).
-For the noisy responses of $f_1,Y_2$ we find sign of overfitting for $n_{FPC}$ = 4.
+For the noisy responses of $f_1,Y_2$ we find signs of overfitting for $n_{FPC}$ = 4.
 In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions.
-The Monomial basis shows the weakest performance for all three bases in each setting.
+The Monomial basis shows the weakest performance out of all three bases in each setting.
 	\vspace{-0.2cm}
@@
 In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting for $n_{FPC} = 4$.
-Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$)
+Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$).
 	\vspace{-0.2cm}
@@
 	\paragraph{Fourier Basis}
-	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$.
-Both specifications using $f_1$ select the lowest number of basis  possible.
-$f_2,Y_1$ displays the greatest relative decline of MSPE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$.
+	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting for $n_{FPC} = 4$.
+Both specifications using $f_1$ select the lowest number of basis functions possible.
+This is interesting as the number of FPC's puts a binding lower bound on the number of basis functions used in their construction.
+An exploration of the implications of this fact is out of the scope of this paper.
 Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} = 2, 3, 4$.
@@
 
-	\subsubsection{Interpretation and Relevance for Application}
+	\subsection{Interpretation and Relevance for Application}
 	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$, only little bias seems to be introduced when choosing a small number of basis functions.
@@
 The described convex behavior of the MSPE might also be partially attributable to the bias-variance tradeoff.
-
 	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC's could be found.
-The MSPE of FPCR seems to be comparatively more stable when changing the number of basis functions than for basis expansion regression.
-It seems like the chosen number of FPC's is more significant, especially for the two high signal-to-noise ratio settings which display a higher relative decrease of MSPE in $n_{FPC}$.
+The MSPE of FPCR seems to be comparatively more stable when changing the number of basis functions than for Basis Expansion Regression.
+It seems like the chosen number of FPC's is more significant, especially for the two high signal-to-noise ratio settings which display a higher absolute and relative decrease of MSPE in $n_{FPC}$.\\
+
 	To examine this relationship further, we conducted additional simulations (Appendix \ref{Tables_sim_additional}) for B-spline basis specifications with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$.
@@
 The additional simulations revealed evidence for a relationship from $n_{FPC} = 3$ onwards for all setups.
-For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be the first sign of an $L$ that is chosen too large and creates undersmoothing.
-Following this, it seems that once a sufficient number of basis functions is used to expand the curves, FPCR with B-splines performs better using a lower number of basis functions.
-While a higher number of $n_{FPC}$ decreases the MSPE of $f_1,Y_1$ and $f_2,Y_1$ for $L = 50$ compared to the main simulations, this holds not true for the two setups with noisy responses.
-This strengthens our hypothesis of the high significance of $n_{FPC}$ for the high signal-to-noise ratio setup.
+For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions.
+This might be the first sign of an $L$ that is chosen too large and creates undersmoothing.
+It seems that once a sufficient number of basis functions is used to expand the curves, FPCR with B-splines performs better using a lower number of basis functions.
+While a higher number of $n_{FPC}$ decreases the MSPE of $f_1,Y_1$ and $f_2,Y_1$ for $L = 50$ compared to the main simulations, this does not hold true for the two setups with noisy responses.
+This strengthens our hypothesis of the high importance of $n_{FPC}$ for the high signal-to-noise ratio setup.
 For $n_{FPC} \in \{2, 3, 4 \}$, the additional B-splines simulations perform worse for these high number of basis functions compared to the main simulation.
@@
 In total, we conducted 1000 repetitions for each setting, choosing different fold partitions for each run.
-Over all specifications, the best-performing model is FPCR using 4 FPC's built on 7 Fourier basis functions (0.0435), followed by basis expansion regression using 10 B-spline basis functions (0.04574).
+Over all specifications, the best-performing model is FPCR using 4 FPC's built on 7 Fourier basis functions (0.0435), followed by Basis Expansion Regression using 10 B-spline basis functions (0.04574).
 
@@
 	\paragraph{Collinearity Problems in Basis Expansion Regression}
-	Except for the Fourier basis, the basis expansion regression was in part limited by the numerical instability of the estimation procedure.
+	Except for the Fourier basis, the Basis Expansion Regression was in part limited by the numerical instability of the estimation procedure.
 This is mainly due to an increase in collinearity of the derived regressor matrix shown in Definition \ref{regressor_mat_1}.
@@
 \cite{Dattoli_2001}).
-Due to their orthogonality, the problem of collinearity in the regressor matrix is greatly reduced, which could allow for larger numbers of basis functions in the basis expansion regression approach.
+Due to their orthogonality, the problem of collinearity in the regressor matrix is greatly reduced, which could allow for larger numbers of basis functions in the Basis Expansion Regression approach.
 The first eight Legendre polynomials are shown in Appendix \ref{Basis_Plots}.

### 2022-02-11 Paper/main.tex
Final_v1

@@
 \usepackage{graphicx}
-\usepackage{hyperref}
 \usepackage[english]{babel}
@@
 \usepackage{amssymb}
-\usepackage{hyperref}
+\usepackage[hidelinks=true]{hyperref}
 \usepackage{overpic}
@@
 	\section{Definitions and Proofs}
-	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.
+	The following proofs are adapted from \cite{alexanderian_KLexpansion_2015}.
 
@@
 	where $c \in \mathbb{L}^2(\mathcal{A} \times \mathcal{A})$.
-Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, by
-
-	\begin{equation}
+Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, defined by Equation \ref{HS_OP}.
+	\begin{equation}\label{HS_OP}
 		[K\nu](x) = \int_{\mathcal{A}} c(x,y) \nu(y) \mathrm{d}y
 	\end{equation}
-	When an integral operator $K$ is linear and bounded, it is called a Hilbert-Schmidt operator.
-The linearity of the operator $K$ is simply proved.
-Additionaly assume that $\alpha, \beta \in \mathbb{R}$ and $\theta \in \mathbb{L}^2(\mathcal{A})$.
-	\begin{equation}
+
+	When an integral operator $K$ is linear and bounded, it is called a Hilbert-Schmidt integral operator.
+The linearity of the operator $K$ is proved as shown in Equation \ref{Linearity}.
+Additionally, assume that $\alpha, \beta \in \mathbb{R}$ and $\theta \in \mathbb{L}^2(\mathcal{A})$.
+
+	\begin{equation}\label{Linearity}
 		\begin{split}
@@
 	\end{equation}
-	For boundedness of the oprator $K$,
+	For boundedness of the operator $K$ we need to show the following.
 	\begin{equation}
@@
 	\subsection{Lemma (Three Traits of Scores)} \label{Proof1}
-	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}.
+	The random function $X(t)$ realizing in $\mathbb{L}^2[0,1]$ is expanded by its Eigenfunctions $\{\nu^m\}$ as shown in Equation \ref{KarhunenLoeve}.
 The coefficients $\xi^{m}$ corresponding to Eigenfunctions $\nu^m$ satisfy the following properties:
@@
 		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
-		The second claim is proved as:
-
+
+		The second claim is proved as
 		\begin{equation}\label{Lemma2}
@@
 
-		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as the first property.
-		The last assertion is confirmed from the above two properties.
-
+		where $\mathbb{E}[\xi^m] = \mathbb{E}[\xi^n] = 0$ as shown in the first property.
+		The last assertion is confirmed from the two properties above.
 		\begin{equation}\label{Lemma3}
@@
 		The original process $X(t)$ also has the same properties as the centered one since
-
-		\begin{equation}
-			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{m=1}^{\infty}\xi^m\nu^m(t)
+		\begin{equation}
+			X(t) = \mathbb{E}[X(t)] + F(t) = \mu(t) + \sum_{m=1}^{\infty}\xi^m\nu^m(t)
 		\end{equation}
@@
 
-	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process, namely, $\lim\limits_{\epsilon \rightarrow 0} \mathbb{E}[(X(t+\epsilon) - X(t))^2]$ = 0, such that $X \in \mathbb{L}^{2}[0,1]$.
-Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
-
+	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process, meaning 
+	\begin{equation}
+		\lim\limits_{\epsilon \rightarrow 0} \mathbb{E}[(X(t+\epsilon) - X(t))^2] = 0
+	\end{equation}
+	such that $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$ we have the following representation.
 	\begin{equation}
@@
 
-	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)\mathrm{d}t$. These coefficients satisfy the following conditions.
+	Here, $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)\mathrm{d}t$. These coefficients satisfy the following conditions.
 
@@
 			\begin{split}
-				\epsilon_{N}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m 	\nu^m(t)\bigg)^2 \right]\\
-				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{m=1}^{N}\xi^m\nu^m(t)\bigg] + \mathbb{E}\bigg[\sum_{m=1}^{N}\sum_{n=1}^{N}\xi^m\xi^n\nu^m(t)\nu^n(t)\bigg]
+				\epsilon_{N}(t) &= \mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m 	\nu^m(t)\bigg)^2 \right]\\
+				&= \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{m=1}^{N}\xi^m\nu^m(t)\bigg] + \mathbb{E}\bigg[\sum_{m=1}^{N}\sum_{n=1}^{N}\xi^m\xi^n\nu^m(t)\nu^n(t)\bigg]
 			\end{split}
@@
 			\begin{split}
-				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)\mathrm{d}s\bigg)} \nu^m(t) \right]\\
-				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)\mathrm{d}s\bigg) \nu^m(t) \right]\\
-				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)\mathrm{d}s\bigg)\nu^m(t)\\
-				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)\mathrm{d}s\bigg)}\nu^m(t)\\
-				= & \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\
-				= &\sum_{m=1}^{N}{\color{teal}\lambda^m\nu^m(t)}\nu^m(t) = \sum_{m=1}^{N}\lambda^m\nu^m(t)^{2}
-			\end{split}
-		\end{equation}
-
-		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}.
-It turns out the product of the Eigenfunction and the corresponding Eigenvalue.
-For the last term, we derive from Equation \ref{Lemma2} that
+				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] &= \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)\mathrm{d}s\bigg)} \nu^m(t) \right]\\
+				&= \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)\mathrm{d}s\bigg) \nu^m(t) \right]\\
+				&= \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)\mathrm{d}s\bigg)\nu^m(t)\\
+				&= \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)\mathrm{d}s\bigg)}\nu^m(t)\\
+				&= \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\
+				&= \sum_{m=1}^{N}{\color{teal}\lambda^m\nu^m(t)}\nu^m(t) = \sum_{m=1}^{N}\lambda^m\nu^m(t)^{2}
+			\end{split}
+		\end{equation}
+
+		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}. For the last term, we derive from Equation \ref{Lemma2} that
 
@@
 
-		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by Equations \ref{Thr1}, \ref{Thr2}, and \ref{Thr3} we obtain
-
+		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0.
+
+		Therefore, by Equations \ref{Thr1}, \ref{Thr2}, and \ref{Thr3} we obtain
 		\begin{equation}

### 2022-02-11 Paper/main.tex
Correction on proof
Slight adjustments

@@
 
-	Here, the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
+	Here, the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by the following equation.
 	\begin{equation}\label{HSKernal}
-		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
+		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
 	\end{equation}
@@
 
-	Here, the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of Equation \ref{HSKernal} and the random variables $\xi^{m}(\omega)$, which are called scores, satisfy the following properties.
+	Here, the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of $[K \nu](t) = \lambda \nu(t)$.
+The random variables $\xi^{m}(\omega)$, which are called scores, satisfy the following properties.
 	\begin{multicols}{2}
@@
 	In the following, we will call the $\hat{\nu}^m(t)$ Functional Principal Components (FPC's) to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(t)$.
-As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf.
+As in the case of ordinary principal components, the number of FPC's corresponding to non-zero Eigenvalues is limited (cf.
 \cite{ramsay_functional_2005}).
@@
 	\end{equation}
-	such that $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$ we have the following representation.
+	such that $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\nu^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$ we have the following representation.
 	\begin{equation}

### 2022-02-11 Paper/main.tex
iid errorterm rearrangement, unifying stuff in NIR appendix

--- 2022-02-11 Paper/main.tex
@@
 		 We created two different error-terms by generating an i.i.d.
-standard normal error term and multiplying it by two error variations $\sigma_e $.
+standard normal error term 	$Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $.
 The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses.
@@
 
-		Here, $Z \sim \mathcal{N}(0,1)$.
 		 In total, we created four combinations, using the two coefficient functions and the two error terms.
@@
 	\subsection{Near-infrared (NIR) Spectroscopy}\label{NIR}
-	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
+	NIR spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm).
 It measures the absorption and interaction of this spectrum of radiation with the sample.
-NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample.
+NIR spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample.
 It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare.
-Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf .
+Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf .
 \cite{FR_li_et_al_2020}).
@@
 	In the context of this paper, the gasoline data set which is used for the simulation and the application is constructed using NIR spectroscopy.
-According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).
+According to \cite{Bohacs_Ovadi_Salgo1998}, NIR spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules).
 While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al.

### 2022-02-11 Paper/main.tex
Miniature Change

@@
 
-		 We created two different error-terms by generating an i.i.d.
-standard normal error term 	$Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $.
+		 We created two different error-terms by generating i.i.d.
+standard normal errors  $Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $.
 The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses.
